### 2016-08-04 SMGI/qph_vla_v3.tex
jxp

%% Preprint Format 
%\documentclass[12pt,preprint]{aastex}
%\epsscale{1.0}

% ApJ Format
\documentclass[iop,revtex4,twocolumn,apj,numberedappendix,appendixfloats]{emulateapj}
\usepackage{/Users/fu/Documents/latex/apj/apjfonts99}
\usepackage{pdflscape}

\shorttitle{CGM of SMGs} 
\shortauthors{Fu et al.}
\journalinfo{}
\submitted{}

% New commands
\newcommand{\eg}{e.g.,}
\newcommand{\ie}{i.e.,}
% Facilities
\newcommand{\hers}{{\it Herschel}}
\newcommand{\spit}{{\it Spitzer}}
% Units
\newcommand{\kms}{{km s$^{-1}$}}
\newcommand{\cmsq}{{cm$^{-2}$}}
\newcommand{\ms}{$M_{\rm star}$}
\newcommand{\mg}{$M_{\rm gas}$}
\newcommand{\mh}{$M_{\rm halo}$}
\newcommand{\mbh}{$M_{\rm BH}$}
\newcommand{\msun}{$M_{\odot}$}
\newcommand{\msunyr}{${\rm M}_{\odot}~{\rm yr}^{-1}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\um}{$\mu$m}
\newcommand{\uJy}{$\mu$Jy}
\newcommand{\nd}{\nodata}
\newcommand{\sqdeg}{deg$^2$}
% emission/absorption lines
\newcommand{\Ha}{H$\alpha$}
\newcommand{\lya}{Ly$\alpha$}
\newcommand{\lyb}{Ly$\beta$}
\newcommand{\HI}{H\,{\sc i}}
\newcommand{\CII}{C\,{\sc ii}}
\newcommand{\SiIV}{Si\,{\sc iv}}
% forbidden lines
\newcommand{\OII}{[O\,{\sc ii}]}
\newcommand{\OIIexpanded}{[O\,{\sc ii}]\,$\lambda$3727}
\newcommand{\SII}{[S\,{\sc ii}]}
\newcommand{\OIII}{[O\,{\sc iii}]}
\newcommand{\OIIIexpanded}{[O\,{\sc iii}]\,$\lambda$5007}
\newcommand{\NII}{[N\,{\sc ii}]}
\newcommand{\MgII}{Mg\,{\sc ii}}
% special 
\newcommand{\nod}{\nodata}
\newcommand{\sqps}{SMG$-$QSO pairs}
\newcommand{\sqp}{SMG$-$QSO pair}

\begin{document}

\title{Probing the Circumgalactic Medium of Submillimeter Galaxies with QSO Absorption Spectroscopy}

%\input{authors/authors.tex}
\author{
Hai~Fu\altaffilmark{1} and Collaborators
}
\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}

\begin{abstract}
Submillimeter galaxies (SMGs) are dusty starbursts in the early universe that may have evolved into massive ellipticals today. Their clustering strength suggests that they inhabit $10^{13}$~\msun\ halos. The physical state of the circumgalactic medium of SMGs carries key information to decode massive galaxy formation yet are unexplored observationally. We exploit QSO absorption spectroscopy to probe the diffuse gas around SMGs.
% 
We first compile a sample of \sqps\ with angular separations less than 35\arcsec\ from \hers\ surveys. We then use the Very Large Array (VLA) to determine the positions of the \hers\ sources. Finally, we use near-infrared spectrographs to determine the redshifts of the five VLA-detected SMGs and optical spectrographs to obtain their QSO absorption spectra. 
%
Our survey yielded three \sqps\ with secure redshift identification for both components. The QSO sightlines probe transverse proper distances between 110 and 200~kpc. We detect strong \HI\ \lya\ absorption with rest-frame equivalent widths $W_{\rm Ly\alpha} = 1.7-2.0$~\AA\ around all three SMGs. One of the \lya\ system shows only 40\% absorption at the line center, so it is clearly optically thin (${\rm log}(N_{\rm HI}) < 17$~\cmsq) and the high $W_{\rm Ly\alpha}$ is due to line-blending. The high equivalent widths and the line center depths of the other two systems are consistent with optically thick absorbers with $18 < {\rm log}(N_{\rm HI}) < 19$~\cmsq. However, neither are convincingly optically thick, because our spectral resolution is insufficient to reveal the damping wings of the \lya\ line and the low-ionization metal lines commonly associated with optically thick absorbers are buried in the \lya\ forest. Compared to the QSOs at $z \sim 2$, our limited sample suggest that SMGs' surrounding media have lower covering fraction of optically thick cool gas. 
\end{abstract}

\keywords{galaxies: halos --- quasars: absorption lines --- intergalactic medium}

\section{Introduction} \label{sec:intro}

\begin{deluxetable*}{rrrccc crrcc}
\tablewidth{0pt}
\tablecaption{VLA Observed \hers\ Sources
\label{tab:vlaphoto}}
\tablehead{
\colhead{Pair Name} & \colhead{RA$_{250}$} & \colhead{DEC$_{250}$} & \colhead{$S_{250}$} & \colhead{$S_{350}$} & \colhead{$S_{500}$} & \colhead{Int Time} & \colhead{RA$_{\rm 6 GHz}$} & \colhead{DEC$_{\rm 6 GHz}$} & \colhead{$S^{\rm peak}_{\rm 6 GHz}$} & \colhead{$S^{\rm int}_{\rm 6 GHz}$} \\
%
\colhead{} & \colhead{(deg)} & \colhead{(deg)} & \colhead{(mJy)} & \colhead{(mJy)} &  \colhead{(mJy)} &  \colhead{(min)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{(\uJy/bm)} & \colhead{(\uJy)} \\
%
\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} &  \colhead{(8)} & \colhead{(9)} & \colhead{(10)} & \colhead{(11)} 
}
\startdata
%\input{/Users/fu/casa/15a266/figs/tables/paper_tab1.tex}
HeLMS 0015$+$0404  &  3.9286&$+$4.0715 & 61.7$\pm$6.0 & 67.8$\pm$5.7 & 54.3$\pm$7.2&26.5&  3.93038&$+$4.07262  & 69.4$\pm$6.7 & 72.4$\pm$13.4\\
%HeLMS 0028$+$0107  &  7.1544&$+$1.1213 & 54.7$\pm$6.1 & 57.8$\pm$5.6 & 45.9$\pm$7.1&31.5& \nodata & \nodata & $<$14.7& \nodata  \\
HeLMS 0041$-$0410  & 10.3541&$-$4.1679 & 80.8$\pm$6.2 & 83.0$\pm$6.5 & 43.6$\pm$7.0&15.8& \nodata & \nodata & $<$35.1& \nodata  \\
%HeLMS 0059$+$0459  & 14.9780&$+$4.9917 &101.2$\pm$6.5 &108.6$\pm$6.5 & 61.6$\pm$7.5&14.8& \nodata & \nodata & $<$23.4& \nodata  \\
L6-XMM 0223$-$0605 & 35.8056&$-$6.0860 & 33.8$\pm$2.3 & 40.3$\pm$2.5 & 24.2$\pm$3.5&69.7& \nodata & \nodata & $<$14.4& \nodata  \\
G09 0918$-$0039    &139.6159&$-$0.6644 & 41.1$\pm$6.9 & 49.7$\pm$8.1 & 31.2$\pm$9.1&18.9& \nodata & \nodata & $<$17.7& \nodata  \\
G09 0920$+$0024    &140.2475&$+$0.4049 & 35.0$\pm$7.0 & 51.6$\pm$8.1 & 32.0$\pm$8.9&22.9& \nodata & \nodata & $<$18.6& \nodata  \\ 
NGP 1313$+$2924    &198.4530&$+$29.4126& 59.7$\pm$5.6 & 78.5$\pm$6.6 & 53.6$\pm$7.8&17.2& \nodata & \nodata & $<$42.3& \nodata  \\
NGP 1330$+$2540    &202.5866&$+$25.6749& 49.2$\pm$5.8 & 54.3$\pm$6.4 & 29.3$\pm$7.8&18.0& \nodata & \nodata & $<$15.3& \nodata  \\ 
NGP 1333$+$2357    &203.3743&$+$23.9592& 30.4$\pm$5.4 & 31.8$\pm$6.4 & 29.1$\pm$7.5&55.2&203.37514&$+$23.95909 & 20.0$\pm$3.0 & 31.0$\pm$8.1 \\
NGP 1335$+$2805    &203.9409&$+$28.0986& 41.7$\pm$5.5 & 49.8$\pm$6.4 & 38.2$\pm$7.7&27.6&203.94249&$+$28.09750 & 38.3$\pm$4.5 & 51.4$\pm$11.0\\
G15 1413$+$0058    &213.4580&$+$0.9725 & 46.6$\pm$6.4 & 52.8$\pm$7.7 & 36.1$\pm$8.5&16.2&213.45743&$+$0.97321  & 37.3$\pm$5.8 & 37.3$\pm$11.6\\
G15 1435$+$0110    &218.9043&$+$1.1682 & 63.0$\pm$6.7 & 63.8$\pm$8.0 & 56.6$\pm$8.8& 9.2&218.90494&$+$1.16958  & 75.6$\pm$7.3 & 89.1$\pm$16.0\\
G15 1450$+$0026    &222.6773&$+$0.4351 & 47.5$\pm$6.9 & 47.9$\pm$8.1 & 29.1$\pm$8.9&16.3& \nodata & \nodata & $<$18.0& \nodata \\
L6-FLS 1712$+$6001 &258.0352&$+$60.0281& 32.3$\pm$2.2 & 34.0$\pm$2.4 & 22.4$\pm$3.6&30.1&258.03111&$+$60.02722 & 10.8$\pm$2.1 & 10.8$\pm$4.2 
\enddata
\tablecomments{
Columns (2-6) list the \hers\ 250~\um\ positions and the photometry at 250, 350, and 500~\um.
Column 7 is the total VLA on-source integration time.
Columns (8-9) list the positions of the radio counterparts.
Columns (10-11) are the peak flux density in \uJy/bm and the integrated flux density in \uJy, both of which are derived by fitting an elliptical Gaussian model to the source. The uncertainty of peak flux density is given by the rms noise in the map at the source position, while the uncertainty of the integrated flux density is estimated using the formulae provided by \citet{Hopkins03a}, which includes the 1\% uncertainty in the VLA flux-density scale at 6~GHz \citep{Perley13}.  
}
\end{deluxetable*}

The first mJy-level submillimeter surveys discovered a population of high-redshift submillimeter-bright galaxies (SMGs), namely, unresolved sources with 850~\um\ flux density ($S_{850}$) greater than 3~mJy \citep{Smail97,Barger98,Hughes98,Eales99}. The SMGs are massive \citep[\ms\ $\sim 10^{11}$~\msun;][]{Hainline11, Michalowski12, Targett12}, metal-rich \citep[$Z \sim Z_\odot$;][]{Swinbank04}, gas-rich \citep[\mg\ $\sim 3\times10^{10}$~\msun;][]{Greve05, Tacconi08, Ivison11}, extreme star-forming systems (SFR $\gtrsim 500$~\msunyr) at a median redshift of $z \sim 2.5$ \citep{Chapman05,Wardlow11,Yun12,Smolcic12}. Two lines of evidence suggest that SMGs inhabit dark matter halos as massive as $\sim$$10^{13}$~\msun: (1) their strong clustering strength estimated from the cross-correlation function between SMGs and 3.6~\um-selected galaxies \citep[\mh $\sim 9\times10^{12}$~\msun; e.g.,][]{Hickox12}, and (2) their high stellar mass and the \ms$-$\mh\ relation from abundance matching \citep[\mh~$= 6\times10^{12}$~\msun\ for \ms~$= 10^{11}$~\msun\ at $z = 2$; e.g.,][]{Behroozi10}.

It is imperative to know how long this intense star formation would last. For $10^{13}$~\msun\ halos at $z = 2$, the total baryonic accretion rate from the mass growth rate of dark matter haloes is $\dot{M}_{\rm bar} \equiv 0.18 \times \dot{M}_{\rm halo} \sim 1200$~\msunyr\ \citep{Neistein08}. However, all of these baryons are expected to be shock-heated to the virial temperature of the halo ($\sim7\times10^6$~K) and the cool gas replenishment timescale is much longer than the gas depletion timescale in such halos \citep[e.g.,][]{Dekel06,Tacchella15}. Therefore, the prolific star formation in SMGs should be unsustainable; the SFR would decline with an $e$-folding timescale of only $\sim$200~Myr \citep[2\mg/SFR; e.g.,][]{Tacconi08,Bothwell12}. At such a rate, the SMGs would become red sequence galaxies in only a Gyr or 5 $e$-folding times\footnote{This is the time it would take to decrease the specific SFR (SFR/\ms) from $\sim$$10^{-9}$~Gyr$^{-1}$ for the SMGs at the observed epoch to $\sim$$10^{-11}$~Gyr$^{-1}$ for the red sequence at $z \sim 2$ \citep{Brammer09}.} \citep{Fu13}. Such a short transitional time of a significant high-redshift star-forming population helps explain the rapid build-up of the massive end of the red sequence at $z > 1$ \citep[e.g.,][]{Ilbert13}. It makes it unnecessary to invoke any additional quenching mechanisms such as galactic outflows, which can be suppressed in such massive halos \citep[e.g.,][]{Singh16}.

However, could there be enough cool gas in the circumgalactic medium (CGM) around SMGs that may fuel a prolonged starburst phase \citep[e.g.][]{Narayanan15}? The CGM of co-eval QSOs may give us a hint, because they inhabit comparably massive ($\sim$$10^{12.6}\,M_{\odot}$) halos \citep{White12}. Contrary to the expected dominance of virialized X-ray plasma, absorption line spectroscopy of a statistical sample of $z \sim 2$ projected QSO pairs reveals the prevalence of cool ($T \sim 10^4$~K), metal-enriched ($Z \geq 0.1 Z_\odot$), and optically thick \lya\ absorbers ($N_{\rm HI} \geq 1.6\times10^{17}$~\cmsq) extending to at least the expected viral radius of 160~kpc \citep[the ``Quasar Probing Quasar'' (QPQ) project:][]{Hennawi06,Prochaska13,Prochaska13a}. The high observed covering factor of the cool CGM gas ($\gtrsim 60\%$) in $\sim$$10^{12.6}\,M_{\odot}$ halos has been compared to predictions from numerical simulations, and it has been realized that efficient star-formation-driven feedback from accreted satellite galaxies is required to increase the \HI\ covering factor to the observed level \citep[e.g.,][]{Fumagalli14,Faucher-Giguere15,Rahmati15,Faucher-Giguere16}. The models predict that the covering factor increases with halo mass and is independent of specific SFR, so SMGs are likely to show even higher \HI\ covering factors. To test this, we exploit QSO absorption line spectroscopy to probe the CGM of SMGs. We first present the data sets and the method we used to select projected \sqps\ in \S~\ref{sec:sample}. We then describe our followup observations in \S~\ref{sec:obs}, including radio interferometer imaging, near-infrared spectroscopy, and optical spectroscopy. We present our analysis and results in \S~\ref{sec:result}. Finally, we conclude by comparing the covering fraction of optically thick gas around SMGs with that of $z \sim 2$ QSOs (\S~\ref{sec:discuss}). Throughout we adopt a $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.27$, $\Omega_\Lambda=0.73$ and $H_0$ = 70 km~s$^{-1}$~Mpc$^{-1}$.

% NFW profile
% IDL> nfw,1e13,2.0,/debug
% c_vir =   4.9 R_vir(kpc) = 232.9 r_s(kpc) =  47.3 rho_s(Msun/kpc^3) = 7.9e+06 vdisp (km/s) = 451.3 T_vir (K) =  6.62e+06
% IDL> nfw,1e13,2.5,/debug
% c_vir =   4.6 R_vir(kpc) = 200.9 r_s(kpc) =  43.4 rho_s(Msun/kpc^3) = 1.1e+07 vdisp (km/s) = 482.0 T_vir (K) =  7.68e+06
% sqrt((2 * G * (1e13 solar mass)) / (232.9 kpc)) = 607 825.609 m / s

\section{Selection of Projected SMG$-$QSO Pairs} \label{sec:sample}

Because both high-redshift QSOs and SMGs have low surface densities on the sky, we need large samples of both to come up with a sizable sample of projected \sqps\ with small angular separations. We compiled 464,866 spectroscopically confirmed QSOs from various surveys: primarily, the Sloan Digital Sky Survey \citep[SDSS;][]{Alam15}, the 2dF QSO Redshift Survey \citep[2QZ;][]{Croom04}, the AGN and Galaxy Evolution Survey \citep[AGES;][]{Kochanek12}, and the MMT Hectospec Redshift Survey of 24 {$\mu$}m Sources in the Spitzer First Look Survey \citep{Papovich06}. Since our \hers-selected SMGs likely have redshifts greater than two (see the next paragraph), we keep only the 102,472 QSOs at $z_{\rm QSO} > 2.5$. To select the foreground SMGs, we combined source catalogs from a number of wide-area \hers\ extragalactic surveys: the \hers\ Multi-tiered Extragalactic Survey \citep[HerMES, 95 \sqdeg;][]{Oliver12,Wang14a}, the \hers\ Astrophysical Terahertz Large Area Survey \citep[H-ATLAS, 600 \sqdeg;][]{Eales10,Valiante16}, the \hers\ Large Mode Survey \citep[HeLMS, 301 \sqdeg;][]{Oliver12,Clarke16,Asboth16,Nayyeri16}, the \hers\ Stripe 82 Survey \citep[HerS, 79 \sqdeg;][]{Viero14}. All of these surveys used SPIRE \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} to image the sky at 250, 350, and 500~\um\ and the combined xID250\footnote{250, 350 and 500~\um\ fluxes were all extracted at source positions detected on the 250~\um\ map \citep[e.g.,][]{Roseboom10,Rigby11}.} catalog contain 1,586,047 sources covering a total of 767 \sqdeg\ (there is significant overlap between HerS and HeLMS).

However, most \hers\ sources are not SMGs. To select \hers\ sources that would have been selected as SMGs if observed at 870~\um, we chose only the subsample that satisfies the following criteria: (1) $>$3$\sigma$ detections in all three SPIRE bands, (2) flux densities peak at 350~\um\ ($S_{250} < S_{350}$ and $S_{500} < S_{350}$; i.e., ``350\um\ peakers''), and (3) $S_{500} > 20$~mJy. Criterion 2 is essentially a photometric redshift selection because a typical graybody dust emission at $T = 35$~K would peak at 350~\um\ if redshifted to $z \sim 2.5\pm0.8$. In addition, the blind CO survey of the brightest 350~\um\ peakers ($S_{350} \geq 115$~mJy) has shown a strikingly similar redshift distribution as 850~\um-selected SMGs \citep{Harris12}, even though most of these bright sources are strongly lensed. Criterion 3 is introduced to ensure that the Rayleigh-Jeans extrapolation would give $S_{850} > 3$~mJy, the classic definition of an SMG, given a typical power-law slope of 3.5 (i.e., $\beta = 1.5$). Only 70,823 \hers\ sources remained after this selection, giving an average surface density of 92 per \sqdeg\ (but note that the 500~\um\ depth varies substantially from field to field).

We identified 230 projected \sqps\ with separations\footnote{$\theta_{250}$ is measured between the \hers\ position and the optical position of the QSO.} between 5\arcsec~$\leq \theta_{250} \leq$~36\arcsec\ by cross-matching the QSO and SMG subsamples described above. The corresponding impact parameters ($R_\bot$)\footnote{The impact parameter is defined as the transverse proper distance at the redshift of the foreground SMG, which equals the angular diameter distance of the SMG multiplied by the angular separation on sky ($R_\bot = D_{\rm A}(z) \times \theta$).} are between $40 < R_\bot <$~300~kpc for $z_{\rm SMG} = 2.5$. These QSO sightlines thus probe out to $\sim$1.5 virial radii of $10^{13}$~\msun\ halos ($r_{\rm vir} = 200$~kpc at $z = 2.5$). The 5\arcsec\ lower limit is imposed as an attempt to avoid FIR-bright QSOs, because the 95\%-ile positional uncertainty of the \hers\ positions is $\sim$5\arcsec. Through visual inspection of the QSO spectra, we further excluded 31 pairs whose QSOs exhibit strong broad absorption lines (BALs), have wrong redshifts, or are misclassified. Therefore, our final sample include 199 pairs, among which 90/163 QSOs have $g \leq 21/22$~AB.

\begin{figure*}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/casa/15a266/figs/vla_detect.eps}
\caption{VLA 6~GHz continuum maps for the six VLA-identified SMGs. Each image is 30\arcsec$\times$30\arcsec\ centered on the \hers\ position. The restoring beam of each map is plotted as the red ellipse at the lower right corner. The white cross and the dashed white circle indicate the \hers\ positions and the 18\arcsec\ FWHM of the 250~\um\ PSF. The green square highlights the detected radio source within the \hers\ FWHM. The white diamond marks the optical position of the QSO, if it is within the displayed region. The gray dotted contour is at $-$2$\times$$\sigma$, and the black contours are at ($+$2, $+$4, $+$8)$\times$$\sigma$. Major tickmarks are spaced in 5\arcsec\ intervals. N is up and E is left for all panels.
\label{fig:detections}} 
\end{figure*}

\section{Followup Observations} \label{sec:obs}

Extensive followup observations are needed to perform absorption spectroscopy of SMGs. Our first problem is that the angular resolution of \hers\ (FWHM = 18\arcsec/25\arcsec/36\arcsec\ at 250/350/500~\um) is inadequate for longslit spectroscopic observations. To obtain more accurate positions and to remove blended sources, we have to exploit interferometer observations with the Karl G. Jansky Very Large Array (VLA). Furthermore, once the positions are determined with sub-arcsec accuracy, we need to determine the spectroscopic redshifts of the SMGs with near-IR spectrographs. Finally, a high S/N optical/near-UV spectrum of the background QSO is needed to detect the UV absorption lines imprinted by the diffuse medium around the SMGs. Below we describe these observations in more details.

\subsection{SMG Identification with the VLA}

%The angular resolution of \hers\ is inadequate for longslit spectroscopic followup (FWHM = 18\arcsec/25\arcsec/36\arcsec\ at 250/350/500~\um). To obtain more accurate positions and to remove blended sources, 
We observed 15 \sqps\ with the Karl G. Jansky Very Large Array (VLA) in the B configuration with the C-band (6~GHz) receivers (program ID: 15A-266). We later realized that two of the VLA targets in the HeLMS field are likely spurious detections because of Galactic cirrus (Clarke et al. in prep.), so we excluded them in this discussion. Table~\ref{tab:vlaphoto} lists the \hers\ positions and photometry of the final VLA sample. The receivers have a total bandwidth of 4\,GHz at a central frequency of 5.9985\,GHz. The targets were selected from six different extragalactic fields. To maximize the observing efficiency, we grouped the targets with their R.A. into five scheduling blocks (SBs) of 0.8 to 3.1\,hours. A nearby unresolved calibrator was observed every $\sim$10~min. Depending on the R.A. of the targets, 3C\,48, 3C\,286, or 3C\,295 was observed for bandpass and flux-density calibration. The entire program took 8.3 hrs of VLA time. The on-source integration time ranges from 9 to 70 minutes, allocated based on the 6~GHz flux density estimated from fitting the \hers\ photometry with the SED template of a well-studied lensed SMG at $z = 2.3259$ \citep[SMM~J2135-0102, aka. the ``Eyelash'';][]{Swinbank10b}.

The observations were calibrated using the Common Astronomical Software Applications (CASA) package. We used the VLA pipeline to perform basic flagging and calibration. Additional flagging was performed whenever necessary by inspecting the visibility data. We used the self-calibration technique with bright sources within the primary beam to improve the calibration for four fields: HeLMS\,0015$+$0404, HeLMS\,0041$-$0410, L6-XMM\,0223$-$0605, and NGP\,1313$+$2924. For imaging and deconvolution, we used the standard CASA task {\sc clean} with ``natural'' weighting to achieve the best sensitivity. The resulting restoring beams are on average 1\farcs5$\times$1\farcs2 in FWHM and the rms noise ranges from 2.1 to 11.7~\uJy/bm (primarily driven by the different integration times).

%The VLA detected six of the 13 SMGs (see Table~\ref{tab:vlaphoto} and Fig.~\ref{fig:detections}). For one of those, NGP~1335+2805, the QSO at $z = 2.973$ itself is responsible for the far-IR emission; so it is a far-IR-luminous QSO instead of a projected \sqp.

\subsection{Near-IR Spectroscopy of the VLA-detected SMGs}

\begin{figure*}[!tb]
\epsscale{0.38}
\plotone{/Users/fu/data/qph_nir/gnirs/15bq46/HeLMS_0015+0404/HeLMS_0015+0404.eps}
\plotone{/Users/fu/data/qph_nir/luci1/201504/redux0/NGP_1333+2357.eps}
\plotone{/Users/fu/data/qph_nir/luci1/201504/redux0/L6-FLS_1712+6001.eps}
\caption{Near-infrared spectra of the VLA-identified SMGs. The top panel shows the coadded 2D spectrum. The vertical axis is along the spatial direction, and is centered on the SMG location. The bottom panel shows the flux-calibrated 1D spectrum ({\it black}) and its 1$\sigma$ uncertainty ({\it blue}). Wavelengths affected by strong sky lines show large errors. The dashed lines indicate the redshifted \Ha\,$\lambda$6563 and \NII\,$\lambda\lambda$6548,6583 lines.
\label{fig:smgspec}} 
\end{figure*}

Five VLA-detected SMGs were observed with various IR spectrographs. 
%
We observed G15\,1435$+$0110, L6-FLS\,1712$+$6001, and NGP\,1333$+$2357 with the LUCI-1 spectrograph \citep{Seifert03} on the Large Binocular Telescope (LBT) on 2015 Apr 14. We used the 200 l/mm $H$+$K$ grating at $\lambda_{\rm c} = 1.93$~\um\ and the N1.8 camera (0\farcs25 per pixel) to obtain a spectral range between 1.5 and 2.3~\um. The 1\arcsec-wide 4\arcmin-long slit is centered on the VLA-determined SMG position, and the slit P.A. is chosen to obtain the QSO spectrum simultaneously. The spectral resolution ($R$) is $\sim$940 in $H$-band and $\sim$1290 in $K$-band. We obtained 32$\times$ 120~s exposures for each target. Between exposures, we dithered along the slit among six dithering positions distributed within 40\arcsec. 
%Atmospheric transparency varied dramatically during the night and no telluric star was observed. So we used the telluric star observation from the previous night for an approximate telluric and flux calibration.

We observed HeLMS\,0015$+$0404 with the Gemini near-infrared spectrograph \citep[GNIRS;][]{Elias06} in the queue mode (program ID: GN-2015B-Q-46). We used the cross-dispersing prism with the 31.7 l/mm grating and the short camera to obtain a complete spectral coverage between 0.85-2.5~\um. With the 0\farcs68 short slit, the spectral resolution is $R \sim 750$ across all orders. A total of 14$\times$ 300~s exposures were obtained on 2015 Aug 9, Aug 12, and Oct 18. We dithered by 3\arcsec\ along the 7\arcsec-slit between exposures.

We observed G15\,1413$+$0058 with NIRSPEC \citep{McLean98} on the Keck II telescope on 2015 Jun 13. We used the low resolution mode, the NIRSPEC-7 ($K$-band) filter, the 42\arcsec$\times$0\farcs76 slit. The spectral coverage is between 1.97 and 2.40~\um. The night was cloudy and we only obtained 8$\times$ 300~s exposures.

Data reduction was carried out with a modified version of \texttt{LONGSLIT\_REDUCE} \citep{Becker09} for LUCI-1 by F. Bian \citep{Bian10}, a modified version of Spextool \citep{Cushing04,Vacca03} for GNIRS by Katelyn Allers (private communication), and the original version of \texttt{LONGSLIT\_REDUCE} for NIRSPEC \citep{Becker09}. These IDL packages carry out the standard data reduction steps for longslit near-IR spectra: flat-fielding, wavelength calibration with sky lines, pairwise sky subtraction, residual sky removal, shifting and coadding, spectral extraction, telluric correction, and flux calibration.

\subsection{Optical Spectroscopy of the Background QSOs}

Although optical spectra exist for all of the QSOs in our sample, most of them do not have the necessary wavelength coverage or sufficient S/N for absorption line analysis. So we obtained new optical spectra for the three background QSOs that are associated with the spectroscopically identified SMGs. We observed L6-FLS\,1712$+$6001 on 2015 Jun 13 and HeLMS\,0015$+$0404 and NGP\,1333$+$2357 on 2016 Jan 9 with the Low Resolution Imaging Spectrometer \citep[LRIS;][]{Oke95} on the Keck I telescope. We used the 1\arcsec\ longslit and the 560 Dichroic for both runs. For the former run, we used the 400/3400 Grism on the blue side ($R \simeq 540$) and the 400/8500 grating tilted to a central wavelength of $\lambda_{\rm c} = 8300$~\AA\ on the red side. 
%
For the latter run, we used the 600/4000 Grism on the blue side ($R \simeq 920$) and the 600/7500 grating at $\lambda_{\rm c} = 7407$~\AA\ on the red side. With the chosen dispersive elements, the spectral resolutions in FWHM are $\sim$4-7~\AA\ and $\sim$5-7~\AA\ for the blue and red spectra, respectively. The total integration time for each source ranged between 30 min and 40 min. Conditions were non-photometric for both nights.

We reduced the raw data with \texttt{XIDL}\footnote{http://www.ucolick.org/$\sim$xavier/IDL/}, an IDL data reduction package for a number of spectrographs written by two of us (JXP and JH). The pipeline follows the standard data reduction steps and reduces the blue and red channels separately. It begins by subtracting a super bias from the raw CCD frames, tracing the slit profiles using flat fields, and deriving the 2D wavelength solution for each slit using the arcs. Then it flat-fields each slit and rejects cosmic-rays, identifies objects automatically in the slit, and builds the 2D bspline super sky model without rectification \citep{Kelson03}. After subtracting the super sky model, it performs optimal 1D extraction based on the spatial profile of the QSO \citep{Horne86}. Finally, it removes instrument flexure using isolated sky lines, performs heliocentric correction, and does flux calibration.

\begin{deluxetable*}{rccccc ccccc}
\tablewidth{0pt}
\tablecaption{Redshifts and Absorption Line Measurements
\label{tab:NHI}}
\tablehead{
\colhead{Pair Name} & \colhead{SMG} & \colhead{$z_{\rm SMG}$} & \colhead{log($L_{\rm IR}$)} & \colhead{$q_{\rm IR}$}  & \colhead{QSO} & \colhead{$z_{\rm QSO}$} & \colhead{$\theta_{\rm 6GHz}$} & 
\colhead{$R_\bot$} &  \colhead{$W_{\rm Ly\alpha}$} & \colhead{flag} \\
\colhead{} & \colhead{(J2000)} & \colhead{}  & \colhead{(\lsun)} & \colhead{} &  \colhead{(J2000)} & \colhead{} & \colhead{(\arcsec)} & \colhead{(kpc)} & \colhead{(\AA)} & \colhead{} %\\
%\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} &  \colhead{(8)} & \colhead{(9)}
}
\startdata
\input{/Users/fu/casa/15a266/figs/tables/table4.tex}
\enddata
%\tablecomments{
%}
\end{deluxetable*}

\begin{figure*}[!tb]
\epsscale{0.38}
\plotone{/Users/fu/data/qph_opt/lris/plot/HeLMS_0015+0404_abs2.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/NGP_1333+2357_abs2.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/L6-FLS_1712+6001_abs2.eps}
\caption{Absorption line velocity profiles for \lya, \CII\,$\lambda$1335, and \SiIV\,$\lambda\lambda$1394,1403. The Keck/LRIS spectra of the background QSOs have been normalized by a model of the QSO continuum. All panels show the region $\pm$3000~\kms\ around the systemic redshifts of the SMGs. The top panels show Gaussian fits to the \lya\ absorption line. The vertical dashed line shows the centroid velocity.
\label{fig:abs}} 
\end{figure*}

\section{Results} \label{sec:result}

\subsection{Radio Detections and Astrometry}

% HeLMS_0015+0404HeLMS 0015$+$0404       7.4730953
% NGP_1333+2357NGP 1333$+$2357       2.7322102
% NGP_1335+2805NGP 1335$+$2805       6.4301388
% G15_1413+0058G15 1413$+$0058       3.3868686
% G15_1435+0110G15 1435$+$0110       5.4763202
% L6-FLS_1712+6001L6-FLS 1712$+$6001       7.8733087

We targeted the \hers\ sources in 13 \sqps\ with the VLA and made six clear detections (46\% detection rate; Fig.~\ref{fig:detections}). The VLA-detected SMGs have 6~GHz peak flux densities between 11 and 76~\uJy\ with a mean of $\sim$40~\uJy\ (Table~\ref{tab:vlaphoto}). For these detections, there is a clear non-linear correlation between the observed flux densities at 6~GHz and 500~\um: 
%$S_{\rm 6GHz,\mu Jy} \simeq 1.8 \times S_{\rm 500,mJy} - 32$ or 
$S_{\rm 6GHz,\mu Jy} \simeq 0.026 \times S_{\rm 500,mJy}^2$. The 3$\sigma$ upper limits from the non-detections all lie within 0.2~dex of this correlation, indicating that they are undetected because of the redshift uncertainty and the intrinsic scatter of the FIR-radio correlation \citep[e.g.][]{Ivison10c}. 
%
%(1) multiple fainter sources have contributed to the \hers\ flux and/or (2) these sources have hotter dusts ($T > 40$~K) and are at higher than expected redshifts ($z > 3$). 
%
%When folding in both the detections and the upper limits from the non-detections in a Monte Carlo realization, we estimate that the average 6~GHz flux density is $\sim$XX~\uJy\ for \hers-selected 350~\um\ peakers with $S_{500} > 20$~mJy. This implies that one needs to reach an rms sensitivity of XX~\uJy\ at 6~GHz to detect bulk of the population. 
%
The offsets between the \hers\ positions and the VLA positions range between 2.7\arcsec\ and 7.9\arcsec. The average offset of 5.6\arcsec\ is comparable to the reported 5\arcsec\ 95\%-ile positional uncertainty of \hers\ catalogs. However, 2/3 of the sources show offset greater than 5\arcsec, indicating that the uncertainty is underestimated. As a result, some of the pairs with small angular separations ($\theta_{250} \lesssim$ 8\arcsec) are probably single sources, i.e., QSOs that are FIR-luminous. For example, NGP\,1335$+$2805 is such a case ($\theta_{250} = 6.5$\arcsec). But L6-FLS 1712$+$6001 is not, despite an even smaller separation ($\theta_{250} = 5.4$\arcsec).

\subsection{Physical Properties of the SMGs}

We obtained deep near-IR spectra for the five VLA-detected SMGs whose spectroscopic redshifts are unknown. We detected \Ha\ and \NII\ lines from three of the five sources, enabling accurate determination of the spectroscopic redshifts (Fig.~\ref{fig:smgspec}). The two remaining sources, G15\,1413+0058 and G15\,1435+0110, show near-IR continuum emission with neither emission lines nor stellar absorption features. It is possible that the emission lines either fall into one of the telluric absorption bands or are simply outside of the spectral range. Our redshift success rate is thus 60\%, comparable to previous redshift surveys of SMGs \citep[e.g.,][]{Chapman05}. Atmosphere transparency varied substantially during the observations, so we do not have reliable flux measurements for the emission lines.

With the photometry from \hers\ and the VLA and spectroscopic redshifts, we can estimate the total rest-frame 8$-$1000~\um\ luminosity ($L_{\rm IR}$) and the IR-to-radio luminosity ratio ($q_{\rm IR}$). From the best-fit graybody models (where we fixed $\beta = 1.5$), we find that they are all Ultra-Luminous IR Galaxies (ULIRGs) with SFR$_{\rm IR}$ = 470-1500~\msunyr, when $L_{\rm IR}$ are converted to SFR using the calibration of \citet{Murphy11} for a \citet{Kroupa02} initial mass function:
\begin{equation}
 {\rm SFR}/M_{\odot}~{\rm yr}^{-1} = 1.5\times10^{-10}~L_{\rm IR}/L_{\odot}
\end{equation} 
The extrapolated 850~\um\ flux densities range between $7 \leq S_{850} \leq 18$~mJy, confirming that they are {\it bona fide} SMGs.

The IR-to-radio luminosity/flux ratio is estimated following \citet{Ivison10c}:
\begin{equation}
q_{\rm IR} = {\rm log} \frac{S_{\rm IR}/3.75\times10^{12}~{\rm W}~{\rm m}^{-2}}{S_{\rm 1.4 GHz}/{\rm W}~{\rm m}^{-2}~{\rm Hz}^{-1}}
\end{equation}
where $S_{\rm IR}$ is integrated 8-1000~\um\ flux and $S_{\rm 1.4GHz}$ is the 1.4~GHz flux density, both measured in the rest frame (assuming $S_\nu \propto \nu^{-0.8}$. The three SMGs show $2.1 \leq q_{\rm IR} \leq 2.6$, consistent with the observed radio-IR correlation for \hers\ sources \citep[$q_{\rm IR} = 2.4\pm0.5$;][]{Ivison10c}. This indicates that our radio-detected sample is not biased to radio-loud AGNs.

\subsection{Absorption Line Systems}

We searched for \HI\ \lya\ absorption from the SMGs in the QSO spectra. Strong \lya\ absorption lines are detected in all three systems (Fig.~\ref{fig:abs}). We report their rest-frame equivalent widths in Table~\ref{tab:NHI}. As we have found in our earlier QSO absorption line studies, systematic error associated with continuum placement and line blending generally dominates the statistical error of the QSO spectra. So we estimate the error of $W_{\rm Ly\alpha}$ assuming 10\% error in the continuum placement. All three systems show strong \lya\ absorption lines with $W_{\rm Ly\alpha} = 1.7-2.0$~\AA) within the halo escape velocity ($V_{\rm esc} = 610$~\kms\ at $R = 230$~kpc, which is the virial radius of a $10^{13}$~\msun\ NFW halos at $z = 2$).

Because of the large uncertainty ($\delta z \simeq 0.8$) of the photometric redshifts from \hers\ photometry, the redshift differences between the SMGs and the QSOs cannot be controlled effectively. For three three spectroscopically confirmed pairs, the redshifts of the SMG and the QSO differ by more than 0.2. The \HI\ \lya\ absorption from the foreground SMGs thus lie blue-ward of the QSOs' \lyb\ lines; i.e., they fall in the \lyb\ forest. Hence, contamination from the \lyb\ lines of systems in the \lya\ forest is a concern. Assuming the detected absorption is \lyb, we searched for the corresponding \lya\ lines but did not find any, indicating that \lyb\ contamination is not a serious issue for these systems.

We also searched for the strongest metal lines commonly observed in optically thick absorption systems \citep[e.g.,][]{Hennawi13}: Si\,{\sc ii}\,$\lambda$1260,1304,1527, O\,{\sc i}\,$\lambda$1302, \CII\,$\lambda$1335, Si\,{\sc iv}\,$\lambda$1394,1403, C\,{\sc iv}\,$\lambda$1548,1551, Fe\,{\sc ii}\,$\lambda$1608,2383,2600, Al\,{\sc ii}\,$\lambda$1671, and Mg\,{\sc ii}\,$\lambda$2796, 2804. Most of these lines are not detected in any of the systems, so we only show the possible detections of \CII\ and \SiIV\ lines in Fig.~\ref{fig:abs}. In the following, we discuss the systems individually:

\begin{itemize}
\item HeLMS\,0015$+$0404 ($z_{\rm SMG} = 2.515, z_{\rm QSO} = 3.256, R_\bot = 157$~kpc): This system shows a strong \lya\ absorption at $+$504~\kms\ with $W_{\rm Ly\alpha} = 2.0\pm0.2$~\AA. There is also a \CII\ absorption at $+$400~\kms\ ($W_{\rm CII} = 1.2$~\AA). Given these measurements, one would have concluded that this is an optically thick absorber with $N_{\rm HI} \sim 10^{19}$~cm$^{-2}$ if the absorption is dominated by a single component. The column density is estimated from the theoretical curve of growth where $W_{\rm Ly\alpha} = 7.3~(N_{\rm HI}/10^{20}~{\rm cm}^{-2})^{0.5}$~\AA\ for $N_{\rm HI} > 10^{18}$~cm$^{-2}$ \citep[][\S16.4.4]{Mo10}. However, the \CII\ absorption could be a false positive, because it is buried in the \lya\ forest and we did not detect other low-ionization metal lines to support the \CII\ detection. 
%This case is therefore inconclusive and we assign the \HI\ absorber an optical thickness flag of ambiguous. 
Without solid detections of strong metal lines and the detection of the damping wings in \lya, we cannot conclude that the absorber is optically thick based on current data because the high $W_{\rm Ly\alpha}$ could be due to line blending. We therefore classify this system as ambiguous.

\item NGP\,1333$+$2357 ($z_{\rm SMG} = 2.184, z_{\rm QSO} = 3.108, R_\bot = 198$~kpc): This system shows a strong \lya\ absorption at $-34$~\kms\ with $W_{\rm Ly\alpha} = 1.7\pm0.2$~\AA. The \CII\ and \SiIV\ absorption profiles are distinctly different: there appear to be two strong absorption components on both sides of the \HI\ absorption but the metal absorption is very weak at the velocity of the \HI\ \lya. The mismatch in velocity profiles indicates that the metal lines are spurious. Similar to the previous case, this system is ambiguous.

\item L6-FLS\,1712$+$6001 ($z_{\rm SMG} = 2.033, z_{\rm QSO} = 2.821, R_\bot = 112$~kpc): There is a strong \lya\ absorption at $-325$~\kms\ with $W_{\rm Ly\alpha} = 1.7\pm0.2$~\AA. Despite the high EW, this system is unlikely optically thick because the line center drops only to 40\% of the continuum intensity. The associated low-ionization metal lines are either very weak ($W \lesssim 0.1$~\AA) or completely absent. Hence, we classify this system as optically thin.

\end{itemize}

In summary, we have identified one clearly optically thin case and two ambiguous cases with three QSO sight-lines covering impact parameters between $100 < R_\bot < 200$~kpc around SMGs at $2.0 < z < 2.6$.

\section{Conclusions} \label{sec:discuss}

The CGM of high redshift QSOs is $\gtrsim$60\% filled by \HI\ absorbers that are optically thick at the Lyman limit. The high \HI\ covering fraction extends to at least the expected viral radius of $\sim$160~kpc \citep[][]{Hennawi06,Prochaska13,Prochaska13a}. In Figure~\ref{fig:covfrac}, we compare (1) the SMG sample distribution with the QSOs from the QPQ project, and (2) the covering fraction of optically thick \HI\ gas around SMGs with that around QSOs. The two samples overlap nicely in the plane of foreground redshift vs. impact parameter: the SMGs cover the same redshift range as the QSOs in the intermediate impact parameter range between 100 and 200~kpc. We calculate the 1$\sigma$ binomial confidence intervals of the optically thick fraction using the quantiles of the beta distribution \citep{Cameron11}. The covering fractions for the QSOs are considered lower limits because some of the ambiguous cases ({\it open symbols}) may be optically thick. Because there is no convincingly optically thick absorber among the three systems we analyzed, our 1$\sigma$ confidence interval of the covering fraction is 4.2$-$36.9\% for $k = 0$ and $n = 3$. For a fair comparison, we consider all of the QSO sightlines with $100 < R_\bot < 200$~kpc from QPQ and we find the \HI\ covering fraction is $64^{+7}_{-9}$\% for 21 optically thick systems among 33 systems. Despite our small sample, the 1$\sigma$ upper limit is 3$\sigma$ below the best-estimated covering fraction around QSOs. Therefore, the surrounding medium of SMGs seems more deprived of cool neutral gas than that of QSOs at $z \sim 2$, suggesting that the star formation cannot last longer than the $\sim$200~Myr timescale to exhaust the gas in the disk. This conclusion is clearly limited by the small sample size. A more robust comparison awaits a larger sample of spectroscopically confirmed \sqps.

\begin{figure}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/work/qph/qpq/covfrac.eps}
\caption{The covering fraction of optically thick gas around SMGs ({\it red downward arrow}: our 1$\sigma$ upper limit) vs. impact parameter, compared to that around QSOs from the QPQ survey \citep[{\it blue/gray squares} with error bars;][]{Prochaska13}. The blue and gray squares are estimates of the covering fraction based on 100~kpc-wide bins and 50~kpc-wide bins, respectively. The red stars and the black circles show the sample distribution in foreground redshift (right $Y$-axis) vs. impact parameter for the SMGs from this study and the QSOs from the QPQ survey, respectively. The black-filled, gray-filled, and open symbols correspond to systems that are optically thick, optically thin, and ambiguous at the Lyman limit, respectively.   
\label{fig:covfrac}} 
\end{figure}

%\section{Conclusions} \label{sec:conclusion}

\acknowledgments

We thank K.~Mooley and D.~Perley for taking the LRIS spectrum of L6-FLS\,1712$+$6001.

% JPL
%H.F. and D.M. were partially supported by NASA JPL award 1495624 and University of Iowa funds. 
% NRAO
The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc. Support for this work was provided by the NSF through award GSSP SOSPA3-016 from the NRAO.
% LBT
The LBT is an international collaboration among institutions in the United States, Italy and Germany. LBT Corporation partners are: The University of Arizona on behalf of the Arizona university system; Istituto Nazionale di Astrofisica, Italy; LBT Beteiligungsgesellschaft, Germany, representing the Max-Planck Society, the Astrophysical Institute Potsdam, and Heidelberg University; The Ohio State University, and The Research Corporation, on behalf of The University of Notre Dame, University of Minnesota and University of Virginia.
% Keck
Some of the data presented herein were obtained at the W.M. Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California and the National Aeronautics and Space Administration. The Observatory was made possible by the generous financial support of the W.M. Keck Foundation.
% Mauna Kea
The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.  We are most fortunate to have the opportunity to conduct observations from this mountain.
% Gemini
Based on observations obtained at the Gemini Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under a cooperative agreement with the NSF on behalf of the Gemini partnership: the National Science Foundation (United States), the National Research Council (Canada), CONICYT (Chile), Ministerio de Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina), and Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil).

{\it Facilities}: Herschel, Sloan, Keck/LRIS, Keck/NIRSPEC, VLA, LBT/LUCI, Gemini/GNIRS, VLT/SINFONI, Sloan

\bibliographystyle{/Users/fu/Documents/latex/apj/apj}
\bibliography{/Users/fu/Documents/bibliography/exgal_ref}

%%%%%%%%%%%%
% Appendix
%%%%%%%%%%%%
\clearpage

\appendix

The following pages show earlier versions of tables and figures that have been dropped from the main content. Nevertheless, they show the full data set that are useful for the analysis.

\clearpage
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

\begin{deluxetable*}{rrrccrrccc}[!h]
\tablewidth{0pt}
\tablecaption{VLA-Observed \sqps.}
\tablehead{ 
\colhead{Pair Name} & \colhead{RA$_{\rm QSO}$} & \colhead{DEC$_{\rm QSO}$} & \colhead{$z_{\rm QSO}$} & \colhead{$g_{\rm QSO}$} & \colhead{RA$_{250}$} & \colhead{DEC$_{250}$} & \colhead{$S_{250}$} & \colhead{$S_{350}$} & \colhead{$S_{500}$} \\
\colhead{} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{(mag)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{(mJy)} & \colhead{(mJy)} &  \colhead{(mJy)} \\
\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} &  \colhead{(8)} & \colhead{(9)} & \colhead{(10)} 
}
\startdata
\input{/Users/fu/casa/15a266/figs/tables/table1.tex}
\enddata
\tablecomments{
}
\end{deluxetable*}
%
\begin{deluxetable*}{rcccrrrccc}
\tablewidth{0pt}
\tablecaption{VLA 6~GHz Source Positions and Photometry.}
\tablehead{
\colhead{Pair Name} & \colhead{Int Time} & \colhead{rms} & \colhead{Beam} & \colhead{PA} & \colhead{RA$_{\rm 6 GHz}$} & \colhead{DEC$_{\rm 6 GHz}$} & \colhead{$S^{\rm peak}_{\rm 6 GHz}$} & \colhead{$S^{\rm int}_{\rm 6 GHz}$} & \colhead{$\theta$} \\
\colhead{} & \colhead{(min)} & \colhead{(\uJy/bm)} & \colhead{(\arcsec)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{(\uJy/bm)} & \colhead{(\uJy)} & \colhead{(\arcsec)} \\
\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} &  \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
}
\startdata
\input{/Users/fu/casa/15a266/figs/tables/table3.tex}
\enddata
\tablecomments{
$S^{\rm peak}_{\rm 6 GHz}$ and $S^{\rm int}_{\rm 6 GHz}$ are the peak flux density in \uJy/bm and the integrated flux density in \uJy, both of which are derived by fitting an elliptical Gaussian model to the source. The uncertainty of $S^{\rm peak}_{\rm 6 GHz}$ is given by the rms noise in the map at the source position, while the uncertainty of the $S^{\rm int}_{\rm 6 GHz}$ is estimated using the formulae provided by \citet{Hopkins03a}, which includes the 1\% uncertainty in the VLA flux-density scale at 6~GHz \citep{Perley13}.  
}
\end{deluxetable*}

\begin{figure*}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/casa/15a266/figs/vla_all.eps}
\caption{VLA C-band continuum maps for the 15 observed \sqps\ in 15A-266. The restoring beam of each map is plotted as the red ellipse at the lower right corner. The white cross and the dashed white circle indicate the \hers\ positions and the 18\arcsec\ FWHM of the 250~\um\ PSF. The green squares highlight the seven detected radio sources within the \hers\ FWHM, and the red circles highlight the two tentative detections. Blue diamonds mark the optical positions of the QSOs in each pair, when they are within the displayed 30\arcsec$\times$30\arcsec\ region centered on the \hers\ position. The gray dotted contour is at $-$2$\times$$\sigma$, and the black contours are at ($+$2, $+$4, $+$8)$\times$$\sigma$. Major tickmarks are spaced in 5\arcsec\ intervals. N is up and E is left for all panels.} 
\end{figure*}

\begin{figure*}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/data/qph_opt/lris/plot/HeLMS_0015+0404.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/HeLMS_0015+0404_abs.eps}
\caption{Keck LRIS optical spectra of the background QSOs. The wavelengths of absorption lines at the redshift of the SMGs are marked by dashed lines. } 
\end{figure*}

\begin{figure*}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/data/qph_opt/lris/plot/NGP_1333+2357.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/NGP_1333+2357_abs.eps}
\caption{Keck LRIS optical spectra of the background QSOs. The wavelengths of absorption lines at the redshift of the SMGs are marked by dashed lines. } 
\end{figure*}

\begin{figure*}[!tb]
\epsscale{1.18}
\plotone{/Users/fu/data/qph_opt/lris/plot/L6-FLS_1712+6001.eps}
\plotone{/Users/fu/data/qph_opt/lris/plot/L6-FLS_1712+6001_abs.eps}
\caption{Keck LRIS optical spectra of the background QSOs. The wavelengths of absorption lines at the redshift of the SMGs are marked by dashed lines. } 
\end{figure*}

%
%\section{VLA nondetections}
%
%
%\begin{figure*}[!tb]
%\epsscale{1.18}
%%\plotone{}
%\caption{Constraints on redshifts from VLA upper limits.
%\label{fig:photoz}} 
%\end{figure*}

\end{document}

### 2016-08-04 SMGI/qph_vla_v4.tex
jxp

--- 2016-08-04 SMGI/qph_vla_v3.tex
@@
 Submillimeter galaxies (SMGs) are dusty starbursts in the early universe that may have evolved into massive ellipticals today.
-Their clustering strength suggests that they inhabit $10^{13}$~\msun\ halos.
 The physical state of the circumgalactic medium of SMGs carries key information to decode massive galaxy formation yet are unexplored observationally.
@@
 
-The first mJy-level submillimeter surveys discovered a population of high-redshift submillimeter-bright galaxies (SMGs), namely, unresolved sources with 850~\um\ flux density ($S_{850}$) greater than 3~mJy \citep{Smail97,Barger98,Hughes98,Eales99}.
+The first mJy-level submillimeter surveys discovered a population of high-redshift submillimeter-bright galaxies (SMGs), namely, unresolved sources with 850~\um\ flux density ($S_{850}$) greater than 3-5~mJy \citep{Smail97,Barger98,Hughes98,Eales99}.
 The SMGs are massive \citep[\ms\ $\sim 10^{11}$~\msun;][]{Hainline11, Michalowski12, Targett12}, metal-rich \citep[$Z \sim Z_\odot$;][]{Swinbank04}, gas-rich \citep[\mg\ $\sim 3\times10^{10}$~\msun;][]{Greve05, Tacconi08, Ivison11}, extreme star-forming systems (SFR $\gtrsim 500$~\msunyr) at a median redshift of $z \sim 2.5$ \citep{Chapman05,Wardlow11,Yun12,Smolcic12}.
@@
 For $10^{13}$~\msun\ halos at $z = 2$, the total baryonic accretion rate from the mass growth rate of dark matter haloes is $\dot{M}_{\rm bar} \equiv 0.18 \times \dot{M}_{\rm halo} \sim 1200$~\msunyr\ \citep{Neistein08}.
-However, all of these baryons are expected to be shock-heated to the virial temperature of the halo ($\sim7\times10^6$~K) and the cool gas replenishment timescale is much longer than the gas depletion timescale in such halos \citep[e.g.,][]{Dekel06,Tacchella15}.
+However, all of these
+%% JFH There is always some cold accretion even in massive systems. So I would
+%% say something less definitive, like most of these baryons or a high fraction
+%% of these baryosn etc, i.e. ``In such massive DM halos, it is expected
+%% that most of the baryosn will be shock-heated to the virial temperature
+%% of hte halo ~ 10^7 K (not your number 7e6 is low for a 10^13 Msun halo, and
+%% is more appropriate for 1e12)
+baryons are expected to be shock-heated to the virial temperature of the halo ($\sim7\times10^6$~K) and the cool gas replenishment timescale is much longer than the gas depletion timescale in such halos \citep[e.g.,][]{Dekel06,Tacchella15}.
 Therefore, the prolific star formation in SMGs should be unsustainable; the SFR would decline with an $e$-folding timescale of only $\sim$200~Myr \citep[2\mg/SFR; e.g.,][]{Tacconi08,Bothwell12}.
 At such a rate, the SMGs would become red sequence galaxies in only a Gyr or 5 $e$-folding times\footnote{This is the time it would take to decrease the specific SFR (SFR/\ms) from $\sim$$10^{-9}$~Gyr$^{-1}$ for the SMGs at the observed epoch to $\sim$$10^{-11}$~Gyr$^{-1}$ for the red sequence at $z \sim 2$ \citep{Brammer09}.} \citep{Fu13}.
-Such a short transitional time of a significant high-redshift star-forming population helps explain the rapid build-up of the massive end of the red sequence at $z > 1$ \citep[e.g.,][]{Ilbert13}.
+Such a short transitional time of a significant high-redshift star-forming population
+%% JFH I have less faith in these models than you. I would say ``such a short
+%% transitional time ... might help explain....''
+helps explain the rapid build-up of the massive end of the red sequence at $z > 1$ \citep[e.g.,][]{Ilbert13}.
 It makes it unnecessary to invoke any additional quenching mechanisms such as galactic outflows, which can be suppressed in such massive halos \citep[e.g.,][]{Singh16}.
@@
 The CGM of co-eval QSOs may give us a hint, because they inhabit comparably massive ($\sim$$10^{12.6}\,M_{\odot}$) halos \citep{White12}.
-Contrary to the expected dominance of virialized X-ray plasma, absorption line spectroscopy of a statistical sample of $z \sim 2$ projected QSO pairs reveals the prevalence of cool ($T \sim 10^4$~K), metal-enriched ($Z \geq 0.1 Z_\odot$), and optically thick \lya\ absorbers ($N_{\rm HI} \geq 1.6\times10^{17}$~\cmsq) extending to at least the expected viral radius of 160~kpc \citep[the ``Quasar Probing Quasar'' (QPQ) project:][]{Hennawi06,Prochaska13,Prochaska13a}.
-The high observed covering factor of the cool CGM gas ($\gtrsim 60\%$) in $\sim$$10^{12.6}\,M_{\odot}$ halos has been compared to predictions from numerical simulations, and it has been realized that efficient star-formation-driven feedback from accreted satellite galaxies is required to increase the \HI\ covering factor to the observed level \citep[e.g.,][]{Fumagalli14,Faucher-Giguere15,Rahmati15,Faucher-Giguere16}.
+Contrary to the expected dominance of virialized X-ray plasma, absorption line spectroscopy of a statistical sample of $z \sim 2$ projected QSO pairs reveals the prevalence of cool ($T \sim 10^4$~K), metal-enriched ($Z \geq 0.1 Z_\odot$), and optically thick \lya\ absorbers ($N_{\rm HI} \geq 1.6\times10^{17}$~\cmsq) extending to at least the expected virial radius of 160~kpc \citep[the ``Quasar Probing Quasar'' (QPQ) project:][]{Hennawi06,Prochaska13,Prochaska13a}.
+The high observed covering factor of the cool CGM gas ($\gtrsim 60\%$) in $\sim$$10^{12.6}\,M_{\odot}$ halos
+%% JFH You are citing the wrong paper here for QPQ1, i.e. it is
+%% Hennawi, Prochaska, Burles et al., not the 2006 paper on binary
+%% quasars. I would also appreciate a citation to QPQ2, i.e. Hennawi
+%% and Prochaska 2007 where we showed explicitly that cool gas is strongly
+%% clustered around QSOs. 
+has been compared to predictions from numerical simulations, and it has been realized that efficient star-formation-driven feedback from accreted satellite galaxies is required to increase the \HI\ covering factor to the observed level \citep[e.g.,][]{Fumagalli14,Faucher-Giguere15,Rahmati15,Faucher-Giguere16}.
+%% JFH The situation here is more nuanced with the theory. Fumgalli et al. 2014
+%% and FG15 found that current simulations cannot explain the high covering
+%% factor of optically thick gas around QSOs. Rahmati found that he could
+%% explain it, but he made very optimistic (and erroneous) assumptions
+%% about the masses of halos populated by QSOs. FG16 found that he can
+%% only match the results with high-resolution simualtions that resolve
+%% feedback from small galaxies, and notably, Rahmatic has nowhere near
+%% this resolution. Anyway, I'd say that ``While several studies
+%% found that they cannot reproduce the high covering factor around
+%% quasars (Fumgalli14, FG15, but see Rahmatic), it has been
+%% argued that efficient star-formation-driven feedback from accreted
+%% satellite galaxies is required to increase the \HI\ covering factor to
+%% the observed level which is only resolved in the highest resolution
+%% cosmological zoom simulations (FG16). 
 The models predict that the covering factor increases with halo mass and is independent of specific SFR, so SMGs are likely to show even higher \HI\ covering factors.
@@
 
+%% JFH Would be useful to quote rough numbers for the # QSOs per deg^2 roughly
+%% (I think BOSS is about 20 per deg^2, and the number of SMGs per deg^2
+%%
+
 However, most \hers\ sources are not SMGs.
@@
 In addition, the blind CO survey of the brightest 350~\um\ peakers ($S_{350} \geq 115$~mJy) has shown a strikingly similar redshift distribution as 850~\um-selected SMGs \citep{Harris12}, even though most of these bright sources are strongly lensed.
-Criterion 3 is introduced to ensure that the Rayleigh-Jeans extrapolation would give $S_{850} > 3$~mJy, the classic definition of an SMG, given a typical power-law slope of 3.5 (i.e., $\beta = 1.5$).
-Only 70,823 \hers\ sources remained after this selection, giving an average surface density of 92 per \sqdeg\ (but note that the 500~\um\ depth varies substantially from field to field).
+Criterion 3 is introduced to ensure that the Rayleigh-Jeans extrapolation would give $S_{850} > 3$~mJy, the classic definition of an SMG, given a typical power-law slope of 3.5 for a modified blackbody with a frequency-dependent absorption cross section ($\kappa \propto \nu^{1.5}$).
+Only 70,823 \hers\ sources remained after this selection, giving an average surface density of 92 per \sqdeg, which is consistent with the observed 870~\um\ source count function above $S_{870} \gtrsim 3$~mJy \citep{Weis09,Coppin06}.
+%; but note that the 500~\um\ depth varies substantially from field to field.
 
@@
 The 5\arcsec\ lower limit is imposed as an attempt to avoid FIR-bright QSOs, because the 95\%-ile positional uncertainty of the \hers\ positions is $\sim$5\arcsec.
-Through visual inspection of the QSO spectra, we further excluded 31 pairs whose QSOs exhibit strong broad absorption lines (BALs), have wrong redshifts, or are misclassified.
-Therefore, our final sample include 199 pairs, among which 90/163 QSOs have $g \leq 21/22$~AB.
+Through visual inspection of the QSO spectra, we further excluded 31 pairs whose QSOs exhibit strong broad absorption lines (BALs),
+%%JFH add parenthetically that this makes them unsuitable for absorption line
+%% work. 
+have wrong redshifts, or are misclassified. Therefore, our final sample include 199 pairs, among which 90/163 QSOs have SDSS $g \leq 21/22$.
 
@@
 \epsscale{1.18}
-\plotone{/Users/fu/casa/15a266/figs/vla_detect.eps}
+\plotone{/Users/fu/casa/15a266/figs/vla_detect2.eps}
 \caption{VLA 6~GHz continuum maps for the six VLA-identified SMGs.
@@
 The restoring beam of each map is plotted as the red ellipse at the lower right corner.
-The white cross and the dashed white circle indicate the \hers\ positions and the 18\arcsec\ FWHM of the 250~\um\ PSF.
-The green square highlights the detected radio source within the \hers\ FWHM.
-The white diamond marks the optical position of the QSO, if it is within the displayed region.
-The gray dotted contour is at $-$2$\times$$\sigma$, and the black contours are at ($+$2, $+$4, $+$8)$\times$$\sigma$.
+The cross and the dashed circle indicate the \hers\ positions and the 18\arcsec\ FWHM of the 250~\um\ PSF.
+The red square highlights the detected radio source within the \hers\ FWHM.
+The blue diamond marks the optical position of the QSO, if it is within the displayed region.
+The contours are at ($+$2, $+$4)$\times$$\sigma$.
 Major tickmarks are spaced in 5\arcsec\ intervals.
@@
 Our first problem is that the angular resolution of \hers\ (FWHM = 18\arcsec/25\arcsec/36\arcsec\ at 250/350/500~\um) is inadequate for longslit spectroscopic observations.
-To obtain more accurate positions and to remove blended sources, we have to exploit interferometer observations with the Karl G.
+%% JFH Clarify this. Explain first that the CGM analysis requires a precise redshift
+%% for the foreground SMG. However the 5'' final positional uncertainity of the
+%% Herschel positions precludes longslit spectroscopic observations with typical
+%% slit width ~ 1.0'
+To obtain more accurate positions and to remove blended sources, we exploit interferometer observations of 15 \sqps\ with the Karl G.
 Jansky Very Large Array (VLA).
 Furthermore, once the positions are determined with sub-arcsec accuracy, we need to determine the spectroscopic redshifts of the SMGs with near-IR spectrographs.
+%% JFH Maybe clarify that success rate is much higher in near-IR for the SMGs. 
 Finally, a high S/N optical/near-UV spectrum of the background QSO is needed to detect the UV absorption lines imprinted by the diffuse medium around the SMGs.
@@
 \subsection{SMG Identification with the VLA}
+
+%% JFH State the zeroth order idea here, i.e. we get better positions
+%% using the faint radio continuum, where the emission is synchrotron emission
+%% from shocked gas in massive star winds, etc. according to FIR-radio correlation
+%% etc. etc.
 
@@
 For imaging and deconvolution, we used the standard CASA task {\sc clean} with ``natural'' weighting to achieve the best sensitivity.
-The resulting restoring beams are on average 1\farcs5$\times$1\farcs2 in FWHM and the rms noise ranges from 2.1 to 11.7~\uJy/bm (primarily driven by the different integration times).
+The resulting restoring beams are on average 1\farcs5$\times$1\farcs2 in FWHM and the rms noise ranges from 2.1 to 14.1~\uJy/bm with a mean at 6~\uJy/bm.
+The variation in rms is primarily driven by systematic noise (e.g., confusion sources).
+The different integration times play a minor role.
+
+%% JFH Quote a number for the final positional accuracy of the VLA data
+%% for a typical case i.e. S/N.
+
+%% JFH I guess Figure 1 should be reference in this section but it is not.
 
@@
 %
-We observed G15\,1435$+$0110, L6-FLS\,1712$+$6001, and NGP\,1333$+$2357 with the LUCI-1 spectrograph \citep{Seifert03} on the Large Binocular Telescope (LBT) on 2015 Apr 14.
+We observed G15\,1435$+$0110, L6-FLS\,1712$+$6001, and NGP\,1333$+$2357 with the LUCI-1
+%% JFH Spell out instrument acronym on first usage. 
+spectrograph \citep{Seifert03} on the Large Binocular Telescope (LBT) on 2015 Apr 14.
 We used the 200 l/mm $H$+$K$ grating at $\lambda_{\rm c} = 1.93$~\um\ and the N1.8 camera (0\farcs25 per pixel) to obtain a spectral range between 1.5 and 2.3~\um.
@@
 
+%% JFH So in this Table, I'd suggest changing ``flag'' to ``classification'' 
 \begin{deluxetable*}{rccccc ccccc}
@@
 The Keck/LRIS spectra of the background QSOs have been normalized by a model of the QSO continuum.
-All panels show the region $\pm$3000~\kms\ around the systemic redshifts of the SMGs.
-The top panels show Gaussian fits to the \lya\ absorption line.
-The vertical dashed line shows the centroid velocity.
+All panels show the region $\pm$3000~\kms\ around the systemic redshifts of the foreground
+%% JFH I added foreground here. 
+  SMGs. The top panels show Gaussian fits to the \lya\ absorption line. The vertical dashed line shows the centroid velocity.
 \label{fig:abs}} 
@@
 $S_{\rm 6GHz,\mu Jy} \simeq 0.026 \times S_{\rm 500,mJy}^2$.
-The 3$\sigma$ upper limits from the non-detections all lie within 0.2~dex of this correlation, indicating that they are undetected because of the redshift uncertainty and the intrinsic scatter of the FIR-radio correlation \citep[e.g.][]{Ivison10c}.
+%% JFH You should provide another sentence on background explaining why
+%% an non-linear corrleation of this form is expected. 
+The 3$\sigma$ upper limits from the non-detections all lie within 0.2~dex of this correlation, indicating that they are undetected because of the redshift uncertainty and the intrinsic scatter of the FIR-radio
+%% JFH Note this is the first time you mention FIR-radio correlatoin. See my comment
+%% earlier that you should add a sentence explaining the basic idea of
+%% targeting the SMGs in the radio. 
+correlation \citep[e.g.][]{Ivison10c}. 
 %
@@
 However, 2/3 of the sources show offset greater than 5\arcsec, indicating that the uncertainty is underestimated.
-As a result, some of the pairs with small angular separations ($\theta_{250} \lesssim$ 8\arcsec) are probably single sources, i.e., QSOs that are FIR-luminous.
-For example, NGP\,1335$+$2805 is such a case ($\theta_{250} = 6.5$\arcsec).
-But L6-FLS 1712$+$6001 is not, despite an even smaller separation ($\theta_{250} = 5.4$\arcsec).
+As a result, some of the pairs with small angular separations ($\theta_{250} \lesssim$ 8\arcsec) may be single sources, i.e., QSOs that are FIR-luminous.
+%% JFH I guess you should clarify here that you refer here to objects
+%% from the the VLA sample which were not actually detected. Or which
+%% sample are you referring to exactly??
+In our VLA sample, NGP\,1335$+$2805,
+%% JFH Reference Figure 1 here, so that the reader can see what you mean. 
+with $\theta_{250} = 6.5$\arcsec, is the only such case.
+%% JFH Clarify here with ``since this VLA position is coincident with the
+%% optical quasar position within the VLA error of XX"''
+But on the other hand, the SMG in L6-FLS 1712$+$6001 is a separate source from the QSO, despite its even smaller separation ($\theta_{250} = 5.4$\arcsec).
+
+%% JFH I see that the 250um beam is 18'', but I think it would also be useful
+%% to show the quoted 5'' positional uncertaintiy as a second cirucle in Figure
+%% 1.
 
@@
 It is possible that the emission lines either fall into one of the telluric absorption bands or are simply outside of the spectral range.
+%% JFH I would advocate that you should show what these spectra look like for the
+%% failures. 
 Our redshift success rate is thus 60\%, comparable to previous redshift surveys of SMGs \citep[e.g.,][]{Chapman05}.
 Atmosphere transparency varied substantially during the observations, so we do not have reliable flux measurements for the emission lines.
+%% JFH Why can't we use the telluric standards for this flux calibration??
+
+%% JFH I'm not sure I believe Figure 2 L6-FLS. I think in the upper panel, you
+%% should be plotting the chi-map, i.e. chi = (data - sky_model)/noise. It is
+%% much easier to convince yourself that a line detection is real in such a map,
+%% since things inconsistent with the background will be high n-sigma peaks.
 
@@
 \begin{equation}
- {\rm SFR}/M_{\odot}~{\rm yr}^{-1} = 1.5\times10^{-10}~L_{\rm IR}/L_{\odot}
+ {\rm SFR}/M_{\odot}~{\rm yr}^{-1} = 1.5\times10^{-10}~L_{\rm IR}/L_{\odot}. 
 \end{equation} 
@@
 
+%% JFH I would provide a basic overview first of what we want to measure.
+%% Maybe say we focus on classifying optically thick absorbers, based on
+%% the previous QPQ work, with the aim of characterizing the covering
+%% factor around SMGs. We also measure Ly-a EWs which can be compared to
+%% QPQ6, where a large number of such measurements are available for QSOs.
+
+%% JFH You need to state what your search window is for the strong absorbers
+%% here. In QPQ I believe we adopted 2000 km/s to be conservative, since the
+%% QSO redshift errors are large. You don't have that problem here, so you could
+%% adopt a smaller window comaprable to a typical virial velocity of an SMG
+%% like < 1000 km/s. Technically a different velocity window than the
+%% QSOs makes the comparison apples to oranges, but given that the number of
+%% optically thick absobers expected at random in a 2000 km/s window is like
+%% 2%, it is fine to mix different velocity scales.
+
 We searched for \HI\ \lya\ absorption from the SMGs in the QSO spectra.
@@
 So we estimate the error of $W_{\rm Ly\alpha}$ assuming 10\% error in the continuum placement.
-All three systems show strong \lya\ absorption lines with $W_{\rm Ly\alpha} = 1.7-2.0$~\AA) within the halo escape velocity ($V_{\rm esc} = 610$~\kms\ at $R = 230$~kpc, which is the virial radius of a $10^{13}$~\msun\ NFW halos at $z = 2$).
+All three systems show strong \lya\ absorption lines with $W_{\rm Ly\alpha} = 1.7-2.0$~\AA) within the halo escape velocity ($V_{\rm esc} = 610$~\kms\ at $R = 230$~kpc, which is the virial radius of a $10^{13}$~\msun\ NFW halo at $z = 2$).
+%% JFH Need to more explicitly state the velocity window over which this EW
+%% is being measured.
 
-Because of the large uncertainty ($\delta z \simeq 0.8$) of the photometric redshifts from \hers\ photometry, the redshift differences between the SMGs and the QSOs cannot be controlled effectively.
-For three three spectroscopically confirmed pairs, the redshifts of the SMG and the QSO differ by more than 0.2.
-The \HI\ \lya\ absorption from the foreground SMGs thus lie blue-ward of the QSOs' \lyb\ lines; i.e., they fall in the \lyb\ forest.
-Hence, contamination from the \lyb\ lines of systems in the \lya\ forest is a concern.
-Assuming the detected absorption is \lyb, we searched for the corresponding \lya\ lines but did not find any, indicating that \lyb\ contamination is not a serious issue for these systems.
+Because of the large uncertainty ($\delta z \simeq 0.8$) in the photometric redshifts from our initial selection of SMGs from the \hers\ photometry, in some cases the \HI\ \lya\ absorption from the SMG in the QSO spectrum may lie within the QSO Ly$\beta$ forest.
+This will be the case if $z_{QSO} - z_{SMG} \gtrsim 0.2$.
+%% JFH This statement is incorrect. If z_QSO =2.5, then the Ly-a forest extends
+%% from z_Lya = 2.5 to z_Lyb = (1 + 2.5)*1025.7/(1215.67) - 1.0 = 1.95. So there
+%% is actually path length of dz =0.5 per QSO. I'm not sure where you are getting
+%% this 0.2 number, but it is incorrect. 
+All three of our pairs fall in this category, so contamination from \lyb\ lines in systems in the \lya\ forest is a concern.
+However, assuming the detected absorption to be \lyb\ in each case, we searched for the corresponding \lya\ lines but did not find any, indicating that \lyb\ contamination is not a serious issue for these systems.
 
@@
 The column density is estimated from the theoretical curve of growth where $W_{\rm Ly\alpha} = 7.3~(N_{\rm HI}/10^{20}~{\rm cm}^{-2})^{0.5}$~\AA\ for $N_{\rm HI} > 10^{18}$~cm$^{-2}$ \citep[][\S16.4.4]{Mo10}.
+%% JFH Curve of growth requires a b-parameter. What did you use?? b-parameters
+%% in the IGM can be very large. 
 However, the \CII\ absorption could be a false positive, because it is buried in the \lya\ forest and we did not detect other low-ionization metal lines to support the \CII\ detection. 
@@
 We therefore classify this system as ambiguous.
+
+%% JFH For an absorption line person, I found the full velocity plots
+%% for all metal ions thatyou showed in Figure S2-4 more informative than
+%% only focusing on a CII and SiIV. You might consider still showing this
+%% in the appendix, and also consider adding more metal line species
+%% to the figure in the main text.
+
+%% JFH I don't think it is useful to highlight the metals in red in Figure 3,
+%% since you ahve not convincingly detected any.
+
+%% JFH I strongly suggest you adopt a histogram linestyle for plotting the
+%% the spectra. It looks much better.
+
+%% JFH I think it would be useful to simply draw a red vertical line
+%% at the velocity where you fit the strong HI line, to show that it is not
+%% obviously consistent with metals.
+
+%% JFH Is there a reason why you are not showing the CIV lines as well? Those
+%% should lie outside of the forest. Not sure why you focus only on SiIV
 
@@
 
+%% JFH I think Figure 4 would look better as a two panel plot. Upper panel
+%% just the R_perp vs. z distribution. Bottom point, the covering factors.
+%% In this way it would be a lot less busy, and less difficult to read/understand.
+
 The CGM of high redshift QSOs is $\gtrsim$60\% filled by \HI\ absorbers that are optically thick at the Lyman limit.
-The high \HI\ covering fraction extends to at least the expected viral radius of $\sim$160~kpc \citep[][]{Hennawi06,Prochaska13,Prochaska13a}.
+The high \HI\ covering fraction extends to at least the expected virial radius of $\sim$160~kpc \citep[][]{Hennawi06,Prochaska13,Prochaska13a}.
 In Figure~\ref{fig:covfrac}, we compare (1) the SMG sample distribution with the QSOs from the QPQ project, and (2) the covering fraction of optically thick \HI\ gas around SMGs with that around QSOs.
@@
 The covering fractions for the QSOs are considered lower limits because some of the ambiguous cases ({\it open symbols}) may be optically thick.
+%% JFH So the lower limit thing also applies to your SMGs, and if you
+%% are not careful with the discussion, that would seem to nullify
+%% your conclusion that the two samples are different. It is always
+%% possible that we are incomplete to LLSs. However, the bottom line
+%% here is that taken at face value, the same analysis (i.e. same
+%% classification, similar spectral quality) applied to QSOs and SMGs,
+%% yields results that don't agree. So I'd omit the lower limits from
+%% the QSO covering factor points altogether, but explains this issues
+%% somewhere in the text. 
 Because there is no convincingly optically thick absorber among the three systems we analyzed, our 1$\sigma$ confidence interval of the covering fraction is 4.2$-$36.9\% for $k = 0$ and $n = 3$.
+%% JFH YOu have not defined here what k and n are. I understand what they are
+%% but this is ambiguous and confusing. 
 For a fair comparison, we consider all of the QSO sightlines with $100 < R_\bot < 200$~kpc from QPQ and we find the \HI\ covering fraction is $64^{+7}_{-9}$\% for 21 optically thick systems among 33 systems.
 Despite our small sample, the 1$\sigma$ upper limit is 3$\sigma$ below the best-estimated covering fraction around QSOs.
-Therefore, the surrounding medium of SMGs seems more deprived of cool neutral gas than that of QSOs at $z \sim 2$, suggesting that the star formation cannot last longer than the $\sim$200~Myr timescale to exhaust the gas in the disk.
+Therefore, the surrounding medium of SMGs seems more deprived of cool neutral
+%% JFH Note most LLSs are actually highly ionized. So I would just say
+%% optically thick absorbers, or ``cool gas'', but omit neutral. 
+gas than that of QSOs at $z \sim 2$, suggesting that the star formation cannot last longer than the $\sim$200~Myr timescale to exhaust the gas in the disk.
 This conclusion is clearly limited by the small sample size.
@@
 
-We thank K.~Mooley and D.~Perley for taking the LRIS spectrum of L6-FLS\,1712$+$6001.
-
+We thank K.~Mooley and D.~Perley for taking the LRIS spectrum of L6-FLS\,1712$+$6001 and Z.-Y.~Zhang and D.~Ludovici for helping with the VLA data calibration. 
 % JPL

### 2016-10-12 QPQ9/qpq9_draft.tex
copy everything from svn

\documentclass[12pt,preprint]{aastex}
\usepackage{natbib,amsmath}
\special{papersize=8.5in,11in}
\begin{document}

\newcommand\ntot{2x}
\newcommand\nhigh{1x}
\newcommand\ncii{X5}
\newcommand\nciv{x5}
%\newcommand\vfct{0.71 \pm 0.08} % f_C for CII to 200kpc
\newcommand\vfct{0.73 \pm 0.10} % f_C for CII to 160kpc
\newcommand\dndz{2.1 \pm 0.2}
\newcommand\vro{7.5^{+2.8}_{-1.4} \, \mhMpc}
\def\mdv{\delta v}
\def\DV#1{$\Delta v_{90}^{#1}$}
\def\DRMS#1{$\sigma v_{90}^{#1}$}
\newcommand\vgmm{1.7^{+0.1}_{-0.2}}
\def\N#1{{N({\rm #1})}}
\newcommand\mlstar{L^*}
\newcommand\lstar{$\mlstar$}
\def \mmccgm {M_{\rm CGM}^{\rm cool}}
\def \mccgm {$\mmccgm$}
\def \mnhalo {n_{\rm halo}}
\def \nhalo {$\mnhalo$}
\def \mmminq {M_{\rm min}^{\rm QPQ}}
\def \mminq {$\mmminq$}
\def \mncom {n_{\rm com}}
\def \ncom {$\mncom$}
\def \mrcom {R^{\rm com}_\perp}
\def \rcom {$\mrcom$}
\def \mzem {z_{\rm em}}
\def \zem {$\mzem$}
\def \zbg {$z_{\rm bg}$}
\def \zfg {$z_{\rm fg}$}
\def \mzfg {z_{\rm fg}}
\def \mzlya {z_{\rm Ly\alpha}}
\def \zlya {$\mzlya$}
\def \mavgz{\langle z \rangle}
\def \avgz{$\mavgz$}
\def \wlya {$W_{\rm Ly\alpha}$}
\def \wsubj {$W_{\rm Ly\alpha}^{\rm line}$}
\def \mwsubj {W_{\rm Ly\alpha}^{\rm line}}
\def \mwlya {W_{\rm Ly\alpha}}
\def \mrphys {R_\perp}
\def \rphys {$\mrphys$}
\def \lbol {$L_{\rm Bol}$}
\def \guv {$g_{\rm UV}$}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \kms  {\, km~s$^{-1}$}
\def \mkms  {{\rm km~s^{-1}}}
\def \lya  {Ly$\alpha$}
\def \mlya  {{\rm Ly\alpha}}
\def \lyb  {Ly$\beta$}
\def \hMpc      {h^{-1}{\rm\ Mpc}}
\def \msol      {M_\odot}
\def \msun      {\msol}
\def\cm#1{\, {\rm cm^{#1}}}
\def \cgsflux   {{\rm erg\ s^{-1}\ cm^{-2}}}
\def \cgssflux   {{\rm erg\ s^{-1}\ Hz^{-1} cm^{-2}}}
\def\sci#1{{\; \times \; 10^{#1}}}
\def \msnlya {{\rm S/N}_{\rm Ly\alpha}}
\def \snlya {$\msnlya$}
\newcommand{\civt}{\ion{C}{4}~1548}
\newcommand{\ciit}{\ion{C}{2}~1334}
\newcommand{\mgiit}{\ion{Mg}{2}~2796}
\newcommand{\nvt}{\ion{N}{5}~1238}
\newcommand\mwciv{W_{1548}}
\newcommand\wciv{$\mwciv$}
\newcommand\mwcii{W_{1334}}
\newcommand\wcii{$\mwcii$}
\newcommand\avgcii{$\left < \mwcii \right >$}
\newcommand\mwmgii{W_{2796}}
\newcommand\wmgii{$\mwmgii$}
\newcommand\mavmgs{\left < \mwmgii \right >^{\rm S}}
\newcommand\avmgs{$\mavmgs$}
\newcommand\mavmgw{\left < \mwmgii \right >^{\rm w}}
\newcommand\avmgw{$\mavmgw$}
\newcommand\mtavmg{\left < \mwmgii \right >}
\newcommand\tavmg{$\mtavmg$}
\newcommand\mwnv{W_{1238}}
\newcommand\wmwnv{$\mwnv$}
\def \mfc {f_C}
\def \fc {$\mfc$}
\def \mfcs {f_C}
\def \fcs {$\mfcs$}
\newcommand\mmetal{$M_{\rm metal}^{\rm cool}$}
\newcommand\mwlim{W^{\rm lim}}
\newcommand\wlim{$\mwlim$} 
\newcommand\mxiq{\xi_{\rm Q-Q}}
\newcommand\xiq{$\mxiq$}
\newcommand\mxic{\xi_{\rm CIV-Q}}
\newcommand\xic{$\mxic$}
\newcommand\mxia{\xi_{\rm CIV-CIV}}
\newcommand\xia{$\mxia$}
\newcommand\mxixi{(\bar\mxiq \bar\mxia)^{1/2}} 
\newcommand\xixi{$\mxixi$}
\newcommand\mlxmg{\ell(X)_{\rm MgII}}
\newcommand\lxmg{$\mlxmg$}
\newcommand\mlxciv{\ell(X)_{\rm CIV}}
\newcommand\mlciv{\ell(z)_{\rm CIV}}
\newcommand\lciv{$\mlciv$}
\def \mhMpc{h^{-1}{\rm\ Mpc}}
\def \hMpc{$h^{-1}{\rm\ Mpc}$}
\def \mrvir {r_{\rm vir}}
\def \rvir {$\mrvir$}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }

\title{Quasars Probing Quasars IX. 
  Probing the Circumgalactic Flows of Quasars [v1.0]
}

\author{
J. Xavier Prochaska\altaffilmark{1},
Joseph F. Hennawi\altaffilmark{2}
Marie Wingyee Lau\altaffilmark{1},
}
\altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick
  Observatory, University of California, 1156 High Street, Santa Cruz,
  CA 95064}
\altaffiltext{2}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17,
  D-69115 Heidelberg, Germany}

\begin{abstract}
Blah
\end{abstract}

\keywords{absorption lines -- intergalactic medium -- Lyman limit
  systems}

\section{Introduction}

%\begin{itemize}
%\item Flows
%\item Mass (Kaiser, Schaye)
%\item Directionality/symmetry
%\item Break the symmetry
%\end{itemize}

%Take words from my summary of SomervilleDave15.

The formation and evolution of stars are dictated
by the flow of gas and metals/dust.  [This transport
varies directly with the stellar stage
and a lesser extent stellar mass.]
The accretion onto a protostellar  core eventually
initiates nuclear fusion.  The main sequence is characterized
by gentler stellar winds, with the most massive
stars shedding a cumulative mass of XX\%.
Stellar deaths, meanwhile, are frequently accompanied by terrific
mass loss, occasionally punctuated by a highly energetic,
supernova phase.

By analogy, galaxy formation and evolution are driven by the
flows into/out of their interstellar medium.
In contrast to most stars, however, current theories
predict (even demand) that the star-forming galaxies
maintin these flows. [add]

Akin to stars, direct observations of galactic flows are
difficult to acquire.  Even detecting the gas is challenging:
the gas mass is either too small or the gas density too low
for the [detection] of line-emission (e.g. 21cm, \lya,
or H$\alpha$ from Hydrogen).  Resolving the kinematics
and establish the mass-flux represent a far greater challenge.
These challenges are accentuated for distant, young galaxies
where flows are predicted to prevail \citep{keres,fumagalli}.
Therefore, with rare exceptions \citep[e.g.][]{slug,jackpot},
the community has relied on absorption-line spectroscopy
to detect and characterize the gas surrounding galaxies
\citep[e.g.][]{bergeron,steidel10,pro11,tumlinson13}.
With this experiment, researcher have had recent success
in characterizing the large-scale flows around star-forming
galaxies to reveal a net inflow \cite{rakic13} and
provide unique constraints on the mass of the underlying
potential well \cite{rakic14}.

A significant limitation of standard absorption-line
analysis, especially regarding sutyding galactic flows,
is the inherent symmetry of the experiment.
Because one generally lacks any constraint on the distance
of the gas along the sightline,
postive or negative velocities with respect to the
galaxy may be interpreted as gas flowing either towards
or away from the system.
So-called `down-the-barrel' observations break this
symmetry, and have generally provided evidence for flows
away from galaxies \citep{rupke,martin,weiner,rubin}.
However, these data are frequently at low spectral resolution
which limits one's sensitivity to inflowing gas.

In this Letter, we examine the flows of gas in the environments
of massive galaxies hosting quasars.  Our approach leverages
a large dataset of quasar pairs \citep{hennawi}
to use the standard technique of absorption-line spectroscopy
with background quasars. [word]
These quasar pairs have angular
separations that correspond to less than 300\,kpc physical
separation at the f/g quasar redshift.
Our previous publications from these quasar pairs
have established that these galaxies are surrounded
by a massive, cool, and enriched circumgalactic medium
\citep{QPQ1,QPQ5,QPQ6,QPQ7}.
We have collected a sample of \ntot~spectra passing within
300\,kpc from a f/g quasar with a precisely measured
redshift.  Our primary scientific interests are twofold:
(i) search for signatures of galactic-scale outflows from the
central galaxy, presumably driven by recent star-formation
and/or AGN feedback;
(ii) characterize the dynamics of galactic flows around these
massive system.  We further descrbie an aspect of this
experiment that offers a unique opportunity to study galactic
flows. [detail??]

Throughout this manuscript, we adopt a $\Lambda$CDM cosmology with
$\Omega_M = 0.26, \Omega_\Lambda = 0.74$, and $H_0 = 70 {\rm km \,
  s^{-1} \, Mpc^{-1}}$.  When referring to comoving distances we include 
explicitly an $h_{70}^{-1}$ term and follow modern convention of scaling
to a Hubble constant of 70\kms\,Mpc$^{-1}$.  All equivalent width measurements are
presented in the rest-frame, unless otherwise specified.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Experiment}
\label{sec:data}

From our QPQ survey\footnote{www.qpqsurvey.org} \citep{QPQ1},
we have analyzed the \ntot~systes that pass within 300\,kpc
(physical) from a f/g quasar with $xx < z < xx$.
We restrict the sample to f/g quasars with redshift measured
from \ion{Mg}{2}, [\ion{O}{3}], or XX emission giving 
a precision of $\sigma < 300 \mkms$ \citep{hewittwild}.
We include only those spectra with S/N~$> XX$\AA\ at the
observed wavelengths of \lya, \ion{C}{2}~1334, or 
\ion{C}{4}~1548 transitions.  Of the \ntot~sightlines, 
\nhigh\ have spectral resolution ~$> 5,000$ from echellette
or echelle observations (QPQ8).  This high-dispersion 
sample is analyzed [separately] throughout the paper.
Figure~\ref{fig:exp} summarizes the experimental design.
Refer to previous QPQ
publications for details on data reduction
and continuum normalzaton (QPQ6, QPQ7, QPQ8).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
\label{sec:analysis}

In QPQ8, we measured the velocity widths of the \ion{C}{2}~1334
and \ion{C}{4}~1548 transitions finding that the CGM
frequently exhibits large flows:
median \DV{1334},\DV{1548} = $XX,XX \mkms$ with and
RMS \DRMS{1334},\DRMS{1548} = $XX, XX \mkms$ from
a sample of \ncii\ and \nciv\ systems.
These velocity fields exceed all previous measurements from
galaxies and/or absorption systems at any epoch.  For
Figure~\ref{fig:stack}, we present these absorption lines
and \ion{H}{1}~\lya, also including lower-dispersion 
sightlines meeting the selection criteria.

To assess the `average' absorption of these transitions,
we have combined the data with a novel technique.
We have fitted the combined dataset using a cubic b-spline
with knots at every 100\,\kms.  We weighted each data
point by the velocity width of the pixel to insure that 
each sightline makes an equal contribution to the stack.
These b-spline profiles are presented in the figure
and a trivial integration gives the reported equivalent
widths.
[consider down-weighting systems with $<3\sigma$ EW]
[Comnent on EW from 'standard' technique]

Two results are evident from the figure:
 (i) the data exhibit excess absorptoin at 
 $\mdv \approx 0 \mkms$;
 (ii) the absorption is skewed towards positive velocities
 $\mdv > 0 \mkms$.
We measure absorption-weigthed ($1-f$) centroids
of $\mdv = XX-XX \mkms$ for these transitions
(Table~\ref{tab:summ}).
This suggests an asymmetry that contradicts the [standard]
expectation.

Given the small sample size, one must 
scrutinize the statistical significance of the measured offset.
Indeed, a small offset $\mdv < 10 \mkms$ may be expected
even with large samples.  To assess the statistical significance,
we have perfomed a boostrap analysis by randomly resampling
from the full sample. [DISCUSS]

[Discuss systematics here??]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:discussion}

[Add a cartoon fig with cone]
[Is it really obvious that this works??]

%%%%%%%%%%%%%%%%
\acknowledgements

JXP and ML acknowledge support from the National
Science Foundation (NSF) grant AST-1010004 and AST-XX. 
JXP thanks the Alexander
von Humboldt foundation for a visitor fellowship to the MPIA where
part of this work was performed, as well as the staff at MPIA for
their hospitality during his visits.
JFH acknowledges generous support from the Alexander von Humboldt
foundation in the context of the Sofja Kovalevskaja Award. The
Humboldt foundation is funded by the German Federal Ministry for
Education and Research.

%Much of the data presented herein were obtained at the W.M. Keck
%Observatory, which is operated as a scientific partnership among the
%California Institute of Technology, the University of California, and
%the National Aeronautics and Space Administration. The Observatory was
%made possible by the generous financial support of the W.M. Keck
%Foundation.  Some of the Keck data were obtained through the NSF
%Telescope System Instrumentation Program (TSIP), supported by AURA
%through the NSF under AURA Cooperative Agreement AST 01-32798 as
%amended.
%
%Some of the data herein were obtained at the Gemini Observatory, which
%is operated by the Association of Universities for Research in
%%Astronomy, Inc., under a cooperative agreement with the NSF on behalf
%of the Gemini partnership: the NSF (United
%States), the Science and Technology Facilities Council (United
%Kingdom), the National Research Council (Canada), CONICYT (Chile), the
%Australian Research Council (Australia), Minist\'{e}rio da
%Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil) and Ministerio de
%Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina). 
%
%The authors wish to recognize and acknowledge the very
%significant cultural role and reverence that the summit of Mauna Kea
%has always had within the indigenous Hawaiian community. We are most
%fortunate to have the opportunity to conduct observations from this
%mountain.

\bibliographystyle{/u/xavier/paper/Bibli/apj}
\bibliography{/u/xavier/paper/Bibli/allrefs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{../Tables/tab_sub_qpq7_spectra.tex}
\input{Tables/tab_summ.tex}
\input{Tables/tab_summ_Hab.tex}
%\input{tab1_sub.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\begin{figure}
\includegraphics[width=5in]{Figures/fig_experiment.pdf}
%\includegraphics[width=5in,angle=90]{../Figuref1.eps}
\caption{Experimental design
}
\label{fig:exp}
\end{figure}

\begin{figure}
\includegraphics[width=5in]{Figures/fig_simple_stack.pdf}
%\includegraphics[width=5in,angle=90]{f2.eps}
\caption{Simple stack
}
\label{fig:stack}
\end{figure}

\end{document}

### 2016-10-12 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py

@@ -1,0 +1,188 @@
+#Module for QPQ9 boot-strapping
+# Imports
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, os, sys, copy
+from scipy import stats as scistats
+
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy.table import QTable
+from astropy.io import ascii, fits
+from astropy import units as u
+from astropy import constants as const
+
+from xastropy.igm.abs_sys import abssys_utils as abssys
+from xastropy import spec as xspec
+from xastropy.spec.lines_utils import AbsLine
+from xastropy.plotting import utils as xputils
+from xastropy.xutils import xdebug as xdb
+from xastropy.obs import radec as xor
+from xastropy.atomic import ionization as xai
+
+# Local
+sys.path.append(os.path.abspath("../py"))
+import qpq9_analy as qpq9a
+import qpq_spec as qpqs
+
+####
+#  Bootstrap one transition
+def boot_trans(wrest=None, outfil=None, nboot=10000,
+    vmnx = (-3000., 3000.)*u.km/u.s, stack_tup=None,
+    passback=False, debug=False, qpq9=None):
+    ''' Bootstrap on a single transition
+
+    Parameters:
+    ----------
+    wrest: Quantity, optional
+      Rest wavelength [CII 1334]
+    nboot: int, optional
+      Number of bootstraps [10000]
+
+    Returns:
+    --------
+    Outputs an image of the bootstraps
+    '''
+
+    # Todo
+    #   Have symbol size indicate near-IR for redshift
+    reload(qpq9a)
+
+    # Rest wavelength
+    if wrest is None:
+        wrest = 1334.5323*u.AA
+
+    # Continuum ranges
+    cranges = [ (-2400., -1600)*u.km/u.s, 
+        (1600., 2500)*u.km/u.s]
+    EW_range = (-1600., 1600)*u.km/u.s
+
+    # Load QPQ9
+    if qpq9 is None:
+        qpq9 = qpq9a.load_qpq(wrest)
+
+    if outfil is None:
[…]

### 2016-10-12 QPQ9/Analysis/Redshifts/py/qpq_z.py

@@ -1,0 +1,338 @@
+"""
+#;+ 
+#; NAME:
+#; qpq_spec
+#;    Version 1.0
+#;
+#; PURPOSE:
+#;    Module for QPQ redshifts
+#;   May-2015 by JXP
+#;-
+#;------------------------------------------------------------------------------
+"""
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+# imports
+import numpy as np
+import glob, os, sys, copy
+import multiprocessing
+
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy.stats import sigma_clip
+from astropy.nddata import StdDevUncertainty
+from astropy.coordinates import SkyCoord
+from astropy.units import Unit
+from astropy.io import fits
+from astropy import units as u
+from astropy import constants as const
+from astropy.table import QTable, Table, Column 
+
+from linetools.spectra import io as lsio
+from linetools.spectra.xspectrum1d import XSpectrum1D
+
+from xastropy.xutils import fits as xxf
+from xastropy.stats import basic as xsb
+
+from xastropy.xutils import xdebug as xdb
+
+from enigma.qso import hewittwildz as hw10z
+
+def parse_o2_zstruct(xx=None):
+    ''' Parse the output file from JFH
+    Parameters:
+    -------------
+    xx: str, optional
+      Line to focus on (MgII, Ha, Hb)
+
+    Returns:
+    --------------
+    qsos 
+    zline
+    '''
+    # Read O2 file
+    qsozout = os.getenv('DROPBOX_DIR') + '/O2_zsys/qsos_o2_zstruct.fits'
+    qsos = Table.read(qsozout)
+    # Cut on good [OII]
+    good_o2 = ((qsos['ZSYS_ZSYS'] > 0.0)&# AND $   ;; systemic redshift not zero
+        (qsos['ZSYS_OII_QUAL'] == 1)&# AND $ ;; received
+        (qsos['M_I_Z2'] <= -23.0)&# AND $   ;; bright enough to be a QSO and not Seyfert
[…]

### 2016-10-12 QPQ9/Analysis/Redshifts/py/tst_dr7.py

@@ -1,0 +1,194 @@
+"""
+#;+ 
+#; NAME:
+#; tst_dr7
+#;    Version 1.0
+#;
+#; PURPOSE:
+#;    Module for running our HW10 code on DR7
+#;   Jul-2015 by JXP
+#;-
+#;------------------------------------------------------------------------------
+"""
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+# imports
+import numpy as np
+import glob, os, sys, copy
+import multiprocessing
+import cPickle as pickle
+
+from scipy import signal as sci_signal
+
+from astropy.nddata import StdDevUncertainty
+from astropy.coordinates import SkyCoord
+from astropy.units import Unit
+from astropy.io import fits
+from astropy import units as u
+from astropy import constants as const
+from astropy.table import QTable, Column
+
+from xastropy.obs import radec as xrad
+from xastropy.xutils import xdebug as xdb
+from xastropy.xutils import fits as xxf
+from xastropy.sdss import quasars as sdssq
+from xastropy.sdss import qso as sdssqso
+
+sys.path.append(os.path.abspath("./py"))
+import qpq_z as qpqz
+import hewittwildz as hw10z
+
+# Hewitt&Wild Prescription
+
+# Generate globals for mapping
+
+# Read HW10 table
+fil = os.getenv('QPQ9')+'Analysis/Redshifts/hw10_tab4.fits.gz'
+hw10_tab4 = QTable.read(fil)
+
+# JXP DR7
+sdss_dr7 = sdssq.SdssQuasars(verbose=False)
+
+def mgii_in_hw10(parallel=True, nproc=8):
+    '''Analyze quasars good for MgII in HW10 and DR7
+    
+    Parameters:
+    ------------
+    parallel: bool, optional
+      Run code in parallel (with pool.map)
+    nproc: int, optional
+      Number of processors for parallel
+
+    Returns:
+    --------
+    '''
+
+    # Parse
+    zmnx = [1.5,2.2]
+    gdhw = np.where( (hw10_tab4['z']>zmnx[0]) & (hw10_tab4['z']<zmnx[1]))[0]
+    print('We have {:d} DR7 quasars to try.'.format(len(gdhw)))
+
+    testing = True
+    if testing:
[…]

### 2016-10-12 QPQ9/Analysis/Redshifts/py/zsys_figs.py

@@ -1,0 +1,379 @@
+# Module for zsys QA
+
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import subprocess, glob, copy, os
+
+from scipy.signal import medfilt
+
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy import constants as const
+from astropy import units as u
+from astropy.units import Unit
+from astropy.io import ascii, fits
+from astropy.table import QTable, Table, Column
+from astropy.coordinates import SkyCoord
+from astropy.cosmology import FlatLambdaCDM
+from astropy.relativity import velocities as arv
+
+from xastropy.xutils import fits as xxf
+from xastropy.plotting import utils as xputils
+from xastropy.spec import readwrite as xsr
+from xastropy.xutils import xdebug as xdb
+
+
+##
+def zsys_flag_str(idx):  
+    ''' 
+    List of the lines used
+    '''
+    val = [ r'H$\alpha$', 
+        r'H$\beta$',
+        'MgII',
+        'CIII]' ,           # 3
+        'CIV'   ,           # 4
+        'SiIV'  ,           # 5
+        'SiIV-CIV' ,        # 6
+        'SiIV-CIII]' ,      # 7
+        'CIV-CIII]' ,       # 8
+        'SiIV-CIV-CIII]' ,  # 9
+        r'Ly$\alpha$', 
+        '[OIII]'  ,         # 11
+        '[OII]']            # 12
+    # Return
+    try:
+        return val[idx]
+    except IndexError:
+        return 'NULL'
+
+##
+def zsys_qa(zem_fil, outfil=None, clobber=False):
+    '''
+    Generate a QA PDF file from a zem_fil
+    '''
+    # Outfil
+    i0 = zem_fil.find('/')+1
+    i1 = zem_fil.find('_zem')
+    outfil = 'zQA/'+ zem_fil[i0:i1] + '_zQA.pdf'
+    name = zem_fil[i0:i1]
+
+    # Check
+    dum = glob.glob(outfil)
+    if (len(dum) > 0) & (not clobber):
[…]

### 2016-10-12 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -1,0 +1,183 @@
+#Module for QPQ9 stacking
+# Imports
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, os, sys, copy
+from scipy import stats as scistats
+
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy.table import QTable
+from astropy.io import ascii, fits
+from astropy import units as u
+from astropy import constants as const
+
+from linetools.spectra.xspectrum1d import XSpectrum1D
+
+from xastropy.igm.abs_sys import abssys_utils as abssys
+from xastropy import spec as xspec
+from xastropy.plotting import utils as xputils
+from xastropy.xutils import xdebug as xdb
+from xastropy.obs import radec as xor
+from xastropy.atomic import ionization as xai
+
+sys.path.append(os.path.abspath("../../../../py"))
+from enigma.qpq import spec as qpqs
+from enigma.qpq import stacks as qpqk
+from enigma.qpq import qpq as eqpq
+
+# Local
+sys.path.append(os.path.abspath("../py"))
+import qpq9_analy as qpq9a
+
+####
+def qpq9_NIR(wrest=None, outfil=None, nboot=10000,
+    vmnx = (-3000., 3000.)*u.km/u.s, stack_tup=None,
+    passback=False, debug=False): 
+    ''' Stack the QPQ9 sample
+    To do: add MgII redshifts to the QPQ9 structure
+    Find out what are the null redshifts
+    '''
+
+    # To do: Have symbol size indicate near-IR for redshift
+    reload(qpq9a)
+
+    # Rest wavelength
+    if wrest is None:
+        wrest = 1334.5323*u.AA
+
+    # Load QPQ9
+    qpq9 = eqpq.QPQ('QPQ9')
+    # Avoid Lya forest
+    qpq9.cull(wrest,4)
+    print('length of sample after and before culling',len(qpq9.data),len(qpq9._fulldata))
+    
+    if outfil is None:
+        outfil = 'Output/QPQ9_zNIR_{:d}.fits'.format(int(wrest.value))
+
+    # Load the stack image
+    if stack_tup is None:
[…]

### 2016-10-12 QPQ9/Analysis/Stacks/py/qpq9_stacks_qpq7.py

@@ -1,0 +1,185 @@
+#Module for QPQ9 stacking
+# Imports
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, os, sys, copy
+from scipy import stats as scistats
+
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy.table import QTable
+from astropy.io import ascii, fits
+from astropy import units as u
+from astropy import constants as const
+
+from linetools.spectra.xspectrum1d import XSpectrum1D
+
+from xastropy.igm.abs_sys import abssys_utils as abssys
+from xastropy import spec as xspec
+from xastropy.plotting import utils as xputils
+from xastropy.xutils import xdebug as xdb
+from xastropy.obs import radec as xor
+from xastropy.atomic import ionization as xai
+
+sys.path.append(os.path.abspath("../../../../py"))
+from enigma.qpq import spec as qpqs
+from enigma.qpq import stacks as qpqk
+from enigma.qpq import qpq as eqpq
+
+# Local
+sys.path.append(os.path.abspath("../py"))
+import qpq9_analy as qpq9a
+
+####
+def qpq7_allz(wrest=None, outfil=None, nboot=10000,
+    vmnx = (-3000., 3000.)*u.km/u.s, stack_tup=None,
+    passback=False, debug=False): 
+    ''' Stack the QPQ7 sample
+    '''
+
+    # To do: Have symbol size indicate near-IR for redshift
+    reload(qpq9a)
+
+    # Rest wavelength
+    if wrest is None:
+        wrest = 1334.5323*u.AA
+
+    # Load QPQ9
+    qpq7 = eqpq.QPQ('QPQ7')
+    # Avoid Lya forest
+    qpq7.cull(wrest,4)
+    print('length of sample after and before culling',len(qpq7.data),len(qpq7._fulldata))
+    
+    # Cut on 300 kpc
+    gdR = np.where(qpq7.data['R_PHYS'] < 300)[0]
+
+    if outfil is None:
+        outfil = 'Output/QPQ7_allz_{:d}.fits'.format(int(wrest.value))
+
+    # Load the stack image
+    if stack_tup is None:
[…]

### 2016-10-12 QPQ9/Analysis/py/qpq9_analy.py

@@ -1,0 +1,332 @@
+# Module for QPQ9 analysis
+
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, copy, os, sys
+
+from scipy.interpolate import interp1d
+from scipy.interpolate import splev, splrep # bspline
+
+
+from astropy import units as u
+from astropy.units import Unit
+from astropy.io import ascii, fits
+from astropy.table import QTable, Table, Column
+from astropy.coordinates import SkyCoord
+from astropy import constants as const
+
+from linetools.spectralline import AbsLine
+from linetools.lists import linelist as lll
+
+from xastropy.xutils import fits as xxf
+from xastropy.xutils import xdebug as xdb
+from xastropy.atomic import ionization as xai
+from xastropy.xguis import utils as xxgu
+
+# Local 
+sys.path.append(os.path.abspath("./py"))
+import qpq_spec as qpqs
+
+high_res_inst = ['ESI', 'MAGE', 'MIKE', 'HIRES', 'XSHOOTER', 'UVES']
+
+
+##
+def stack_bspline(in_tup, dv=100*u.km/u.s, debug=False, **kwargs):
+    '''Provided a table of b/g QSOs or a stack image,
+      stack their spectra with a b-spline approach
+
+    Parameters:
+    ------------
+    in_tup: Tuple
+      (QPQ9 Table, wrest)
+      (fin_velo, stck_img, stck_msk, all_dict)
+    dv: Quantity, optional
+      Velocity spacing of breakpoints [100 km/s]
+
+    Returns:
+    ------------
+    fin_velo
+    fin_flx
+    all_dict
+    '''
+    reload(qpqs)
+
+    # Generate the image
+    if len(in_tup) == 2: 
+        fin_velo, stck_img, stck_msk, all_dict = load_stack_img(
+            in_tup[0], in_tup[1], **kwargs)
+    else:
+        fin_velo, stck_img, stck_msk, all_dict = in_tup
+
+    # Generate the full array for b-spline action
+    list_vel = []
+    list_fx = []
+    list_wgt = []
+    for tdict in all_dict:
+        if tdict is None:
+            continue
+        vel = tdict['spec'].velo[tdict['spec'].sub_pix]
+        idv = np.median(vel - np.roll(vel,1))
+        # Save
[…]

### 2016-10-12 QPQ9/Analysis/py/qpq9_strct.py

@@ -1,0 +1,153 @@
+# Module for QPQ9 structure
+
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, copy, os, sys
+
+import sdsspy as spy
+
+from astropy import units as u
+from astropy.units import Unit
+from astropy.io import ascii, fits
+from astropy.table import QTable, Table, Column
+from astropy.coordinates import SkyCoord
+from astropy.cosmology import FlatLambdaCDM
+from astropy.relativity import velocities as arv
+from astropy import constants as const
+
+from xastropy.xutils import fits as xxf
+from xastropy.xutils import xdebug as xdb
+
+sys.path.append(os.path.abspath(os.getenv('QPQ9')+"Analysis/Redshifts/py"))
+import zsys_figs as qpqz
+
+sys.path.append(os.path.abspath(os.getenv('QPQ9')+"Analysis/py"))
+import qpq_sample as qpqsmp
+
+##
+def mk_qpq9(outfil=None):
+
+    # Imports
+    reload(qpqsmp)
+
+    # Init
+    if outfil is None:
+        outfil = 'qpq9_final.fits'
+        
+    # Read
+    bgfil = 'QPQ-CGM-IR_00.000-00.300_Sat-Apr-25-21:33:45-2015_qsobg.fits.gz'
+    fgfil = 'QPQ-CGM-IR_00.000-00.300_Sat-Apr-25-21:33:45-2015_qsofg.fits.gz'
+    ''' Getting too few Lya files in this one
+    Not sure why
+    bgfil = 'QPQ-CGM-IR_00.000-00.300_Tue-May-26-18:12:57-2015_qsobg.fits'
+    fgfil = 'QPQ-CGM-IR_00.000-00.300_Tue-May-26-18:12:57-2015_qsofg.fits'
+    '''
+    qso_bg = xxf.bintab_to_table(os.getenv('DROPBOX_DIR')+'/QSOPairs/QSO-CGM-IR/'+bgfil)
+    qso_fg = xxf.bintab_to_table(os.getenv('DROPBOX_DIR')+'/QSOPairs/QSO-CGM-IR/'+fgfil)
+
+    # Collate
+    qpq9 = copy.deepcopy(qso_bg)
+    # Add/replce key columns from qso_fg
+    oldc = ['Z_IR','SIGMA_ZIR', 'RA', 'DEC']
[…]

### 2016-10-12 QPQ9/Analysis/py/qpq_sample.py

@@ -1,0 +1,128 @@
+"""
+#;+ 
+## DEPRECATED
+## DEPRECATED
+## DEPRECATED
+#
+#; NAME:
+#; qpq_spec
+#;    Version 1.0
+#;
+#; PURPOSE:
+#;    Module for dealing with QPQ samples
+#;   May-2015 by JXP
+#;-
+#;------------------------------------------------------------------------------
+"""
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+# imports
+import numpy as np
+import glob, os 
+
+from scipy.interpolate import interp1d
+
+from astropy.cosmology.core import LambdaCDM
+from astropy.coordinates import SkyCoord
+from astropy.units import Unit
+from astropy.io import fits, ascii
+from astropy import units as u
+from astropy.utils import isiterable
+
+from xastropy.spec import readwrite as xsr
+from xastropy.obs import radec as xrad
+from xastropy.xutils import fits as xxf
+from xastropy.xutils import xdebug as xdb
+from xastropy.files import general as xfg
+
+##
+def sdss_flux2mag(flux, filt):
+    '''
+    Calculate the magnitude given a flux
+
+    Parameters:
+    -----------
+    flux: float
+      Flux, usually de-reddened
+    filter: string
+      SDSS filter:  ugriz
+
+    Returns:
+    -----------
+    mag: float
+      apparent magnitude
+    '''
+    #  Smoothing parameter
+    b_parms = {'u': 1.4, 'g': 0.9, 'r': 1.2, 'i': 1.8, 'z': 7.4}
+    b_parm = b_parms[filt]
+
+    # Calculate
+    a = 1.08574
+    ln10_min10 = -23.02585
+    # 
+    m = -a*(np.arcsinh(5.0*flux/b_parm)+ln10_min10 + np.log(b_parm))    
+
+    # Return
+    return m
+
+##
+def m_iz2_qso(mag, ztot, omega_m=0.3, omega_v=0.7, w=1.0, lit_h=0.7):
+    '''
+    Calculate Absolute magnitude
+       Note these are M_i(z = 2) absolute magnitudes. 
+
+    Parameters:
+    -----------
+    mag:  float
+      SDSS magnitude
+    ztot:  float
+      Redshift of interest
+    omega_m: float (0.3)
+      Dark matter parameter
+    omega_v: float (0.7)
+      Vacuum energy parameter
[…]

### 2016-10-12 QPQ9/Analysis/py/qpq_spec.py

@@ -1,0 +1,46 @@
+"""
+## DEPRECATED
+###   see enigma.qpq.spec
+#;+ 
+#; NAME:
+#; qpq_spec
+#;    Version 1.0
+#;
+#; PURPOSE:
+#;    Module for dealing with spectra in the QPQ dataset 
+#;   May-2015 by JXP
+#;-
+#;------------------------------------------------------------------------------
+"""
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+# imports
+import numpy as np
+import glob, os, copy
+
+from astropy.coordinates import SkyCoord
+from astropy.units import Unit
+from astropy.io import fits
+from astropy import units as u
+from astropy import constants as const
+
+from linetools.spectra import io as lsio
+
+from xastropy.obs import radec as xrad
+from xastropy.xutils import fits as xxf
+from xastropy.xutils import xdebug as xdb
+from xastropy.files import general as xfg
+
+
+
+# ################
+if __name__ == "__main__":
+
+    flg_fig = 0 
+    flg_fig += 2**0  # Test file grabbing
+    #flg_fig += 2**1  # Test with spectrum
+    
+    # 
+    if (flg_fig % 2**1) >= 2**0:
+        bg_qso = 'J005718.90-000134.7'
+        get_spec_files(bg_qso)

### 2016-10-12 QPQ9/Figures/py/qpq9_figs.py

@@ -1,0 +1,546 @@
+#Module for QPQ9 figures
+# Imports
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, os, sys, copy
+from scipy import stats as scistats
+
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy.table import QTable, Table
+from astropy.io import ascii
+from astropy import units as u
+from astropy import constants as const
+
+from linetools.spectralline import AbsLine
+
+from xastropy.igm.abs_sys import abssys_utils as abssys
+from xastropy import spec as xspec
+from xastropy.plotting import utils as xputils
+from xastropy.xutils import xdebug as xdb
+from xastropy.obs import radec as xor
+from xastropy.atomic import ionization as xai
+
+sys.path.append(os.path.abspath("../../../py"))
+from enigma.qpq import utils as qpqutils
+from enigma.qpq import spec as qpqs
+
+# Local
+sys.path.append(os.path.abspath("../Analysis/py"))
+import qpq9_analy as qpq9a
+
+####
+#  Plot the Experiment
+def experiment(outfil=None, qpq9=None, spec_files=None, spec_dicts=None):
+
+    # Todo
+    #   Have symbol size indicate near-IR for redshift
+
+    # Imports
+    reload(xai)
+
+    if outfil is None:
+        outfil = 'fig_experiment.pdf'
+
+    # Read QPQ9
+    if qpq9 is None:
+        qpq9 = QTable.read('../Analysis/qpq9_final.fits')
+    if spec_files is None:
+        spec_files = qpqs.get_spec_files([(iqpq9['RA']*u.degree,iqpq9['DEC']*u.degree) for iqpq9 in qpq9]) 
+    '''
+    spec_files = []
+    for iqpq9 in qpq9:
+        i_spec_files = qpqs.get_spec_files((iqpq9['RA']*u.degree,iqpq9['DEC']*u.degree)) 
+        spec_files.append(i_spec_files)
+        # Missing?
+        if len(i_spec_files) == 0:
[…]

### 2016-10-12 QPQ9/Figures/py/qpq9_figs_marie.py

@@ -1,0 +1,565 @@
+#Module for QPQ9 figures
+# Imports
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, os, sys, copy
+from scipy import stats as scistats
+
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy.table import QTable, Table
+from astropy.io import ascii
+from astropy import units as u
+from astropy import constants as const
+
+from linetools.spectralline import AbsLine
+
+from xastropy.igm.abs_sys import abssys_utils as abssys
+from xastropy import spec as xspec
+from xastropy.plotting import utils as xputils
+from xastropy.xutils import xdebug as xdb
+from xastropy.obs import radec as xor
+from xastropy.atomic import ionization as xai
+
+sys.path.append(os.path.abspath("../../../py"))
+from enigma.qpq import utils as qpqutils
+from enigma.qpq import spec as qpqs
+
+# Local
+sys.path.append(os.path.abspath("../Analysis/py"))
+import qpq9_analy as qpq9a
+
+####
+#  Plot the Experiment
+def experiment(outfil=None, qpq9=None, spec_files=None, spec_dicts=None):
+
+    # Todo
+    #   Have symbol size indicate near-IR for redshift
+
+    # Imports
+    reload(xai)
+
+    if outfil is None:
+        outfil = 'fig_experiment.pdf'
+
+    # Read QPQ9
+    if qpq9 is None:
+        qpq9 = QTable.read('../Analysis/qpq9_final.fits')
+#    if spec_files is None:
+#        spec_files = qpqs.get_spec_files([(iqpq9['RA']*u.degree,iqpq9['DEC']*u.degree) for iqpq9 in qpq9]) 
+    '''
+    spec_files = []
+    for iqpq9 in qpq9:
+        i_spec_files = qpqs.get_spec_files((iqpq9['RA']*u.degree,iqpq9['DEC']*u.degree)) 
+        spec_files.append(i_spec_files)
+        # Missing?
+        if len(i_spec_files) == 0:
[…]

### 2016-10-12 QPQ9/Tables/py/qpq9_tables.py

@@ -1,0 +1,188 @@
+#Module for Tables for QPQ9
+# Imports
+from __future__ import print_function, absolute_import, division, unicode_literals
+
+import numpy as np
+import glob, os, sys, copy
+from scipy import stats as scistats
+
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from astropy.io import ascii, fits
+from astropy import units as u
+from astropy.table import QTable
+
+from xastropy.plotting import utils as xputils
+from xastropy.xutils import xdebug as xdb
+from xastropy.atomic import ionization as xai
+
+# Local
+sys.path.append(os.path.abspath("../Analysis/py"))
+import qpq9_analy as qpq9a
+import qpq_spec as qpqs
+
+# ##################### #####################
+# ##################### #####################
+# Summary table of all transitions measured
+def mktab_summ(outfil='tab_summ.tex', vcut=None, all_tups=None,
+    passback=False, use_oiii=True):
+    '''Summary table
+    Parameters:
+    -----------
+    use_oiii: bool, optional
+      Require [OIII]?  [Default=True]
+    '''
+
+    # Todo
+    #   Include NHI on the label
+    # Imports
+    reload(qpq9a)
+    reload(qpqs)
+
+    # Read
+    qpq9 = QTable.read('../Analysis/qpq9_final.fits')
+    qpq9_adict = qpq9a.qpq9_init()
+
+    #lines = [1548.195]  * u.AA
+    lines = [1215.6701, 1334.5323, 1548.195]  * u.AA
+    # 
+    summ_dicts = []
+    for ii in range(len(lines)):
+        summ_dicts.append(dict(Nqpq=0, Nhigh=0,avgz=0.,avgR=0.))
+    measures = dict(Nqpq=r'$N$', Nhigh=r'$N_{\rm high}$',
+        avgz=r'$<z>$',avgR='\\rphys')
+    formats = dict(Nqpq='{:d}', Nhigh='{:d}', avgz='{:.2f}',
+        avgR='{:.1f}')
+    order = ['Nqpq', 'Nhigh', 'avgz', 'avgR']
+    if all_tups is None:
+        all_tups = []
+
+    # Loop on lines
+    for kk,wrest in enumerate(lines):
+        summ_dict = {}
[…]

### 2016-10-14 QPQ9/Analysis/Stacks/py/qpq9_stacks.py
read new QPQ9 data structure

@@ -36,7 +36,7 @@ sys.path.append(os.path.abspath("../py"))
 import qpq9_analy as qpq9a
 
 ####
-def qpq9_NIR(wrest=None, outfil=None, nboot=10000,
+def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     vmnx = (-3000., 3000.)*u.km/u.s, stack_tup=None,
     passback=False, debug=False): 
     ''' Stack the QPQ9 sample
@@ -58,7 +58,7 @@ def qpq9_NIR(wrest=None, outfil=None, nboot=10000,
     print('length of sample after and before culling',len(qpq9.data),len(qpq9._fulldata))
     
     if outfil is None:
-        outfil = 'Output/QPQ9_zNIR_{:d}.fits'.format(int(wrest.value))
+        outfil = 'Output/QPQ9_IRMgII_{:d}.fits'.format(int(wrest.value))
 
     # Load the stack image
     if stack_tup is None:
@@ -89,7 +89,7 @@ def plt_qpq9(stack_tup=None, wrest=None):
     vmnx = [-3000., 3000] * u.km/u.s
     ymnx = (-0.1, 1.1)
     if stack_tup is None:
-        stack_tup = qpq9_NIR(wrest=wrest, passback=True)
+        stack_tup = qpq9_IRMgII(wrest=wrest, passback=True)
     fin_velo, stck_img, stck_msk, all_dict = stack_tup
 
 
@@ -99,7 +99,7 @@ def plt_qpq9(stack_tup=None, wrest=None):
     nrow = 5
     for ipage in range(pages):
         # Start the plot 
-        outfil = 'plt_qpq9_zNIR_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+        outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
         pp = PdfPages(outfil)
         plt.figure(figsize=(8,5))
         plt.clf()

### 2016-10-14 QPQ9/Analysis/Stacks/py/qpq9_stacks_qpq7.py

@@ -36,7 +36,7 @@ sys.path.append(os.path.abspath("../py"))
 import qpq9_analy as qpq9a
 
 ####
-def qpq7_allz(wrest=None, outfil=None, nboot=10000,
+def qpq7_MgII(wrest=None, outfil=None, nboot=10000,
     vmnx = (-3000., 3000.)*u.km/u.s, stack_tup=None,
     passback=False, debug=False): 
     ''' Stack the QPQ7 sample
@@ -52,14 +52,14 @@ def qpq7_allz(wrest=None, outfil=None, nboot=10000,
     # Load QPQ9
     qpq7 = eqpq.QPQ('QPQ7')
     # Avoid Lya forest
-    qpq7.cull(wrest,4)
+    qpq7.cull(wrest,4,vsig_cut=300*u.km/u.s)
     print('length of sample after and before culling',len(qpq7.data),len(qpq7._fulldata))
     
     # Cut on 300 kpc
     gdR = np.where(qpq7.data['R_PHYS'] < 300)[0]
 
     if outfil is None:
-        outfil = 'Output/QPQ7_allz_{:d}.fits'.format(int(wrest.value))
+        outfil = 'Output/QPQ7_MgII_{:d}.fits'.format(int(wrest.value))
 
     # Load the stack image
     if stack_tup is None:
@@ -90,7 +90,7 @@ def plt_qpq7(stack_tup=None, wrest=None):
     vmnx = [-3000., 3000] * u.km/u.s
     ymnx = (-0.1, 1.1)
     if stack_tup is None:
-        stack_tup = qpq7_allz(wrest=wrest, passback=True)
+        stack_tup = qpq7_MgII(wrest=wrest, passback=True)
     fin_velo, stck_img, stck_msk, all_dict = stack_tup
 
 
@@ -100,7 +100,7 @@ def plt_qpq7(stack_tup=None, wrest=None):
     nrow = 5
     for ipage in range(pages):
         # Start the plot 
-        outfil = 'plt_qpq7_allz_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+        outfil = 'plt_qpq7_MgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
         pp = PdfPages(outfil)
         plt.figure(figsize=(8,5))
         plt.clf()

### 2017-01-03 QPQ9/Analysis/Stacks/py/qpq9_stacks.py
Updated sample Added z_fg cut

@@ -23,7 +23,7 @@ from enigma.qpq import qpq as eqpq
 def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
                 vmnx = (-3000., 3000.)*u.km/u.s,
                 vsig_cut = None,
-                zfg_cut = None,
+                zfg_mnx = (-9999,9999),
                 S2N_cut = None,
                 atmosphere_cut = False,
                 stack_tup=None,passback=False,debug=False):
@@ -38,7 +38,7 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     # Load QPQ9
     qpq9 = eqpq.QPQ('QPQ9')
     # Avoid Lya forest
-    qpq9.cull(wrest,4,vsig_cut=vsig_cut,zfg_cut=zfg_cut)
+    qpq9.cull(wrest,4,vsig_cut=vsig_cut,zfg_mnx=zfg_mnx)
     print('length of sample after and before culling',len(qpq9.data),len(qpq9._fulldata))
     
     if outfil is None:

### 2017-01-04 TPE/Analysis/py/tpe_sample.py
tpe analysis

@@ -118,12 +118,65 @@ def make_sample(min_logLV, outfil=None, tpe_sav=None):
     # Return
     return tpe_tbl
 
+def tpe_chk_spec(tpe_file):
+    """ Check spectrum exists and then look for continuum
+
+    Parameters
+    ----------
+    tpe_file
+
+    Returns
+    -------
+
+    """
+    from astropy import units as u
+
+    # Load spectral datasets
+    igmsp = IgmSpec()
+    qpq_file = os.getenv('DROPBOX_DIR')+'/QSOPairs/spectra/qpq_oir_spec.hdf5'
+    qpq = IgmSpec(db_file=qpq_file, skip_test=True)
+    # Load TPE table
+    tpe = Table.read(tpe_file)
+    b_coords = SkyCoord(ra=tpe['BG_RA'], dec=tpe['BG_DEC'], unit='deg')
+    uni_instr = np.unique(tpe['BG_LYA_INSTRUMENT'])
+
+    # Instrument dict
+    inst_dict = {}
+    for instr in uni_instr:
+        inst_dict[instr] = {}
+        inst_dict[instr]['NO_CO'] = 0
+    inst_dict['LRIS']['GRATING'] = '1200/3400'
+    inst_dict['BOSS']['GROUP'] = 'BOSS_DR12'
+    inst_dict['SDSS']['GROUP'] = 'SDSS_DR7'
+
+    # Scan
+    for instr in uni_instr:
+        # Parse
+        idx = np.where(tpe['BG_LYA_INSTRUMENT'] == instr)[0]
+        inst_dict[instr]['NSPEC'] = len(idx)
+        gd_b_coords = b_coords[idx]
+        # Load
+        if instr in ['BOSS', 'SDSS']:
+            spec, meta = igmsp.coords_to_spectra(gd_b_coords, inst_dict[instr]['GROUP'], all_spec=False)
+        else:
+            continue
+        # Checks
+        for ii,iidx in enumerate(idx):
+            lya = (1+tpe['FG_Z'][iidx]) * 1215.67 * u.AA
+            spec.select = ii
+            iwave = np.argmin(np.abs(spec.wavelength-lya))
+            if np.isclose(spec.co[iwave], 0.) or np.isclose(spec.co[iwave],1.):
+                print("BG source {} at z={} has no continuum at Lya".format(b_coords[iidx],
[…]

### 2017-01-04 TPE/Analysis/py/tpe_stack.py

@@ -22,6 +22,8 @@ from linetools.spectra import utils as lspu
 from specdb.specdb import IgmSpec
 from specdb import cat_utils
 
+from xastropy.xutils import xdebug as xdb
+
 this_file = __file__
 
 
@@ -75,7 +77,7 @@ def tpe_stack_boss(dv=100*u.km/u.s):
 
     # Slice to good co
     print("{:d} BOSS spectra with a continuum".format(np.sum(has_co)))
-    co_spec = spec.slice(has_co)
+    co_spec = spec[has_co]
     co_spec.normed = True  # Apply continuum
 
     # NEED TO ZERO OUT REGIONS WITHOUT CONTINUUM
@@ -90,10 +92,20 @@ def tpe_stack_boss(dv=100*u.km/u.s):
     zarr = gd_tpe['FG_Z'][has_co]
     rebin_spec = lspu.rebin_to_rest(co_spec, zarr, dv)
 
+    # Check 2D
+    check_td = True
+    if check_td:
+        fx = rebin_spec.data['flux']
+        sig = rebin_spec.data['sig']
+        gds = sig > 0.
+        fx[~gds] = 0.
+        xdb.set_trace() # xdb.ximshow(fx)
+
     # Stack
     stack = lspu.smash_spectra(rebin_spec)
     # Plot
     plot_stack(stack, 'BOSS_stack.pdf')
+    print('Wrote')
 
     return stack
 
@@ -143,7 +155,7 @@ def tpe_stack_lris(dv=100*u.km/u.s):
 
     # Find the rows
     idx = cat_utils.match_ids(gd_IDs, meta['PRIV_ID'])
-    rows = meta['GROUP_ID'][idx]  # Will change to GROUP_ID
+    rows = meta['GROUP_ID'][idx]
     pdb.set_trace()
 
     spec,meta = qpq.coords_to_spectra(gd_b_coords, 'LRIS', all_spec=False)
@@ -164,7 +176,7 @@ def tpe_stack_lris(dv=100*u.km/u.s):
 
     # Slice to good co
     print("{:d} BOSS spectra with a continuum".format(np.sum(has_co)))
-    co_spec = spec.slice(has_co)
+    co_spec = spec[has_co]
     co_spec.normed = True  # Apply continuum
 
     # NEED TO ZERO OUT REGIONS WITHOUT CONTINUUM
[…]

### 2017-01-11 TPE/Analysis/py/tpe_sample.py
tpe spectra

@@ -118,6 +118,7 @@ def make_sample(min_logLV, outfil=None, tpe_sav=None):
     # Return
     return tpe_tbl
 
+
 def tpe_chk_spec(tpe_file):
     """ Check spectrum exists and then look for continuum
 
@@ -148,6 +149,17 @@ def tpe_chk_spec(tpe_file):
     inst_dict['LRIS']['GRATING'] = '1200/3400'
     inst_dict['BOSS']['GROUP'] = 'BOSS_DR12'
     inst_dict['SDSS']['GROUP'] = 'SDSS_DR7'
+
+    # Standard process
+    # -- Find all b/g spectra covering Lya (igmspec, QPQ): Generate list (INSTR,GRATING)
+    # -- Order by: UVES/HIRES/MIKE,
+    #              MagE/ESI/XShooter,
+    #              LRIS+B1200,  B600?, B400?
+    #              MODS?/GMOS+B600?
+    #              BOSS/SDSS
+
+    # Query catalogs
+    igm_cat = igmsp.qcat.query_coords(b_coords)
 
     # Scan
     for instr in uni_instr:

### 2017-01-12 QPQ9/qpq9_draft.tex
Updated sample Added z_fg cut
notebooks included binning in g_UV, R_perp, and velocity separations

@@
-\documentclass[12pt,preprint]{aastex}
-\usepackage{natbib,amsmath}
-\special{papersize=8.5in,11in}
+%\documentclass[12pt,preprint]{aastex}
+\documentclass[iop]{emulateapj}
+\usepackage{natbib,amsmath,graphicx,longtable,amssymb,latexsym,epsf}
 \begin{document}
 
-\newcommand\ntot{2x}
-\newcommand\nhigh{1x}
-\newcommand\ncii{X5}
-\newcommand\nciv{x5}
-%\newcommand\vfct{0.71 \pm 0.08} % f_C for CII to 200kpc
-\newcommand\vfct{0.73 \pm 0.10} % f_C for CII to 160kpc
-\newcommand\dndz{2.1 \pm 0.2}
-\newcommand\vro{7.5^{+2.8}_{-1.4} \, \mhMpc}
-\def\mdv{\delta v}
-\def\DV#1{$\Delta v_{90}^{#1}$}
-\def\DRMS#1{$\sigma v_{90}^{#1}$}
-\newcommand\vgmm{1.7^{+0.1}_{-0.2}}
-\def\N#1{{N({\rm #1})}}
-\newcommand\mlstar{L^*}
-\newcommand\lstar{$\mlstar$}
-\def \mmccgm {M_{\rm CGM}^{\rm cool}}
-\def \mccgm {$\mmccgm$}
-\def \mnhalo {n_{\rm halo}}
-\def \nhalo {$\mnhalo$}
-\def \mmminq {M_{\rm min}^{\rm QPQ}}
-\def \mminq {$\mmminq$}
-\def \mncom {n_{\rm com}}
-\def \ncom {$\mncom$}
-\def \mrcom {R^{\rm com}_\perp}
-\def \rcom {$\mrcom$}
-\def \mzem {z_{\rm em}}
-\def \zem {$\mzem$}
-\def \zbg {$z_{\rm bg}$}
-\def \zfg {$z_{\rm fg}$}
-\def \mzfg {z_{\rm fg}}
-\def \mzlya {z_{\rm Ly\alpha}}
-\def \zlya {$\mzlya$}
-\def \mavgz{\langle z \rangle}
-\def \avgz{$\mavgz$}
-\def \wlya {$W_{\rm Ly\alpha}$}
-\def \wsubj {$W_{\rm Ly\alpha}^{\rm line}$}
-\def \mwsubj {W_{\rm Ly\alpha}^{\rm line}}
-\def \mwlya {W_{\rm Ly\alpha}}
-\def \mrphys {R_\perp}
-\def \rphys {$\mrphys$}
-\def \lbol {$L_{\rm Bol}$}
-\def \guv {$g_{\rm UV}$}
-\def \nhi  {$N_{\rm HI}$}
-\def \mnhi  {N_{\rm HI}}
-\def \kms  {\, km~s$^{-1}$}
-\def \mkms  {{\rm km~s^{-1}}}
-\def \lya  {Ly$\alpha$}
-\def \mlya  {{\rm Ly\alpha}}
-\def \lyb  {Ly$\beta$}
-\def \hMpc      {h^{-1}{\rm\ Mpc}}
-\def \msol      {M_\odot}
-\def \msun      {\msol}
-\def\cm#1{\, {\rm cm^{#1}}}
-\def \cgsflux   {{\rm erg\ s^{-1}\ cm^{-2}}}
-\def \cgssflux   {{\rm erg\ s^{-1}\ Hz^{-1} cm^{-2}}}
-\def\sci#1{{\; \times \; 10^{#1}}}
-\def \msnlya {{\rm S/N}_{\rm Ly\alpha}}
-\def \snlya {$\msnlya$}
-\newcommand{\civt}{\ion{C}{4}~1548}
-\newcommand{\ciit}{\ion{C}{2}~1334}
-\newcommand{\mgiit}{\ion{Mg}{2}~2796}
-\newcommand{\nvt}{\ion{N}{5}~1238}
-\newcommand\mwciv{W_{1548}}
-\newcommand\wciv{$\mwciv$}
-\newcommand\mwcii{W_{1334}}
-\newcommand\wcii{$\mwcii$}
-\newcommand\avgcii{$\left < \mwcii \right >$}
-\newcommand\mwmgii{W_{2796}}
-\newcommand\wmgii{$\mwmgii$}
-\newcommand\mavmgs{\left < \mwmgii \right >^{\rm S}}
-\newcommand\avmgs{$\mavmgs$}
-\newcommand\mavmgw{\left < \mwmgii \right >^{\rm w}}
-\newcommand\avmgw{$\mavmgw$}
-\newcommand\mtavmg{\left < \mwmgii \right >}
-\newcommand\tavmg{$\mtavmg$}
-\newcommand\mwnv{W_{1238}}
-\newcommand\wmwnv{$\mwnv$}
-\def \mfc {f_C}
-\def \fc {$\mfc$}
-\def \mfcs {f_C}
-\def \fcs {$\mfcs$}
-\newcommand\mmetal{$M_{\rm metal}^{\rm cool}$}
-\newcommand\mwlim{W^{\rm lim}}
-\newcommand\wlim{$\mwlim$} 
-\newcommand\mxiq{\xi_{\rm Q-Q}}
-\newcommand\xiq{$\mxiq$}
-\newcommand\mxic{\xi_{\rm CIV-Q}}
-\newcommand\xic{$\mxic$}
-\newcommand\mxia{\xi_{\rm CIV-CIV}}
-\newcommand\xia{$\mxia$}
-\newcommand\mxixi{(\bar\mxiq \bar\mxia)^{1/2}} 
-\newcommand\xixi{$\mxixi$}
-\newcommand\mlxmg{\ell(X)_{\rm MgII}}
-\newcommand\lxmg{$\mlxmg$}
-\newcommand\mlxciv{\ell(X)_{\rm CIV}}
-\newcommand\mlciv{\ell(z)_{\rm CIV}}
-\newcommand\lciv{$\mlciv$}
-\def \mhMpc{h^{-1}{\rm\ Mpc}}
-\def \hMpc{$h^{-1}{\rm\ Mpc}$}
-\def \mrvir {r_{\rm vir}}
-\def \rvir {$\mrvir$}
-\def\ltk{\left [ \,}
-\def\ltp{\left ( \,}
-\def\ltb{\left \{ \,}
-\def\rtk{\, \right  ] }
-\def\rtp{\, \right  ) }
-\def\rtb{\, \right \} }
+\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.1]}
 
-\title{Quasars Probing Quasars IX. 
-  Probing the Circumgalactic Flows of Quasars [v1.0]
+\author{Marie Wingyee Lau\altaffilmark{1}, J. Xavier Prochaska\altaffilmark{1}, 
+Joseph F. Hennawi\altaffilmark{2}
 }
-
-\author{
-J. Xavier Prochaska\altaffilmark{1},
-Joseph F. Hennawi\altaffilmark{2}
-Marie Wingyee Lau\altaffilmark{1},
-}
-\altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick
-  Observatory, University of California, 1156 High Street, Santa Cruz,
-  CA 95064}
-\altaffiltext{2}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17,
-  D-69115 Heidelberg, Germany}
+\altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick Observatory, University of 
+California, 1156 High Street, Santa Cruz, CA 95064}
+\altaffiltext{2}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69115 Heidelberg, 
+Germany}
 
@@
 
-\keywords{absorption lines -- intergalactic medium -- Lyman limit
-  systems}
+\keywords{glaxies: clusters: intracluster medium -- galaxies: formation -- galaxies: halos -- 
+intergalactic medium -- quasars: absorption lines -- quasars: general}
 
@@
 the gas mass is either too small or the gas density too low
-for the [detection] of line-emission (e.g. 21cm, \lya,
+for the [detection] of line-emission (e.g. 21cm, lya,
 or H$\alpha$ from Hydrogen).  Resolving the kinematics
@@
 
-In this Letter, we examine the flows of gas in the environments
+In this paper, we examine the flows of gas in the environments
 of massive galaxies hosting quasars.  Our approach leverages
@@
 \citep{QPQ1,QPQ5,QPQ6,QPQ7}.
-We have collected a sample of \ntot~spectra passing within
+We have collected a sample of ntot~spectra passing within
 300\,kpc from a f/g quasar with a precisely measured
@@
 
-Throughout this manuscript, we adopt a $\Lambda$CDM cosmology with
-$\Omega_M = 0.26, \Omega_\Lambda = 0.74$, and $H_0 = 70 {\rm km \,
-  s^{-1} \, Mpc^{-1}}$.  When referring to comoving distances we include 
-explicitly an $h_{70}^{-1}$ term and follow modern convention of scaling
-to a Hubble constant of 70\kms\,Mpc$^{-1}$.  All equivalent width measurements are
-presented in the rest-frame, unless otherwise specified.
+Throughout this manuscript we adopt a $\Lambda$CDM cosmology with $\Omega_M=0.26, \Omega_\Lambda
+=0.74$, and $H_0=70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. All distances are proper unless otherwise 
+stated. 
+%When referring to comoving distances we include explicitly an $h^{-1}$ term and 
+%follow modern convention of scaling to a Hubble constant of $70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. All 
+%equivalent width measurements are presented in the rest-frame, unless otherwise specified.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{The Experiment}
@@
 
-From our QPQ survey\footnote{www.qpqsurvey.org} \citep{QPQ1},
-we have analyzed the \ntot~systes that pass within 300\,kpc
-(physical) from a f/g quasar with $xx < z < xx$.
-We restrict the sample to f/g quasars with redshift measured
-from \ion{Mg}{2}, [\ion{O}{3}], or XX emission giving 
-a precision of $\sigma < 300 \mkms$ \citep{hewittwild}.
+From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed 195~systems 
+that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict the sample 
+to foreground quasars with redshift measured from \ion{Mg}{2}, [\ion{O}{3}], H$\alpha$, or 
+H$\beta$ emission, giving a precision of $400\,{\rm km\,s^{-1}}$ or lower. [\ion{O}{3}] has the 
+smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the 
+sub-sample with [\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift 
+of $27\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
+redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
+$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
+$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 we have 
+quantified the precision of H$\alpha$ and H$\beta$ to be 
+$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. 
+\citep{hewittwild}.
 We include only those spectra with S/N~$> XX$\AA\ at the
-observed wavelengths of \lya, \ion{C}{2}~1334, or 
-\ion{C}{4}~1548 transitions.  Of the \ntot~sightlines, 
-\nhigh\ have spectral resolution ~$> 5,000$ from echellette
+observed wavelengths of lya, \ion{C}{2}~1334, or 
+\ion{C}{4}~1548 transitions.  Of the ntot~sightlines, 
+nhigh\ have spectral resolution ~$> 5,000$ from echellette
 or echelle observations (QPQ8).  This high-dispersion 
@@
 frequently exhibits large flows:
-median \DV{1334},\DV{1548} = $XX,XX \mkms$ with and
-RMS \DRMS{1334},\DRMS{1548} = $XX, XX \mkms$ from
-a sample of \ncii\ and \nciv\ systems.
+median DV{1334},DV{1548} = $XX,XX kms$ with and
+RMS DRMS{1334},DRMS{1548} = $XX, XX kms$ from
+a sample of ncii\ and nciv\ systems.
 These velocity fields exceed all previous measurements from
@@
 Figure~\ref{fig:stack}, we present these absorption lines
-and \ion{H}{1}~\lya, also including lower-dispersion 
+and \ion{H}{1}~lya, also including lower-dispersion 
 sightlines meeting the selection criteria.
@@
 We have fitted the combined dataset using a cubic b-spline
-with knots at every 100\,\kms.  We weighted each data
+with knots at every 100\,kms.  We weighted each data
 point by the velocity width of the pixel to insure that 
@@
  (i) the data exhibit excess absorptoin at 
- $\mdv \approx 0 \mkms$;
+ $mdv \approx 0 kms$;
  (ii) the absorption is skewed towards positive velocities
- $\mdv > 0 \mkms$.
+ $mdv > 0 mkms$.
 We measure absorption-weigthed ($1-f$) centroids
-of $\mdv = XX-XX \mkms$ for these transitions
+of $mdv = XX-XX mkms$ for these transitions
 (Table~\ref{tab:summ}).
@@
 scrutinize the statistical significance of the measured offset.
-Indeed, a small offset $\mdv < 10 \mkms$ may be expected
+Indeed, a small offset $mdv < 10 kms$ may be expected
 even with large samples.  To assess the statistical significance,
@@
 %mountain.
+%Acknowledge TK Chan. CP Choi.
 
@@
 \input{Tables/tab_summ.tex}
-\input{Tables/tab_summ_Hab.tex}
+%\input{Tables/tab_summ_Hab.tex}
 %\input{tab1_sub.tex}
@@
 \begin{figure}
-\includegraphics[width=5in]{Figures/fig_simple_stack.pdf}
+%\includegraphics[width=5in]{Figures/fig_simple_stack.pdf}
 %\includegraphics[width=5in,angle=90]{f2.eps}

### 2017-01-12 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py

@@ -87,7 +87,7 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
 
         # Centroid of pseudo-optical depth within +/- 2000 km/s
         tau = np.log(1./cfx)
-        start = np.int((sz[1]-1)*1./6.)
+        start = np.int((sz[1]-1)*1./6.)-1
         end = np.int((sz[1]-1)*5./6.)+1
         tau_cen[qq] = np.sum(fin_velo[start:end]*tau[start:end])/np.sum(tau[start:end])
 

### 2017-01-12 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -38,9 +38,12 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     # Load QPQ9
     qpq9 = eqpq.QPQ('QPQ9')
     # Avoid Lya forest
-    qpq9.cull(wrest,4,vsig_cut=vsig_cut,zfg_mnx=zfg_mnx)
-    print('length of sample after and before culling',len(qpq9.data),len(qpq9._fulldata))
-    
+    qpq9.cull(wrest,4,vsig_cut=vsig_cut)
+    # Cut on redshift
+    zfg = qpq9._fulldata['Z_FG']
+    bad = np.where((zfg < zfg_mnx[0]) | (zfg > zfg_mnx[1]))[0]
+    qpq9.mask[bad] = False
+
     if outfil is None:
         outfil = 'Output/QPQ9_IRMgII_{:d}.fits'.format(int(wrest.value))
 
@@ -65,7 +68,7 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     return stack_tup
 
 #######
-def plt_qpq9(stack_tup=None, wrest=None):
+def plt_qpq9(stack_tup=None, wrest=None, outfil=None):
 
     # Rest wavelength
     if wrest is None:
@@ -83,8 +86,9 @@ def plt_qpq9(stack_tup=None, wrest=None):
     ncol = 3 
     nrow = 5
     for ipage in range(pages):
-        # Start the plot 
-        outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+        # Start the plot
+        if outfil is None:
+            outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
         pp = PdfPages(outfil)
         plt.figure(figsize=(8,5))
         plt.clf()

### 2017-01-12 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py
small changes

@@ -75,8 +75,8 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
         boot_img[qq,:] = fx
 
         # Continuum "fit"
-        pix = np.where( (velo > cranges[0][0]) & (velo<cranges[0][1]) |
-            (velo > cranges[1][0]) & (velo<cranges[1][1]))[0]
+        pix = np.where(((velo >= cranges[0][0]) & (velo <= cranges[0][1])) |
+                       ((velo >= cranges[1][0]) & (velo <= cranges[1][1])))[0]
         fit = np.polyfit(velo[pix].value, fx[pix], 0)
         pv = np.poly1d(fit)
         conti = pv(velo.value)

### 2017-02-09 QPQ9/qpq9_draft.tex
small changes

@@
 
-From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed 195~systems 
-that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict the sample 
-to foreground quasars with redshift measured from \ion{Mg}{2}, [\ion{O}{3}], H$\alpha$, or 
-H$\beta$ emission, giving a precision of $400\,{\rm km\,s^{-1}}$ or lower. [\ion{O}{3}] has the 
-smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the 
-sub-sample with [\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift 
-of $27\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
+Our primary scientific interest is to measure the average velocity fields of the C$^+$, C$^{3+}$, 
+and Mg$^+$ absorption associated with the CGM of the massive galaxies hosting $z\sim 2.4$ quasars.
+
+From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed a subset of 195 
+systems that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict
+ the sample to foreground quasars with redshift measured from \ion{Mg}{2}\,2800, 
+[\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
+$400\,{\rm km\,s^{-1}}$ or lower. 
+%#[\ion{O}{3}] has the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, 
+%and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
+The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
+redshift \citep{Boroson05}, which has been added when we compute the 
 redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
 $272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
-$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 we have 
+$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8. we have 
 quantified the precision of H$\alpha$ and H$\beta$ to be 
 $300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. 
-\citep{hewittwild}.
-We include only those spectra with S/N~$> XX$\AA\ at the
-observed wavelengths of lya, \ion{C}{2}~1334, or 
-\ion{C}{4}~1548 transitions.  Of the ntot~sightlines, 
-nhigh\ have spectral resolution ~$> 5,000$ from echellette
-or echelle observations (QPQ8).  This high-dispersion 
-sample is analyzed [separately] throughout the paper.
-Figure~\ref{fig:exp} summarizes the experimental design.
-Refer to previous QPQ
-publications for details on data reduction
-and continuum normalzaton (QPQ6, QPQ7, QPQ8).
+%\citep{HewittWild10}. 
+Of the 195 sightlines, 13 have spectral resolution $> 5000$ from echellette or echelle 
+observations. This high-dispersion sample has been analyzed separately in QPQ8. 
+Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
+QPQ publications for the redshift centroiding algorithm, and details on data reduction and 
+continuum normalization (QPQ6, QPQ8).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+As in the previous QPQ papers, we make a cut on velocity difference between the redshifts of the 
+two quasars in a pair of $>3000\,{\rm km\,s^{-1}}$ to avoid physically associated binary quasars. 
+The cut on velocity difference is motivated by the typical redshift uncertainty of 
+$\approx500\,{\rm km\,s^{-1}}$. In QPQ8, it was required that the observed wavelengths of the 
+metal ion transitions fall outside the Ly$\alpha$ forest of the background quasar. In this paper, 
+we make a more aggressive Ly$\alpha$ forest cut. For stacked profile analysis, a good estimate of 
+the continuum level is neessary. In QPQ8 we found that absorption associated to 
+the foreground quasar occurs within $\pm2000\,{\rm km\,s^{-1}}$ around $z_{\rm fg}$. Therefore, it 
+is desirable to keep a $\approx\pm3000\,{\rm km\,s^{-1}}$ window relatively free of contamination 
+from Ly$\alpha$ forest. Taking into account the redshift uncertainty of the background quasar, 
+we decide that at least one transition among \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
+\ion{Mg}{2}\,2796) at $z_{\rm fg}$ should lie redward of 
+$(1215.6701+20)\times(1+z_{\rm bg})\,{\rm \AA}$, for a pair to be included in the analysis.
+
+Furthermore, we include only those spectra with average signal-to-noise (S/N) ratio exceeding 5.5 
+per rest-frame \AA \ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths 
+of the metal ion transitions. This criterion is a compromise between maximizing sample size versus 
+maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame 
+\AA \ is 
+necessary for properly estimating the continuum, as well as identifying mini-broad absorption line 
+systems associated to the background quasar, which will significantly depress the flux level and 
+bias the results. We also require that the $\pm2000\,{\rm km\,s^{-1}}$ window centered on the 
+observed wavelengths of the metal ion transitions, where absorption associated to the foreground 
+quasar is found, does not overlap with strong atmospheric ${\rm O}_2$ bands. The ${\rm O}_2$ 
+A-band and B-band span 7595\textrm{--}7680\,AA \ and 6868\textrm{--}6926\,AA \ respectively.
+
+In Table~\ref{tab:summ}, we list the sample size, the median redshift, and the median projected 
+separation between the pair of the sub-samples that survive the above selection criteria for 
+\ion{C}{2}\,1334, \ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively.
+
+We then create composite spectra, that average over the intrinsic scatter in quasar environments, 
+continuum placement errors, and redshift errors. The individual spectra 
+of background quasars are shifted to the rest-frame of the foreground quasar at the transitions of 
+interest. Each spectrum has been linearly 
+interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
+$100\,{\rm km\,s^{-1}}$. For velocity bin of this size, it is unncessary to smooth the data to a 
+common spectral resolution. The individual spectra are then combined with mean 
+or median in a $\pm3000\,{\rm km\,s^{-1}}$ velocity window around $z_{\rm fg}$, where a velocity 
+of $0\,{\rm km\,s^{-1}}$ corresponds to the wavelength of the metal ion transition at 
+$z_{\rm fg}$. Bad pixels in the individual spectra have been masked before generating the 
+composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
+weighting in the stacked profiles. We do not weight the spectra by the measured S/N value of the 
+metal ion transitions at $z_{\rm fg}$, since scatter in the stacked spectra is dominated by 
+randomness in the CGM instead of error sources. The mean statistic of the individual spectra 
+yields a good estimate of the average absorption and preserves equivalent width. On the other 
+hand, a median statistic is less sensitive to outliers, however the averaged equivalent width is 
+smaller and a measurement of the veloity width becomes more uncertain. We have stacked spectra 
+using both the mean and the median statistic.
+
 \section{Analysis}
@@
 
-JXP and ML acknowledge support from the National
+JXP and MWL acknowledge support from the National
 Science Foundation (NSF) grant AST-1010004 and AST-XX. 
@@
 %mountain.
-%Acknowledge TK Chan. CP Choi.
+%MWL thanks T.-K. Chan for a discussion on CGM simulations. MWL 
+%thanks Chi Po Choi for a discussion on statistics.
 

### 2017-02-09 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py

@@ -89,7 +89,7 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
         tau = np.log(1./cfx)
         start = np.int((sz[1]-1)*1./6.)-1
         end = np.int((sz[1]-1)*5./6.)+1
-        tau_cen[qq] = np.sum(fin_velo[start:end]*tau[start:end])/np.sum(tau[start:end])
+        tau_cen[qq] = np.sum(fin_velo[start:end+1]*tau[start:end+1])/np.sum(tau[start:end+1])
 
         # Pseudo-EW
         EWpix = np.where( (velo > EW_range[0]) & (velo<EW_range[1]))[0]

### 2017-02-09 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -25,7 +25,8 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
                 vsig_cut = None,
                 zfg_mnx = (-9999,9999),
                 S2N_cut = None,
-                atmosphere_cut = False,
+                atmosphere_cut = True,
+                stack_fg = False,
                 stack_tup=None,passback=False,debug=False):
     ''' Stack the QPQ9 sample
     To do: add MgII redshifts to the QPQ9 structure
@@ -50,7 +51,8 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     # Load the stack image
     if stack_tup is None:
         stack_tup = qpqk.load_stack_img(qpq9.data,wrest,vmnx=vmnx,spec_dv=100.*u.km/u.s,high_res=0,
-                                        S2N_cut=S2N_cut)
+                                        S2N_cut=S2N_cut,atmosphere_cut=atmosphere_cut,
+                                        stack_fg=stack_fg)
         if passback:
             return stack_tup
 

### 2017-02-10 QPQ9/Analysis/Stacks/py/qpq9_stacks.py
Monte carlo, new continua, g_UV new calculations, stack foreground spectra

@@ -70,7 +70,9 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     return stack_tup
 
 #######
-def plt_qpq9(stack_tup=None, wrest=None, outfil=None):
+def plt_qpq9(stack_tup=None,wrest=None,outfil=None,
+             S2N_cut=None,atmosphere_cut=True,
+             stack_fg=False,zfg_mnx=(-9999,9999)):
 
     # Rest wavelength
     if wrest is None:
@@ -79,7 +81,10 @@ def plt_qpq9(stack_tup=None, wrest=None, outfil=None):
     vmnx = [-3000., 3000] * u.km/u.s
     ymnx = (-0.1, 1.1)
     if stack_tup is None:
-        stack_tup = qpq9_IRMgII(wrest=wrest, passback=True)
+        stack_tup = qpq9_IRMgII(wrest=wrest,S2N_cut=S2N_cut,
+                                atmosphere_cut=atmosphere_cut,
+                                stack_fg=stack_fg,zfg_mnx=zfg_mnx,
+                                passback=True)
     fin_velo, stck_img, stck_msk, all_dict = stack_tup
 
 
@@ -90,7 +95,10 @@ def plt_qpq9(stack_tup=None, wrest=None, outfil=None):
     for ipage in range(pages):
         # Start the plot
         if outfil is None:
-            outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+            if stack_fg == True:
+                outfil = 'plt_qpq9_IRMgII_{:d}_fg_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+            else:
+                outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
         pp = PdfPages(outfil)
         plt.figure(figsize=(8,5))
         plt.clf()

### 2017-02-19 QPQ9/qpq9_draft.tex
Generate stack figures, wrote draft

@@
 
-From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed a subset of 195 
+From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed a subset of  
 systems that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict
@@
 $400\,{\rm km\,s^{-1}}$ or lower. 
-%#[\ion{O}{3}] has the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, 
-%and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
+[\ion{O}{3}] emission-line redshifts have the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about 
+the systemic redshift, and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
 The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
@@
 quantified the precision of H$\alpha$ and H$\beta$ to be 
-$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. 
-%\citep{HewittWild10}. 
-Of the 195 sightlines, 13 have spectral resolution $> 5000$ from echellette or echelle 
-observations. This high-dispersion sample has been analyzed separately in QPQ8. 
+$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. We further supplement the 
+dataset with quasar pairs selected from the igmspec 
+database\footnote{https://github.com/specdb/igmspec}, which comes with the package of software for
+accessing spectra of sources useful for probing the intergalactic medium \citep{Prochaska17}. 
+We reach a total of 195 sightlines in the final sample. Among them, 13 have spectral resolution 
+$> 5000$ from echellette or echelle observations and have been analyzed separately in QPQ8. 
 Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
@@
 
-In Table~\ref{tab:summ}, we list the sample size, the median redshift, and the median projected 
-separation between the pair of the sub-samples that survive the above selection criteria for 
-\ion{C}{2}\,1334, \ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively.
+In Table~\ref{tab:summary}, we list the sample size, the median redshift, and the median projected 
+separation of the quasar pairs that survive the above selection criteria for \ion{C}{2}\,1334, 
+\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively. In Table~\ref{tab:summary_OIII}, we provide 
+the summary for the sub-sample with $z_{\rm fg}$ measured from [\ion{O}{3}].
 
@@
 
-In QPQ8, we measured the velocity widths of the \ion{C}{2}~1334
-and \ion{C}{4}~1548 transitions finding that the CGM
-frequently exhibits large flows:
-median DV{1334},DV{1548} = $XX,XX kms$ with and
-RMS DRMS{1334},DRMS{1548} = $XX, XX kms$ from
-a sample of ncii\ and nciv\ systems.
-These velocity fields exceed all previous measurements from
-galaxies and/or absorption systems at any epoch.  For
-Figure~\ref{fig:stack}, we present these absorption lines
-and \ion{H}{1}~lya, also including lower-dispersion 
-sightlines meeting the selection criteria.
+In QPQ8, we measured the velocity widths of the \ion{C}{2}\,1334 and \ion{C}{4}\,1548 transitions, 
+finding that the CGM frequently exhibits large flows. From a sample of 7 \ion{C}{2} systems and 10 
+\ion{C}{4} systems, we measured the velocity interval that encompasses 90\% of the total optical 
+depth, $\Delta v_90$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$. 
+The median $\Delta v_90$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is 
+$342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for 
+\ion{C}{2}\,1334 and is $495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed 
+all previous measurements fromgalaxies and/or absorption systems at any epoch.  
+In Figure~\ref{fig:stack_CII}, Figure~\ref{fig:stack_CIV}, and Figure~\ref{fig:stack_MgII}, we 
+present mean and median stacks of \ion{C}{2}\,1334, \ion{C}{4}\,1548, and \ion{Mg}{2}2796 
+absorption, including lower-dispersion sightlines meeting the selection criteria. For interpreting 
+the kinematics, we will focus on the analysis results of the \ion{C}{2} mean stack. The median 
+stacks have lower absorption equivalent widths, while \ion{C}{4} and \ion{Mg}{2} are doublet 
+transitions and hence interpret their kinematics becomes more challenging.
 
-To assess the `average' absorption of these transitions,
-we have combined the data with a novel technique.
-We have fitted the combined dataset using a cubic b-spline
-with knots at every 100\,kms.  We weighted each data
-point by the velocity width of the pixel to insure that 
-each sightline makes an equal contribution to the stack.
-These b-spline profiles are presented in the figure
-and a trivial integration gives the reported equivalent
-widths.
-[consider down-weighting systems with $<3\sigma$ EW]
-[Comnent on EW from 'standard' technique]
+%To assess the average absorption of these transitions,
+%we have combined the data with a novel technique.
+%We have fitted the combined dataset using a cubic b-spline
+%with knots at every 100\,kms.  We weighted each data
+%point by the velocity width of the pixel to insure that 
+%each sightline makes an equal contribution to the stack.
+%These b-spline profiles are presented in the figure
+%and a trivial integration gives the reported equivalent
+%widths.
+%[consider down-weighting systems with $<3\sigma$ EW]
+%[Comnent on EW from 'standard' technique]
 
-Two results are evident from the figure:
- (i) the data exhibit excess absorptoin at 
- $mdv \approx 0 kms$;
- (ii) the absorption is skewed towards positive velocities
- $mdv > 0 mkms$.
-We measure absorption-weigthed ($1-f$) centroids
-of $mdv = XX-XX mkms$ for these transitions
-(Table~\ref{tab:summ}).
-This suggests an asymmetry that contradicts the [standard]
-expectation.
+Two results are evident from Figure~\ref{fig:stack_II}: (i) the mean stack exhibits excess 
+absorption spanning a large velocity width; (ii) the mean absorption is skewed toward positive 
+velocities. Our sign convention is that positive velocities are flowing away. To model the 
+absorption, we introduce a Gaussian profile while allowing the constant continuum level to vary. 
+From the $\chi^2$ best-fit to the data, we measure the centroid to be $+170\,{\rm km\,s^{-1}}$ and 
+the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
+contradicts the standard expectation, while the dispersion is larger than  The median stack, on 
+the other hand, shows weaker absorption, and the Gaussian model has a centroid closer to zero.
 
-Given the small sample size, one must 
-scrutinize the statistical significance of the measured offset.
-Indeed, a small offset $mdv < 10 kms$ may be expected
-even with large samples.  To assess the statistical significance,
-we have perfomed a boostrap analysis by randomly resampling
-from the full sample. [DISCUSS]
+We also create mean and median 
+stack for the sub-sample with [\ion{O}{3}] redshifts and model the absorption with Gaussian 
+best-fit. The mean stack for this sub-sample has a centroid at $+207\,{\rm km\,s^{-1}}$, and a 
+dispersion of $355\,{\rm km\,s^{-1}}$. The median stack of this sub-sample has a centroid at 
+$60\,{\rm km\,s^{-1}}$ and a dispersion of $307\,{\rm km\,s^{-1}}$. These values are consistent 
+with the stacks of full sample.
 
-[Discuss systematics here??]
+To model the mean and median stacks of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce two 
+Gaussians with separation equal to the doublet separation of $498\,{\rm km\,s^{-1}}$ and 
+$769\,{\rm km\,s^{-1}}$ respectively, and tie the dispersion of the two lines in a doublet. The 
+modeling results show that the \ion{C}{4} and \ion{Mg}{2} absorption are consistent with 
+\ion{C}{2}, that the velocity field is large and skewed toward positive velocities.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The above analysis are summarized in Table~\ref{tab:summary} and 
+Table~\ref{tab:summary_OIII}. The Gaussian and continuum models are overplotted on the data stacks 
+in Figure~\ref{fig:stack_CII}, Figure~\ref{fig:stack_CIV}, and Figure~\ref{fig:stack_MgII}.
+
+\subsection{Significance of the asymmetry}
+\label{sec:sigificance_+ve}
+
+Given the small sample size, one must scrutinize the statistical significance of the measured 
+offsets from $0\,{\rm km\,s^{-1}}$. To assess the statistical significance, we perform a boostrap 
+analysis by randomly sampling from the full sample 10000 times. We measure the pixel optical 
+depth-weighted centroid of each bootstrap realization, and 
+quote the standard deviation in the bootstrap realizations to be the uncertainty of the 
+centroid of the data. The uncertainties are comparable 
+to the measured offsets, indicating large intrinsic variation in quasar CGM environments.
+
+One may also ask whether the measured positive offsets come from systematic biases in redshift 
+measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, 
+the [\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
+less luminous low-$z$ quasars. To test for this potential source of systematic bias, we consider 
+the mean stack at \ion{C}{2}\,1334. We replace the [\ion{O}{3}] redshifts by a \ion{Mg}{2}, 
+H$\alpha$, or H$\beta$ redshift, when available, and create a mean stack for new 
+sample. We have a redshift replacement for 13 out of the 14 systems with [\ion{O}{3}] redshifts in 
+the original sample. The new stack is similiar in velocity structure and shows a similar positive 
+offset. We thus conclude that our algorithm for measuring emission-line redshift is not biased by 
+the blue wing of the [\ion{O}{3}] emission-line.
+
+We also generate a stack spectrum for \ion{Mg}{2} for lower redshift quasar pairs, using the same 
+selection criteria as the main QPQ9 sample. The quasar pairs are selected from the igmspec 
+data base. The 
+are 231 quasar pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $\R_\perp$ of 
+208\,kpc. We present the mean and median stack in Figure~\ref{fig:stack_MgII_z1}. The absorption 
+is weaker than the $z\approx2$ QPQ9 main sample. Gaussian absorption models of the \ion{Mg}[2} 
+doublet fitted to the mean stack recovers a centroid of $47\pm338\,{\rm km\,s^{-1}}$ and a 
+dispersion of $119\,{\rm km\,s^{-1}}$, while the fit to the median stack recovers a centroid of 
+$14\pm500\,{\rm km\,s^{-1}}$ and a dispersion of $211\,{\rm km\,s^{-1}}$. The offsets 
+from $0\,{\rm km\,s^{-1}}$ are smaller than the offsets in the $z\approx2$ sample.
+
+To conclude, the large uncertainties in the velocity centroids represent intrinsic variation not 
+redshift errors. Together with the possible difference in $z\approx1$ and $\zapprox2$ quasar 
+CGM environments revealed in the stacks for \ion{Mg}{2}, the hint of asymmetry warrants an attempt 
+for explanation.
+
+%Indeed, a small offset $mdv < 10 kms$ may be expected even with large samples.
+
+\subsection{Significance of the high-velocity flows}
+\label{sec:significance_width}
+
+The dispersion in the \ion{C}{2} mean stack is a result of the intrinsic velocity width of the 
+absorption combined with the error in redshift measurements. Using the relation 
+$\sigma_v^2 = \sigma_{\rm intrinsic}^2 + \sigma_{error}^2$, we solve for the intrinsic dispersion 
+in the stack of the full sample and that in the stack of the sub-sample with $z_{\rm fg}$ measured 
+from [\ion{O}{3}]. We recover $\sigma_{\rm intrinsic}^{\rm full}=317\,{\rm km\,s^{-1}}$ and 
+$\sigma_{\rm intrinsic}^{\rm [OIII]}=352\,{\rm km\,s^{-1}}$. In QPQ8, we reported the 
+line-of-sight velocity dispersion typical of QPQ dark matter halo mass is 
+$\sigma_{\rm 1D}=212\,{\rm km\,s^{-1}}$. We investigate whether gravitational motions and Hubble 
+flows are sufficient to reproduce the dispersion in the \ion{C}{2} mean stack using Monte Carlo 
+methods.
+
+We assume all \ion{C}{2} 
+systems arise in optically thick absorbers, and adopt the clustering analysis results of QPQ6. For 
+each quasar pair, we calculate the expected number of optically thick absorbers within 
+$\pm3000\,{\rm km\,s^{-1}}$ at a distance $R_\perp$ from the foreground quasar and at 
+$z_{\rm fg}$. Then we generate 1000 mock spectra. The number of absorbers for each mock sightline 
+is randomly selected from a Poisson distribution with mean equals the average number of absorbers. 
+The absorbers are randomly assigned Hubble velocities with probabilities according to the 
+quasar-absorber correlation functions. The absorbers are randomly assigned additional peculiar 
+velocities drawn from a normal distribution with mean equals $0\,{\rm km\,s^{-1}}$ and standard 
+deviation equals $\sigma_{\rm 1D}$ of the typical dark matter halo mass. For each absorber, we 
+assume a rest equivalent width for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
+above procedure for all 34 quasar pairs, and create a mean stack of the 34000 mock spectra 
+generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
+the stack of mock spectra. We adjust the rest equivalent width adopted for the \ion{C}{2} 
+absorbers until the ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
+amplitude of the stack of the observational data. We find that an equivalent width of 0.6\,\AA \ 
+well reproduces the amptlitude, and we note that the dispersion in the Gaussian is insensitive to 
+the equivalent width or absorption profile for one absorber. The resulting stack of mock spectra 
+has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, which is less than the 
+intrinsic dispersion in the data. In order to recover an intrinsic dispersion of 
+$317\text{--}352\,{\rm km\,s^{-1}}$, a peculiar velocity of $\approx280\,{\rm km\,s^{-1}}$ is 
+required. We thus conclude the observed velocity width likely requires outflows.
+
 \section{Discussion}
@@
 
-%%%%%%%%%%%%%%%%
 \acknowledgements
@@
 
-\bibliographystyle{/u/xavier/paper/Bibli/apj}
-\bibliography{/u/xavier/paper/Bibli/allrefs}
+\bibliographystyle{/lwymarie/Documents/Bibli/apj}
+\bibliography{/lwymarie/Documents/Bibli/allrefs}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{../Tables/tab_sub_qpq7_spectra.tex}
 \input{Tables/tab_summ.tex}
-%\input{Tables/tab_summ_Hab.tex}
-%\input{tab1_sub.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{Tables/tab_summ_OIII.tex}
 
@@
 \begin{figure}
-\includegraphics[width=5in]{Figures/fig_experiment.pdf}
+\includegraphics[width=3.5in]{Figures/fig_experiment.pdf}
 %\includegraphics[width=5in,angle=90]{../Figuref1.eps}
-\caption{Experimental design
+\caption{These panels summarize properties of the QPQ9 dataset. The QPQ survey selects 
+quasar pairs of projected separation $R_\perp < 300$\,kpc and $z_{\rm fg}>1.6$. Assuming that the 
+foreground quasars emit isotropically and at a distance equal to the impact parameter, we estimate 
+enhancement in the UV flux relative to the extragalactic UV background $g_{\rm UV}$. Smaller 
+symbols correspond to foreground quasars with the most precise redshift measurement from 
+[\ion{O}{3}]\,5007 emission, while larger symbols correspond to foreground quasars with redshift 
+measurement from \ion{Mg}{2}\,2796, H$\alpha$, or H$\beta$ emission. The top panel shows 
+quasar pairs with coverage of \ion{C}{2}\,1334 at $z_{\rm fg}$ in the background quasar spectra. 
+The middle panel shows pairs with coverage of \ion{C}{4}\,1548. The bottom panel shows 
+pairs with coverage of \ion{Mg}{2}\,2796. 
 }
-\label{fig:exp}
+\label{fig:experiment}
 \end{figure}

### 2017-02-19 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py

@@ -86,10 +86,17 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
         cfx = fx/conti
 
         # Centroid of pseudo-optical depth within +/- 2000 km/s
-        tau = np.log(1./cfx)
-        start = np.int((sz[1]-1)*1./6.)-1
-        end = np.int((sz[1]-1)*5./6.)+1
+        start = np.int((sz[1]-1)*1./6.)
+        end = np.int((sz[1]-1)*5./6.)
+        # Centroid of pseudo-optical depth outside of continuum ranges
+#        pix = np.where((velo >= cranges[0][1]) & (velo <= cranges[1][0]))[0]
+#        start = pix[0]
+#        end = pix[-1]
+#        tau = np.log(1./cfx)
+#        tau[np.where(tau < 0.)] = 0 # floor for weights should be zero
+        tau = np.log(1./fx) # don't divide by continuum. do not want negative weights
         tau_cen[qq] = np.sum(fin_velo[start:end+1]*tau[start:end+1])/np.sum(tau[start:end+1])
+
 
         # Pseudo-EW
         EWpix = np.where( (velo > EW_range[0]) & (velo<EW_range[1]))[0]
@@ -115,9 +122,8 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
     print('Equivalent width skewness: Mean={:g}, Median={:g}, std={:g} for Ntrials={:d}'
           .format(mu_frac,med_frac,std_frac,nboot))
     mu_taucen = np.mean(tau_cen)
-    med_taucen = np.median(tau_cen)
     std_taucen = np.std(tau_cen)
-    print('Tau-weighted centroid: Mean = {:g}, std={:g}'.format(mu_taucen,med_taucen,std_taucen))
+    print('Tau-weighted centroid: Mean = {:g}, std={:g}'.format(mu_taucen,std_taucen))
 
     # Write
     prihdu = fits.PrimaryHDU()

### 2017-02-19 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -27,6 +27,7 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
                 S2N_cut = None,
                 atmosphere_cut = True,
                 stack_fg = False,
+                plot_indiv = True,
                 stack_tup=None,passback=False,debug=False):
     ''' Stack the QPQ9 sample
     To do: add MgII redshifts to the QPQ9 structure
@@ -52,7 +53,7 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     if stack_tup is None:
         stack_tup = qpqk.load_stack_img(qpq9.data,wrest,vmnx=vmnx,spec_dv=100.*u.km/u.s,high_res=0,
                                         S2N_cut=S2N_cut,atmosphere_cut=atmosphere_cut,
-                                        stack_fg=stack_fg)
+                                        stack_fg=stack_fg,plot_indiv=plot_indiv)
         if passback:
             return stack_tup
 
@@ -72,7 +73,7 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
 #######
 def plt_qpq9(stack_tup=None,wrest=None,
              S2N_cut=None,atmosphere_cut=True,
-             stack_fg=False,zfg_mnx=(-9999,9999)):
+             stack_fg=False,zfg_mnx=(-9999,9999),plot_indiv=False):
 
     # Rest wavelength
     if wrest is None:
@@ -84,6 +85,7 @@ def plt_qpq9(stack_tup=None,wrest=None,
         stack_tup = qpq9_IRMgII(wrest=wrest,S2N_cut=S2N_cut,
                                 atmosphere_cut=atmosphere_cut,
                                 stack_fg=stack_fg,zfg_mnx=zfg_mnx,
+                                plot_indiv=plot_indiv,
                                 passback=True)
     fin_velo, stck_img, stck_msk, all_dict = stack_tup
 

### 2017-02-19 QPQ9/Figures/py/qpq9_figs.py

@@ -2,9 +2,7 @@
 # Imports
 from __future__ import print_function, absolute_import, division, unicode_literals
 
-import copy
-import os
-import sys
+import copy,os,sys,imp
 
 import matplotlib as mpl
 import numpy as np
@@ -12,10 +10,12 @@ mpl.rcParams['font.family'] = 'stixgeneral'
 from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib import pyplot as plt
 import matplotlib.gridspec as gridspec
-from matplotlib.ticker import MaxNLocator
 
 from astropy.table import QTable, Table
+from astropy.io import ascii,fits
 from astropy import units as u
+from astropy.utils.misc import isiterable
+from astropy.modeling import models
 
 from linetools.spectralline import AbsLine
 
@@ -26,474 +26,260 @@ sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
 import qpq9_stacks as qpq9k
 
 #  Plot the Experiment
-def experiment(outfil=None,wrest=1334.5323*u.AA,S2N_cut=5.5/u.AA,zfg_mnx=(1.6,9999)):
-
-    # Get line info
-    aline = AbsLine(wrest)
+def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2N_cut=5.5/u.AA,
+               zfg_mnx=(1.6,9999)):
 
     if outfil is None:
-        outfil = 'fig_experiment_'+xai.ion_name(aline.data)+'.pdf'
+        outfil = 'fig_experiment.pdf'
+    fontsize = 20
 
-    fontsize = 40
+    # fixes
+    if not isiterable(wrest):
+        wrest = [wrest]
 
-    # Load stack_tup
-    stack_tup0 = qpq9k.qpq9_IRMgII(passback=True,wrest=wrest,S2N_cut=S2N_cut,zfg_mnx=zfg_mnx)
-    # Mask
-    fin_velo, stck_img, stck_msk, all_dict = stack_tup0
-    stck_mskN = copy.deepcopy(stck_msk)
-    idx_mask = []
-    for ii,idict in enumerate(all_dict):
-        if idict is None:
-            continue
-        if 'J1508+3635' in idict['qpq']['NAME']: #DLA not excluded by forest cut, should be excluded now
-            idx_mask.append(ii)
-    for idx in idx_mask:
-        stck_mskN[idx,:] = 0.
[…]

### 2017-02-23 TPE/Analysis/py/tpe_sample.py
jxp

@@ -85,7 +85,8 @@ def run_wide_query(outfil, R_MAX=15.*u.Mpc):
     thdulist.writeto(outfil, overwrite=True)
 
 
-def make_tpe(min_logLV, R, qso_fg=None, qso_bg=None, outfil=None, qpqquery_file=None):
+def make_tpe(min_logLV, R, qso_fg=None, qso_bg=None, outfil=None, qpqquery_file=None,
+             ascii=False):
     """ Generate TPE sample from QPQ query
     Parameters
     ----------
@@ -93,6 +94,8 @@ def make_tpe(min_logLV, R, qso_fg=None, qso_bg=None, outfil=None, qpqquery_file=
     R : float
       Cut in physical Mpc
     outfil : str
+    ascii : bool, optional
+      Generate an ASCII table too (used for rejecting pairs afterwards)
 
     Returns
     -------
@@ -222,6 +225,8 @@ def make_tpe(min_logLV, R, qso_fg=None, qso_bg=None, outfil=None, qpqquery_file=
     if outfil is not None:
         print("Writing {:s}".format(outfil))
         final_tpe.write(outfil, overwrite=True)
+        # ASCII?
+        if ascii:
     # Return
     return final_tpe
 
@@ -429,7 +434,8 @@ if __name__ == '__main__':
         run_wide_query('QPQ_v2000_R15_novette.fits', R_MAX=15.*u.Mpc) # TEST
 
     if flg_fig & (2**3):
-        make_tpe(31.5, 4., qpqquery_file='QPQ_v2000_R15_novette.fits', outfil='TPE_31.5_4pMpc.fits')
+        make_tpe(31.5, 4., qpqquery_file='QPQ_v2000_R15_novette.fits',
+                 outfil='TPE_31.5_4pMpc.fits', ascii=True)
 
     if flg_fig & (2**4):
         make_tpe([31.2,31.5], 4., qpqquery_file='QPQ_v2000_R15_novette.fits', outfil='TPE_31.2_31.5_4pMpc.fits')

### 2017-02-23 QPQ9/qpq9_draft.tex
Added tables. Draft version 1.2

--- 2017-01-12 QPQ9/qpq9_draft.tex
@@
 
-\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.1]}
+\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.2]}
 
@@
 \begin{abstract}
-Blah
+Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
+difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
+environments of massive galaxies hosting quasars at $z\sim2$. We employ 195 projected quasar pairs 
+to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
+have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
+background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
+\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large intrinsic velocity fields, and have velocity 
+centroids that show a small positive offset relative to the systemic. We argue the results can be 
+explained by outflowing gas combined with anisotropic or intermittent ionizing radiation of the 
+quasars. 
 \end{abstract}
@@
 \section{Introduction}
-
+\label{sec:introduction}
 %\begin{itemize}
@@
 
-%Take words from my summary of SomervilleDave15.
+Galaxy formation and evolution are driven by the flows into and out of their interstellar medium. 
+Current theories demand that star-forming galaxies maintain these flows. Gas accretes, cools, and 
+adds to the fuel supply, while star formation feedback heats gas, blows it out of galaxies, and 
+regulates star formation \citep[for a review see][]{SomervilleDave15}.
 
-The formation and evolution of stars are dictated
-by the flow of gas and metals/dust.  [This transport
-varies directly with the stellar stage
-and a lesser extent stellar mass.]
-The accretion onto a protostellar  core eventually
-initiates nuclear fusion.  The main sequence is characterized
-by gentler stellar winds, with the most massive
-stars shedding a cumulative mass of XX\%.
-Stellar deaths, meanwhile, are frequently accompanied by terrific
-mass loss, occasionally punctuated by a highly energetic,
-supernova phase.
+Direction observations of galactic flows are difficult to acquire. Detecting the presence of 
+the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for 
+the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving 
+the kinematics and establishing the mass flux pose an even greater challenge. These challenges are 
+accentuated for distant, young galaxies, where flows are predicted to prevail 
+\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions, 
+\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy 
+to detect and characterize the gas surrounding galaxies 
+\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}. With this 
+experiment, researchers have had success in characterizing the large-scale flows around 
+star-forming galaxies to reveal a net inflow, or a Kaiser effect for gas \citep{Rakic+12}.
 
-By analogy, galaxy formation and evolution are driven by the
-flows into/out of their interstellar medium.
-In contrast to most stars, however, current theories
-predict (even demand) that the star-forming galaxies
-maintin these flows. [add]
+A significant limitation of absorption-line analysis, especially regarding galactic flows, 
+is the inherent symmetry of the experiment. One generally lacks any constraint on the distance of 
+the gas along the sightline. Positive or negative velocities with respect to the galaxy may be 
+interpreted as gas flowing either toward or away from the system. ``Down-the-barrel'' observations 
+break this symmetry, and have generally provided evidence for flows away from galaxies 
+\citep{Rupke+05,Martin05,Weiner+09,Rubin+14}. However, these data are frequently at low spectral 
+resolution which limits one's sensitivity to inflowing gas.
 
-Akin to stars, direct observations of galactic flows are
-difficult to acquire.  Even detecting the gas is challenging:
-the gas mass is either too small or the gas density too low
-for the [detection] of line-emission (e.g. 21cm, lya,
-or H$\alpha$ from Hydrogen).  Resolving the kinematics
-and establish the mass-flux represent a far greater challenge.
-These challenges are accentuated for distant, young galaxies
-where flows are predicted to prevail \citep{keres,fumagalli}.
-Therefore, with rare exceptions \citep[e.g.][]{slug,jackpot},
-the community has relied on absorption-line spectroscopy
-to detect and characterize the gas surrounding galaxies
-\citep[e.g.][]{bergeron,steidel10,pro11,tumlinson13}.
-With this experiment, researcher have had recent success
-in characterizing the large-scale flows around star-forming
-galaxies to reveal a net inflow \cite{rakic13} and
-provide unique constraints on the mass of the underlying
-potential well \cite{rakic14}.
+In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
+galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
+\citep[][QPQ1]{QPQ1} to use the 
+standard technique of absorption-line spectroscopy with background quasars. These quasar pairs 
+have angular separations that correspond to less than 300\,kpc projected separation at the 
+foreground quasar's redshift. Our previous publications from these quasar pairs have established 
+that these galaxies are surrounded by a massive, cool, and enriched circumgalactic medium 
+\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 195 background 
+spectra that are paired with foreground quasars with precisely measured redshifts. Our primary 
+scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
+central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
+(ii) characterize the dynamics of galactic flows around these massive system. We further describe 
+an aspect of this experiment that offers a unique opportunity to study galactic flows: we argue 
+that, the anisotropic or intermittent radiation of the foreground quasars breaks the symmetry in 
+the velocity field of circumgalactic absorbers.
 
-A significant limitation of standard absorption-line
-analysis, especially regarding sutyding galactic flows,
-is the inherent symmetry of the experiment.
-Because one generally lacks any constraint on the distance
-of the gas along the sightline,
-postive or negative velocities with respect to the
-galaxy may be interpreted as gas flowing either towards
-or away from the system.
-So-called `down-the-barrel' observations break this
-symmetry, and have generally provided evidence for flows
-away from galaxies \citep{rupke,martin,weiner,rubin}.
-However, these data are frequently at low spectral resolution
-which limits one's sensitivity to inflowing gas.
+Among the sightlines in the QPQ9 sample, 13 have spectral resolution $> 5000$ from echellette or 
+echelle observations, and have been analyzed separately in QPQ8 \citep{QPQ8}. We measured the 
+velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the CGM frequently exhibits 
+large flows that are offset from the systemic redshift. The offsets, $\delta v$, are often 
+positive, with the sign convention that positive velocities are flowing away from the observer. 
+From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4} systems, we measured the velocity 
+interval that encompasses 90\% of the total optical depth, $\Delta v_{90}$, and the $1\sigma$ 
+dispersion relative to the profile centroid, $\sigma_v$. The median $\Delta v_{90}$ is 
+$555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is $342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. 
+The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is 
+$495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed all previous 
+measurements from galaxies and/or absorption systems at any epoch.
 
-In this paper, we examine the flows of gas in the environments
-of massive galaxies hosting quasars.  Our approach leverages
-a large dataset of quasar pairs \citep{hennawi}
-to use the standard technique of absorption-line spectroscopy
-with background quasars. [word]
-These quasar pairs have angular
-separations that correspond to less than 300\,kpc physical
-separation at the f/g quasar redshift.
-Our previous publications from these quasar pairs
-have established that these galaxies are surrounded
-by a massive, cool, and enriched circumgalactic medium
-\citep{QPQ1,QPQ5,QPQ6,QPQ7}.
-We have collected a sample of ntot~spectra passing within
-300\,kpc from a f/g quasar with a precisely measured
-redshift.  Our primary scientific interests are twofold:
-(i) search for signatures of galactic-scale outflows from the
-central galaxy, presumably driven by recent star-formation
-and/or AGN feedback;
-(ii) characterize the dynamics of galactic flows around these
-massive system.  We further descrbie an aspect of this
-experiment that offers a unique opportunity to study galactic
-flows. [detail??]
+%The formation and evolution of stars are dictated
+%by the flow of gas and metals/dust.  [This transport
+%varies directly with the stellar stage
+%and a lesser extent stellar mass.]
+%The accretion onto a protostellar  core eventually
+%initiates nuclear fusion.  The main sequence is characterized
+%by gentler stellar winds, with the most massive
+%stars shedding a cumulative mass of XX\%.
+%Stellar deaths, meanwhile, are frequently accompanied by terrific
+%mass loss, occasionally punctuated by a highly energetic,
+%supernova phase.
+%By analogy, galaxy formation and evolution are driven by the
+%flows into/out of their interstellar medium.
+%In contrast to most stars, however, current theories
+%predict (even demand) that the star-forming galaxies
+%maintin these flows. [add]
+%Akin to stars, direct observations of galactic flows are
+%difficult to acquire. Even detecting the gas is challenging:
+%the gas mass is either too small or the gas density too low
+%for the [detection] of line-emission (e.g. 21cm, lya,
+%or H$\alpha$ from Hydrogen).  Resolving the kinematics
+%and establish the mass-flux represent a far greater challenge.
+%These challenges are accentuated for distant, young galaxies
+%where flows are predicted to prevail \citep{keres,fumagalli}.
+%Therefore, with rare exceptions \citep[e.g.][]{slug,jackpot},
+%the community has relied on absorption-line spectroscopy
+%to detect and characterize the gas surrounding galaxies
+%\citep[e.g.][]{bergeron,steidel10,pro11,tumlinson13}.
+%With this experiment, researcher have had recent success
+%in characterizing the large-scale flows around star-forming
+%galaxies to reveal a net inflow \cite{rakic13} and
+%provide unique constraints on the mass of the underlying
+%potential well \cite{rakic14}.
+%A significant limitation of standard absorption-line
+%analysis, especially regarding sutyding galactic flows,
+%is the inherent symmetry of the experiment.
+%Because one generally lacks any constraint on the distance
+%of the gas along the sightline,
+%postive or negative velocities with respect to the
+%galaxy may be interpreted as gas flowing either towards
+%or away from the system.
+%So-called `down-the-barrel' observations break this
+%symmetry, and have generally provided evidence for flows
+%away from galaxies \citep{rupke,martin,weiner,rubin}.
+%However, these data are frequently at low spectral resolution
+%which limits one's sensitivity to inflowing gas.
+%In this paper, we examine the flows of gas in the environments
+%of massive galaxies hosting quasars.  Our approach leverages
+%a large dataset of quasar pairs \citep{hennawi}
+%to use the standard technique of absorption-line spectroscopy
+%with background quasars. [word]
+%These quasar pairs have angular
+%separations that correspond to less than 300\,kpc physical
+%separation at the f/g quasar redshift.
+%Our previous publications from these quasar pairs
+%have established that these galaxies are surrounded
+%by a massive, cool, and enriched circumgalactic medium
+%\citep{QPQ1,QPQ5,QPQ6,QPQ7}.
+%We have collected a sample of ntot~spectra passing within
+%300\,kpc from a f/g quasar with a precisely measured
+%redshift.  Our primary scientific interests are twofold:
+%(i) search for signatures of galactic-scale outflows from the
+%central galaxy, presumably driven by recent star-formation
+%and/or AGN feedback;
+%(ii) characterize the dynamics of galactic flows around these
+%massive system.  We further descrbie an aspect of this
+%experiment that offers a unique opportunity to study galactic
+%flows. [detail??]
 
-Throughout this manuscript we adopt a $\Lambda$CDM cosmology with $\Omega_M=0.26, \Omega_\Lambda
-=0.74$, and $H_0=70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. All distances are proper unless otherwise 
-stated. 
-%When referring to comoving distances we include explicitly an $h^{-1}$ term and 
-%follow modern convention of scaling to a Hubble constant of $70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. All 
-%equivalent width measurements are presented in the rest-frame, unless otherwise specified.
+We adopt a $\Lambda$CDM cosmology with $\Omega_M=0.26, \Omega_\Lambda=0.74$, and 
+$H_0=70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. Distances are proper unless otherwise stated. When referring 
+to comoving distances we include explicitly an $h^{-1}$ term and follow modern convention of 
+scaling to a Hubble constant of $70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. 
+%All equivalent width measurements are presented in the rest-frame, unless otherwise specified.
 
 \section{The Experiment}
-\label{sec:data}
+\label{sec:experiment}
 
-From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed 195~systems 
-that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict the sample 
-to foreground quasars with redshift measured from \ion{Mg}{2}, [\ion{O}{3}], H$\alpha$, or 
-H$\beta$ emission, giving a precision of $400\,{\rm km\,s^{-1}}$ or lower. [\ion{O}{3}] has the 
-smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the 
-sub-sample with [\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift 
-of $27\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
+\begin{figure}
+\includegraphics[width=3in]{Figures/fig_experiment.pdf}
+\caption{These panels summarize properties of the QPQ9 dataset. The QPQ survey selects 
+quasar pairs of $R_\perp < 300$\,kpc and $z_{\rm fg}>1.6$. Assuming that the foreground quasars 
+emit isotropically and at a distance equal to the impact parameter, the aenhancement in the UV 
+flux relative to the extragalactic UV background, $g_{\rm UV}$, can be estimated. Large 
+symbols correspond to foreground quasars with the most precise redshift measurement from 
+[\ion{O}{3}]\,5007, while small symbols correspond to $z_{\rm fg}$ 
+measurements from \ion{Mg}{2}\,2800, H$\alpha$, or H$\beta$ emission. The top panel shows 
+quasar pairs with coverage of \ion{C}{2}\,1334 at $z_{\rm fg}$ in the background quasar spectra. 
+The middle panel shows pairs with coverage of \ion{C}{4}\,1548. The bottom panel shows 
+pairs with coverage of \ion{Mg}{2}\,2796. 
+}
+\label{fig:experiment}
+\end{figure}
+
+The goal of our experiment is to measure the average velocity fields of the absorption from C$^+$, 
+C$^{3+}$, and Mg$^+$ ions associated with the CGM of the massive galaxies hosting $z\sim 2$ 
+quasars.
+
+From our QPQ survey\footnote{http://www.qpqsurvey.org}, we have analyzed a subset of systems that 
+pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
+$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
+\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
+$400\,{\rm km\,s^{-1}}$ or better. 
+[\ion{O}{3}] emission-line redshifts have the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about 
+the systemic redshift, and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
+The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
+redshift \citep{Boroson05}, which has been added when we compute the 
 redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
 $272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
-$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 we have 
-quantified the precision of H$\alpha$ and H$\beta$ to be 
-$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. 
-\citep{hewittwild}.
-We include only those spectra with S/N~$> XX$\AA\ at the
-observed wavelengths of lya, \ion{C}{2}~1334, or 
-\ion{C}{4}~1548 transitions.  Of the ntot~sightlines, 
-nhigh\ have spectral resolution ~$> 5,000$ from echellette
-or echelle observations (QPQ8).  This high-dispersion 
-sample is analyzed [separately] throughout the paper.
-Figure~\ref{fig:exp} summarizes the experimental design.
-Refer to previous QPQ
-publications for details on data reduction
-and continuum normalzaton (QPQ6, QPQ7, QPQ8).
+$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 
+\citep{QPQ8}, we have quantified the precision of H$\alpha$ and H$\beta$ to be 
+$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. We further add to the QPQ 
+dataset with quasar pairs selected from the public dataset of 
+igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
+catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
+Twelfth Data Release \citep{Paris+17}. We 
+only select pairs with $z_{\rm fg}$ measured by \cite{HewettWild10} using the \ion{Mg}{2}\,1800 
+emission-line. We reached a final sample size of 195. Figure~\ref{fig:experiment} summarizes the 
+experimental design. We refer the reader to previous QPQ publications for the details on the 
+redshift centroiding algorithm, data reduction, and continuum normalization (QPQ6; QPQ8).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+As in the previous QPQ papers, we select the quasar pairs to have redshift difference 
+$>3000\,{\rm km\,s^{-1}}$, to exclude physically associated binary quasars. The cut on velocity 
+difference is motivated by the typical redshift uncertainty of $\approx500\,{\rm km\,s^{-1}}$ of 
+the background quasars. In QPQ8, it was required that the observed wavelengths of the 
+metal ion transitions fall outside the Ly$\alpha$ forest of the background quasar. In this paper, 
+we exclude a small window around the Ly$\alpha$ emission, in additional to the Ly$\alpha$ forest, 
+from analysis. For stacked profile analysis, a good estimate of 
+the continuum level is neessary. In QPQ8 we found that absorption associated to 
+the foreground quasar occurs within $\pm2000\,{\rm km\,s^{-1}}$ around $z_{\rm fg}$. Therefore, it 
+is desirable to keep a $\approx\pm3000\,{\rm km\,s^{-1}}$ window relatively free of contamination 
+from Ly$\alpha$ forest. Taking into account the redshift uncertainties, 
+we decide that at least one transition among \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
+\ion{Mg}{2}\,2796 at $z_{\rm fg}$ must lie redward of 
+$(1215.6701+20)\times(1+z_{\rm bg})\,{\rm \AA}$, for a pair to be included in the analysis.
+
+Furthermore, we include only those spectra with average signal-to-noise ratio (S/N) exceeding 5.5 
+per rest-frame \AA \ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths 
+of the metal ion transitions. This criterion is a compromise between maximizing sample size versus 
+maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame 
+\AA \ is 
+necessary for properly estimating the continuum, as well as identifying mini-broad absorption line 
+systems associated to the background quasar, which will significantly depress the flux level. We 
+also require that the region of the spectrum that is $\pm3000\,{\rm km\,s^{-1}}$ around a 
+considered metal ion transition does not overlap with strong atmospheric ${\rm O}_2$ bands. 
+The ${\rm O}_2$ A- and B-band span 7595\textendash7680\,\AA \ and 6868\textendash6926\,\AA \ 
+respectively.
+
+Table~\ref{tab:sample} lists the full QPQ9 sample. 
+In Table~\ref{tab:summary}, we list the sample size, the median $z_{\rm fg}$, and the median 
+$R_\perp$ of the quasar pairs that survive the above selection criteria for \ion{C}{2}\,1334, 
+\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively. In Table~\ref{tab:summary_OIII}, we provide 
+the summary for the sub-sample with $z_{\rm fg}$ measured from [\ion{O}{3}].
+
+\input{Tables/tab_sample.tex}
+\input{Tables/tab_summ.tex}
+\input{Tables/tab_summ_OIII.tex}
+
 \section{Analysis}
@@
 
-In QPQ8, we measured the velocity widths of the \ion{C}{2}~1334
-and \ion{C}{4}~1548 transitions finding that the CGM
-frequently exhibits large flows:
-median DV{1334},DV{1548} = $XX,XX kms$ with and
-RMS DRMS{1334},DRMS{1548} = $XX, XX kms$ from
-a sample of ncii\ and nciv\ systems.
-These velocity fields exceed all previous measurements from
-galaxies and/or absorption systems at any epoch.  For
-Figure~\ref{fig:stack}, we present these absorption lines
-and \ion{H}{1}~lya, also including lower-dispersion 
-sightlines meeting the selection criteria.
+\begin{figure}
+\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
+\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
+\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thick, 
+black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
+from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thin, blue. 
+For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
+included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
+lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$.  
+}
+\label{fig:stacks_and_fits}
+\end{figure}
 
-To assess the `average' absorption of these transitions,
-we have combined the data with a novel technique.
-We have fitted the combined dataset using a cubic b-spline
-with knots at every 100\,kms.  We weighted each data
-point by the velocity width of the pixel to insure that 
-each sightline makes an equal contribution to the stack.
-These b-spline profiles are presented in the figure
-and a trivial integration gives the reported equivalent
-widths.
-[consider down-weighting systems with $<3\sigma$ EW]
-[Comnent on EW from 'standard' technique]
+We create composite spectra that average over the intrinsic scatter in quasar environments, 
+continuum placement errors, and redshift errors. The individual spectra of background quasars are 
+shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
+has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
+$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unncessary to smooth the data to a 
+common spectral resolution. The individual spectra are then combined with a mean or a median 
+statistic. Bad pixels in the individual spectra have been masked before generating the 
+composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
+weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
+metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
+than error sources. The mean statistic of the individual spectra yields a good estimate of the 
+average absorption and preserves equivalent width. The median statistic is less sensitive to 
+outliers, however the averaged equivalent width is smaller and the analysis on the velocity field 
+becomes more uncertain. In the following we present stacked spectra using both the mean and the 
+median statistic.
 
-Two results are evident from the figure:
- (i) the data exhibit excess absorptoin at 
- $mdv \approx 0 kms$;
- (ii) the absorption is skewed towards positive velocities
- $mdv > 0 mkms$.
-We measure absorption-weigthed ($1-f$) centroids
-of $mdv = XX-XX mkms$ for these transitions
-(Table~\ref{tab:summ}).
-This suggests an asymmetry that contradicts the [standard]
-expectation.
+[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]
 
-Given the small sample size, one must 
-scrutinize the statistical significance of the measured offset.
-Indeed, a small offset $mdv < 10 kms$ may be expected
-even with large samples.  To assess the statistical significance,
-we have perfomed a boostrap analysis by randomly resampling
-from the full sample. [DISCUSS]
+In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
+\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
+analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
+and it is more challenging to interpret their kinematics, while the median stacks have smaller 
+equivalent widths.
 
-[Discuss systematics here??]
+%To assess the average absorption of these transitions,
+%we have combined the data with a novel technique.
+%We have fitted the combined dataset using a cubic b-spline
+%with knots at every 100\,kms.  We weighted each data
+%point by the velocity width of the pixel to insure that 
+%each sightline makes an equal contribution to the stack.
+%These b-spline profiles are presented in the figure
+%and a trivial integration gives the reported equivalent
+%widths.
+%[consider down-weighting systems with $<3\sigma$ EW]
+%[Comnent on EW from 'standard' technique]
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
+exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is skewed 
+toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
+allowing a constant pseudo-continuum level to vary. From the $\chi^2$ best-fit to the data, 
+we measure the centroid of the \ion{C}{2} stack to be $+170\,{\rm km\,s^{-1}}$ and 
+the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
+contradicts the standard expectation, while the dispersion suggests extreme kinematics. The 
+median stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid 
+closer to zero.
+
+We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the 
+absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
+$+207\,{\rm km\,s^{-1}}$, and a dispersion of $355\,{\rm km\,s^{-1}}$, consistent with the full 
+sample.
+
+To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a  
+second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and 
+$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. The 
+modeling results show that the velocity fields of \ion{C}{4} and \ion{Mg}{2} are consistent with 
+\ion{C}{2}, i.e.\ large dispersion and centroid is skewed toward positive velocities.
+
+The above analyses are summarized in Table~\ref{tab:summary} and Table~\ref{tab:summary_OIII}. The 
+Gaussian models normalized to pseudo-continuum are overplotted on the data stacks in 
+Figure~\ref{fig:stacks_and_fits}.
+
+\subsection{Significance of the asymmetric absorption}
+\label{sec:significance_+ve}
+
+\begin{figure*}[!h]
+\begin{minipage}[!bp]{0.35\textwidth}
+\includegraphics[width=\textwidth]{Figures/fig_stack_z1.pdf}
+\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
+$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
+approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
+}
+\label{fig:stack_z1}
+\end{minipage}%
+\hspace{0.5in}
+\begin{minipage}[!bp]{0.55\textwidth}
+\includegraphics[width=\textwidth]{Figures/fig_stacks_fg.pdf}
+\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
+\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
+excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
+absorbers at all distances, shows a large, blueshifted mean velocity field.
+}
+\label{fig:stacks_fg}
+\end{minipage}
+\end{figure*}
+
+Given the small sample size, one must scrutinize the statistical significance of the measured 
+velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
+randomly sampling from the full sample 10000 times. We measure the flux-weighted centroid of each 
+bootstrap realization, and quote the standard deviation in the bootstrap realizations to be the 
+scatter in the centroid of the data. The scatters $\approx100\,{\rm \,s^{-1}}$ are comparable 
+to the measured offsets, indicating large intrinsic variation in quasar CGM environments (see 
+also QPQ8). Given the large intrinsic scatter, we do not attempt to explore whether there exists 
+relative asymmetry between \ion{C}{2} and \ion{C}{4} absorption due to different ionization 
+potentials.
+
+One may also ask whether the measured positive offsets come from systematic bias in redshift 
+measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
+[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
+less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
+stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2}, H$\alpha$, or 
+H$\beta$ redshift. We are able to replace for 13 out of the 14 systems with [\ion{O}{3}] redshifts 
+in the original sample. The new stack is similiar in velocity structure and again shows a positive 
+offset. We thus conclude that our algorithm for measuring redshifts is not severely biased by 
+the blue wing of the [\ion{O}{3}] emission-line.
+
+We also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs, 
+using the same selection criteria as the main QPQ9 sample. The quasar pairs are selected from the 
+igmspec database, with $z_{\rm fg}$ measured by \cite{HewettWild10}. There are 231 pairs selected, 
+with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present the mean and 
+median stacks in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
+sample. Gaussian absorption models fitted to the stack recover a centroid of 
+$47\pm122\,{\rm km\,s^{-1}}$ and a dispersion of $119\,{\rm km\,s^{-1}}$. The offsets from 
+$0\,{\rm km\,s^{-1}}$ are smaller than the offsets in the $z\sim2$ sample.
+
+Since the large scatters in the centroids represent intrinsic variation rather than redshift 
+errors, and the \ion{Mg}{2} stack for lower redshift does not suggest a similar offset, the hint 
+of asymmetry cannot be ignored. In the Discussion section, we discuss two possible explanations 
+for the asymmetry.
+
+%Indeed, a small offset $mdv < 10 kms$ may be expected even with large samples.
+
+\subsection{Significance of the large velocity fields}
+\label{sec:significance_width}
+
+Under the assumption that the intrinsic velocity field and the redshift uncertainty add in 
+quadrature to give the observed width, we solve for the intrinsic dispersion in the \ion{C}{2} 
+mean stacks. For the full sample, the mean $\sigma_{\rm error}^{\rm full}=224\,{\rm km\,s^{-1}}$ 
+and we recover $\sigma_{\rm intrinsic}^{\rm full}=317\,{\rm km\,s^{-1}}$. For the sub-sample with 
+$z_{\rm fg}$ measured from [\ion{O}{3}], we recover 
+$\sigma_{\rm intrinsic}^{\rm [OIII]}=352\,{\rm km\,s^{-1}}$. In QPQ8, we reported the 
+line-of-sight velocity dispersion typical of QPQ dark matter halo mass is 
+$\sigma_{\rm 1D}=212\,{\rm km\,s^{-1}}$. We can investigate whether gravitational motions and 
+Hubble flows are sufficient to reproduce the dispersion in the \ion{C}{2} mean stack using Monte 
+Carlo methods.
+
+Since \ion{C}{2} systems arise in optically thick absorbers, we may adopt the clustering analysis 
+results of QPQ6. In the absence of clustering, the expected number of absorbers per unit redshift 
+interval for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
+respectively $\ell_{\rm IGM}^{\rm LLS}(z)\approx1.05((1+z)/(1+2.5))^{2.1}$, 
+$\ell_{\rm IGM}^{\rm SLLS}(z)\approx0.44((1+z)/(1+2.5))^{2.1}$, and 
+$\ell_{\rm IGM}^{\rm DLA}(z)\approx0.2((1+z)/(1+2.5))^{2.1}$. The quasar-absorber correlation 
+functions for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
+respectively $\xi_{\rm QA}^{\rm LLS}(r)=(r/(12.5\,h^{-1}\,{\rm Mpc}))^{-1.68}$, 
+$\xi_{\rm QA}^{\rm SLLS}(r)=(r/(14.0\,h^{-1}\,{\rm Mpc}))^{-1.68}$, and 
+$\xi_{\rm QA}^{\rm DLA}(r)=(r/(3.9\,h^{-1}\,{\rm Mpc}))^{-1.6}$. 
+For each quasar pair, we calculate the expected number of all optically thick absorbers within 
+$\pm3000\,{\rm km\,s^{-1}}$ at a distance $R_\perp$ from the foreground quasar and at 
+$z_{\rm fg}$. Then we generate 1000 mock sightlines. The number of absorbers for each mock 
+spectrum is randomly selected from a Poisson distribution with mean equal to the expected number 
+calculated as above. The absorbers are randomly assigned Hubble velocities, with a probability 
+distribution according to the quasar-absorber correlation functions. The absorbers are randomly 
+assigned additional peculiar velocities drawn from a normal distribution with mean equal to 
+$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we 
+assume a rest equivalent width for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
+above procedure for all 34 quasar pairs, and create a mean stack of the 34000 mock spectra 
+generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
+the stack of mock spectra. We adjust the rest equivalent width adopted for the \ion{C}{2} 
+absorbers until the ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
+amplitude of the stack of the observational data. We find that a rest equivalent width of 
+0.6\,\AA\ well reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
+insensitive to the assumed equivalent width or line profile for one absorber. The resulting 
+stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, which is 
+smaller than the intrinsic dispersion in the data. We also test for the sensitivity of this 
+measured dispersion to the correlation functions adopted. The QPQ6 clustering analysis is 
+performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ sightline may in 
+fact intercept more than one optically thick absorber. We double the number of absorbers for each 
+mock sightline, and find the measured dispersion only increases by several ${\rm km\,s^{-1}}$. 
+In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
+velocity of $\approx280\,{\rm km\,s^{-1}}$ is required. Thus, the observed velocity width is 
+indicative of dynamical processes in addition to gravitational motions and Hubble flows.
+
+In the previous QPQ papers, we argued that optically thick absorbers in the vicinity of quasars 
+are distributed anisotropically. In Figure~\ref{fig:stacks_fg}, we present mean stacks of 
+foreground quasar spectra for the pairs in the QPQ9 sample. We require that the spectra survive a 
+S/N cut of 5.5 per rest-frame \AA\ at \ion{C}{2}\,1334, \ion{C}{4}\,1548, or \ion{Mg}{2}\,2796 at 
+$z_{\rm fg}$. In constrast to the large equivalent widths exhibited in the stacks of background 
+spectra, \ion{C}{2} and \ion{Mg}{2} do not show excess mean absorption at $z_{\rm fg}$ in the 
+stacks of foreground quasar spectra. This supports a scenario where the ionizing radiation of the 
+foreground quasars are anisotropic or intermittent. For \ion{C}{4}\,1548, this stack of all 
+line-of-sight absorbers, which include absorbers intrinsic to and far away from the quasar, shows 
+a large, blueshifted velocity field.
+
 \section{Discussion}
@@
 
-[Add a cartoon fig with cone]
-[Is it really obvious that this works??]
+\begin{figure*}[!h]
+\begin{minipage}[!bp]{0.28\textwidth}
+\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
+\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
+absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation. 
+}
+\label{fig:monopolar}
+\end{minipage}%
+\hspace{0.3in}
+\begin{minipage}[!bp]{0.67\textwidth}
+\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
+\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
+asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining 
+long enough for its ionizing radiation to reach the gas behind it, when the light from the 
+background quasar reaches. The setup on the right shows the scenario after an amount of time 
+comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar 
+has been ionized, by the time the light from the background quasar reaches. 
+}
+\label{fig:lighttravel}
+\end{minipage}
+\end{figure*}
 
-%%%%%%%%%%%%%%%%
+Given the large intrinsic scatter, we place generous upper limits to the small offset of the 
+centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption. For the full QPQ9 sample, the 
+$3\sigma$ upper limit is $\delta v<+485\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
+redshifts, $\delta v<+426\,{\rm km\,s^{-1}}$. In the following, we explore two possible 
+explanations for the putative non-dynamical process that provides the asymmetry.
+
+One possibility is an asymmetric radiation field that preferentially ionizes the gas moving toward 
+the observer, where the quasar is known to shine. In Figure~\ref{fig:monopolar}, we show a cartoon 
+of a quasar that is blocked in the direction pointing away from the observer. The gas 
+observed in absorption preferentially lies behind the quasar. The asymmetric absorption arises 
+from a transverse proxmity effect. 
+\cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy 
+inlcuding thermal AGN feedback and calculated radiative transfer in post-processing. They found 
+the ionization radiation is typically asymmetric, due to either a dense clump that lies on one 
+edge of the black hole or the black hole's location being slightly above the disk.
+
+Another possible explanation arises from the finite lifetime of quasar episodes. 
+Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. Light from the 
+background quasar will travel smaller distance to reach the gas behind the foreground quasar 
+than the gas in front of it. The light from the background quasar may arrive at the gas behind 
+the foreground quasar before the ionizing radiation from the foreground quasar arrives. In 
+QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average 
+extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of 
+$\sim10^6$\,Myr, which lies within existing constraints of quasar lifetime from observations 
+\citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
+
+As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, 
+outflow speeds of $500\textendash700\,{\rm km\,s^{-/1}}$ and quasar opening angles of 
+$100^\circ\textendash120^\circ$ may reproduce the observed centroid and intrinsic dispersion of 
+the \ion{C}{2} mean absorption. 
+The first explanation above to asymmetric absorption requires that the quasars emit their ionizing 
+radiation anisotropically, while the second explanation requires the quasars emit their ionizing 
+radiation intermittently. Both explanations will require the gas to be either outflowing or in 
+Hubble flow. Were the gas inflowing instead, the velocity centroid would be negative. 
+\cite{KirkmanTytler08} reported an asymmetry in \ion{H}{1} absorption on scales larger than 
+the CGM, and gave similar arguments on anisotropy or intermittence. We are assembling a sample of 
+quasar pairs with precise 
+$z_{\rm fg}$ measurements to study this asymmetry in \ion{H}{1} (J. F. Hennawi et al. 2017, in 
+preparation).
+
+In conclusion, we observe large and positively skewed velocity fields in absorption, of metal ions 
+in the CGM of $z\sim2$ massive galaxies hosting quasars. We interpret the results as evidence that 
+the detected gas is outflowing, and that the quasars either shine anisotropically or 
+intermittently.
+
 \acknowledgements
+[NSF grant number?]
 
-JXP and ML acknowledge support from the National
-Science Foundation (NSF) grant AST-1010004 and AST-XX. 
-JXP thanks the Alexander
-von Humboldt foundation for a visitor fellowship to the MPIA where
-part of this work was performed, as well as the staff at MPIA for
-their hospitality during his visits.
-JFH acknowledges generous support from the Alexander von Humboldt
-foundation in the context of the Sofja Kovalevskaja Award. The
-Humboldt foundation is funded by the German Federal Ministry for
-Education and Research.
+%JXP and MWL acknowledge support from the National
+%Science Foundation (NSF) grant AST-1010004 and AST-XX. 
+%JXP thanks the Alexander
+%von Humboldt foundation for a visitor fellowship to the MPIA where
+%part of this work was performed, as well as the staff at MPIA for
+%their hospitality during his visits.
+%JFH acknowledges generous support from the Alexander von Humboldt
+%foundation in the context of the Sofja Kovalevskaja Award. The
+%Humboldt foundation is funded by the German Federal Ministry for
+%Education and Research.
 
@@
 %mountain.
-%Acknowledge TK Chan. CP Choi.
+%MWL thanks T.-K. Chan for a discussion on CGM simulations. MWL 
+%thanks Chi Po Choi for a discussion on statistics.
 
-\bibliographystyle{/u/xavier/paper/Bibli/apj}
-\bibliography{/u/xavier/paper/Bibli/allrefs}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{../Tables/tab_sub_qpq7_spectra.tex}
-\input{Tables/tab_summ.tex}
-%\input{Tables/tab_summ_Hab.tex}
-%\input{tab1_sub.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\begin{figure}
-\includegraphics[width=5in]{Figures/fig_experiment.pdf}
-%\includegraphics[width=5in,angle=90]{../Figuref1.eps}
-\caption{Experimental design
-}
-\label{fig:exp}
-\end{figure}
-
-\begin{figure}
-%\includegraphics[width=5in]{Figures/fig_simple_stack.pdf}
-%\includegraphics[width=5in,angle=90]{f2.eps}
-\caption{Simple stack
-}
-\label{fig:stack}
-\end{figure}
+\bibliographystyle{/Users/lwymarie/Documents/Bibli/apj}
+\bibliography{/Users/lwymarie/Documents/Bibli/allrefs}
 

### 2017-02-23 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py

@@ -88,15 +88,23 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
         # Centroid of pseudo-optical depth within +/- 2000 km/s
         start = np.int((sz[1]-1)*1./6.)
         end = np.int((sz[1]-1)*5./6.)
+        # Centroid of pseudo-optical depth within +/- 3000 km/s
+#        start = 0
+#        end = sz[1]-1
         # Centroid of pseudo-optical depth outside of continuum ranges
 #        pix = np.where((velo >= cranges[0][1]) & (velo <= cranges[1][0]))[0]
 #        start = pix[0]
 #        end = pix[-1]
 #        tau = np.log(1./cfx)
-#        tau[np.where(tau < 0.)] = 0 # floor for weights should be zero
-        tau = np.log(1./fx) # don't divide by continuum. do not want negative weights
-        tau_cen[qq] = np.sum(fin_velo[start:end+1]*tau[start:end+1])/np.sum(tau[start:end+1])
-
+#        tau = np.log(1./fx) # don't divide by continuum; do not want negative weights
+#        tau[np.where(tau < 0.)] = 0. # floor for weights should be zero
+#        tau_cen[qq] = np.sum(fin_velo[start:end+1]*tau[start:end+1])/np.sum(tau[start:end+1])
+        # Do pseudo-continuum normalized flux weighted centroid instead
+#        cfx[np.where(cfx > 1.)] = 1.  # floor for weights should be zero
+#        tau_cen[qq] = np.sum(fin_velo[start:end+1]*(1-cfx[start:end+1]))/np.sum(1-cfx[start:end+1])
+        # Do flux weighted centroid instead
+        fx[np.where(fx > 1.)] = 1.  # floor for weights should be zero
+        tau_cen[qq] = np.sum(fin_velo[start:end+1]*(1-fx[start:end+1]))/np.sum(1-fx[start:end+1])
 
         # Pseudo-EW
         EWpix = np.where( (velo > EW_range[0]) & (velo<EW_range[1]))[0]
@@ -123,7 +131,7 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
           .format(mu_frac,med_frac,std_frac,nboot))
     mu_taucen = np.mean(tau_cen)
     std_taucen = np.std(tau_cen)
-    print('Tau-weighted centroid: Mean = {:g}, std={:g}'.format(mu_taucen,std_taucen))
[…]

### 2017-02-23 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -73,17 +73,18 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
 #######
 def plt_qpq9(stack_tup=None,wrest=None,
              S2N_cut=None,atmosphere_cut=True,
+             vmnx=(-3000.,3000.)*u.km/u.s,
              stack_fg=False,zfg_mnx=(-9999,9999),plot_indiv=False):
 
     # Rest wavelength
     if wrest is None:
         wrest = 1334.5323*u.AA
 
-    vmnx = [-3000., 3000] * u.km/u.s
     ymnx = (-0.1, 1.2)
     if stack_tup is None:
         stack_tup = qpq9_IRMgII(wrest=wrest,S2N_cut=S2N_cut,
                                 atmosphere_cut=atmosphere_cut,
+                                vmnx=vmnx,
                                 stack_fg=stack_fg,zfg_mnx=zfg_mnx,
                                 plot_indiv=plot_indiv,
                                 passback=True)

### 2017-02-23 QPQ9/Figures/py/qpq9_figs.py

@@ -10,6 +10,7 @@ mpl.rcParams['font.family'] = 'stixgeneral'
 from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib import pyplot as plt
 import matplotlib.gridspec as gridspec
+from matplotlib.ticker import MaxNLocator
 
 from astropy.table import QTable, Table
 from astropy.io import ascii,fits
@@ -93,9 +94,9 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
                 sv_zfg.append(idict['qpq']['Z_FG'])
                 sv_gUV.append(idict['qpq']['G_UV'])
             if idict['qpq']['ZFG_LINE'] == '[OIII]':
-                sv_symsize.append(35)
-            else:
                 sv_symsize.append(70)
+            else:
+                sv_symsize.append(35)
 
         # Axes
         ax = plt.subplot(gs[kk,0])
@@ -137,15 +138,15 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
 def stacks_and_fits(outfil=None):
 
     if outfil is None:
-        outfil = 'fig_stack_and_fits.pdf'
-    fontsize = 15
+        outfil = 'fig_stacks_and_fits.pdf'
+    fontsize = 25
 
     # Lines
     lines = [1334.5323,1548.195,2796.354]*u.AA
 
     # Start the plot
     pp = PdfPages(outfil)
-    fig = plt.figure(figsize=(10,8))
+    fig = plt.figure(figsize=(10,10))
     fig.clf()
     gs = gridspec.GridSpec(len(lines),2)
 
@@ -230,7 +231,7 @@ def stack_z1(outfil=None):
 
     if outfil is None:
         outfil = 'fig_stack_z1.pdf'
-    fontsize = 30
+    fontsize = 35
 
     line = 2796.354*u.AA
 
@@ -269,6 +270,7 @@ def stack_z1(outfil=None):
     ax.text((ax.get_xlim()[1]-ax.get_xlim()[0])*0.05+ax.get_xlim()[0],
              (ax.get_ylim()[1]-ax.get_ylim()[0])*0.05+ax.get_ylim()[0],
              xai.ion_name(aline.data)+', $z\sim0.9$, mean',size=fontsize)
+    ax.yaxis.set_major_locator(MaxNLocator(nbins=5))
 
[…]

### 2017-02-25 QPQ9/qpq9_draft.tex
added figure of monte carlo simulation

@@
 difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
-environments of massive galaxies hosting quasars at $z\sim2$. We employ 195 projected quasar pairs 
+environments of massive galaxies hosting quasars at $z\sim2$. We employ 115 projected quasar pairs 
 to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
@@
 that these galaxies are surrounded by a massive, cool, and enriched circumgalactic medium 
-\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 195 background 
+\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 115 background 
 spectra that are paired with foreground quasars with precisely measured redshifts. Our primary 
@@
 
+\input{Tables/tab_sample.tex}
+%\input{tab_sample.tex}
+
 \begin{figure}
 \includegraphics[width=3in]{Figures/fig_experiment.pdf}
+%\includegraphics[width=3in]{f01.pdf}
 \caption{These panels summarize properties of the QPQ9 dataset. The QPQ survey selects 
@@
 only select pairs with $z_{\rm fg}$ measured by \cite{HewettWild10} using the \ion{Mg}{2}\,1800 
-emission-line. We reached a final sample size of 195. Figure~\ref{fig:experiment} summarizes the 
+emission-line. We reached a final sample size of 115. Figure~\ref{fig:experiment} summarizes the 
 experimental design. We refer the reader to previous QPQ publications for the details on the 
@@
 
-\input{Tables/tab_sample.tex}
-\input{Tables/tab_summ.tex}
-\input{Tables/tab_summ_OIII.tex}
-
 \section{Analysis}
@@
 \includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
+%\includegraphics[width=3.5in]{f02.pdf}
 \caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
@@
 included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
-lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$.  
+lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
+$1\sigma$ modeling error of the centroid and dispersion of the \ion{C}{2} mean stack is 
+$\approx35\,{\rm km\,s^{-1}}$, which is also the typical modeling errors of the other stacks. 
 }
@@
 
-[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]
+%[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]
 
@@
 toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
-allowing a constant pseudo-continuum level to vary. From the $\chi^2$ best-fit to the data, 
-we measure the centroid of the \ion{C}{2} stack to be $+170\,{\rm km\,s^{-1}}$ and 
-the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
-contradicts the standard expectation, while the dispersion suggests extreme kinematics. The 
-median stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid 
-closer to zero.
+allowing a constant pseudo-continuum level to vary. We perform $\chi^2$ minimization with each 
+channel by equal weight. From the best-fit to the data, we measure the centroid of the \ion{C}{2} 
+stack to be $+170\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. 
+The centroid suggests an asymmetry that contradicts the standard expectation, while the dispersion 
+suggests extreme kinematics. The median stack, on the other hand, shows weaker absorption, and the 
+Gaussian model has a centroid closer to zero.
 
@@
 
-\subsection{Significance of the asymmetric absorption}
-\label{sec:significance_+ve}
+\input{Tables/tab_summ.tex}
+%\input{tab_summ.tex}
+\input{Tables/tab_summ_OIII.tex}
+%\input{tab_summ_OIII.tex}
 
-\begin{figure*}[!h]
+\begin{figure*}[!th]
 \begin{minipage}[!bp]{0.35\textwidth}
 \includegraphics[width=\textwidth]{Figures/fig_stack_z1.pdf}
+%\includegraphics[width=\textwidth]{f03.pdf}
 \caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
@@
 \label{fig:stack_z1}
+\includegraphics[width=\textwidth]{Figures/fig_monte.pdf}
+%\includegraphics[width=\textwidth]{f07.pdf}
+\caption{The same \ion{C}{2} mean stack shown in the first panel of 
+Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
+the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
+Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
+analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
+shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
+data. The model has a smaller dispersion than the data by two times the modeling error.
+}
+\label{fig:monte}
 \end{minipage}%
@@
 \includegraphics[width=\textwidth]{Figures/fig_stacks_fg.pdf}
+%\includegraphics[width=\textwidth]{f04.pdf}
 \caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
@@
 \end{figure*}
+
+\subsection{Significance of the asymmetric absorption}
+\label{sec:significance_+ve}
 
@@
 0.6\,\AA\ well reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
-insensitive to the assumed equivalent width or line profile for one absorber. The resulting 
-stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, which is 
-smaller than the intrinsic dispersion in the data. We also test for the sensitivity of this 
+insensitive to the assumed equivalent width or line profile for one absorber. In 
+Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
+absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is 
+broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, 
+which is smaller than the intrinsic dispersion in the data by two times the $1\sigma$ modeling 
+error. We also test for the sensitivity of this 
 measured dispersion to the correlation functions adopted. The QPQ6 clustering analysis is 
@@
 In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
-velocity of $\approx280\,{\rm km\,s^{-1}}$ is required. Thus, the observed velocity width is 
-indicative of dynamical processes in addition to gravitational motions and Hubble flows.
+velocity of $\approx280\,{\rm km\,s^{-1}}$ is required. Thus, the observed velocity width suggests 
+a hint of dynamical processes in addition to gravitational motions and Hubble flows.
 
@@
 
-\begin{figure*}[!h]
+\begin{figure*}[!th]
 \begin{minipage}[!bp]{0.28\textwidth}
 \includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
+%\includegrpahics[width=\textwidth]{f05.pdf}
 \caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
@@
 \includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
+%\includegraphics[width=\textwidth]{f06.pdf}
 \caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
@@
 \acknowledgements
-[NSF grant number?]
 
-%JXP and MWL acknowledge support from the National
-%Science Foundation (NSF) grant AST-1010004 and AST-XX. 
-%JXP thanks the Alexander
-%von Humboldt foundation for a visitor fellowship to the MPIA where
-%part of this work was performed, as well as the staff at MPIA for
-%their hospitality during his visits.
-%JFH acknowledges generous support from the Alexander von Humboldt
-%foundation in the context of the Sofja Kovalevskaja Award. The
-%Humboldt foundation is funded by the German Federal Ministry for
-%Education and Research.
-
-%Much of the data presented herein were obtained at the W.M. Keck
-%Observatory, which is operated as a scientific partnership among the
-%California Institute of Technology, the University of California, and
-%the National Aeronautics and Space Administration. The Observatory was
-%made possible by the generous financial support of the W.M. Keck
-%Foundation.  Some of the Keck data were obtained through the NSF
-%Telescope System Instrumentation Program (TSIP), supported by AURA
-%through the NSF under AURA Cooperative Agreement AST 01-32798 as
-%amended.
-%
-%Some of the data herein were obtained at the Gemini Observatory, which
-%is operated by the Association of Universities for Research in
-%%Astronomy, Inc., under a cooperative agreement with the NSF on behalf
-%of the Gemini partnership: the NSF (United
-%States), the Science and Technology Facilities Council (United
-%Kingdom), the National Research Council (Canada), CONICYT (Chile), the
-%Australian Research Council (Australia), Minist\'{e}rio da
-%Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil) and Ministerio de
-%Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina). 
-%
-%The authors wish to recognize and acknowledge the very
-%significant cultural role and reverence that the summit of Mauna Kea
-%has always had within the indigenous Hawaiian community. We are most
-%fortunate to have the opportunity to conduct observations from this
-%mountain.
-%MWL thanks T.-K. Chan for a discussion on CGM simulations. MWL 
-%thanks Chi Po Choi for a discussion on statistics.
+JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1412981. The 
+authors gratefully acknowledge the support which enabled these observations at the Keck, Gemini, 
+Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar Observatories. MWL 
+thanks T.-K. Chan for a discussion on CGM simulations and Chi Po Choi for a discussion on 
+statistics.
 

### 2017-02-25 QPQ9/Figures/py/qpq9_figs.py

@@ -321,7 +321,10 @@ def stacks_fg(outfil=None):
         ax.tick_params(labelsize=fontsize,length=5,width=1)
         # Labels
         ax.set_ylabel('Normalized Flux')
-        ax.set_xlabel('Relative Velocity (km/s)')
+        if kk < len(lines)-1:
+            ax.set_xticklabels("",visible=False)
+        else:
+            ax.set_xlabel('Relative Velocity (km/s)')
         ax.text((ax.get_xlim()[1]-ax.get_xlim()[0])*0.05+ax.get_xlim()[0],
                 (ax.get_ylim()[1]-ax.get_ylim()[0])*0.05+ax.get_ylim()[0],
                 xai.ion_name(aline.data)+', f/g, mean',size=fontsize)
@@ -339,3 +342,67 @@ def stacks_fg(outfil=None):
     pp.savefig(bbox_inches='tight')
     pp.close()
     print('stacks_fg: Wrote {:s}'.format(outfil))
+
+# Overplot monte carlo simulation result on CII mean stack
+def monte(outfil=None):
+
+    if outfil is None:
+        outfil = 'fig_monte.pdf'
+    fontsize = 35
+
+    # Get line info
+    line = 1334.5323*u.AA
+    aline = AbsLine(line)
+
+    # Start the plot
+    pp = PdfPages(outfil)
+    fig = plt.figure(figsize=(10,6))
+    fig.clf()
+    gs = gridspec.GridSpec(1,1)
+
+    # Load the mean stack
+    path = '../Analysis/Stacks/'
+    mean_stack = fits.open(path+'Output/QPQ9_zIRMgII_1334_mean.fits')
+    relativistic_equiv = u.doppler_relativistic(line)
+    velo = (mean_stack[1].data*u.AA).to(u.km/u.s,equivalencies=relativistic_equiv)
+
+    # Load the monte carlo model parameters
+    monte_params = (ascii.read('../Analysis/monte.dat'))[0]
+    # Load the CII mean stack Gaussian fit model parameters
+    Gaussian_params = (ascii.read(path+'CII_MgII_mean_fit.dat'))[0]
+    model_conti = models.Const1D(amplitude=Gaussian_params['amplitude_0'])
+    model_gauss = models.GaussianAbsorption1D(
+        amplitude=Gaussian_params['amplitude_1'],mean=Gaussian_params['mean_1'],
[…]

### 2017-02-28 QPQ9/qpq9_draft.tex
Calculate scatters in bootstrap with Gaussian fitting

@@
 
-\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.2]}
+\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.4]}
 
@@
 background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
-\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large intrinsic velocity fields, and have velocity 
-centroids that show a small positive offset relative to the systemic. We argue the results can be 
-explained by outflowing gas combined with anisotropic or intermittent ionizing radiation of the 
-quasars. 
+\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large velocity widths, and have velocity 
+centroids that show a small positive offset relative to the systemic. We argue that a possible 
+explanation to the observed velocity fields is outflowing gas combined with anisotropic or 
+intermittent ionizing radiation of the quasars. 
 \end{abstract}
@@
 
-\begin{figure*}[!th]
-\begin{minipage}[!bp]{0.35\textwidth}
-\includegraphics[width=\textwidth]{Figures/fig_stack_z1.pdf}
-%\includegraphics[width=\textwidth]{f03.pdf}
+\begin{figure}
+\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
+%\includegraphics[width=2.5in]{f03.pdf}
 \caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
@@
 \label{fig:stack_z1}
-\includegraphics[width=\textwidth]{Figures/fig_monte.pdf}
-%\includegraphics[width=\textwidth]{f07.pdf}
-\caption{The same \ion{C}{2} mean stack shown in the first panel of 
-Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
-the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
-Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
-analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
-shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
-data. The model has a smaller dispersion than the data by two times the modeling error.
-}
-\label{fig:monte}
-\end{minipage}%
-\hspace{0.5in}
-\begin{minipage}[!bp]{0.55\textwidth}
-\includegraphics[width=\textwidth]{Figures/fig_stacks_fg.pdf}
-%\includegraphics[width=\textwidth]{f04.pdf}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
+%\includegraphics[width=3.4in]{f04.pdf}
 \caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
@@
 \label{fig:stacks_fg}
-\end{minipage}
-\end{figure*}
+\end{figure}
 
@@
 \label{sec:significance_width}
+
+\begin{figure}
+\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
+%\includegraphics[width=2.5in]{f07.pdf}
+\caption{The same \ion{C}{2} mean stack shown in the first panel of 
+Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
+the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
+Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
+analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
+shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
+data. The model has a smaller dispersion than the data by two times the modeling error.
+}
+\label{fig:monte}
+\end{figure}
 
@@
 In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
-velocity of $\approx280\,{\rm km\,s^{-1}}$ is required. Thus, the observed velocity width suggests 
+velocity of $\approx285\,{\rm km\,s^{-1}}$ is required. The observed velocity width thus suggests 
 a hint of dynamical processes in addition to gravitational motions and Hubble flows.
@@
 In conclusion, we observe large and positively skewed velocity fields in absorption, of metal ions 
-in the CGM of $z\sim2$ massive galaxies hosting quasars. We interpret the results as evidence that 
-the detected gas is outflowing, and that the quasars either shine anisotropically or 
+in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
+explained if the detected gas is outflowing, and the quasars either shine anisotropically or 
 intermittently.

### 2017-02-28 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py

@@ -12,16 +12,18 @@ import matplotlib.gridspec as gridspec
 from astropy.table import QTable
 from astropy.io import ascii, fits
 from astropy import units as u
+from astropy.modeling import models,fitting
 from xastropy.xutils import xdebug as xdb
 sys.path.append(os.path.abspath("../../../../py"))
 from enigma.qpq import stacks as qpqk
 
 #  Bootstrap one transition
-def boot_trans(wrest=None,outfil=None,nboot=10000,
-    cranges=None,
-    stack_tup=None,
-    median=False,
-    debug=False):
+def boot_trans(wrest=1334.5323*u.AA,full_sample=True,
+               outfil=None,nboot=10000,
+               cranges=None,
+               stack_tup0=None,
+               median=False,
+               debug=False):
     ''' Bootstrap on a single transition
 
     Parameters:
@@ -36,26 +38,33 @@ def boot_trans(wrest=None,outfil=None,nboot=10000,
     Outputs an image of the bootstraps
     '''
 
-    # Rest wavelength
-    if wrest is None:
-        wrest = 1334.5323*u.AA
-
-    # Continuum ranges
-    if cranges is None:
-        cranges = [(-3000.,-1300.)*u.km/u.s,(1300.,3000.)*u.km/u.s]
-    EW_range = (cranges[0][1],cranges[1][0])
-
     if outfil is None:
         outfil = 'Output/boot_{:d}.fits'.format(int(wrest.value))
 
     # For convenience            
-    fin_velo, stck_img, stck_msk, all_dict = stack_tup
+    fin_velo, stck_img0, stck_msk0, all_dict0 = stack_tup0
+    stck_msk = np.zeros(len(fin_velo))
+    stck_img = np.zeros(len(fin_velo))
+    all_dict = []
+    for ii,idict in enumerate(all_dict0):
+        if idict is None:
+            continue
+        if np.sum(stck_msk0[ii,:]) == 0:
+            continue
+        stck_msk = np.vstack([stck_msk,stck_msk0[ii,:]])
+        stck_img = np.vstack([stck_img,stck_img0[ii,:]])
+        all_dict.append(idict)
+    stck_msk = stck_msk[1:,:]
+    stck_img = stck_img[1:,:]
+    stack_tup = fin_velo,stck_img,stck_msk,all_dict
+
     boot_list = [item for item in stack_tup]
 
[…]

### 2017-03-01 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py
small changes

@@ -102,7 +102,7 @@ def boot_trans(wrest=1334.5323*u.AA,full_sample=True,
             g1548_init = models.GaussianAbsorption1D(amplitude=g1548_amp,mean=g1548_mean,stddev=g1548_stddev)
             g1550_init = models.GaussianAbsorption1D(amplitude=g1550_amp,mean=g1550_mean,stddev=g1550_stddev)
             model_init = c_init*g1548_init*g1550_init
-#            model_init.amplitude_1.bounds = [0.,1.]
+            model_init.amplitude_1.bounds = [0.,1.]
             def tie_mean2(model):
                 mean_2 = model.mean_1 + 498.
                 return mean_2

### 2017-03-03 QPQ9/qpq9_draft.tex
draft version 1.4

@@
 
-\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.4]}
+\title{Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding 
+$z\sim2$ Quasars [v1.4]}
 
@@
 \begin{abstract}
-Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
-difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
-environments of massive galaxies hosting quasars at $z\sim2$. We employ 115 projected quasar pairs 
-to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
-have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
-background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
-\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large velocity widths, and have velocity 
+We examine the kinematics of the gas in the environments of massive galaxies hosting quasars at 
+$z\sim2$. We employ 112 projected quasar pairs to study the circumgalactic gas of the foreground 
+quasars in absorption. The foreground quasars have precise redshift measurements, using 
+emission-lines with uncertainty $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
+systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
+foreground quasar's systemic redshift. The mean absorption in \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large velocity widths, and have velocity 
 centroids that show a small positive offset relative to the systemic. We argue that a possible 
@@
 \label{sec:introduction}
-%\begin{itemize}
-%\item Flows
-%\item Mass (Kaiser, Schaye)
-%\item Directionality/symmetry
-%\item Break the symmetry
-%\end{itemize}
 
-Galaxy formation and evolution are driven by the flows into and out of their interstellar medium. 
-Current theories demand that star-forming galaxies maintain these flows. Gas accretes, cools, and 
-adds to the fuel supply, while star formation feedback heats gas, blows it out of galaxies, and 
-regulates star formation \citep[for a review see][]{SomervilleDave15}.
+Galaxy formation and evolution are driven by the flows of gas into and out of their interstellar 
+medium. Current theories demand that star-forming galaxies maintain these flows. Gas accretes, 
+cools, and adds to the fuel supply, while star formation feedback heats gas, blows it out of 
+galaxies, and regulates star formation \citep[for a review see][]{SomervilleDave15}.
 
-Direction observations of galactic flows are difficult to acquire. Detecting the presence of 
+Direct observations of galactic flows are difficult to acquire. Detecting the presence of 
 the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for 
@@
 the kinematics and establishing the mass flux pose an even greater challenge. These challenges are 
-accentuated for distant, young galaxies, where flows are predicted to prevail 
+accentuated for distant, young galaxies, where flows of gas are predicted to prevail 
 \citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions, 
@@
 to detect and characterize the gas surrounding galaxies 
-\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}. With this 
-experiment, researchers have had success in characterizing the large-scale flows around 
-star-forming galaxies to reveal a net inflow, or a Kaiser effect for gas \citep{Rakic+12}.
+\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}. 
+In a previous paper of the Qussars Probing Quasars series\citep[][QPQ8]{QPQ8}, we 
+measured the velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the 
+circumgalactic medium frequently exhibits large velocity widths that are offset from the systemic 
+redshift. The offsets, $\delta v$, are often positive, with the sign convention that positive 
+velocities indicate a redshift from the systemic. From a sample of 7 \ion{C}{2} systems and 10 
+\ion{C}{4} systems, we measured the velocity interval that encompasses 90\% of the total optical 
+depth, $\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$. 
+The median $\Delta v_{90}$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is 
+$342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for 
+\ion{C}{2}\,1334 and is $495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed 
+all previous measurements from galaxies and/or absorption systems at any epoch.
 
-A significant limitation of absorption-line analysis, especially regarding galactic flows, 
-is the inherent symmetry of the experiment. One generally lacks any constraint on the distance of 
-the gas along the sightline. Positive or negative velocities with respect to the galaxy may be 
-interpreted as gas flowing either toward or away from the system. ``Down-the-barrel'' observations 
-break this symmetry, and have generally provided evidence for flows away from galaxies 
-\citep{Rupke+05,Martin05,Weiner+09,Rubin+14}. However, these data are frequently at low spectral 
-resolution which limits one's sensitivity to inflowing gas.
+With absorption-line spectroscopy of background sightlines, other researchers also have had 
+success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
+large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on on 
+1\textendash2\,Mpc scales. \cite{Johnson+15} studied the CGM surrounding $z\sim1$ quasars, and 
+found large peculiar motions in the gas exceeding the expected virial velocity, which they 
+interpret as quasar-driven outflows. However, the velocity spreads were not well quantified. Other 
+existing studies that found large velocity spreads are limited to single sightlines with most of 
+the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11}, or with gas tracing 
+a higher ionization state than the QPQ absorption systems\citep[e.g., ][]{Churchill+12}, or where 
+the average velocity spread is smaller than that measured in QPQ8 
+\citep[e.g., ][]{Gauthier13,Muzahid+15,Zahedy+16}.
+
+A significant limitation of absorption-line analysis of transverse sightlines, especially 
+regarding galactic-scale flows, is the inherent symmetry of the experiment. One generally lacks 
+any constraint on the distance of the gas along the sightline. Positive or negative velocities 
+with respect to the galaxy may be interpreted as gas flowing either toward or away from the 
+system. ``Down-the-barrel'' observations break this symmetry, and have generally provided evidence 
+for flows away from galaxies \citep{Rupke+05,Martin05,Weiner+09,Rubin+14}. However, these data are 
+frequently at low spectral resolution which limits one's sensitivity to inflowing gas.
 
@@
 galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
-\citep[][QPQ1]{QPQ1} to use the 
-standard technique of absorption-line spectroscopy with background quasars. These quasar pairs 
+\citep[][QPQ1]{QPQ1} to use the standard technique of absorption-line spectroscopy with background 
+quasars. These quasar pairs 
 have angular separations that correspond to less than 300\,kpc projected separation at the 
 foreground quasar's redshift. Our previous publications from these quasar pairs have established 
-that these galaxies are surrounded by a massive, cool, and enriched circumgalactic medium 
-\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 115 background 
-spectra that are paired with foreground quasars with precisely measured redshifts. Our primary 
+that these galaxies are surrounded by a massive, cool, and enriched CGM 
+\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 112 background 
+spectra that are paired with foreground quasars with precisely measured redshifts. 
+Among the sightlines in the QPQ9 sample, 13 have spectral resolution $> 5000$ from echellette or 
+echelle observations, and have been analyzed separately in QPQ8. Our primary 
 scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
 central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
-(ii) characterize the dynamics of galactic flows around these massive system. We further describe 
-an aspect of this experiment that offers a unique opportunity to study galactic flows: we argue 
-that, the anisotropic or intermittent radiation of the foreground quasars breaks the symmetry in 
-the velocity field of circumgalactic absorbers.
-
-Among the sightlines in the QPQ9 sample, 13 have spectral resolution $> 5000$ from echellette or 
-echelle observations, and have been analyzed separately in QPQ8 \citep{QPQ8}. We measured the 
-velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the CGM frequently exhibits 
-large flows that are offset from the systemic redshift. The offsets, $\delta v$, are often 
-positive, with the sign convention that positive velocities are flowing away from the observer. 
-From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4} systems, we measured the velocity 
-interval that encompasses 90\% of the total optical depth, $\Delta v_{90}$, and the $1\sigma$ 
-dispersion relative to the profile centroid, $\sigma_v$. The median $\Delta v_{90}$ is 
-$555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is $342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. 
-The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is 
-$495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed all previous 
-measurements from galaxies and/or absorption systems at any epoch.
+(ii) characterize the dynamics of flows of gas around these massive system. We further describe 
+an aspect of this experiment that offers a unique opportunity to study galactic-scale flows: we 
+argue that, the anisotropic or intermittent radiation of the foreground quasars may break the 
+symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation field is 
+asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar 
+lifetime will result in different radiation fields impinged on the gas closer to versus 
+further away from the background quasar, due to different light travel times.
 
@@
 $z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
-\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
-$400\,{\rm km\,s^{-1}}$ or better. 
-[\ion{O}{3}] emission-line redshifts have the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about 
-the systemic redshift, and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
-The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
-redshift \citep{Boroson05}, which has been added when we compute the 
-redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
-$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
-$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 
-\citep{QPQ8}, we have quantified the precision of H$\alpha$ and H$\beta$ to be 
-$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. We further add to the QPQ 
-dataset with quasar pairs selected from the public dataset of 
+\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, or H$\alpha$ emission, giving a precision of 
+$300\,{\rm km\,s^{-1}}$ or better and an average offset from the systemic redshift of 
+$|100\,{\rm km\,s^{-1}}|$ or less. According to \citep{Shen+16}, the [\ion{O}{3}] emission-line 
+redshifts have the smallest total scatter (due to intrinsic scatter and measurement error) of 
+$68\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the sub-sample with 
+[\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift of 
+$48\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
+redshift of the line. The scatter and average offset of [\ion{O}{3}] redshifts reported by 
+\cite{Shen+16} is consistent with the numbers reported by \cite{Boroson05} using a larger but 
+lower redshift sample. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
+$226\,{\rm km\,s^{-1}}$ according to \cite{Shen+16}, and we have taken into account their 
+reported median blueshift of $57\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from the systemic. We note that 
+\cite{Richards+02} reported a median redshift of $97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from 
+[\ion{O}{3}] using a larger but lower redshift sample. In QPQ8 \citep{QPQ8}, we quantified 
+the precision of H$\alpha$ to be $300\,{\rm km\,s^{-1}}$ and the median offset from the systemic 
+redshift is close to zero, consistent with the velocity shifts measured by \cite{Shen+11}. 
+Although H$\beta$ is a narrow emission-line, we do not consider its redshift sufficiently reliable 
+for use as systemic redshift. H$\beta$ redshifts have a large scatter about the systemic 
+$\approx400\,{\rm km\,s^{-1}}$, and a large average offset about the systemic 
+$\approx100\,{\rm km\,s^{-1}}$ \citep[][; QPQ8]{Shen+16}. 
+We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
 igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
 catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
-Twelfth Data Release \citep{Paris+17}. We 
-only select pairs with $z_{\rm fg}$ measured by \cite{HewettWild10} using the \ion{Mg}{2}\,1800 
-emission-line. We reached a final sample size of 115. Figure~\ref{fig:experiment} summarizes the 
-experimental design. We refer the reader to previous QPQ publications for the details on the 
-redshift centroiding algorithm, data reduction, and continuum normalization (QPQ6; QPQ8).
+Twelfth Data Release \citep{Paris+17}. We only select pairs with $z_{\rm fg}$ measured by 
+\cite{HewettWild10} using the \ion{Mg}{2}\,2800 emission-line, and we add the median blueshift of 
+\ion{Mg}{2} from the systemic to these redshifts. We reached a final sample size of 112. 
+Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
+QPQ publications for the details on the redshift centroiding algorithm, data reduction, and 
+continuum normalization (QPQ6; QPQ8).
 
@@
 maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame 
-\AA \ is 
-necessary for properly estimating the continuum, as well as identifying mini-broad absorption line 
-systems associated to the background quasar, which will significantly depress the flux level. We 
-also require that the region of the spectrum that is $\pm3000\,{\rm km\,s^{-1}}$ around a 
-considered metal ion transition does not overlap with strong atmospheric ${\rm O}_2$ bands. 
-The ${\rm O}_2$ A- and B-band span 7595\textendash7680\,\AA \ and 6868\textendash6926\,\AA \ 
-respectively.
+\AA \ is necessary for properly estimating the continuum, as well as identifying mini-broad 
+absorption line systems associated to the background quasar, which will significantly depress the 
+flux level. We also require that the region of the spectrum that is $\pm3000\,{\rm km\,s^{-1}}$ 
+around a considered metal ion transition does not overlap with strong atmospheric ${\rm O}_2$ 
+bands. The ${\rm O}_2$ A- and B-band span 7595\textendash7680\,\AA \ and 6868\textendash6926\,\AA 
+\ respectively.
 
-Table~\ref{tab:sample} lists the full QPQ9 sample. 
-In Table~\ref{tab:summary}, we list the sample size, the median $z_{\rm fg}$, and the median 
-$R_\perp$ of the quasar pairs that survive the above selection criteria for \ion{C}{2}\,1334, 
-\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively. In Table~\ref{tab:summary_OIII}, we provide 
-the summary for the sub-sample with $z_{\rm fg}$ measured from [\ion{O}{3}].
+Table~\ref{tab:sample} lists the full QPQ9 sample. In Table~\ref{tab:summary}, we first list the 
+sample size, the median $z_{\rm fg}$, and the median $R_\perp$ of the quasar pairs that survive 
+the above selection criteria for \ion{C}{2}\,1334, \ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 
+respectively. We then provide the summary for the sub-sample with $z_{\rm fg}$ measured from 
+[\ion{O}{3}].
 
@@
 \label{sec:analysis}
+
+\subsection{Stacked Profiles}
+\label{sec:stacks}
 
@@
 has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
-$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unncessary to smooth the data to a 
-common spectral resolution. The individual spectra are then combined with a mean or a median 
+$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to 
+a common spectral resolution. The individual spectra are then combined with a mean or a median 
 statistic. Bad pixels in the individual spectra have been masked before generating the 
@@
 metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
-than error sources. The mean statistic of the individual spectra yields a good estimate of the 
-average absorption and preserves equivalent width. The median statistic is less sensitive to 
-outliers, however the averaged equivalent width is smaller and the analysis on the velocity field 
-becomes more uncertain. In the following we present stacked spectra using both the mean and the 
-median statistic.
-
-%[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]
+than scatter in the flux of individual observations. The mean statistic of the individual spectra 
+yields a good estimate of the average absorption and preserves equivalent width. The median 
+statistic is less sensitive to outliers, however the averaged equivalent width is smaller and the 
+analysis on the velocity field becomes more uncertain. In the following we present stacked spectra 
+using both the mean and the median statistic.
 
@@
 analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
-and it is more challenging to interpret their kinematics, while the median stacks have smaller 
-equivalent widths.
-
+and it is more challenging to interpret their kinematics.
 %To assess the average absorption of these transitions,
@@
 %[Comnent on EW from 'standard' technique]
-
 Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
-exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is skewed 
-toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
+exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
+skewed toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
 allowing a constant pseudo-continuum level to vary. We perform $\chi^2$ minimization with each 
-channel by equal weight. From the best-fit to the data, we measure the centroid of the \ion{C}{2} 
-stack to be $+170\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. 
-The centroid suggests an asymmetry that contradicts the standard expectation, while the dispersion 
-suggests extreme kinematics. The median stack, on the other hand, shows weaker absorption, and the 
-Gaussian model has a centroid closer to zero.
+channel given equal weight. From the best-fit to the data, we measure the centroid of the 
+\ion{C}{2} stack to be $+208\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be 
+$312\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the standard 
+expectation, while the dispersion suggests extreme kinematics. The median stack, on the other 
+hand, shows weaker absorption, and the Gaussian model has a centroid closer to zero.
 
@@
 absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
-$+207\,{\rm km\,s^{-1}}$, and a dispersion of $355\,{\rm km\,s^{-1}}$, consistent with the full 
+$+239\,{\rm km\,s^{-1}}$, and a dispersion of $349\,{\rm km\,s^{-1}}$, consistent with the full 
 sample.
@@
 
-The above analyses are summarized in Table~\ref{tab:summary} and Table~\ref{tab:summary_OIII}. The 
+The above analyses are summarized in Table~\ref{tab:summary}. The 
 Gaussian models normalized to pseudo-continuum are overplotted on the data stacks in 
@@
 
-\input{Tables/tab_summ.tex}
-%\input{tab_summ.tex}
-\input{Tables/tab_summ_OIII.tex}
-%\input{tab_summ_OIII.tex}
+\input{Tables/tab_summary.tex}
+%\input{tab_summary.tex}
+
+\begin{figure}
+\subsection{Interpretation of the asymmetric absorption}
+\label{sec:significance_+ve}
+
+\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
+%\includegraphics[width=2.5in]{f03.pdf}
+\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
+for the \ion{C}{2} mean stack. 98\% of the centroids are positively offset from $z_{\rm fg}$.}
+\label{fig:histogram_cen}
+\end{figure}
 
@@
 \includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
-%\includegraphics[width=2.5in]{f03.pdf}
+%\includegraphics[width=2.5in]{f04.pdf}
 \caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
@@
 
-\begin{figure}
-\includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
-%\includegraphics[width=3.4in]{f04.pdf}
-\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
-\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
-excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
-absorbers at all distances, shows a large, blueshifted mean velocity field.
-}
-\label{fig:stacks_fg}
-\end{figure}
-
-\subsection{Significance of the asymmetric absorption}
-\label{sec:significance_+ve}
-
 Given the small sample size, one must scrutinize the statistical significance of the measured 
 velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
-randomly sampling from the full sample 10000 times. We measure the flux-weighted centroid of each 
-bootstrap realization, and quote the standard deviation in the bootstrap realizations to be the 
-scatter in the centroid of the data. The scatters $\approx100\,{\rm \,s^{-1}}$ are comparable 
-to the measured offsets, indicating large intrinsic variation in quasar CGM environments (see 
-also QPQ8). Given the large intrinsic scatter, we do not attempt to explore whether there exists 
-relative asymmetry between \ion{C}{2} and \ion{C}{4} absorption due to different ionization 
-potentials.
+randomly sampling from the full sample 10000 times. We introduce a Gaussian absorption profile to 
+model each bootstrap realization, and quote the standard deviation in the the bootstrap 
+realizations to be the scatter in the centroid of the data. The scatters 
+$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
+variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show 
+the distribution of the absorption centroids of the bootstrap realizations. We find that 98\% of 
+the centroids are at positive velocities. We place a generous $3\sigma$ upper limit to the small 
+offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
+$\delta v<+451\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore 
+whether there exists relative asymmetry between \ion{C}{2} and \ion{C}{4} absorption due to 
+different ionization potentials.
 
@@
 less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
-stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2}, H$\alpha$, or 
-H$\beta$ redshift. We are able to replace for 13 out of the 14 systems with [\ion{O}{3}] redshifts 
-in the original sample. The new stack is similiar in velocity structure and again shows a positive 
-offset. We thus conclude that our algorithm for measuring redshifts is not severely biased by 
-the blue wing of the [\ion{O}{3}] emission-line.
+stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2} or H$\alpha$ 
+redshift when available. We are able to replace for 8 out of the 14 systems with [\ion{O}{3}] 
+redshifts in the original sample. The new stack is similiar in velocity structure and again shows 
+a positive offset $\approx+240\,{\rm km\,s^{-1}}$. We thus conclude that our algorithm for 
+measuring redshifts is not severely biased by the blue wing of the [\ion{O}{3}] emission-line.
 
-We also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs, 
-using the same selection criteria as the main QPQ9 sample. The quasar pairs are selected from the 
-igmspec database, with $z_{\rm fg}$ measured by \cite{HewettWild10}. There are 231 pairs selected, 
-with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present the mean and 
-median stacks in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
+Motivated by the study of \ion{Mg}{2} absorbers surrounding $z\sim1$ quasars by \cite{Johnson+15}, 
+we also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs.  
+We select quasars with $0.4<z_{\rm fg}<1.6$ and use the same other selection criteria as the main 
+QPQ9 sample. The quasar pairs are selected from the igmspec database, with $z_{\rm fg}$ measured 
+by \cite{HewettWild10}. For quasars with $z_{\rm fg}<0.84$, as redshift determination is dominated 
+by [\ion{O}{3}] emission, a shift of $+48\,{\rm km\,s^{-1}}$ is applied to bring the emission-line 
+redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is 
+dominated by \ion{Mg}{2} emission, a shift of $57\,{\rm km\,s^{-1}}$ is applied. There are 231 
+pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present 
+the mean tack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
 sample. Gaussian absorption models fitted to the stack recover a centroid of 
-$47\pm122\,{\rm km\,s^{-1}}$ and a dispersion of $119\,{\rm km\,s^{-1}}$. The offsets from 
-$0\,{\rm km\,s^{-1}}$ are smaller than the offsets in the $z\sim2$ sample.
+$-13\pm410\,{\rm km\,s^{-1}}$ and a dispersion of $155\,{\rm km\,s^{-1}}$. The average offset 
+from $0\,{\rm km\,s^{-1}}$ is smaller than the offsets in the $z\sim2$ sample.
 
-Since the large scatters in the centroids represent intrinsic variation rather than redshift 
-errors, and the \ion{Mg}{2} stack for lower redshift does not suggest a similar offset, the hint 
-of asymmetry cannot be ignored. In the Discussion section, we discuss two possible explanations 
-for the asymmetry.
+Since the large scatter in the centroids represent intrinsic variation rather than redshift 
+errors, and the \ion{Mg}{2} stack for lower redshift does not suggest a similar offset, we 
+consider that the asymmetry signal in the $z\sim2$ sample is likely to be real. In the Discussion 
+section, we discuss two possible explanations for the asymmetry.
 
-%Indeed, a small offset $mdv < 10 kms$ may be expected even with large samples.
-
-\subsection{Significance of the large velocity fields}
+\subsection{Interpretation of the large velocity fields}
 \label{sec:significance_width}
@@
 \includegraphics[width=2.5in]{Figures/fig_monte.pdf}
-%\includegraphics[width=2.5in]{f07.pdf}
+%\includegraphics[width=2.5in]{f05.pdf}
 \caption{The same \ion{C}{2} mean stack shown in the first panel of 
-Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
-the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
-Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
-analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
-shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
-data. The model has a smaller dispersion than the data by two times the modeling error.
+Figure~\ref{fig:stacks_and_fits} is shown in thick, black. In thin, green, we overplot the 
+Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering 
+argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the 
+stack of the observational data, shifted to the centroid of the stack of the data, and broadened 
+by the mean redshift error in the data. The model is a good description of the data, with a 
+dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
+absorption profile with $\sigma_v=658\,{\rm km\,s^{-1}}$. Motions that produce this width are 
+ruled out at $3\sigma$ confidence by bootstrap analysis on the observational data. 
 }
@@
 quadrature to give the observed width, we solve for the intrinsic dispersion in the \ion{C}{2} 
-mean stacks. For the full sample, the mean $\sigma_{\rm error}^{\rm full}=224\,{\rm km\,s^{-1}}$ 
-and we recover $\sigma_{\rm intrinsic}^{\rm full}=317\,{\rm km\,s^{-1}}$. For the sub-sample with 
-$z_{\rm fg}$ measured from [\ion{O}{3}], we recover 
-$\sigma_{\rm intrinsic}^{\rm [OIII]}=352\,{\rm km\,s^{-1}}$. In QPQ8, we reported the 
-line-of-sight velocity dispersion typical of QPQ dark matter halo mass is 
-$\sigma_{\rm 1D}=212\,{\rm km\,s^{-1}}$. We can investigate whether gravitational motions and 
-Hubble flows are sufficient to reproduce the dispersion in the \ion{C}{2} mean stack using Monte 
-Carlo methods.
+mean stack. For the full QPQ9 sample, with the mean 
+$\sigma_{\rm error(z)}^{\rm full}=182\,{\rm km\,s^{-1}}$, we recover 
+$\sigma_{\rm intrinsic}^{\rm full}=253\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
+redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=342\,{\rm km\,s^{-1}}$. In QPQ8, we 
+reported the line-of-sight velocity 
+dispersion typical of QPQ dark matter halo mass is $\sigma_{\rm 1D}=212\,{\rm km\,s^{-1}}$. We can 
+investigate whether gravitational motions and Hubble flows are sufficient to reproduce the 
+dispersion in the \ion{C}{2} mean stack using Monte Carlo methods.
 
@@
 $\xi_{\rm QA}^{\rm DLA}(r)=(r/(3.9\,h^{-1}\,{\rm Mpc}))^{-1.6}$. 
-For each quasar pair, we calculate the expected number of all optically thick absorbers within 
+For each quasar pair, we calculate the expected number of optically thick absorbers within 
 $\pm3000\,{\rm km\,s^{-1}}$ at a distance $R_\perp$ from the foreground quasar and at 
@@
 assigned additional peculiar velocities drawn from a normal distribution with mean equal to 
-$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we 
-assume a rest equivalent width for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
-above procedure for all 34 quasar pairs, and create a mean stack of the 34000 mock spectra 
+$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we assume a rest 
+equivalent width $W_{\rm CII}$ for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
+above procedure for all 32 quasar pairs, and create a mean stack of the 32000 mock spectra 
 generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
-the stack of mock spectra. We adjust the rest equivalent width adopted for the \ion{C}{2} 
-absorbers until the ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
-amplitude of the stack of the observational data. We find that a rest equivalent width of 
-0.6\,\AA\ well reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
-insensitive to the assumed equivalent width or line profile for one absorber. In 
+the stack of mock spectra. We adjust the $W_{\rm CII}$ adopted for the absorbers until the 
+ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
+amplitude of the stack of the observational data. We find that $W_{\rm CII}=0.7\,{\rm \AA}$ well 
+reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
+insensitive to the assumed $W_{\rm CII}$ or line profile for one absorber. In 
 Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
@@
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, 
-which is smaller than the intrinsic dispersion in the data by two times the $1\sigma$ modeling 
-error. We also test for the sensitivity of this 
-measured dispersion to the correlation functions adopted. The QPQ6 clustering analysis is 
-performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ sightline may in 
-fact intercept more than one optically thick absorber. We double the number of absorbers for each 
-mock sightline, and find the measured dispersion only increases by several ${\rm km\,s^{-1}}$. 
-In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
-velocity of $\approx285\,{\rm km\,s^{-1}}$ is required. The observed velocity width thus suggests 
-a hint of dynamical processes in addition to gravitational motions and Hubble flows.
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $244\,{\rm km\,s^{-1}}$. This is 
+within $1\sigma$ modeling error of the intrinsic dispersion in the \ion{C}{2} mean stack for the 
+full sample, and about 3 times larger than the modeling error of the intrinsic 
+dispersion in the stack of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
+sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering 
+analysis is performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ 
+sightline may in fact intercept more than one optically thick absorber. We double the number of 
+absorbers for each mock sightline, and find the measured dispersion only increases by several 
+${\rm km\,s^{-1}}$. Thus, the hypothesis that the observed velocity width is only produced by a 
+combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical 
+processes are not necessary to explain the large velocity fields. From the bootstrap analysis of 
+the observed dispersion, a width of $\sigma_v>658\,{\rm km\,s^{-1}}$ is ruled out at 3$\sigma$ 
+confidence (overplotted in Figure~\ref{fig:monte}). In other words, motions in additional to 
+gravitational and Hubble flows that will produce $\sigma_v>611\,{\rm km\,s^{-1}}$ are ruled out.
+
+\subsection{Line-of-sight absorption}
+\label{sec:los_stacks}
+
+\begin{figure}
+\includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
+%\includegraphics[width=3.4in]{f06.pdf}
+\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
+\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, the mean absorption is 
+weaker than that in the background stacks, and there is no evidence for an excess at $z_{\rm fg}$. 
+The stack for \ion{C}{4}, which include line-of-sight absorbers at all distances, shows a large, 
+blueshifted mean velocity field.
+}
+\label{fig:stacks_fg}
+\end{figure}
 
 In the previous QPQ papers, we argued that optically thick absorbers in the vicinity of quasars 
-are distributed anisotropically. In Figure~\ref{fig:stacks_fg}, we present mean stacks of 
-foreground quasar spectra for the pairs in the QPQ9 sample. We require that the spectra survive a 
-S/N cut of 5.5 per rest-frame \AA\ at \ion{C}{2}\,1334, \ion{C}{4}\,1548, or \ion{Mg}{2}\,2796 at 
-$z_{\rm fg}$. In constrast to the large equivalent widths exhibited in the stacks of background 
-spectra, \ion{C}{2} and \ion{Mg}{2} do not show excess mean absorption at $z_{\rm fg}$ in the 
-stacks of foreground quasar spectra. This supports a scenario where the ionizing radiation of the 
-foreground quasars are anisotropic or intermittent. For \ion{C}{4}\,1548, this stack of all 
-line-of-sight absorbers, which include absorbers intrinsic to and far away from the quasar, shows 
-a large, blueshifted velocity field.
+are distributed anisotropically. We now have the means to show this anisotropic clustering 
+explicitly. Given that the techniques for stacking spectra are established, it is straightforward 
+to apply the same techniques to stack the foreground quasar spectra. In 
+Figure~\ref{fig:stacks_fg}, we present mean stacks of foreground quasar spectra for the pairs in 
+the QPQ9 sample. We require that the spectra survive a S/N cut of 5.5 per rest-frame \AA\ at 
+\ion{C}{2}\,1334, \ion{C}{4}\,1548, or \ion{Mg}{2}\,2796 at $z_{\rm fg}$. In constrast to the 
+large equivalent widths exhibited in the stacks of background spectra, \ion{C}{2} and \ion{Mg}{2} 
+mean absorption along the line-of-sight to the foreground quasars is weaker, and an excess at 
+$z_{\rm fg}$ is absent. This supports a scenario where the ionizing radiation of the foreground 
+quasars are anisotropic and/or intermittent. For \ion{C}{4}\,1548, this stack of all line-of-sight 
+absorbers, which include absorbers intrinsic to and far away from the quasar, shows a large, 
+blueshifted velocity field.
 
@@
 \includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
-%\includegrpahics[width=\textwidth]{f05.pdf}
+%\includegrpahics[width=\textwidth]{f07.pdf}
 \caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
@@
 \includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
-%\includegraphics[width=\textwidth]{f06.pdf}
+%\includegraphics[width=\textwidth]{f08.pdf}
 \caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
@@
 
-Given the large intrinsic scatter, we place generous upper limits to the small offset of the 
-centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption. For the full QPQ9 sample, the 
-$3\sigma$ upper limit is $\delta v<+485\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
-redshifts, $\delta v<+426\,{\rm km\,s^{-1}}$. In the following, we explore two possible 
-explanations for the putative non-dynamical process that provides the asymmetry.
+In the following, we explore two possible explanations for the putative non-dynamical process that 
+provides the asymmetry.
 
@@
 outflow speeds of $500\textendash700\,{\rm km\,s^{-/1}}$ and quasar opening angles of 
-$100^\circ\textendash120^\circ$ may reproduce the observed centroid and intrinsic dispersion of 
-the \ion{C}{2} mean absorption. 
-The first explanation above to asymmetric absorption requires that the quasars emit their ionizing 
-radiation anisotropically, while the second explanation requires the quasars emit their ionizing 
-radiation intermittently. Both explanations will require the gas to be either outflowing or in 
-Hubble flow. Were the gas inflowing instead, the velocity centroid would be negative. 
-\cite{KirkmanTytler08} reported an asymmetry in \ion{H}{1} absorption on scales larger than 
-the CGM, and gave similar arguments on anisotropy or intermittence. We are assembling a sample of 
-quasar pairs with precise 
-$z_{\rm fg}$ measurements to study this asymmetry in \ion{H}{1} (J. F. Hennawi et al. 2017, in 
-preparation).
+$120^\circ\textendash140^\circ$ may reproduce the observed centroid and intrinsic dispersion of 
+the \ion{C}{2} mean absorption. The first explanation above to asymmetric absorption requires that 
+the quasars emit their ionizing radiation anisotropically, while the second explanation requires 
+the quasars emit their ionizing radiation intermittently. Both explanations will require the gas 
+to be either outflowing or in Hubble flow. Were the gas inflowing instead, the velocity centroid 
+would be negative. \cite{KirkmanTytler08} reported an asymmetry in \ion{H}{1} absorption on scales 
+larger than the CGM, and gave similar arguments on anisotropy or intermittence. We are assembling 
+a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study this asymmetry in 
+\ion{H}{1} (J. F. Hennawi et al. 2017, in preparation).
 
@@
 in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
-explained if the detected gas is outflowing, and the quasars either shine anisotropically or 
-intermittently.
+explained if the detected gas is in gravitational motion, Hubble flow, or outflow, and the quasars 
+either shine anisotropically or intermittently.
 

### 2017-03-03 QPQ9/Figures/py/qpq9_figs.py

@@ -28,7 +28,7 @@ import qpq9_stacks as qpq9k
 
 #  Plot the Experiment
 def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2N_cut=5.5/u.AA,
-               zfg_mnx=(1.6,9999)):
+               zfg_mnx=(1.6,9999),vsig_cut=400*u.km/u.s):
 
     if outfil is None:
         outfil = 'fig_experiment.pdf'
@@ -59,7 +59,8 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
         aline = AbsLine(line)
 
         # Load stack_tup
-        stack_tup0 = qpq9k.qpq9_IRMgII(passback=True,wrest=line,S2N_cut=S2N_cut,zfg_mnx=zfg_mnx,plot_indiv=False)
+        stack_tup0 = qpq9k.qpq9_IRMgII(passback=True,wrest=line,S2N_cut=S2N_cut,zfg_mnx=zfg_mnx,
+                                       vsig_cut=400*u.km/u.s,plot_indiv=False)
         # Mask
         fin_velo, stck_img, stck_msk, all_dict = stack_tup0
         stck_mskN = copy.deepcopy(stck_msk)
@@ -176,11 +177,14 @@ def stacks_and_fits(outfil=None):
         # Axes
         ax = plt.subplot(gs[kk,0])
         ax.set_xlim(-2500,2500)
-        ax.set_ylim(0.79,1.03)
+        ax.set_ylim(0.82,1.03)
         ax.tick_params(labelsize=fontsize,length=5,width=1)
         # Labels
         ax.set_ylabel('Normalized Flux')
-        ax.set_xlabel('Relative Velocity (km/s)')
+        if kk < len(lines)-1:
+            ax.set_xticklabels("",visible=False)
+        else:
+            ax.set_xlabel('Relative Velocity (km/s)')
         ax.text((ax.get_xlim()[1]-ax.get_xlim()[0])*0.05+ax.get_xlim()[0],
                 (ax.get_ylim()[1]-ax.get_ylim()[0])*0.05+ax.get_ylim()[0],
                 xai.ion_name(aline.data)+', mean',size=fontsize)
@@ -209,7 +213,10 @@ def stacks_and_fits(outfil=None):
         ax.set_xlim(-2500,2500)
         ax.set_ylim(0.79,1.03)
[…]

### 2017-03-10 QPQ9/qpq9_draft.tex
Remove .idea files

@@
 
-\author{Marie Wingyee Lau\altaffilmark{1}, J. Xavier Prochaska\altaffilmark{1}, 
-Joseph F. Hennawi\altaffilmark{2}
+\author{Marie Wingyee Lau\altaffilmark{1,2}, J. Xavier Prochaska\altaffilmark{2}, 
+Joseph F. Hennawi\altaffilmark{3}
 }
-\altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick Observatory, University of 
+\altaffiltext{1}{Email: lwymarie@ucolick.org}
+\altaffiltext{2}{Department of Astronomy and Astrophysics, UCO/Lick Observatory, University of 
 California, 1156 High Street, Santa Cruz, CA 95064}
-\altaffiltext{2}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69115 Heidelberg, 
-Germany}
+\altaffiltext{3}{Department of Physics, Broida Hall, University of California, Santa Barbara, 
+CA 93106-9530}
 
 \begin{abstract}
-We examine the kinematics of the gas in the environments of massive galaxies hosting quasars at 
-$z\sim2$. We employ 112 projected quasar pairs to study the circumgalactic gas of the foreground 
-quasars in absorption. The foreground quasars have precise redshift measurements, using 
-emission-lines with uncertainty $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
+We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
+We employ 112 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
+absorption. The sample selects foreground quasars with precise redshift measurements, using 
+emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
 systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
-foreground quasar's systemic redshift. The mean absorption in \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large velocity widths, and have velocity 
-centroids that show a small positive offset relative to the systemic. We argue that a possible 
-explanation to the observed velocity fields is outflowing gas combined with anisotropic or 
-intermittent ionizing radiation of the quasars. 
+foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4}, 
+and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths 
+$\sigma_v>300\,{\rm km\,s^{-1}}$. We show that, gas in gravitational motion, Hubble flow, or 
+galactic-scale outflows are all consistent with the observed widths. Furthermore, we find that the 
+mean absorptions are asymmetric about the systemic redshift. The mean absorption centroids exhibit 
+small redshift relative to the systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large 
+intrinsic scatter in the centroid velocities of the individual absorption systems. We show 
+that the observed offsets may be produced by anisotropic or intermittent ionizing radiation from 
+the foreground quasars. 
 \end{abstract}
@@
 \citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}. 
-In a previous paper of the Qussars Probing Quasars series\citep[][QPQ8]{QPQ8}, we 
+In a previous paper of the Qussars Probing Quasars series \citep[][, hereafter QPQ8]{QPQ8}, we 
 measured the velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the 
@@
 success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
-large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on on 
+large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on 
 1\textendash2\,Mpc scales. \cite{Johnson+15} studied the CGM surrounding $z\sim1$ quasars, and 
@@
 the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11}, or with gas tracing 
-a higher ionization state than the QPQ absorption systems\citep[e.g., ][]{Churchill+12}, or where 
+a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
 the average velocity spread is smaller than that measured in QPQ8 
@@
 galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
-\citep[][QPQ1]{QPQ1} to use the standard technique of absorption-line spectroscopy with background 
-quasars. These quasar pairs 
+\citep[][, hereafter QPQ1]{QPQ1} to use the standard techniques of absorption-line spectroscopy 
+with background quasars. These quasar pairs 
 have angular separations that correspond to less than 300\,kpc projected separation at the 
@@
 spectra that are paired with foreground quasars with precisely measured redshifts. 
-Among the sightlines in the QPQ9 sample, 13 have spectral resolution $> 5000$ from echellette or 
+Among the sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or 
 echelle observations, and have been analyzed separately in QPQ8. Our primary 
@@
 central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
-(ii) characterize the dynamics of flows of gas around these massive system. We further describe 
+(ii) characterize the dynamics of the gas around these massive systems. We further describe 
 an aspect of this experiment that offers a unique opportunity to study galactic-scale flows: we 
-argue that, the anisotropic or intermittent radiation of the foreground quasars may break the 
+argue that, the anisotropic or intermittent radiation from the foreground quasars may break the 
 symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation field is 
@@
 further away from the background quasar, due to different light travel times. 
+\cite{KirkmanTytler08} reported an asymmetry in \ion{H}{1} absorption on scales larger than the 
+CGM, and gave similar arguments on anisotropy or intermittence.
 
@@
 quasar pairs of $R_\perp < 300$\,kpc and $z_{\rm fg}>1.6$. Assuming that the foreground quasars 
-emit isotropically and at a distance equal to the impact parameter, the aenhancement in the UV 
+emit isotropically and at a distance equal to the impact parameter, the enhancement in the UV 
 flux relative to the extragalactic UV background, $g_{\rm UV}$, can be estimated. Large 
@@
 The goal of our experiment is to measure the average velocity fields of the absorption from C$^+$, 
-C$^{3+}$, and Mg$^+$ ions associated with the CGM of the massive galaxies hosting $z\sim 2$ 
-quasars.
+C$^{3+}$, and Mg$^+$ ions associated with the CGM of the galaxies hosting $z\sim 2$ quasars.
 
-From our QPQ survey\footnote{http://www.qpqsurvey.org}, we have analyzed a subset of systems that 
+From our QPQ survey\footnote{http://www.qpqsurvey.org}, we analyze a subset of systems that 
 pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
@@
 $300\,{\rm km\,s^{-1}}$ or better and an average offset from the systemic redshift of 
-$|100\,{\rm km\,s^{-1}}|$ or less. According to \citep{Shen+16}, the [\ion{O}{3}] emission-line 
-redshifts have the smallest total scatter (due to intrinsic scatter and measurement error) of 
+$|100\,{\rm km\,s^{-1}}|$ or less. According to \cite{Shen+16}, the [\ion{O}{3}] emission-line 
+redshifts have the smallest scatter (intrinsic scatter and measurement error combined) of 
 $68\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the sub-sample with 
@@
 \cite{Richards+02} reported a median redshift of $97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from 
-[\ion{O}{3}] using a larger but lower redshift sample. In QPQ8 \citep{QPQ8}, we quantified 
+[\ion{O}{3}] using a larger but lower redshift sample. In QPQ8, we quantified 
 the precision of H$\alpha$ to be $300\,{\rm km\,s^{-1}}$ and the median offset from the systemic 
@@
 $\approx400\,{\rm km\,s^{-1}}$, and a large average offset about the systemic 
-$\approx100\,{\rm km\,s^{-1}}$ \citep[][; QPQ8]{Shen+16}. 
+$\approx100\,{\rm km\,s^{-1}}$ \citep[][QPQ8]{Shen+16}. 
 We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
@@
 \cite{HewettWild10} using the \ion{Mg}{2}\,2800 emission-line, and we add the median blueshift of 
-\ion{Mg}{2} from the systemic to these redshifts. We reached a final sample size of 112. 
+\ion{Mg}{2} from the systemic to these redshifts. We reach a final sample size of 112. 
 Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
@@
 from analysis. For stacked profile analysis, a good estimate of 
-the continuum level is neessary. In QPQ8 we found that absorption associated to 
+the continuum level is necessary. In QPQ8 we found that absorption associated to 
 the foreground quasar occurs within $\pm2000\,{\rm km\,s^{-1}}$ around $z_{\rm fg}$. Therefore, it 
@@
 expectation, while the dispersion suggests extreme kinematics. The median stack, on the other 
-hand, shows weaker absorption, and the Gaussian model has a centroid closer to zero.
+hand, shows weaker absorption, and the Gaussian model has a centroid with smaller offset and 
+comparable dispersion.
 
@@
 
-\begin{figure}
 \subsection{Interpretation of the asymmetric absorption}
@@
 
-\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
-%\includegraphics[width=2.5in]{f03.pdf}
-\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
-for the \ion{C}{2} mean stack. 98\% of the centroids are positively offset from $z_{\rm fg}$.}
-\label{fig:histogram_cen}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
-%\includegraphics[width=2.5in]{f04.pdf}
-\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
-$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
-approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
-}
-\label{fig:stack_z1}
-\end{figure}
-
 Given the small sample size, one must scrutinize the statistical significance of the measured 
 velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
-randomly sampling from the full sample 10000 times. We introduce a Gaussian absorption profile to 
-model each bootstrap realization, and quote the standard deviation in the the bootstrap 
-realizations to be the scatter in the centroid of the data. The scatters 
+randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
+to model each bootstrap realization, and quote the standard deviation in the the bootstrap 
+realizations to be the scatter in the centroids of the data. The scatters 
 $\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
 variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show 
-the distribution of the absorption centroids of the bootstrap realizations. We find that 98\% of 
-the centroids are at positive velocities. We place a generous $3\sigma$ upper limit to the small 
-offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
+the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
+find that 98\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper 
+limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
 $\delta v<+451\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore 
-whether there exists relative asymmetry between \ion{C}{2} and \ion{C}{4} absorption due to 
-different ionization potentials.
+whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
+absorption.
 
@@
 pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present 
-the mean tack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
+the mean stack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
 sample. Gaussian absorption models fitted to the stack recover a centroid of 
-$-13\pm410\,{\rm km\,s^{-1}}$ and a dispersion of $155\,{\rm km\,s^{-1}}$. The average offset 
-from $0\,{\rm km\,s^{-1}}$ is smaller than the offsets in the $z\sim2$ sample.
+$-9\pm388\,{\rm km\,s^{-1}}$ and a dispersion of $161\,{\rm km\,s^{-1}}$. The average offset 
+from $0\,{\rm km\,s^{-1}}$ is much smaller than the offsets in the $z\sim2$ sample.
 
-Since the large scatter in the centroids represent intrinsic variation rather than redshift 
-errors, and the \ion{Mg}{2} stack for lower redshift does not suggest a similar offset, we 
+Since the large scatter in the centroids represents intrinsic variation rather than redshift 
+errors, and the \ion{Mg}{2} stack for lower redshift suggests a different centroid, we 
 consider that the asymmetry signal in the $z\sim2$ sample is likely to be real. In the Discussion 
 section, we discuss two possible explanations for the asymmetry.
+
+\begin{figure}
+\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
+%\includegraphics[width=2.5in]{f03.pdf}
+\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
+for the \ion{C}{2} mean stack. 98\% of the centroids are positively offset from $z_{\rm fg}$.}
+\label{fig:histogram_cen}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
+%\includegraphics[width=2.5in]{f04.pdf}
+\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
+$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
+approximately at $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
+}
+\label{fig:stack_z1}
+\end{figure}
 
@@
 dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
-absorption profile with $\sigma_v=658\,{\rm km\,s^{-1}}$. Motions that produce this width are 
-ruled out at $3\sigma$ confidence by bootstrap analysis on the observational data. 
+absorption profile with $\sigma_v=654\,{\rm km\,s^{-1}}$, that is ruled out. Motions that produce 
+this width are ruled out at $3\sigma$ confidence by bootstrap analysis on the observational data. 
 }
@@
 
-Under the assumption that the intrinsic velocity field and the redshift uncertainty add in 
+Under the assumption that the intrinsic dispersion and the redshift uncertainty add in 
 quadrature to give the observed width, we solve for the intrinsic dispersion in the \ion{C}{2} 
 mean stack. For the full QPQ9 sample, with the mean 
-$\sigma_{\rm error(z)}^{\rm full}=182\,{\rm km\,s^{-1}}$, we recover 
+$\sigma_{{\rm error}(z)}^{\rm full}=182\,{\rm km\,s^{-1}}$, we recover 
 $\sigma_{\rm intrinsic}^{\rm full}=253\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
-redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=342\,{\rm km\,s^{-1}}$. In QPQ8, we 
-reported the line-of-sight velocity 
-dispersion typical of QPQ dark matter halo mass is $\sigma_{\rm 1D}=212\,{\rm km\,s^{-1}}$. We can 
-investigate whether gravitational motions and Hubble flows are sufficient to reproduce the 
-dispersion in the \ion{C}{2} mean stack using Monte Carlo methods.
+redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=342\,{\rm km\,s^{-1}}$.
+
+\cite{Eftekharzadeh+15} measured the clustering of quasars in the range $2.2<z<2.8$ while 
+\cite{RodriguezTorres+16} measured the clustering of quasars in the range $1.8<z<2.2$. They 
+estimated that these quasars are hosted by dark matter halos with mass $10^{12.5}\,M_\odot$ and 
+$10^{12.6}\,M_\odot$ respectively. If QPQ dark matter halos have a characteristic mass 
+$10^{12.5}\,M_\odot$ and follow an NFW profile \citep{NavarroFrenkWhite97} with concentration 
+parameter $c=4$, at $z\approx2$ the maximum circular velocity is $319\,{\rm km\,s^{-1}}$. 
+According to \cite{Tormen97}, the maximum circular velocity is $\approx1.4$ times larger than the 
+one-dimensional velocity dispersion $\sigma_{\rm 1D}$. Hence, the line-of-sight velocity 
+dispersion typical of QPQ halos is $\sigma_{\rm 1D}=228\,{\rm km\,s^{-1}}$. We can investigate 
+whether gravitational motions and Hubble flows are sufficient to reproduce the dispersion in the 
+data, using Monte Carlo methods to simulate the absorption signals.
 
@@
 $0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we assume a rest 
-equivalent width $W_{\rm CII}$ for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
+equivalent width for \ion{C}{2} $W_{\rm CII}$ and a Gaussian absorption profile. We repeat the 
 above procedure for all 32 quasar pairs, and create a mean stack of the 32000 mock spectra 
@@
 the stack of mock spectra. We adjust the $W_{\rm CII}$ adopted for the absorbers until the 
-ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
+amplitude of the best-fit Gaussian of the stack of mock spectra matches the 
 amplitude of the stack of the observational data. We find that $W_{\rm CII}=0.7\,{\rm \AA}$ well 
 reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
-insensitive to the assumed $W_{\rm CII}$ or line profile for one absorber. In 
-Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
+insensitive to the assumed $W_{\rm CII}$ or line profile for one absorber.
+
+In Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
 absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is 
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $244\,{\rm km\,s^{-1}}$. This is 
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $263\,{\rm km\,s^{-1}}$. This is 
 within $1\sigma$ modeling error of the intrinsic dispersion in the \ion{C}{2} mean stack for the 
-full sample, and about 3 times larger than the modeling error of the intrinsic 
-dispersion in the stack of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
+full sample, and about 2 times the modeling error away from the intrinsic dispersion in the stack 
+of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
 sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering 
@@
 processes are not necessary to explain the large velocity fields. From the bootstrap analysis of 
-the observed dispersion, a width of $\sigma_v>658\,{\rm km\,s^{-1}}$ is ruled out at 3$\sigma$ 
-confidence (overplotted in Figure~\ref{fig:monte}). In other words, motions in additional to 
-gravitational and Hubble flows that will produce $\sigma_v>611\,{\rm km\,s^{-1}}$ are ruled out.
+the observed dispersion, a width of $\sigma_v>654\,{\rm km\,s^{-1}}$ is ruled out at 3$\sigma$ 
+confidence (overplotted in Figure~\ref{fig:monte}). In other words, motions additional to 
+gravitational and Hubble flows that will produce intrinsic dispersion 
+$\sigma_v>628\,{\rm km\,s^{-1}}$ are ruled out.
+
+On the contrary, $\sigma_{\rm 1D}<175\,{\rm km\,s^{-1}}$ together with Hubble velocities will 
+result in a velocity width that is more than three times the modeling error away from the observed 
+intrinsic width. This implies that if the characteristic dark matter halo mass 
+$<10^{12.2}\,M_\odot$, additional dynamical processes are required to explain the observed width.
 
@@
 weaker than that in the background stacks, and there is no evidence for an excess at $z_{\rm fg}$. 
-The stack for \ion{C}{4}, which include line-of-sight absorbers at all distances, shows a large, 
+The stack for \ion{C}{4}, which includes line-of-sight absorbers at all distances, shows a large, 
 blueshifted mean velocity field.
@@
 to apply the same techniques to stack the foreground quasar spectra. In 
-Figure~\ref{fig:stacks_fg}, we present mean stacks of foreground quasar spectra for the pairs in 
+Figure~\ref{fig:stacks_fg}, we present mean stacks of foreground quasar spectra for 
 the QPQ9 sample. We require that the spectra survive a S/N cut of 5.5 per rest-frame \AA\ at 
@@
 absorbers, which include absorbers intrinsic to and far away from the quasar, shows a large, 
-blueshifted velocity field.
+blueshifted velocity field. This excess \ion{C}{4} absorption has been well studied as narrow 
+associated absorption line systems \citep[e.g., ][]{Wild+08}.
 
@@
 One possibility is an asymmetric radiation field that preferentially ionizes the gas moving toward 
-the observer, where the quasar is known to shine. In Figure~\ref{fig:monopolar}, we show a cartoon 
-of a quasar that is blocked in the direction pointing away from the observer. The gas 
-observed in absorption preferentially lies behind the quasar. The asymmetric absorption arises 
-from a transverse proxmity effect. 
+the observer, where the quasar is known to shine. Alternatively, the asymmetric radiation field 
+may preferentially ionizes the gas at smaller Hubble velocity than the quasar. In 
+Figure~\ref{fig:monopolar}, we show a cartoon of a quasar that is blocked in the direction 
+pointing away from the observer. The gas observed in absorption preferentially lies behind the 
+quasar. The asymmetric absorption arises from a transverse proxmity effect. 
 \cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy 
@@
 
-As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, 
-outflow speeds of $500\textendash700\,{\rm km\,s^{-/1}}$ and quasar opening angles of 
-$120^\circ\textendash140^\circ$ may reproduce the observed centroid and intrinsic dispersion of 
-the \ion{C}{2} mean absorption. The first explanation above to asymmetric absorption requires that 
-the quasars emit their ionizing radiation anisotropically, while the second explanation requires 
-the quasars emit their ionizing radiation intermittently. Both explanations will require the gas 
-to be either outflowing or in Hubble flow. Were the gas inflowing instead, the velocity centroid 
-would be negative. \cite{KirkmanTytler08} reported an asymmetry in \ion{H}{1} absorption on scales 
-larger than the CGM, and gave similar arguments on anisotropy or intermittence. We are assembling 
-a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study this asymmetry in 
-\ion{H}{1} (J. F. Hennawi et al. 2017, in preparation).
+As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, radial 
+speeds relative to the foreground quasar of $500\textendash700\,{\rm km\,s^{-1}}$ and quasar 
+opening angles of $120^\circ\textendash140^\circ$ may reproduce the observed centroid and 
+intrinsic dispersion of the \ion{C}{2} mean absorption. The first explanation above to asymmetric 
+absorption requires that the quasars emit their ionizing radiation anisotropically, while the 
+second explanation requires the quasars emit their ionizing radiation intermittently. Both 
+explanations will require the gas to be either outflowing or in Hubble flow. Were the gas 
+inflowing instead, the velocity centroid would be negative.
 
-In conclusion, we observe large and positively skewed velocity fields in absorption, of metal ions 
+Motivated by the asymmetry found in metal ion absorption in the CGM using precise $z_{\rm fg}$ 
+measurements, and the asymmetry found by \cite{KirkmanTytler08} in \ion{H}{1} on larger 
+scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study 
+this asymmetry in \ion{H}{1} (J. F. Hennawi et al. 2017, in preparation). In conclusion, we 
+observe large and positively skewed velocity fields in absorption, of metal ions 
 in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
 explained if the detected gas is in gravitational motion, Hubble flow, or outflow, and the quasars 
-either shine anisotropically or intermittently.
+either shine preferentially toward the observer or shine intermittently.
 

### 2017-03-10 QPQ9/Figures/py/qpq9_figs.py

@@ -391,7 +391,7 @@ def monte(outfil=None):
     model_monte = model_conti*model_monte_gauss
     # Extra motion that is ruled out
     model_extra_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude_1'],mean=Gaussian_params['mean_1'],stddev=658.)
+        amplitude=monte_params['amplitude_1'],mean=Gaussian_params['mean_1'],stddev=654.)
     model_extra = model_conti*model_extra_gauss
 
     # Axes

### 2017-03-10 QPQ9/Figures/py/qpq9_figs.py
Put the figures notebook in a module

@@ -26,9 +26,20 @@ from xastropy.atomic import ionization as xai
 sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
 import qpq9_stacks as qpq9k
 
+
+# Make all QPQ9 figures
+def all_figs():
+    experiment()
+    stacks_and_fits()
+    stacks_fg()
+    stack_z1()
+    monte()
+    centroids()
+
+
 #  Plot the Experiment
 def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2N_cut=5.5/u.AA,
-               zfg_mnx=(1.6,9999),vsig_cut=400*u.km/u.s):
+               zfg_mnx=(1.6,9999)):
 
     if outfil is None:
         outfil = 'fig_experiment.pdf'

### 2017-03-10 QPQ9/Figures/py/qpq9_figs.py
Put the figures notebook in a module

@@ -27,16 +27,6 @@ sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
 import qpq9_stacks as qpq9k
 
 
-# Make all QPQ9 figures
-def all_figs():
-    experiment()
-    stacks_and_fits()
-    stacks_fg()
-    stack_z1()
-    monte()
-    centroids()
-
-
 #  Plot the Experiment
 def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2N_cut=5.5/u.AA,
                zfg_mnx=(1.6,9999)):
@@ -474,3 +464,18 @@ def centroids(outfil=None):
     pp.savefig(bbox_inches='tight')
     pp.close()
     print('centroids: Wrote {:s}'.format(outfil))
+
+
+# Make all QPQ9 figures
+def main():
+    experiment()
+    stacks_and_fits()
+    stacks_fg()
+    stack_z1()
+    monte()
+    centroids()
+
+
+# Command line execution
+if __name__ == '__main__':
+    main()

### 2017-03-10 QPQ9/Analysis/rebinning_tests.py
Put rebinning test in a module

@@ -1,0 +1,90 @@
+import numpy as np
+from scipy.interpolate import InterpolatedUnivariateSpline,interp1d
+import matplotlib.pyplot as plt
+
+## Ryan's idea
+
+# Setup the old and new wavelength arrays
+v_old = 3.0   # velocity of old scale
+n_old = 100  # number of data points
+v_new = 7.6  # velocity of new scale
+
+# Generate fake data (wavelength array to start at 5000A)
+f_old = np.random.normal(1.0,0.1,n_old)
+w_old = 5000.0*(1.0+v_old/299792.458)**np.arange(n_old)
+
+# Generate new wavelength array
+n_new = 1+np.int(np.log10((w_old[-1]/w_old[0]))/np.log10((1.0+v_new/299792.458)))
+w_new = 5000.0*(1.0+v_new/299792.458)**np.arange(n_new)
+
+# Create a spline representation of the old wavelength array, k=1 forces linear interpolation
+spl = InterpolatedUnivariateSpline(w_old, f_old, k=1)
+
+# linearly interpolate onto new flux array
+f_new = spl(w_new)
+
+plt.plot(w_old,f_old,'b-',drawstyle='steps')
+plt.plot(w_new,f_new,'r-',drawstyle='steps')
+plt.show()
+
+# Check flux conserving
+gd_old = np.where( (w_old > 5001.) & (w_old < 5004.) )[0]
+gd_new = np.where( (w_new > 5001.) & (w_new < 5004.) )[0]
+sum_old = np.sum( f_old[gd_old] )
+sum_new = np.sum( f_old[gd_new] * v_new/v_old )
+print('The sums are old={:g}, new={:g}'.format(sum_old, sum_new))
+
+## Idea with cumsum
+
+# Endpoints of original pixels
+npix = len(w_old)
+#wvl = (w_old + np.roll(w_old, 1))/2.
+wvh = (w_old + np.roll(w_old, -1))/2.
+#wvl[0] = w_old[0] - (w_old[1] - w_old[0])/2.
+wvh[npix-1] = w_old[npix-1] + (w_old[npix-1] - w_old[npix-2])/2.
+
+# Cumulative Sum
+cumsum = np.cumsum(f_old)
+
+# Interpolate
[…]

### 2017-03-10 QPQ9/Analysis/monte_carlo.py
Put monte_carlo notebook in a module Remove pdf files

@@ -1,0 +1,131 @@
+from __future__ import print_function,absolute_import,division,unicode_literals
+import numpy as np
+import glob,os,sys,copy,imp
+from scipy import stats as scistats
+import matplotlib as mpl
+mpl.rcParams['font.family']='stixgeneral'
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import pyplot as plt
+import matplotlib.gridspec as gridspec
+from astropy.table import QTable,Table
+from astropy.io import ascii,fits
+from astropy import units as u
+from astropy import constants as const
+from astropy.coordinates import SkyCoord
+from linetools.spectralline import AbsLine
+import linetools.utils as ltu
+sys.path.append(os.path.abspath("../../../py"))
+from enigma.qpq import utils as qpqutils
+from enigma.qpq import spec as qpqs
+from enigma.qpq import stacks as qpqk
+sys.path.append(os.path.abspath("./Stacks/py"))
+import qpq9_stacks as qpq9k
+import scipy.integrate as integrate
+from astropy.modeling import models,fitting
+from astropy.cosmology import FlatLambdaCDM
+cosmo = FlatLambdaCDM(H0=70,Om0=0.26)
+
+def gen_stck_img(R_phys,z_fg,Deltav,v_grid,n_trials): # R_phys in kpc, Deltav in km/s
+    probs = np.zeros(len(v_grid))
+    cumulative_probs = np.zeros(len(v_grid))
+    Hubble_h = cosmo.H(0).value/100.
+    ell_IGM_DLA = 0.2*((1+z_fg)/(1+2.5))**2.1
+    ell_IGM_SLLS = 0.44*((1+z_fg)/(1+2.5))**2.1
+    ell_IGM_LLS = 1.05*((1+z_fg)/(1+2.5))**2.1
+    R_comov = R_phys/1000.*(1+z_fg)*Hubble_h # in h^-1 Mpc
+    for ii,vv in enumerate(v_grid):
+        gamma_DLA = 1.6
+        r0_DLA = 3.9
+#        gamma_SLLS = 1.6
+#        r0_SLLS = 15.5
+#        gamma_LLS = 1.6
+#        r0_LLS = 13.9
+        gamma_SLLS = 1.68
+        r0_SLLS = 14.0
+        gamma_LLS = 1.68
+        r0_LLS = 12.5
+        chi_DLA = 1./Deltav*integrate.quad(
[…]

### 2017-03-10 QPQ9/Analysis/py/qpq9_analy.py

@@ -1,332 +1,0 @@
-# Module for QPQ9 analysis
-
-from __future__ import print_function, absolute_import, division, unicode_literals
-
-import numpy as np
-import glob, copy, os, sys
-
-from scipy.interpolate import interp1d
-from scipy.interpolate import splev, splrep # bspline
-
-
-from astropy import units as u
-from astropy.units import Unit
-from astropy.io import ascii, fits
-from astropy.table import QTable, Table, Column
-from astropy.coordinates import SkyCoord
-from astropy import constants as const
-
-from linetools.spectralline import AbsLine
-from linetools.lists import linelist as lll
-
-from xastropy.xutils import fits as xxf
-from xastropy.xutils import xdebug as xdb
-from xastropy.atomic import ionization as xai
-from xastropy.xguis import utils as xxgu
-
-# Local 
-sys.path.append(os.path.abspath("./py"))
-import qpq_spec as qpqs
-
-high_res_inst = ['ESI', 'MAGE', 'MIKE', 'HIRES', 'XSHOOTER', 'UVES']
-
-
-##
-def stack_bspline(in_tup, dv=100*u.km/u.s, debug=False, **kwargs):
-    '''Provided a table of b/g QSOs or a stack image,
-      stack their spectra with a b-spline approach
-
-    Parameters:
-    ------------
-    in_tup: Tuple
-      (QPQ9 Table, wrest)
-      (fin_velo, stck_img, stck_msk, all_dict)
-    dv: Quantity, optional
-      Velocity spacing of breakpoints [100 km/s]
-
-    Returns:
-    ------------
-    fin_velo
-    fin_flx
-    all_dict
-    '''
-    reload(qpqs)
-
-    # Generate the image
-    if len(in_tup) == 2: 
-        fin_velo, stck_img, stck_msk, all_dict = load_stack_img(
-            in_tup[0], in_tup[1], **kwargs)
-    else:
-        fin_velo, stck_img, stck_msk, all_dict = in_tup
-
-    # Generate the full array for b-spline action
-    list_vel = []
-    list_fx = []
-    list_wgt = []
-    for tdict in all_dict:
-        if tdict is None:
-            continue
-        vel = tdict['spec'].velo[tdict['spec'].sub_pix]
-        idv = np.median(vel - np.roll(vel,1))
-        # Save
[…]

### 2017-03-10 QPQ9/Analysis/py/qpq_sample.py

@@ -1,128 +1,0 @@
-"""
-#;+ 
-## DEPRECATED
-## DEPRECATED
-## DEPRECATED
-#
-#; NAME:
-#; qpq_spec
-#;    Version 1.0
-#;
-#; PURPOSE:
-#;    Module for dealing with QPQ samples
-#;   May-2015 by JXP
-#;-
-#;------------------------------------------------------------------------------
-"""
-from __future__ import print_function, absolute_import, division, unicode_literals
-
-# imports
-import numpy as np
-import glob, os 
-
-from scipy.interpolate import interp1d
-
-from astropy.cosmology.core import LambdaCDM
-from astropy.coordinates import SkyCoord
-from astropy.units import Unit
-from astropy.io import fits, ascii
-from astropy import units as u
-from astropy.utils import isiterable
-
-from xastropy.spec import readwrite as xsr
-from xastropy.obs import radec as xrad
-from xastropy.xutils import fits as xxf
-from xastropy.xutils import xdebug as xdb
-from xastropy.files import general as xfg
-
-##
-def sdss_flux2mag(flux, filt):
-    '''
-    Calculate the magnitude given a flux
-
-    Parameters:
-    -----------
-    flux: float
-      Flux, usually de-reddened
-    filter: string
-      SDSS filter:  ugriz
-
-    Returns:
-    -----------
-    mag: float
-      apparent magnitude
-    '''
-    #  Smoothing parameter
-    b_parms = {'u': 1.4, 'g': 0.9, 'r': 1.2, 'i': 1.8, 'z': 7.4}
-    b_parm = b_parms[filt]
-
-    # Calculate
-    a = 1.08574
-    ln10_min10 = -23.02585
-    # 
-    m = -a*(np.arcsinh(5.0*flux/b_parm)+ln10_min10 + np.log(b_parm))    
-
-    # Return
-    return m
-
-##
-def m_iz2_qso(mag, ztot, omega_m=0.3, omega_v=0.7, w=1.0, lit_h=0.7):
-    '''
-    Calculate Absolute magnitude
-       Note these are M_i(z = 2) absolute magnitudes. 
-
-    Parameters:
-    -----------
-    mag:  float
-      SDSS magnitude
-    ztot:  float
-      Redshift of interest
-    omega_m: float (0.3)
-      Dark matter parameter
-    omega_v: float (0.7)
-      Vacuum energy parameter
[…]

### 2017-03-10 QPQ9/Analysis/py/qpq_spec.py

@@ -1,46 +1,0 @@
-"""
-## DEPRECATED
-###   see enigma.qpq.spec
-#;+ 
-#; NAME:
-#; qpq_spec
-#;    Version 1.0
-#;
-#; PURPOSE:
-#;    Module for dealing with spectra in the QPQ dataset 
-#;   May-2015 by JXP
-#;-
-#;------------------------------------------------------------------------------
-"""
-from __future__ import print_function, absolute_import, division, unicode_literals
-
-# imports
-import numpy as np
-import glob, os, copy
-
-from astropy.coordinates import SkyCoord
-from astropy.units import Unit
-from astropy.io import fits
-from astropy import units as u
-from astropy import constants as const
-
-from linetools.spectra import io as lsio
-
-from xastropy.obs import radec as xrad
-from xastropy.xutils import fits as xxf
-from xastropy.xutils import xdebug as xdb
-from xastropy.files import general as xfg
-
-
-
-# ################
-if __name__ == "__main__":
-
-    flg_fig = 0 
-    flg_fig += 2**0  # Test file grabbing
-    #flg_fig += 2**1  # Test with spectrum
-    
-    # 
-    if (flg_fig % 2**1) >= 2**0:
-        bg_qso = 'J005718.90-000134.7'
-        get_spec_files(bg_qso)

### 2017-03-10 QPQ9/Figures/py/qpq9_figs.py

@@ -466,7 +466,7 @@ def centroids(outfil=None):
     print('centroids: Wrote {:s}'.format(outfil))
 
 
-# Make all QPQ9 figures
+#################
 def main():
     experiment()
     stacks_and_fits()

### 2017-03-10 QPQ9/Analysis/Redshifts/py/qpq_z.py
Remove deprecated codes

@@ -1,338 +1,0 @@
-"""
-#;+ 
-#; NAME:
-#; qpq_spec
-#;    Version 1.0
-#;
-#; PURPOSE:
-#;    Module for QPQ redshifts
-#;   May-2015 by JXP
-#;-
-#;------------------------------------------------------------------------------
-"""
-from __future__ import print_function, absolute_import, division, unicode_literals
-
-# imports
-import numpy as np
-import glob, os, sys, copy
-import multiprocessing
-
-from matplotlib import pyplot as plt
-import matplotlib.gridspec as gridspec
-
-from astropy.stats import sigma_clip
-from astropy.nddata import StdDevUncertainty
-from astropy.coordinates import SkyCoord
-from astropy.units import Unit
-from astropy.io import fits
-from astropy import units as u
-from astropy import constants as const
-from astropy.table import QTable, Table, Column 
-
-from linetools.spectra import io as lsio
-from linetools.spectra.xspectrum1d import XSpectrum1D
-
-from xastropy.xutils import fits as xxf
-from xastropy.stats import basic as xsb
-
-from xastropy.xutils import xdebug as xdb
-
-from enigma.qso import hewittwildz as hw10z
-
-def parse_o2_zstruct(xx=None):
-    ''' Parse the output file from JFH
-    Parameters:
-    -------------
-    xx: str, optional
-      Line to focus on (MgII, Ha, Hb)
-
-    Returns:
-    --------------
-    qsos 
-    zline
-    '''
-    # Read O2 file
-    qsozout = os.getenv('DROPBOX_DIR') + '/O2_zsys/qsos_o2_zstruct.fits'
-    qsos = Table.read(qsozout)
-    # Cut on good [OII]
-    good_o2 = ((qsos['ZSYS_ZSYS'] > 0.0)&# AND $   ;; systemic redshift not zero
-        (qsos['ZSYS_OII_QUAL'] == 1)&# AND $ ;; received
-        (qsos['M_I_Z2'] <= -23.0)&# AND $   ;; bright enough to be a QSO and not Seyfert
[…]

### 2017-03-10 QPQ9/Analysis/Redshifts/py/zsys_figs.py

@@ -1,379 +1,0 @@
-# Module for zsys QA
-
-from __future__ import print_function, absolute_import, division, unicode_literals
-
-import numpy as np
-import subprocess, glob, copy, os
-
-from scipy.signal import medfilt
-
-import matplotlib as mpl
-mpl.rcParams['font.family'] = 'stixgeneral'
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib import pyplot as plt
-import matplotlib.gridspec as gridspec
-
-from astropy import constants as const
-from astropy import units as u
-from astropy.units import Unit
-from astropy.io import ascii, fits
-from astropy.table import QTable, Table, Column
-from astropy.coordinates import SkyCoord
-from astropy.cosmology import FlatLambdaCDM
-from astropy.relativity import velocities as arv
-
-from xastropy.xutils import fits as xxf
-from xastropy.plotting import utils as xputils
-from xastropy.spec import readwrite as xsr
-from xastropy.xutils import xdebug as xdb
-
-
-##
-def zsys_flag_str(idx):  
-    ''' 
-    List of the lines used
-    '''
-    val = [ r'H$\alpha$', 
-        r'H$\beta$',
-        'MgII',
-        'CIII]' ,           # 3
-        'CIV'   ,           # 4
-        'SiIV'  ,           # 5
-        'SiIV-CIV' ,        # 6
-        'SiIV-CIII]' ,      # 7
-        'CIV-CIII]' ,       # 8
-        'SiIV-CIV-CIII]' ,  # 9
-        r'Ly$\alpha$', 
-        '[OIII]'  ,         # 11
-        '[OII]']            # 12
-    # Return
-    try:
-        return val[idx]
-    except IndexError:
-        return 'NULL'
-
-##
-def zsys_qa(zem_fil, outfil=None, clobber=False):
-    '''
-    Generate a QA PDF file from a zem_fil
-    '''
-    # Outfil
-    i0 = zem_fil.find('/')+1
-    i1 = zem_fil.find('_zem')
-    outfil = 'zQA/'+ zem_fil[i0:i1] + '_zQA.pdf'
-    name = zem_fil[i0:i1]
-
-    # Check
-    dum = glob.glob(outfil)
-    if (len(dum) > 0) & (not clobber):
[…]

### 2017-03-10 QPQ9/Analysis/Stacks/py/qpq9_stacks_qpq7.py

@@ -1,185 +1,0 @@
-#Module for QPQ9 stacking
-# Imports
-from __future__ import print_function, absolute_import, division, unicode_literals
-
-import numpy as np
-import glob, os, sys, copy
-from scipy import stats as scistats
-
-import matplotlib as mpl
-mpl.rcParams['font.family'] = 'stixgeneral'
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib import pyplot as plt
-import matplotlib.gridspec as gridspec
-
-from astropy.table import QTable
-from astropy.io import ascii, fits
-from astropy import units as u
-from astropy import constants as const
-
-from linetools.spectra.xspectrum1d import XSpectrum1D
-
-from xastropy.igm.abs_sys import abssys_utils as abssys
-from xastropy import spec as xspec
-from xastropy.plotting import utils as xputils
-from xastropy.xutils import xdebug as xdb
-from xastropy.obs import radec as xor
-from xastropy.atomic import ionization as xai
-
-sys.path.append(os.path.abspath("../../../../py"))
-from enigma.qpq import spec as qpqs
-from enigma.qpq import stacks as qpqk
-from enigma.qpq import qpq as eqpq
-
-# Local
-sys.path.append(os.path.abspath("../py"))
-import qpq9_analy as qpq9a
-
-####
-def qpq7_MgII(wrest=None, outfil=None, nboot=10000,
-    vmnx = (-3000., 3000.)*u.km/u.s, stack_tup=None,
-    passback=False, debug=False): 
-    ''' Stack the QPQ7 sample
-    '''
-
-    # To do: Have symbol size indicate near-IR for redshift
-    reload(qpq9a)
-
-    # Rest wavelength
-    if wrest is None:
-        wrest = 1334.5323*u.AA
-
-    # Load QPQ9
-    qpq7 = eqpq.QPQ('QPQ7')
-    # Avoid Lya forest
-    qpq7.cull(wrest,4,vsig_cut=300*u.km/u.s)
-    print('length of sample after and before culling',len(qpq7.data),len(qpq7._fulldata))
-    
-    # Cut on 300 kpc
-    gdR = np.where(qpq7.data['R_PHYS'] < 300)[0]
-
-    if outfil is None:
-        outfil = 'Output/QPQ7_MgII_{:d}.fits'.format(int(wrest.value))
-
-    # Load the stack image
-    if stack_tup is None:
[…]

### 2017-03-24 QPQ9/qpq9_draft.tex
Put the noteobok for making the QPQ9 structure in a module Small changes

@@
 and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths 
-$\sigma_v>300\,{\rm km\,s^{-1}}$. We show that, gas in gravitational motion, Hubble flow, or 
-galactic-scale outflows are all consistent with the observed widths. Furthermore, we find that the 
-mean absorptions are asymmetric about the systemic redshift. The mean absorption centroids exhibit 
-small redshift relative to the systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large 
-intrinsic scatter in the centroid velocities of the individual absorption systems. We show 
-that the observed offsets may be produced by anisotropic or intermittent ionizing radiation from 
-the foreground quasars. 
+$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
+motion and Hubble flow, and galactic-scale outflows are not be required to explain the large 
+widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
+The mean absorption centroids exhibit small redshift relative to the 
+systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid 
+velocities of the individual absorption systems. We show that the observed offsets may be produced 
+if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the 
+gas is not flowing into the galaxy.  
 \end{abstract}
@@
 \caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
-\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thick, 
+\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin, 
 black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
-from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thin, blue. 
+from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue. 
 For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
@@
 \caption{The same \ion{C}{2} mean stack shown in the first panel of 
-Figure~\ref{fig:stacks_and_fits} is shown in thick, black. In thin, green, we overplot the 
+Figure~\ref{fig:stacks_and_fits} is shown in thin, black. In thick, green, we overplot the 
 Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering 
@@
 dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
-absorption profile with $\sigma_v=654\,{\rm km\,s^{-1}}$, that is ruled out. Motions that produce 
-this width are ruled out at $3\sigma$ confidence by bootstrap analysis on the observational data. 
+absorption profile with $\sigma_v=654\,{\rm km\,s^{-1}}$, which is larger than the observed width 
+by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity 
+width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with 
+$\sigma_v=207\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the 
+modeling error. Unless gravitational and Hubble flows together with redshift error broadening 
+produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be 
+required to explain the observation. 
 }
@@
 estimated that these quasars are hosted by dark matter halos with mass $10^{12.5}\,M_\odot$ and 
-$10^{12.6}\,M_\odot$ respectively. If QPQ dark matter halos have a characteristic mass 
-$10^{12.5}\,M_\odot$ and follow an NFW profile \citep{NavarroFrenkWhite97} with concentration 
-parameter $c=4$, at $z\approx2$ the maximum circular velocity is $319\,{\rm km\,s^{-1}}$. 
-According to \cite{Tormen97}, the maximum circular velocity is $\approx1.4$ times larger than the 
-one-dimensional velocity dispersion $\sigma_{\rm 1D}$. Hence, the line-of-sight velocity 
-dispersion typical of QPQ halos is $\sigma_{\rm 1D}=228\,{\rm km\,s^{-1}}$. We can investigate 
-whether gravitational motions and Hubble flows are sufficient to reproduce the dispersion in the 
-data, using Monte Carlo methods to simulate the absorption signals.
+$10^{12.6}\,M_\odot$ respectively. If dark matter halos hosting QPQ9 quasars have a characteristic 
+mass $10^{12.6}\,M_\odot$ and follow an NFW profile \citep{NavarroFrenkWhite97} with concentration 
+parameter $c=4$, at $z\approx2$ the maximum circular velocity is $345\,{\rm km\,s^{-1}}$. 
+\cite{TormenBouchetWhite97} found that the maximum circular velocity is $\approx1.4$ times the 
+maximum of the one-dimensional velocity dispersion $\sigma_{\rm 1D}$. Hence, the line-of-sight 
+velocity dispersion typical of QPQ9 halos is $\sigma_{\rm 1D}=246\,{\rm km\,s^{-1}}$. We can 
+investigate whether gravitational motions and Hubble flows are sufficient to reproduce the 
+dispersion in the data, using Monte Carlo methods to simulate the absorption signals.
 
@@
 amplitude of the best-fit Gaussian of the stack of mock spectra matches the 
-amplitude of the stack of the observational data. We find that $W_{\rm CII}=0.7\,{\rm \AA}$ well 
+amplitude of the stack of the observational data. We find that $W_{\rm CII}=0.8\,{\rm \AA}$ well 
 reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
@@
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $263\,{\rm km\,s^{-1}}$. This is 
-within $1\sigma$ modeling error of the intrinsic dispersion in the \ion{C}{2} mean stack for the 
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $281\,{\rm km\,s^{-1}}$. This is 
+within $1\sigma$ modeling error from the intrinsic dispersion in the \ion{C}{2} mean stack for the 
 full sample, and about 2 times the modeling error away from the intrinsic dispersion in the stack 
@@
 processes are not necessary to explain the large velocity fields. From the bootstrap analysis of 
-the observed dispersion, a width of $\sigma_v>654\,{\rm km\,s^{-1}}$ is ruled out at 3$\sigma$ 
-confidence (overplotted in Figure~\ref{fig:monte}). In other words, motions additional to 
-gravitational and Hubble flows that will produce intrinsic dispersion 
-$\sigma_v>628\,{\rm km\,s^{-1}}$ are ruled out.
+the observed dispersion, a width of $\sigma_v>654\,{\rm km\,s^{-1}}$ would be larger than the 
+observed by three times the scatter (overplotted in Figure~\ref{fig:monte}). In other words, 
+taking into account the redshift errors, motions in addition to gravitational and Hubble 
+flows that will produce an intrinsic dispersion $\sigma_v>628\,{\rm km\,s^{-1}}$ can be ruled out.
 
-On the contrary, $\sigma_{\rm 1D}<175\,{\rm km\,s^{-1}}$ together with Hubble velocities will 
-result in a velocity width that is more than three times the modeling error away from the observed 
-intrinsic width. This implies that if the characteristic dark matter halo mass 
-$<10^{12.2}\,M_\odot$, additional dynamical processes are required to explain the observed width.
+On the contrary, $\sigma_{\rm 1D}<74\,{\rm km\,s^{-1}}$ together with Hubble velocities and 
+broadening by redshift errors will result in a velocity width that is more than three times the 
+modeling error away from the observed width (overplotted in Figure~\ref{fig:monte}). This implies 
+that, unless the characteristic dark matter halo mass $<10^{11.0}\,M_\odot$, additional dynamical 
+processes are not required to explain the observed width.
 
@@
 second explanation requires the quasars emit their ionizing radiation intermittently. Both 
-explanations will require the gas to be either outflowing or in Hubble flow. Were the gas 
-inflowing instead, the velocity centroid would be negative.
+explanations will require the line-of-sight motions of the gas to be in either outflow or Hubble 
+flow. Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
 

### 2017-03-24 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py

@@ -3,17 +3,11 @@
 from __future__ import print_function, absolute_import, division, unicode_literals
 import numpy as np
 import glob, os, sys, copy
-from scipy import stats as scistats
 import matplotlib as mpl
 mpl.rcParams['font.family'] = 'stixgeneral'
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib import pyplot as plt
-import matplotlib.gridspec as gridspec
-from astropy.table import QTable
 from astropy.io import ascii, fits
 from astropy import units as u
 from astropy.modeling import models,fitting
-from xastropy.xutils import xdebug as xdb
 sys.path.append(os.path.abspath("../../../../py"))
 from enigma.qpq import stacks as qpqk
 
@@ -150,7 +144,6 @@ def boot_trans(wrest=1334.5323*u.AA,full_sample=True,
         fit = np.polyfit(velo[pix].value, fx[pix], 0)
         pv = np.poly1d(fit)
         conti = pv(velo.value)
-        ##xdb.xplot(velo, fx, conti)
         ## Normalize
         cfx = fx/conti
         EWpix = np.where( (velo > EW_range[0]) & (velo<EW_range[1]))[0]
@@ -162,10 +155,6 @@ def boot_trans(wrest=1334.5323*u.AA,full_sample=True,
         EWr = np.sum(1. - cfx[EWr_pix])
         ## Equivalent width sknewness
         frac[qq] = (EWr-EWl) / EW
-
-    # Check
-    if debug:
-        xdb.xhist(frac)
 
     # Stats
     mu_frac = np.mean(frac)

### 2017-03-24 QPQ9/Analysis/Redshifts/py/tst_dr7.py

@@ -14,7 +14,7 @@ from __future__ import print_function, absolute_import, division, unicode_litera
 
 # imports
 import numpy as np
-import glob, os, sys, copy
+import glob, os, sys, copy, pdb
 import multiprocessing
 import cPickle as pickle
 
@@ -26,16 +26,11 @@ from astropy.units import Unit
 from astropy.io import fits
 from astropy import units as u
 from astropy import constants as const
-from astropy.table import QTable, Column
+from astropy.table import Table, QTable, Column
 
-from xastropy.obs import radec as xrad
-from xastropy.xutils import xdebug as xdb
-from xastropy.xutils import fits as xxf
 from xastropy.sdss import quasars as sdssq
-from xastropy.sdss import qso as sdssqso
 
 sys.path.append(os.path.abspath("./py"))
-import qpq_z as qpqz
 import hewittwildz as hw10z
 
 # Hewitt&Wild Prescription
@@ -91,7 +86,7 @@ def mgii_in_hw10(parallel=True, nproc=8):
         pool = multiprocessing.Pool(nproc) # initialize thread pool N threads
         all_HWz = pool.map(run_hw10,tst_qsos)
     else:
-        xdb.set_trace() # Next line needs updating
+        pdb.set_trace() # Next line needs updating
         all_HWz = map(run_hw10,gdtst)
 
     # Generate final table
@@ -101,7 +96,7 @@ def mgii_in_hw10(parallel=True, nproc=8):
     JXP_z = Column(np.array([hwz.z_dict['zfin'] for hwz in all_HWz]),name='JXP_z')
     cc_max = Column(np.array([hwz.z_dict['cc_max'] for hwz in all_HWz]),name='cc_max')
     dr7_tst.add_columns([DR7_z,JXP_z,cc_max])
-    xxf.table_to_fits(dr7_tst,'HW_DR7_test.fits')
+    Table(dr7_tst).write('HW_DR7_test.fits',format='fits',overwrite=True)
 
     print('All done!')
 

### 2017-03-24 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -3,19 +3,13 @@
 from __future__ import print_function, absolute_import, division, unicode_literals
 import numpy as np
 import glob, os, sys, copy
-from scipy import stats as scistats
 import matplotlib as mpl
 mpl.rcParams['font.family'] = 'stixgeneral'
 from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib import pyplot as plt
 import matplotlib.gridspec as gridspec
-from astropy.table import QTable
-from astropy.io import ascii, fits
 from astropy import units as u
-from astropy import constants as const
 from linetools.spectra.xspectrum1d import XSpectrum1D
-from xastropy.plotting import utils as xputils
-from xastropy.xutils import xdebug as xdb
 sys.path.append(os.path.abspath("../../../../py"))
 from enigma.qpq import stacks as qpqk
 from enigma.qpq import qpq as eqpq
@@ -136,7 +130,9 @@ def plt_qpq9(stack_tup=None,wrest=None,
             ax.plot(vmnx.value, [1.]*2, 'g:')
             ax.plot([0]*2, ymnx, 'b--')
             # Font
-            xputils.set_fontsize(ax,7.)
+        for item in ([ax.title, ax.xaxis.label, ax.yaxis.label] +
+                         ax.get_xticklabels() + ax.get_yticklabels()):
+            item.set_fontsize(7)
 
         # Layout and save
         try:

### 2017-03-24 QPQ9/Analysis/monte_carlo.py

@@ -1,131 +1,0 @@
-from __future__ import print_function,absolute_import,division,unicode_literals
-import numpy as np
-import glob,os,sys,copy,imp
-from scipy import stats as scistats
-import matplotlib as mpl
-mpl.rcParams['font.family']='stixgeneral'
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib import pyplot as plt
-import matplotlib.gridspec as gridspec
-from astropy.table import QTable,Table
-from astropy.io import ascii,fits
-from astropy import units as u
-from astropy import constants as const
-from astropy.coordinates import SkyCoord
-from linetools.spectralline import AbsLine
-import linetools.utils as ltu
-sys.path.append(os.path.abspath("../../../py"))
-from enigma.qpq import utils as qpqutils
-from enigma.qpq import spec as qpqs
-from enigma.qpq import stacks as qpqk
-sys.path.append(os.path.abspath("./Stacks/py"))
-import qpq9_stacks as qpq9k
-import scipy.integrate as integrate
-from astropy.modeling import models,fitting
-from astropy.cosmology import FlatLambdaCDM
-cosmo = FlatLambdaCDM(H0=70,Om0=0.26)
-
-def gen_stck_img(R_phys,z_fg,Deltav,v_grid,n_trials): # R_phys in kpc, Deltav in km/s
-    probs = np.zeros(len(v_grid))
-    cumulative_probs = np.zeros(len(v_grid))
-    Hubble_h = cosmo.H(0).value/100.
-    ell_IGM_DLA = 0.2*((1+z_fg)/(1+2.5))**2.1
-    ell_IGM_SLLS = 0.44*((1+z_fg)/(1+2.5))**2.1
-    ell_IGM_LLS = 1.05*((1+z_fg)/(1+2.5))**2.1
-    R_comov = R_phys/1000.*(1+z_fg)*Hubble_h # in h^-1 Mpc
-    for ii,vv in enumerate(v_grid):
-        gamma_DLA = 1.6
-        r0_DLA = 3.9
-#        gamma_SLLS = 1.6
-#        r0_SLLS = 15.5
-#        gamma_LLS = 1.6
-#        r0_LLS = 13.9
-        gamma_SLLS = 1.68
-        r0_SLLS = 14.0
-        gamma_LLS = 1.68
-        r0_LLS = 12.5
-        chi_DLA = 1./Deltav*integrate.quad(
[…]

### 2017-03-24 QPQ9/Analysis/py/monte_carlo.py

@@ -1,0 +1,118 @@
+from __future__ import print_function,absolute_import,division,unicode_literals
+import numpy as np
+import glob,os,sys,copy,imp
+from scipy import stats as scistats
+import matplotlib as mpl
+mpl.rcParams['font.family']='stixgeneral'
+from matplotlib import pyplot as plt
+from astropy.table import QTable,Table
+from astropy.io import ascii,fits
+from astropy import units as u
+import linetools.utils as ltu
+sys.path.append(os.path.abspath("../Stacks/py"))
+import qpq9_stacks as qpq9k
+import scipy.integrate as integrate
+from astropy.modeling import models,fitting
+from astropy.cosmology import FlatLambdaCDM
+cosmo = FlatLambdaCDM(H0=70,Om0=0.26)
+
+def gen_stck_img(R_phys,z_fg,Deltav,v_grid,n_trials): # R_phys in kpc, Deltav in km/s
+    probs = np.zeros(len(v_grid))
+    cumulative_probs = np.zeros(len(v_grid))
+    Hubble_h = cosmo.H(0).value/100.
+    ell_IGM_DLA = 0.2*((1+z_fg)/(1+2.5))**2.1
+    ell_IGM_SLLS = 0.44*((1+z_fg)/(1+2.5))**2.1
+    ell_IGM_LLS = 1.05*((1+z_fg)/(1+2.5))**2.1
+    R_comov = R_phys/1000.*(1+z_fg)*Hubble_h # in h^-1 Mpc
+    for ii,vv in enumerate(v_grid):
+        gamma_DLA = 1.6
+        r0_DLA = 3.9
+#        gamma_SLLS = 1.6
+#        r0_SLLS = 15.5
+#        gamma_LLS = 1.6
+#        r0_LLS = 13.9
+        gamma_SLLS = 1.68
+        r0_SLLS = 14.0
+        gamma_LLS = 1.68
+        r0_LLS = 12.5
+        chi_DLA = 1./Deltav*integrate.quad(
+            lambda v:(np.sqrt(R_comov**2+(v/(cosmo.H(z_fg).value/(1+z_fg)))**2)/r0_DLA)**(-gamma_DLA),
+            v_grid[ii]-Deltav/2,v_grid[ii]+Deltav/2)[0]
+        chi_SLLS = 1./Deltav*integrate.quad(
+            lambda v:(np.sqrt(R_comov**2+(v/(cosmo.H(z_fg).value/(1+z_fg)))**2)/r0_SLLS)**(-gamma_SLLS),
[…]

### 2017-03-24 QPQ9/Analysis/py/qpq9_strct.py

@@ -1,153 +1,357 @@
-# Module for QPQ9 structure
-
-from __future__ import print_function, absolute_import, division, unicode_literals
-
+# imports
+import copy, os, glob, imp, shutil
 import numpy as np
-import glob, copy, os, sys
 
-import sdsspy as spy
-
-from astropy import units as u
-from astropy.units import Unit
-from astropy.io import ascii, fits
-from astropy.table import QTable, Table, Column
 from astropy.coordinates import SkyCoord
+from astropy import units as u
+from astropy.table import Column, Table, QTable
+from astropy.io import fits, ascii
+
+from specdb.specdb import IgmSpec, SpecDB
+
+from linetools import utils as ltu
+
 from astropy.cosmology import FlatLambdaCDM
-from astropy.relativity import velocities as arv
-from astropy import constants as const
 
-from xastropy.xutils import fits as xxf
-from xastropy.xutils import xdebug as xdb
+import enigma
 
-sys.path.append(os.path.abspath(os.getenv('QPQ9')+"Analysis/Redshifts/py"))
-import zsys_figs as qpqz
+cosmo = FlatLambdaCDM(H0=70, Om0=0.26)
 
-sys.path.append(os.path.abspath(os.getenv('QPQ9')+"Analysis/py"))
-import qpq_sample as qpqsmp
+## List of near IR redshifts
 
-##
-def mk_qpq9(outfil=None):
+# Load masterlists
+path = enigma.__path__[0]+'/data/redshifts/'
+c_NIR = []
+gnirs = Table.read(path+'gnirs_masterlist.dat',guess=False,format='ascii.csv',comment='#')
+for qq in gnirs:
+    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
+niri = Table.read(path+'niri_masterlist.dat',guess=False,format='ascii.csv',comment='#')
+for qq in niri:
[…]

### 2017-03-24 QPQ9/Figures/py/qpq9_figs.py

@@ -1,9 +1,7 @@
 #Module for QPQ9 figures
 # Imports
 from __future__ import print_function, absolute_import, division, unicode_literals
-
 import copy,os,sys,imp
-
 import matplotlib as mpl
 import numpy as np
 mpl.rcParams['font.family'] = 'stixgeneral'
@@ -19,9 +17,7 @@ from astropy.utils.misc import isiterable
 from astropy.modeling import models
 
 from linetools.spectralline import AbsLine
-
-from xastropy.plotting import utils as xputils
-from xastropy.atomic import ionization as xai
+from linetools.abund import ions
 
 sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
 import qpq9_stacks as qpq9k
@@ -69,13 +65,13 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
         for ii,idict in enumerate(all_dict):
             if idict is None:
                 continue
-            if xai.ion_name(aline.data) == 'CII':
+            if ions.ion_name(aline.data) == 'CII':
                 if 'J1508+3635' in idict['qpq']['NAME']: #DLA, should be excluded now
                     idx_mask.append(ii)
-            if xai.ion_name(aline.data) == 'CIV':
+            if ions.ion_name(aline.data) == 'CIV':
                 if 'J1002+0020' in idict['qpq']['NAME']: #overlaps with BAL of bg quasar
                     idx_mask.append(ii)
-            if xai.ion_name(aline.data) == 'MgII':
+            if ions.ion_name(aline.data) == 'MgII':
                 if (('J0822+1319' in idict['qpq']['NAME']) | ('J0908+4215' in idict['qpq']['NAME']) |
                         ('J1242+1817' in idict['qpq']['NAME']) | ('J1622+2031' in idict['qpq']['NAME'])):
                     #BAL, strange emission, sky emission, sky emission
@@ -114,13 +110,16 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
             ax.set_xlabel(r'$R_\perp$ (kpc)')
         ax.text((ax.get_xlim()[1]-ax.get_xlim()[0])*0.05+ax.get_xlim()[0],
[…]

### 2017-03-24 QPQ9/Tables/py/qpq9_tables.py

@@ -1,188 +1,616 @@
-#Module for Tables for QPQ9
-# Imports
-from __future__ import print_function, absolute_import, division, unicode_literals
-
+# imports
+from __future__ import print_function,absolute_import,division,unicode_literals
 import numpy as np
-import glob, os, sys, copy
-from scipy import stats as scistats
-
+import glob,os,sys,copy,imp
 import matplotlib as mpl
-mpl.rcParams['font.family'] = 'stixgeneral'
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib import pyplot as plt
-import matplotlib.gridspec as gridspec
-
-from astropy.io import ascii, fits
+mpl.rcParams['font.family']='stixgeneral'
+from astropy.table import QTable,Table
+from astropy.io import ascii,fits
 from astropy import units as u
-from astropy.table import QTable
+from astropy.coordinates import SkyCoord
+sys.path.append(os.path.abspath("../../../py"))
+sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
+import qpq9_stacks as qpq9k
+import enigma
 
-from xastropy.plotting import utils as xputils
-from xastropy.xutils import xdebug as xdb
-from xastropy.atomic import ionization as xai
+# Load QPQ9 structure
+path = enigma.__path__[0]+'/data/qpq/'
+QPQ9 = QTable(fits.open(path+'qpq9_final.fits')[1].data)
 
-# Local
-sys.path.append(os.path.abspath("../Analysis/py"))
-import qpq9_analy as qpq9a
-import qpq_spec as qpqs
+## Make the table that lists the full QPQ9 sample
 
-# ##################### #####################
-# ##################### #####################
-# Summary table of all transitions measured
-def mktab_summ(outfil='tab_summ.tex', vcut=None, all_tups=None,
-    passback=False, use_oiii=True):
-    '''Summary table
-    Parameters:
-    -----------
-    use_oiii: bool, optional
-      Require [OIII]?  [Default=True]
-    '''
+# Load the dictionaries of quasars used in stack for CII
[…]

### 2017-04-11 QPQ9/qpq9_draft.tex
contour plot now four levels

@@
 lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
-$1\sigma$ modeling error of the centroid and dispersion of the \ion{C}{2} mean stack is 
-$\approx35\,{\rm km\,s^{-1}}$, which is also the typical modeling errors of the other stacks. 
+$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are 
+$28\,{\rm km\,s^{-1}}$ and $29\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling 
+errors of the other stacks.
 }
@@
 \ion{C}{2} stack to be $+208\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be 
-$312\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the standard 
+$318\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the standard 
 expectation, while the dispersion suggests extreme kinematics. The median stack, on the other 
@@
 absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
-$+239\,{\rm km\,s^{-1}}$, and a dispersion of $349\,{\rm km\,s^{-1}}$, consistent with the full 
+$+249\,{\rm km\,s^{-1}}$, and a dispersion of $362\,{\rm km\,s^{-1}}$, consistent with the full 
 sample.
@@
 dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
-absorption profile with $\sigma_v=654\,{\rm km\,s^{-1}}$, which is larger than the observed width 
+absorption profile with $\sigma_v=573\,{\rm km\,s^{-1}}$, which is larger than the observed width 
 by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity 
 width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with 
-$\sigma_v=207\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the 
+$\sigma_v=231\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the 
 modeling error. Unless gravitational and Hubble flows together with redshift error broadening 
@@
 
+\begin{figure}
+\includegraphics[width=2.5in]{Figures/fig_contour.pdf}
+%\includegraphics[width=2.5in]{f06.pdf}
+\caption{
+Probability distributions of the parameters $W_{\rm CII}$ and $M_{\rm halo}$. The plot shows the 
+degeneracy between $W_{\rm CII}$ and $M_{\rm halo}$ in recovering the intrinsic width of the 
+absorption profile. We mark contours for points that produce an absorption 
+profile of width that is 1, 2, 3, and 4 times the modeling error away from the observed intrinsic 
+width. The intrinsic velocity width corresponding to typical QPQ halo mass is marked with a plus 
+sign, and is well contained within the 2$\sigma$ contour.}
+\label{fig:contour}
+\end{figure}
+
 Under the assumption that the intrinsic dispersion and the redshift uncertainty add in 
@@
 $\sigma_{{\rm error}(z)}^{\rm full}=182\,{\rm km\,s^{-1}}$, we recover 
-$\sigma_{\rm intrinsic}^{\rm full}=253\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
-redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=342\,{\rm km\,s^{-1}}$.
+$\sigma_{\rm intrinsic}^{\rm full}=261\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
+redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=356\,{\rm km\,s^{-1}}$.
 
@@
 \cite{RodriguezTorres+16} measured the clustering of quasars in the range $1.8<z<2.2$. They 
-estimated that these quasars are hosted by dark matter halos with mass $10^{12.5}\,M_\odot$ and 
-$10^{12.6}\,M_\odot$ respectively. If dark matter halos hosting QPQ9 quasars have a characteristic 
-mass $10^{12.6}\,M_\odot$ and follow an NFW profile \citep{NavarroFrenkWhite97} with concentration 
+estimated that these quasars are hosted by dark matter halos with mass 
+$M_{\rm halo}=10^{12.5}\,M_\odot$ and $M_{\rm halo}10^{12.6}\,M_\odot$ respectively. If dark 
+matter halos hosting QPQ9 quasars have a characteristic mass $10^{12.6}\,M_\odot$ and follow an 
+NFW profile \citep{NavarroFrenkWhite97} with concentration 
 parameter $c=4$, at $z\approx2$ the maximum circular velocity is $345\,{\rm km\,s^{-1}}$. 
@@
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $281\,{\rm km\,s^{-1}}$. This is 
-within $1\sigma$ modeling error from the intrinsic dispersion in the \ion{C}{2} mean stack for the 
-full sample, and about 2 times the modeling error away from the intrinsic dispersion in the stack 
-of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $284\,{\rm km\,s^{-1}}$. This is 
+about $1\sigma$ modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack for 
+the full sample, and about 3 times the modeling error away from the intrinsic dispersion in the 
+stack of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
 sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering 
@@
 combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical 
-processes are not necessary to explain the large velocity fields. From the bootstrap analysis of 
-the observed dispersion, a width of $\sigma_v>654\,{\rm km\,s^{-1}}$ would be larger than the 
-observed by three times the scatter (overplotted in Figure~\ref{fig:monte}). In other words, 
-taking into account the redshift errors, motions in addition to gravitational and Hubble 
-flows that will produce an intrinsic dispersion $\sigma_v>628\,{\rm km\,s^{-1}}$ can be ruled out.
+processes are not necessary to explain the large velocity fields.
 
-On the contrary, $\sigma_{\rm 1D}<74\,{\rm km\,s^{-1}}$ together with Hubble velocities and 
+From the bootstrap 
+analysis of the observed dispersion, a width of $\sigma_v>573\,{\rm km\,s^{-1}}$ would be larger 
+than the observed by three times the scatter (overplotted in Figure~\ref{fig:monte}). In other 
+words, taking into account the redshift errors, motions in addition to gravitational and Hubble 
+flows that will produce an intrinsic dispersion $\sigma_v>543\,{\rm km\,s^{-1}}$ can be ruled out.
+
+On the contrary, 
+$\sigma_{\rm 1D}<114\,{\rm km\,s^{-1}}$ together with Hubble velocities and 
 broadening by redshift errors will result in a velocity width that is more than three times the 
 modeling error away from the observed width (overplotted in Figure~\ref{fig:monte}). This implies 
-that, unless the characteristic dark matter halo mass $<10^{11.0}\,M_\odot$, additional dynamical 
-processes are not required to explain the observed width.
+that, unless the characteristic $M_{\rm halo}<10^{11.6}\,M_\odot$, 
+additional dynamical processes are not required to explain the observed width.
+
+In Figure~\ref{fig:contour}, We show the probability distributions of the degenerate parameters 
+$W_{\rm CII}$ and $M_{\rm halo}$ in recovering the intrinsic width of the absorption profile. We 
+require that the amplitude of the absorption is reproduced within 3 times its modeling error, and 
+mark contours for points in ($W_{\rm CII}$, $M_{\rm halo}$)-space that produce an absorption 
+profile of width within 1, 2, 3, and 4 times the modeling error of the observed intrinsic width. 
+From the figure, a higher $W_{\rm CII}$ means the $M_{\rm halo}$ that will reproduce the observed 
+width is higher. If there are no extra dynamical processes, the intrinsic velocity width 
+corresponding to typical QPQ halo mass is well contained within the 2$\sigma$ contour.
 
@@
 \includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
-%\includegraphics[width=3.4in]{f06.pdf}
+%\includegraphics[width=3.4in]{f07.pdf}
 \caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
@@
 \includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
-%\includegrpahics[width=\textwidth]{f07.pdf}
+%\includegrpahics[width=\textwidth]{f08.pdf}
 \caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
@@
 \includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
-%\includegraphics[width=\textwidth]{f08.pdf}
+%\includegraphics[width=\textwidth]{f09.pdf}
 \caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 

### 2017-04-11 QPQ9/Analysis/py/monte_carlo.py

@@ -9,14 +9,23 @@ from astropy.table import QTable,Table
 from astropy.io import ascii,fits
 from astropy import units as u
 import linetools.utils as ltu
-sys.path.append(os.path.abspath("../Stacks/py"))
+sys.path.append(os.path.abspath("./Stacks/py"))
 import qpq9_stacks as qpq9k
 import scipy.integrate as integrate
 from astropy.modeling import models,fitting
 from astropy.cosmology import FlatLambdaCDM
 cosmo = FlatLambdaCDM(H0=70,Om0=0.26)
 
-def gen_stck_img(R_phys,z_fg,Deltav,v_grid,n_trials): # R_phys in kpc, Deltav in km/s
+
+# the constants
+n_trials = 1000
+Deltav = 10.
+v_grid = -2000. + np.arange((2000.-(-2000.))/Deltav+1)*Deltav
+relativistic_equiv = u.doppler_relativistic(1334.5323*u.AA)
+wave_grid = (v_grid*u.km/u.s).to(u.AA,equivalencies=relativistic_equiv)
+
+# Generate a stack image of n_trials monte carlo trials
+def gen_stck_img(R_phys,z_fg,stddev_oneabs,sigma1D): # R_phys in kpc, Deltav in km/s
     probs = np.zeros(len(v_grid))
     cumulative_probs = np.zeros(len(v_grid))
     Hubble_h = cosmo.H(0).value/100.
@@ -44,7 +53,7 @@ def gen_stck_img(R_phys,z_fg,Deltav,v_grid,n_trials): # R_phys in kpc, Deltav in
         chi_LLS = 1./Deltav*integrate.quad(
             lambda v:(np.sqrt(R_comov**2+(v/(cosmo.H(z_fg).value/(1+z_fg)))**2)/r0_LLS)**(-gamma_LLS),
             v_grid[ii]-Deltav/2,v_grid[ii]+Deltav/2)[0]
-        Deltaz = ltu.z_from_v(z_fg,v_grid[ii]+Deltav/2)-ltu.z_from_v(z_fg,v_grid[ii]-Deltav/2)
+        Deltaz = ltu.z_from_dv((v_grid[ii]+Deltav/2)*u.km/u.s,z_fg)-ltu.z_from_dv((v_grid[ii]-Deltav/2)*u.km/u.s,z_fg)
[…]

### 2017-04-11 QPQ9/Figures/py/qpq9_figs.py

@@ -330,7 +330,7 @@ def stacks_fg(outfil=None):
         # Axes
         ax = plt.subplot(gs[kk,0])
         ax.set_xlim(np.min(velo.value)+500,np.max(velo.value)-500)
-        ax.set_ylim(0.90,1.06)
+        ax.set_ylim(0.88,1.09)
         ax.tick_params(labelsize=fontsize,length=5,width=1)
         # Labels
         ax.set_ylabel('Normalized Flux')
@@ -387,19 +387,19 @@ def monte(outfil=None):
     Gaussian_params = (ascii.read(path+'CII_MgII_mean_fit.dat'))[0]
     model_conti = models.Const1D(amplitude=Gaussian_params['amplitude_0'])
     model_monte_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude_1'],mean=Gaussian_params['mean_1'],
-        stddev=np.sqrt((monte_params['stddev_1'])**2.+182**2.))
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],
+        stddev=np.sqrt((monte_params['stddev'])**2.+182**2.))
     print('s.d. in monte carlo model, in monte carlo model with redshift error broadening, in data',
-          monte_params['stddev_1'],np.sqrt((monte_params['stddev_1'])**2.+182**2.),
+          monte_params['stddev'],np.sqrt((monte_params['stddev'])**2.+182**2.),
           Gaussian_params['stddev_1'])
     model_monte = model_conti*model_monte_gauss
     # Extra motion that is ruled out
     model_extra_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude_1'],mean=Gaussian_params['mean_1'],stddev=654.)
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=573.)
     model_extra = model_conti*model_extra_gauss
     # Width that requires outflow
     model_outflow_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude_1'],mean=Gaussian_params['mean_1'],stddev=207.)
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=231.)
     model_outflow = model_conti*model_outflow_gauss
 
     # Axes
[…]

### 2017-04-13 QPQ9/Figures/py/qpq9_figs.py
small changes

@@ -177,7 +177,7 @@ def stacks_and_fits(outfil=None):
         # Axes
         ax = plt.subplot(gs[kk,0])
         ax.set_xlim(-2500,2500)
-        ax.set_ylim(0.82,1.03)
+        ax.set_ylim(0.81,1.03)
         ax.tick_params(labelsize=fontsize,length=5,width=1)
         # Labels
         ax.set_ylabel('Normalized Flux')
@@ -405,7 +405,7 @@ def monte(outfil=None):
     # Axes
     ax = plt.subplot(gs[0,0])
     ax.set_xlim(np.min(velo.value+500),np.max(velo.value-500))
-    ax.set_ylim(0.82,1.03)
+    ax.set_ylim(0.81,1.03)
     ax.tick_params(labelsize=fontsize,length=5,width=1)
     # Labels
     ax.set_ylabel('Normalized Flux')

### 2017-06-08 QPQ9/Submit/qpq9_submit.tex
added submitted manuscript and referee report

--- 2017-04-11 QPQ9/qpq9_draft.tex
@@
 \title{Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding 
-$z\sim2$ Quasars [v1.4]}
+$z\sim2$ Quasars}
 
@@
 $\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
-motion and Hubble flow, and galactic-scale outflows are not be required to explain the large 
+motion and Hubble flow, and galactic-scale outflows are not required to explain the large 
 widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
@@
 large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on 
-1\textendash2\,Mpc scales. \cite{Johnson+15} studied the CGM surrounding $z\sim1$ quasars, and 
+1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of 
+star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
+$z\sim1$ quasars, and 
 found large peculiar motions in the gas exceeding the expected virial velocity, which they 
@@
 
-\input{Tables/tab_sample.tex}
-%\input{tab_sample.tex}
+%\input{Tables/tab_sample.tex}
+\input{tab_sample.tex}
 
 \begin{figure}
-\includegraphics[width=3in]{Figures/fig_experiment.pdf}
-%\includegraphics[width=3in]{f01.pdf}
+%\includegraphics[width=3in]{Figures/fig_experiment.pdf}
+\includegraphics[width=3in]{f01.pdf}
 \caption{These panels summarize properties of the QPQ9 dataset. The QPQ survey selects 
@@
 \begin{figure}
-\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
-%\includegraphics[width=3.5in]{f02.pdf}
+%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
+\includegraphics[width=3.5in]{f02.pdf}
 \caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
@@
 analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
-and it is more challenging to interpret their kinematics.
+and it is more challenging to analyze their kinematics.
 %To assess the average absorption of these transitions,
@@
 
-\input{Tables/tab_summary.tex}
-%\input{tab_summary.tex}
+%\input{Tables/tab_summary.tex}
+\input{tab_summary.tex}
 
@@
 randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
-to model each bootstrap realization, and quote the standard deviation in the the bootstrap 
+to model each bootstrap realization, and quote the standard deviation in the bootstrap 
 realizations to be the scatter in the centroids of the data. The scatters 
@@
 redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is 
-dominated by \ion{Mg}{2} emission, a shift of $57\,{\rm km\,s^{-1}}$ is applied. There are 231 
+dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are 231 
 pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present 
@@
 \begin{figure}
-\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
-%\includegraphics[width=2.5in]{f03.pdf}
+%\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
+\includegraphics[width=2.5in]{f03.pdf}
 \caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
@@
 \begin{figure}
-\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
-%\includegraphics[width=2.5in]{f04.pdf}
+%\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
+\includegraphics[width=2.5in]{f04.pdf}
 \caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
@@
 \begin{figure}
-\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
-%\includegraphics[width=2.5in]{f05.pdf}
+%\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
+\includegraphics[width=2.5in]{f05.pdf}
 \caption{The same \ion{C}{2} mean stack shown in the first panel of 
@@
 \begin{figure}
-\includegraphics[width=2.5in]{Figures/fig_contour.pdf}
-%\includegraphics[width=2.5in]{f06.pdf}
+%\includegraphics[width=2.5in]{Figures/fig_contour.pdf}
+\includegraphics[width=2.5in]{f06.pdf}
 \caption{
@@
 absorption profile. We mark contours for points that produce an absorption 
-profile of width that is 1, 2, 3, and 4 times the modeling error away from the observed intrinsic 
+profile of width that is 1, 2, and 3 times the modeling error away from the observed intrinsic 
 width. The intrinsic velocity width corresponding to typical QPQ halo mass is marked with a plus 
-sign, and is well contained within the 2$\sigma$ contour.}
+sign, and is well contained within the 1$\sigma$ contour.}
 \label{fig:contour}
@@
 \cite{Eftekharzadeh+15} measured the clustering of quasars in the range $2.2<z<2.8$ while 
-\cite{RodriguezTorres+16} measured the clustering of quasars in the range $1.8<z<2.2$. They 
+\cite{RodriguezTorres+17} measured the clustering of quasars in the range $1.8<z<2.2$. They 
 estimated that these quasars are hosted by dark matter halos with mass 
-$M_{\rm halo}=10^{12.5}\,M_\odot$ and $M_{\rm halo}10^{12.6}\,M_\odot$ respectively. If dark 
+$M_{\rm halo}=10^{12.5}\,M_\odot$ and $M_{\rm halo}=10^{12.6}\,M_\odot$ respectively. If dark 
 matter halos hosting QPQ9 quasars have a characteristic mass $10^{12.6}\,M_\odot$ and follow an 
@@
 mark contours for points in ($W_{\rm CII}$, $M_{\rm halo}$)-space that produce an absorption 
-profile of width within 1, 2, 3, and 4 times the modeling error of the observed intrinsic width. 
+profile of width within 1, 2, and 3 times the modeling error of the observed intrinsic width. 
 From the figure, a higher $W_{\rm CII}$ means the $M_{\rm halo}$ that will reproduce the observed 
 width is higher. If there are no extra dynamical processes, the intrinsic velocity width 
-corresponding to typical QPQ halo mass is well contained within the 2$\sigma$ contour.
+corresponding to typical QPQ halo mass is well contained within the 1$\sigma$ contour.
 
@@
 \begin{figure}
-\includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
-%\includegraphics[width=3.4in]{f07.pdf}
+%\includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
+\includegraphics[width=3.4in]{f07.pdf}
 \caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
@@
 \begin{minipage}[!bp]{0.28\textwidth}
-\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
-%\includegrpahics[width=\textwidth]{f08.pdf}
+%\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
+\includegraphics[width=\textwidth]{f08.pdf}
 \caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
@@
 \begin{minipage}[!bp]{0.67\textwidth}
-\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
-%\includegraphics[width=\textwidth]{f09.pdf}
+%\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
+\includegraphics[width=\textwidth]{f09.pdf}
 \caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
@@
 \cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy 
-inlcuding thermal AGN feedback and calculated radiative transfer in post-processing. They found 
+including thermal AGN feedback and calculated radiative transfer in post-processing. They found 
 the ionization radiation is typically asymmetric, due to either a dense clump that lies on one 
@@
 extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of 
-$\sim10^6$\,Myr, which lies within existing constraints of quasar lifetime from observations 
+$\sim10^6$\,yr, which lies within existing constraints of quasar lifetime from observations 
 \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
@@
 
-JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1412981. The 
-authors gratefully acknowledge the support which enabled these observations at the Keck, Gemini, 
-Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar Observatories. MWL 
-thanks T.-K. Chan for a discussion on CGM simulations and Chi Po Choi for a discussion on 
-statistics.
+JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and 
+AST-1412981. The authors gratefully acknowledge the support which enabled these observations at 
+the Keck, Gemini, Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar 
+Observatories. MWL thanks T.-K. Chan for a discussion on CGM simulations and Chi Po Choi for a 
+discussion on statistics.
 
-\bibliographystyle{/Users/lwymarie/Documents/Bibli/apj}
-\bibliography{/Users/lwymarie/Documents/Bibli/allrefs}
+%\bibliographystyle{/Users/lwymarie/Documents/Bibli/apj}
+%\bibliography{/Users/lwymarie/Documents/Bibli/allrefs}
+
+\begin{thebibliography}{45}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Baldwin}(1977)}]{Baldwin77}
+{Baldwin}, J.~A. 1977, \apj, 214, 679
+
+\bibitem[{{Bergeron} \& {Boisse}(1991)}]{BergeronBoisse91}
+{Bergeron}, J., \& {Boisse}, P. 1991, Advances in Space Research, 11, 241
+
+\bibitem[{{Boroson}(2005)}]{Boroson05}
+{Boroson}, T. 2005, \aj, 130, 381
+
+\bibitem[{{Cantalupo} {et~al.}(2014){Cantalupo}, {Arrigoni-Battaia},
+  {Prochaska}, {Hennawi}, \& {Madau}}]{Cantalupo+14}
+{Cantalupo}, S., {Arrigoni-Battaia}, F., {Prochaska}, J.~X., {Hennawi}, J.~F.,
+  \& {Madau}, P. 2014, \nat, 506, 63
+
+\bibitem[{{Churchill} {et~al.}(2012){Churchill}, {Kacprzak}, {Steidel},
+  {Spitler}, {Holtzman}, {Nielsen}, \& {Trujillo-Gomez}}]{Churchill+12}
+{Churchill}, C.~W., {Kacprzak}, G.~G., {Steidel}, C.~C., {Spitler}, L.~R.,
+  {Holtzman}, J., {Nielsen}, N.~M., \& {Trujillo-Gomez}, S. 2012, \apj, 760, 68
+
+\bibitem[{{Eftekharzadeh} {et~al.}(2015){Eftekharzadeh}, {Myers}, {White},
+  {Weinberg}, {Schneider}, {Shen}, {Font-Ribera}, {Ross}, {Paris}, \&
+  {Streblyanska}}]{Eftekharzadeh+15}
+{Eftekharzadeh}, S., {Myers}, A.~D., {White}, M., {Weinberg}, D.~H.,
+  {Schneider}, D.~P., {Shen}, Y., {Font-Ribera}, A., {Ross}, N.~P., {Paris},
+  I., \& {Streblyanska}, A. 2015, \mnras, 453, 2779
+
+\bibitem[{{Fumagalli} {et~al.}(2011){Fumagalli}, {Prochaska}, {Kasen}, {Dekel},
+  {Ceverino}, \& {Primack}}]{Fumagalli+11}
+{Fumagalli}, M., {Prochaska}, J.~X., {Kasen}, D., {Dekel}, A., {Ceverino}, D.,
+  \& {Primack}, J.~R. 2011, \mnras, 418, 1796
+
+\bibitem[{{Gabor} \& {Bournaud}(2014)}]{GaborBournaud14}
+{Gabor}, J.~M., \& {Bournaud}, F. 2014, \mnras, 441, 1615
+
+\bibitem[{{Gauthier}(2013)}]{Gauthier13}
+{Gauthier}, J.-R. 2013, \mnras, 432, 1444
+
+\bibitem[{{Hennawi} {et~al.}(2006){Hennawi}, {Prochaska}, {Burles}, {Strauss},
+  {Richards}, {Schlegel}, {Fan}, {Schneider}, {Zakamska}, {Oguri}, {Gunn},
+  {Lupton}, \& {Brinkmann}}]{QPQ1}
+{Hennawi}, J.~F., {Prochaska}, J.~X., {Burles}, S., {Strauss}, M.~A.,
+  {Richards}, G.~T., {Schlegel}, D.~J., {Fan}, X., {Schneider}, D.~P.,
+  {Zakamska}, N.~L., {Oguri}, M., {Gunn}, J.~E., {Lupton}, R.~H., \&
+  {Brinkmann}, J. 2006, \apj, 651, 61
+
+\bibitem[{{Hennawi} {et~al.}(2015){Hennawi}, {Prochaska}, {Cantalupo}, \&
+  {Arrigoni-Battaia}}]{Hennawi+15}
+{Hennawi}, J.~F., {Prochaska}, J.~X., {Cantalupo}, S., \& {Arrigoni-Battaia},
+  F. 2015, Science, 348, 779
+
+\bibitem[{{Hewett} \& {Wild}(2010)}]{HewettWild10}
+{Hewett}, P.~C., \& {Wild}, V. 2010, \mnras, 405, 2302
+
+\bibitem[{{Ho} {et~al.}(2017){Ho}, {Martin}, {Kacprzak}, \&
+  {Churchill}}]{Ho+17}
+{Ho}, S.~H., {Martin}, C.~L., {Kacprzak}, G.~G., \& {Churchill}, C.~W. 2017,
+  \apj, 835, 267
+
+\bibitem[{{Hopkins} {et~al.}(2005){Hopkins}, {Hernquist}, {Martini}, {Cox},
+  {Robertson}, {Di Matteo}, \& {Springel}}]{Hopkins+05}
+{Hopkins}, P.~F., {Hernquist}, L., {Martini}, P., {Cox}, T.~J., {Robertson},
+  B., {Di Matteo}, T., \& {Springel}, V. 2005, \apjl, 625, L71
+
+\bibitem[{{Johnson} {et~al.}(2015){Johnson}, {Chen}, \&
+  {Mulchaey}}]{Johnson+15}
+{Johnson}, S.~D., {Chen}, H.-W., \& {Mulchaey}, J.~S. 2015, \mnras, 452, 2553
+
+\bibitem[{{Kere\v{s}} {et~al.}(2009){Kere\v{s}}, {Katz}, {Fardal}, {Dav{\'e}},
+  \& {Weinberg}}]{Keres+09}
+{Kere\v{s}}, D., {Katz}, N., {Fardal}, M., {Dav{\'e}}, R., \& {Weinberg}, D.~H.
+  2009, \mnras, 395, 160
+
+\bibitem[{{Kirkman} \& {Tytler}(2008)}]{KirkmanTytler08}
+{Kirkman}, D., \& {Tytler}, D. 2008, \mnras, 391, 1457
+
+\bibitem[{{Lau} {et~al.}(2016){Lau}, {Prochaska}, \& {Hennawi}}]{QPQ8}
+{Lau}, M.~W., {Prochaska}, J.~X., \& {Hennawi}, J.~F. 2016, \apjs, 226, 25
+
+\bibitem[{{Martin}(2005)}]{Martin05}
+{Martin}, C.~L. 2005, \apj, 621, 227
+
+\bibitem[{{Martini}(2004)}]{Martini04}
+{Martini}, P. 2004, Coevolution of Black Holes and Galaxies, 169
+
+\bibitem[{{Muzahid} {et~al.}(2015){Muzahid}, {Kacprzak}, {Churchill},
+  {Charlton}, {Nielsen}, {Mathes}, \& {Trujillo-Gomez}}]{Muzahid+15}
+{Muzahid}, S., {Kacprzak}, G.~G., {Churchill}, C.~W., {Charlton}, J.~C.,
+  {Nielsen}, N.~M., {Mathes}, N.~L., \& {Trujillo-Gomez}, S. 2015, \apj, 811,
+  132
+
+\bibitem[{{Navarro} {et~al.}(1997){Navarro}, {Frenk}, \&
+  {White}}]{NavarroFrenkWhite97}
+{Navarro}, J.~F., {Frenk}, C.~S., \& {White}, S.~D.~M. 1997, \apj, 490, 493
+
+\bibitem[{{P{\^a}ris} {et~al.}(2017){P{\^a}ris}, {Petitjean}, {Ross}, {Myers},
+  {Aubourg}, {Streblyanska}, {Bailey}, {Armengaud}, {Palanque-Delabrouille},
+  {Y{\`e}che}, {Hamann}, {Strauss}, {Albareti}, {Bovy}, {Bizyaev}, {Niel
+  Brandt}, {Brusa}, {Buchner}, {Comparat}, {Croft}, {Dwelly}, {Fan},
+  {Font-Ribera}, {Ge}, {Georgakakis}, {Hall}, {Jiang}, {Kinemuchi},
+  {Malanushenko}, {Malanushenko}, {McMahon}, {Menzel}, {Merloni}, {Nandra},
+  {Noterdaeme}, {Oravetz}, {Pan}, {Pieri}, {Prada}, {Salvato}, {Schlegel},
+  {Schneider}, {Simmons}, {Viel}, {Weinberg}, \& {Zhu}}]{Paris+17}
+{P{\^a}ris}, I., {Petitjean}, P., {Ross}, N.~P., {Myers}, A.~D., {Aubourg},
+  {\'E}., {Streblyanska}, A., {Bailey}, S., {Armengaud}, {\'E}.,
+  {Palanque-Delabrouille}, N., {Y{\`e}che}, C., {Hamann}, F., {Strauss}, M.~A.,
+  {Albareti}, F.~D., {Bovy}, J., {Bizyaev}, D., {Niel Brandt}, W., {Brusa}, M.,
+  {Buchner}, J., {Comparat}, J., {Croft}, R.~A.~C., {Dwelly}, T., {Fan}, X.,
+  {Font-Ribera}, A., {Ge}, J., {Georgakakis}, A., {Hall}, P.~B., {Jiang}, L.,
+  {Kinemuchi}, K., {Malanushenko}, E., {Malanushenko}, V., {McMahon}, R.~G.,
+  {Menzel}, M.-L., {Merloni}, A., {Nandra}, K., {Noterdaeme}, P., {Oravetz},
+  D., {Pan}, K., {Pieri}, M.~M., {Prada}, F., {Salvato}, M., {Schlegel}, D.~J.,
+  {Schneider}, D.~P., {Simmons}, A., {Viel}, M., {Weinberg}, D.~H., \& {Zhu},
+  L. 2017, \aap, 597, A79
+
+\bibitem[{{Prochaska} {et~al.}(2013{\natexlab{a}}){Prochaska}, {Hennawi},
+  {Lee}, {Cantalupo}, {Bovy}, {Djorgovski}, {Ellison}, {Lau}, {Martin},
+  {Myers}, {Rubin}, \& {Simcoe}}]{QPQ6}
+{Prochaska}, J.~X., {Hennawi}, J.~F., {Lee}, K.-G., {Cantalupo}, S., {Bovy},
+  J., {Djorgovski}, S.~G., {Ellison}, S.~L., {Lau}, M.~W., {Martin}, C.~L.,
+  {Myers}, A., {Rubin}, K.~H.~R., \& {Simcoe}, R.~A. 2013{\natexlab{a}}, \apj,
+  776, 136
+
+\bibitem[{{Prochaska} {et~al.}(2013{\natexlab{b}}){Prochaska}, {Hennawi}, \&
+  {Simcoe}}]{QPQ5}
+{Prochaska}, J.~X., {Hennawi}, J.~F., \& {Simcoe}, R.~A. 2013{\natexlab{b}},
+  \apjl, 762, L19
+
+\bibitem[{{Prochaska} {et~al.}(2014){Prochaska}, {Lau}, \& {Hennawi}}]{QPQ7}
+{Prochaska}, J.~X., {Lau}, M.~W., \& {Hennawi}, J.~F. 2014, \apj, 796, 140
+
+\bibitem[{{Prochaska} {et~al.}(2011){Prochaska}, {Weiner}, {Chen}, {Mulchaey},
+  \& {Cooksey}}]{Prochaska+11}
+{Prochaska}, J.~X., {Weiner}, B., {Chen}, H.-W., {Mulchaey}, J., \& {Cooksey},
+  K. 2011, \apj, 740, 91
+
+\bibitem[{{Rakic} {et~al.}(2012){Rakic}, {Schaye}, {Steidel}, \&
+  {Rudie}}]{Rakic+12}
+{Rakic}, O., {Schaye}, J., {Steidel}, C.~C., \& {Rudie}, G.~C. 2012, \apj, 751,
+  94
+
+\bibitem[{{Richards} {et~al.}(2002){Richards}, {Vanden Berk}, {Reichard},
+  {Hall}, {Schneider}, {SubbaRao}, {Thakar}, \& {York}}]{Richards+02}
+{Richards}, G.~T., {Vanden Berk}, D.~E., {Reichard}, T.~A., {Hall}, P.~B.,
+  {Schneider}, D.~P., {SubbaRao}, M., {Thakar}, A.~R., \& {York}, D.~G. 2002,
+  \aj, 124, 1
+
+\bibitem[{{Rodr{\'{\i}}guez-Torres} {et~al.}(2017){Rodr{\'{\i}}guez-Torres},
+  {Comparat}, {Prada}, {Yepes}, {Burtin}, {Zarrouk}, {Laurent}, {Hahn},
+  {Behroozi}, {Klypin}, {Ross}, {Tojeiro}, \& {Zhao}}]{RodriguezTorres+17}
+{Rodr{\'{\i}}guez-Torres}, S.~A., {Comparat}, J., {Prada}, F., {Yepes}, G.,
+  {Burtin}, E., {Zarrouk}, P., {Laurent}, P., {Hahn}, C., {Behroozi}, P.,
+  {Klypin}, A., {Ross}, A., {Tojeiro}, R., \& {Zhao}, G.-B. 2017, \mnras, 468,
+  728
+
+\bibitem[{{Roos} {et~al.}(2015){Roos}, {Juneau}, {Bournaud}, \&
+  {Gabor}}]{Roos+15}
+{Roos}, O., {Juneau}, S., {Bournaud}, F., \& {Gabor}, J.~M. 2015, \apj, 800, 19
+
+\bibitem[{{Rubin} {et~al.}(2014){Rubin}, {Prochaska}, {Koo}, {Phillips},
+  {Martin}, \& {Winstrom}}]{Rubin+14}
+{Rubin}, K.~H.~R., {Prochaska}, J.~X., {Koo}, D.~C., {Phillips}, A.~C.,
+  {Martin}, C.~L., \& {Winstrom}, L.~O. 2014, \apj, 794, 156
+
+\bibitem[{{Rupke} {et~al.}(2005){Rupke}, {Veilleux}, \& {Sanders}}]{Rupke+05}
+{Rupke}, D.~S., {Veilleux}, S., \& {Sanders}, D.~B. 2005, \apjs, 160, 115
+
+\bibitem[{{Schneider} {et~al.}(2010){Schneider}, {Richards}, {Hall}, {Strauss},
+  {Anderson}, {Boroson}, {Ross}, {Shen}, {Brandt}, {Fan}, {Inada}, {Jester},
+  {Knapp}, {Krawczyk}, {Thakar}, {Vanden Berk}, {Voges}, {Yanny}, {York},
+  {Bahcall}, {Bizyaev}, {Blanton}, {Brewington}, {Brinkmann}, {Eisenstein},
+  {Frieman}, {Fukugita}, {Gray}, {Gunn}, {Hibon}, {Ivezi{\'c}}, {Kent}, {Kron},
+  {Lee}, {Lupton}, {Malanushenko}, {Malanushenko}, {Oravetz}, {Pan}, {Pier},
+  {Price}, {Saxe}, {Schlegel}, {Simmons}, {Snedden}, {SubbaRao}, {Szalay}, \&
+  {Weinberg}}]{Schneider+10}
+{Schneider}, D.~P., {Richards}, G.~T., {Hall}, P.~B., {Strauss}, M.~A.,
+  {Anderson}, S.~F., {Boroson}, T.~A., {Ross}, N.~P., {Shen}, Y., {Brandt},
+  W.~N., {Fan}, X., {Inada}, N., {Jester}, S., {Knapp}, G.~R., {Krawczyk},
+  C.~M., {Thakar}, A.~R., {Vanden Berk}, D.~E., {Voges}, W., {Yanny}, B.,
+  {York}, D.~G., {Bahcall}, N.~A., {Bizyaev}, D., {Blanton}, M.~R.,
+  {Brewington}, H., {Brinkmann}, J., {Eisenstein}, D., {Frieman}, J.~A.,
+  {Fukugita}, M., {Gray}, J., {Gunn}, J.~E., {Hibon}, P., {Ivezi{\'c}}, {\v
+  Z}., {Kent}, S.~M., {Kron}, R.~G., {Lee}, M.~G., {Lupton}, R.~H.,
+  {Malanushenko}, E., {Malanushenko}, V., {Oravetz}, D., {Pan}, K., {Pier},
+  J.~R., {Price}, III, T.~N., {Saxe}, D.~H., {Schlegel}, D.~J., {Simmons}, A.,
+  {Snedden}, S.~A., {SubbaRao}, M.~U., {Szalay}, A.~S., \& {Weinberg}, D.~H.
+  2010, \aj, 139, 2360
+
+\bibitem[{{Shen} {et~al.}(2016{\natexlab{a}}){Shen}, {Brandt}, {Richards},
+  {Denney}, {Greene}, {Grier}, {Ho}, {Peterson}, {Petitjean}, {Schneider},
+  {Tao}, \& {Trump}}]{Shen+16}
+{Shen}, Y., {Brandt}, W.~N., {Richards}, G.~T., {Denney}, K.~D., {Greene},
+  J.~E., {Grier}, C.~J., {Ho}, L.~C., {Peterson}, B.~M., {Petitjean}, P.,
+  {Schneider}, D.~P., {Tao}, C., \& {Trump}, J.~R. 2016{\natexlab{a}}, \apj,
+  831, 7
+
+\bibitem[{{Shen} {et~al.}(2016{\natexlab{b}}){Shen}, {Horne}, {Grier},
+  {Peterson}, {Denney}, {Trump}, {Sun}, {Brandt}, {Kochanek}, {Dawson},
+  {Green}, {Greene}, {Hall}, {Ho}, {Jiang}, {Kinemuchi}, {McGreer},
+  {Petitjean}, {Richards}, {Schneider}, {Strauss}, {Tao}, {Wood-Vasey}, {Zu},
+  {Pan}, {Bizyaev}, {Ge}, {Oravetz}, \& {Simmons}}]{Shen16}
+{Shen}, Y., {Horne}, K., {Grier}, C.~J., {Peterson}, B.~M., {Denney}, K.~D.,
+  {Trump}, J.~R., {Sun}, M., {Brandt}, W.~N., {Kochanek}, C.~S., {Dawson},
+  K.~S., {Green}, P.~J., {Greene}, J.~E., {Hall}, P.~B., {Ho}, L.~C., {Jiang},
+  L., {Kinemuchi}, K., {McGreer}, I.~D., {Petitjean}, P., {Richards}, G.~T.,
+  {Schneider}, D.~P., {Strauss}, M.~A., {Tao}, C., {Wood-Vasey}, W.~M., {Zu},
+  Y., {Pan}, K., {Bizyaev}, D., {Ge}, J., {Oravetz}, D., \& {Simmons}, A.
+  2016{\natexlab{b}}, \apj, 818, 30
+
+\bibitem[{{Shen} {et~al.}(2011){Shen}, {Richards}, {Strauss}, {Hall},
+  {Schneider}, {Snedden}, {Bizyaev}, {Brewington}, {Malanushenko},
+  {Malanushenko}, {Oravetz}, {Pan}, \& {Simmons}}]{Shen+11}
+{Shen}, Y., {Richards}, G.~T., {Strauss}, M.~A., {Hall}, P.~B., {Schneider},
+  D.~P., {Snedden}, S., {Bizyaev}, D., {Brewington}, H., {Malanushenko}, V.,
+  {Malanushenko}, E., {Oravetz}, D., {Pan}, K., \& {Simmons}, A. 2011, \apjs,
+  194, 45
+
+\bibitem[{{Somerville} \& {Dav{\'e}}(2015)}]{SomervilleDave15}
+{Somerville}, R.~S., \& {Dav{\'e}}, R. 2015, \araa, 53, 51
+
+\bibitem[{{Steidel} {et~al.}(2010){Steidel}, {Erb}, {Shapley}, {Pettini},
+  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}, \& {Rakic}}]{Steidel+10}
+{Steidel}, C.~C., {Erb}, D.~K., {Shapley}, A.~E., {Pettini}, M., {Reddy}, N.,
+  {Bogosavljevi{\'c}}, M., {Rudie}, G.~C., \& {Rakic}, O. 2010, \apj, 717, 289
+
+\bibitem[{{Tormen} {et~al.}(1997){Tormen}, {Bouchet}, \&
+  {White}}]{TormenBouchetWhite97}
+{Tormen}, G., {Bouchet}, F.~R., \& {White}, S.~D.~M. 1997, \mnras, 286, 865
+
+\bibitem[{{Tripp} {et~al.}(2011){Tripp}, {Meiring}, {Prochaska}, {Willmer},
+  {Howk}, {Werk}, {Jenkins}, {Bowen}, {Lehner}, {Sembach}, {Thom}, \&
+  {Tumlinson}}]{Tripp+11}
+{Tripp}, T.~M., {Meiring}, J.~D., {Prochaska}, J.~X., {Willmer}, C.~N.~A.,
+  {Howk}, J.~C., {Werk}, J.~K., {Jenkins}, E.~B., {Bowen}, D.~V., {Lehner}, N.,
+  {Sembach}, K.~R., {Thom}, C., \& {Tumlinson}, J. 2011, Science, 334, 952
+
+\bibitem[{{Tumlinson} {et~al.}(2013){Tumlinson}, {Thom}, {Werk}, {Prochaska},
+  {Tripp}, {Katz}, {Dav{\'e}}, {Oppenheimer}, {Meiring}, {Ford}, {O'Meara},
+  {Peeples}, {Sembach}, \& {Weinberg}}]{Tumlinson+13}
+{Tumlinson}, J., {Thom}, C., {Werk}, J.~K., {Prochaska}, J.~X., {Tripp}, T.~M.,
+  {Katz}, N., {Dav{\'e}}, R., {Oppenheimer}, B.~D., {Meiring}, J.~D., {Ford},
+  A.~B., {O'Meara}, J.~M., {Peeples}, M.~S., {Sembach}, K.~R., \& {Weinberg},
+  D.~H. 2013, \apj, 777, 59
+
+\bibitem[{{Weiner} {et~al.}(2009){Weiner}, {Coil}, {Prochaska}, {Newman},
+  {Cooper}, {Bundy}, {Conselice}, {Dutton}, {Faber}, {Koo}, {Lotz}, {Rieke}, \&
+  {Rubin}}]{Weiner+09}
+{Weiner}, B.~J., {Coil}, A.~L., {Prochaska}, J.~X., {Newman}, J.~A., {Cooper},
+  M.~C., {Bundy}, K., {Conselice}, C.~J., {Dutton}, A.~A., {Faber}, S.~M.,
+  {Koo}, D.~C., {Lotz}, J.~M., {Rieke}, G.~H., \& {Rubin}, K.~H.~R. 2009, \apj,
+  692, 187
+
+\bibitem[{{Wild} {et~al.}(2008){Wild}, {Kauffmann}, {White}, {York}, {Lehnert},
+  {Heckman}, {Hall}, {Khare}, {Lundgren}, {Schneider}, \& {vanden
+  Berk}}]{Wild+08}
+{Wild}, V., {Kauffmann}, G., {White}, S., {York}, D., {Lehnert}, M., {Heckman},
+  T., {Hall}, P.~B., {Khare}, P., {Lundgren}, B., {Schneider}, D.~P., \&
+  {vanden Berk}, D. 2008, \mnras, 388, 227
+
+\bibitem[{{Zahedy} {et~al.}(2016){Zahedy}, {Chen}, {Rauch}, {Wilson}, \&
+  {Zabludoff}}]{Zahedy+16}
+{Zahedy}, F.~S., {Chen}, H.-W., {Rauch}, M., {Wilson}, M.~L., \& {Zabludoff},
+  A. 2016, \mnras, 458, 2423
+
+\end{thebibliography}
 

### 2017-06-08 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -47,7 +47,9 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
     if stack_tup is None:
         stack_tup = qpqk.load_stack_img(qpq9.data,wrest,vmnx=vmnx,spec_dv=100.*u.km/u.s,high_res=0,
                                         S2N_cut=S2N_cut,atmosphere_cut=atmosphere_cut,
-                                        stack_fg=stack_fg,plot_indiv=plot_indiv)
+                                        stack_fg=stack_fg,plot_indiv=plot_indiv,
+                                        QPQ_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/QPQ/',
+                                        igmspec_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/igmspec/')
         if passback:
             return stack_tup
 

### 2017-07-20 QPQ9/Submit/response.txt
Responded to referee

Editor Walter,

We thank very much the referee for their careful reading of our manuscript, and their comments and criticism.
Following their recommendations, we have revised our manuscript in a number of ways detailed below. We are now
resubmitting to the Astrophysical Journal and ask that you consider it further for publication.
Summary of referee report:

>After carefully reviewing the manuscript, I found multiple significant issues with the study, and consequently it does
>not currently meet the standards for publication. These issues must be addressed before the paper can be accepted, and
>I request the opportunity to review the paper again after the authors have made revisions with the hope that it can be
>accepted for publication. The main issues are summarized below and more detailed discussion follows.
>
>1) The conclusions of the paper rely heavily on accurate quasar redshift measurements because redshift errors will
>influence both the centroid and dispersion measured in the stacked background absorption spectra. Indeed, the measured
>centroids and velocity dispersions in the stacked absorption spectra are comparable with expected quasar redshift
>biases and scatter. In an attempt to address this issue, the authors adopt redshift bias measurements from the
>literature, but the bias measurements used are not appropriate for the redshift measurement techniques that are
>described in the previous QPQ papers (details to follow). Significant additional work is required to demonstrate that
>the offset in the observed absorption centroid is real and not due to redshift measurement errors.

We thank the referee for pointing out the importance of accurate redshift measurements. We have addressed the
suggested additional work in the details to follow.

>2) The authors have not demonstrated that the measured 1-sigma dispersion measured in a mean stack is is a
>representative measure of the velocity spread observed between absorbing gas and the quasar redshift. This may not be
>the case if the absorbing components exhibit a non-Gaussian distribution about the quasar systemic redshift as has
>been seen in other studies (e.g. Lau et al. 2016 and Johnson et al. 2015). In particular, broad wings on the
>distribution will be suppressed in a stack even if they contain a significant amount of the power because the
>absorbing components can be narrow. This is a weakness of analysis based on stacks that could easily be remedied
>because previous QPQ papers published absorber redshifts and even component-by-component velocity structure when
>available. A figure showing this distribution is needed in this publication.

The distribution of absorbing components in velocity is non-Gaussian for each quasar-host associated system. However,
we have 34 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
analysis. The number of individual components can only be larger. The central limit theorem applies and the
distribution of all absorbing components should tend toward Gaussian distribution. A component-by-component analysis
requires echellette or echelle resolution, which is a criterion for the QPQ8 sample. For this current work, we stack
spectra of all resolutions. Text has been added to explain the above and to refer the readers to specific figures in
QPQ8.

>3) Insufficient detail on the doublet fitting is provided, and uncertainty due to degeneracy between doublet ratio and
>velocity centroid are not addressed.

We allowed the doublet ratio to vary from 2:1 to 1:1. The centroids of the doublets are tied at a fixed separation.
More text has been added.

>4) The conclusions of the paper are not self-consistent. In particular, the authors find that the velocity dispersion
>in the mean stack does not require addition motion (beyond gravitational and cosmological), but the explanation for
>the centroid offset requires that the gas is, on average, flowing away from the quasar host galaxy. This discrepancy
>needs to be addressed.

We acknowledge that we did not present the best argument. The centroid offset does not require that the gas is
flowing away from the galaxy. In our Monte Carlo simulations, we are able to reproduce the centroid offset by assuming
that the gas is all ionized within a certain opening angle. For an opening angle >= 120 degrees, The stack of mock
spectra has amplitude, dispersion, and centroid offset all within 2 times the modeling error. Text has been added to
explain the above. We do not present a new figure to show this stack, since our primary goal of performing Monte Carlo
simulations is to reproduce the dispersion. We have removed the outward arrows in the cartoon figure and the estimates
in radial velocities under an outflow scenario. While outflows cannot be ruled out, we prefer to focus on the argument
that outflows are not required.

>5) Several papers in the literature that are cited are mis-represented.

We have studied the papers more carefully, and have modified the text to represent the literature more correctly.
Details to follow below.

>Additional details on each of the points as well as more minor issues are given below, After this, my referee report
>concludes with a discussion of more minor points.
>
>Major point 1: quasar systemic redshift measurements
>
>The authors compile a foreground quasar sample by combining quasars with redshifts measured in their own spectra with
>quasars from the SDSS with redshift measurements from the literature. Very little information is provided on how these
>redshifts are measured and the reader is referred to previous QPQ papers. Given the importance of accurate redshifts
>for this study, this lack of discussion is inappropriate. The authors provide significant detail in how the redshifts
>are measured and demonstrate the accuracy of their redshifs.
>
>After returning to the QPQ papers where redshift measurements are discussed, it appears that the QPQ redshifts are
>based on *centroids* from MgII, [O III], Halpha emission lines. The authors then apply mean bias corrections for these
>redshifts based on the line-dependent bias measured by Shen et al. 2016a. However, Shen et al. 2016a measured the bias
>for redshifts based on line *peak*, not centroid. This may seem subtle but is significant because of the strong
>blue-shifted wings often observed in quasar emission-lines. For example, Shen et al. 2016b fit z~2 quasar emission
>lines with a core component and broad wing component. The broad wings have a mean velocity offset of -600 km/s from
>the systemic redshift and contain 40% of the [O III] flux on average. Consequently, the [O III] centroid will be
>biased from the systemic redshift measured from the peak by ~-200 km/s which is sufficient to explain the redshift
>observed in the stacked absorption profile. Note that this is far larger than the 50 km/s correction that the authors
>applied which was based on peaks not centroids. Redshifts from MgII and Balmer emission line centroids are likely even
>more biased because these lines are broader and more asymmetric. Consequently, the authors must re-measure the quasar
>systemic redshifts using techniques that are self-consistent with the redshift corrections that are applied.
>
>In addition, the authors need to make and display stacked absorption profiles in each ion for quasars with different
>redshift measurement techniques. Some effort along these lines is shown in Table 2, but it is not nearly sufficient to
>demonstrate that the measured absorption centroid is not due to redshift measurement issues.
>
>These steps are a minimum requirement to convincingly demonstrate that the observed redshift in the mean absorption
>profile relative to the quasar systemic is real.

We have added text to explain how redshifts are measured. We acknowledge the confusion in calling the line-centering
algorithm a centroiding method. Our algorithm calculates the mode of a line given by (3*median - 2*mean), applied to
the upper 60% of the emission line. Shen+16 states that difference between the peak and the centroid is not
significant, except for the broad line Hbeta, which we did not use in redshift measurements. We have further obtained
individual measurements of centroids and peaks in Shen+16 thru private communication. There is essentially no
difference between using the centroid versus using the peak for [OIII], and there is about 50 km/s difference for
MgII. We may expect the difference between a mode and a peak is even smaller. Text have been added.

We have explained in the text that, our results cannot be severely biased by [OIII] redshifts. We have tried
replacing the [OIII] redshifts by MgII or Halpha redshifts, and found a similar centroid and dispersion in the stack.
MgII and Halpha are broader, but it has not been reported in any literature that they are more asymmetric.

>Major point 2:
>
>In Lau et al. 2016, the distribution of absorbing components about the quasar systemic redshift is non-Guassian and
>exhibits broad wings that contain significant portion of the optical depth at large velocities. In a mean stack, these
>wings can be suppressed so that the dispersion of the stacked absorption profile does not represent the actual
>velocity spread. For example, if absorbers are distributed in velocity around quasar hosts with a core component
>within |v|<200 km/s and a wing component within |v|=200-1000 km/s, then the wing component will be suppressed by a
>factor of ~8 relative to the core because narrow absorbers are being spread over a larger velocity range. The authors
>need to demonstrate that this is not an issue before adopting the 1-sigma dispersion in the stack as a measure of the
>kinematic spread of the absorbing gas. This is a general weakness of stacked measurements and raises the question of
>why the study does not show a histogram of the velocity difference sbetween the quasar systemic and observed
>absorption centroids in individual cases where the S/N is sufficient. Previous QPQ papers reported absorber redshifts
>(Prochaska et al. 2014) and individual component measurements (Lau et al. 2016). It should therefore be
>straight-forward to measure the actual velocity distribution of absorption systems around quasars directly rather than
>relying on stacked measurements. The authors should include such a histogram in the revised paper.

As explained above, we have sufficient number of absorbing components that they should tend toward a Gaussian
distribution in the stack. We are able to model the stack by a Gaussian multiplied to a pseudocontinuum. Our visual
inspection does not hint at a broader component in the stack. QPQ7 reported the redshift of the strongest Lya
absorption within the search window. The QPQ7 sample has spectra of all resolutions. It requires echellette or
echelle resolution to identify the metal-associated absorbers. In QPQ8, a histogram of the optical depth weighted
centroid of the absorption systems is shown. In the Appendix of QPQ8, the absorption profiles of the individual
components are shown. We have counted 6 of them are at negative velocities, while 15 of them are at positive
velocities. text have been added to reflect these numbers.

>Major point 3:
>
>The authors do not provide enough detail regarding the fit to the mean stack. In particular, for MgII and CIV two
>gaussian with fixed doublet separation and width are fit to the stack. However, no details on the doublet ratio range
>allowed are given. This is particularly important for CIV where the doublets are not well resolved in the stack.
>Consequently, the velocity centroid and doublet ratio will be degenerate and uncertainty due to this degeneracy must
>be addressed.

We thank the referee for pointing out the insufficient detail in the text. The doublet ratio is allowed to vary
between 2:1 to 1:1.

>Major point 4:
>The primary results of the paper are that (1) while the dispersion observed in the stack is large, galactic superwinds
>may not be required to explain the width and (2) the absorption is kinematically offset from the quasar systemic
>redshifts by ~+200 km/s. The authors interpret this offset as due to effects from partial obscuration of the quasar or
>finite quasar lifetimes and light-travel time under the assumption that gas is, on average, flowing away from the
>quasar host. In QPQ VII the CII covering fractions are observed to decrease rapidly from ~80% at projected distances
>of <200 kpc to 20% at 200-500 kpc and <10% at 500-1000 kpc. This rapid fall-off with projected distance suggests that
>the majority of the absorption arises in the quasar host halo. Consequently, motions due to Hubble flow are not likely
>to be significant. Conclusion (2) therefore requires significant outflows in the halo, inconsistent with conclusion
>(1). This discrepancy needs to be addressed in the discussion.

In QPQ8, we have estimated the random incidence of optically thick and CIV absorbers. Text has been added to reflect
these numbers. As our Monte Carlo simulations demonstrate, outflows are not required to reproduce the observed
amplitude and dispersion of the mean absorption.

>Major point 5:
>
>Several papers in the literature that are cited are mis-represented in the introduction. In particular:
>
>Johnson et al. 2015 is cited as concluding that the large velocity of absorbing gas observed around quasars is due to
>outflows. This is not the case. The paper considers several possible explanations including large-scale structure,
>galaxy interactions, and outflows. The conclusion of the paper is that none of these possibilities can satisfactorily
>explain the observed properties of cool gas around quasars.
>
>Gauthier et al. 2013, Muzahid 2015, and Zahedy et al. 2016 exhibit velocity spreads of ~600, 300-400, and 600 km/s
>respectively, which is comparable with those observed in the QPQ survey, contrary to the claim in the paper. This
>inaccurate statement needs to be clarified and corrected.
>
>These misrepresentations combined with the fact that the paper applies redshift bias corrections from the literature
>that are not appropriate for their redshift measurement techniques indicates that the authors need to carefully review
>the paper and ensure that the citations to the literature are correctly represented and applied.

We thank the referee for clarifying the explanation to Johnson+15's results. We have updated the text to reflect that
outflows is only one possibility. Gauthier+13 is a single sightline, and the velocity width Dv90 of the MgII
absorber is less than the average of QPQ8 CII absorber. Muzahid+15 found an absorber with Dv90 less than 555 km/s in
OVI and NV, and still less for other ions. Zahedy+16's sample has average Dv90 elss than that of QPQ8. More text has
been added.

>Minor issues:
>
>Introduction Section:
>
>1) When discussing inflows, the authors should cite Rubin et al. 2012
>2) The definition of h in this paper is not in accordance with the common convention and should be replaced with h_70
>to prevent the casual reader from being confused.
>3) Rudie et al. 2017 should be included in the references for systems with large velocity spread. This paper is
>highly relevant to the discussions in this manuscript.

We have cited Rubin+12 and Rudie+17 in our revised manuscript. We intend that h = H_0 / (100 km s^-1 Mpc^-1), in
accordance with the common convention, that is also widely used in cosmology papers such as Kravtsov+17. We have
state this scaling explicitly in our revised manuscript. We thank the referee for above suggestions.

>Experiment Section:
>
>1) Given the anti-correlation between covering fraction and projected distance, the authors may be able to increase
>the S/N in the average absorption profiles by only considering quasars with projected distances of <100 and <200 kpc
>from the background sightline.

We performed the experiment of separating the sightlines into two bins of projected distance. We found the stack of
sightlines below the median projected distance looks similar to the full sample. We did not find a significant boost
in S/N in the average absorption profiles.

>Analysis Section:
>1) The authors claim that it is not necessary to smooth the spectra before linearly interplating onto a 100 km/s
>pixel grid. This may be true for the low-resolution spectra but is untrue for the moderate and high resolution
>spectra used where linear interpolation onto a coarser pixel scale will have unpredictable results. The authors
>should test that this dues not actually change any results.

For each sightline, we overplotted the original absorption profile and that interpolated onto the common velocity
grid, and visually the overplots. We have confirmed to ourselves that the equivalent widths and the shapes of the
absorption profiles are preserved.

>2) The mean redshifted centroid in the CII profile is observed in the mean stack but not the median at a level that
>is in tension. The study does not address this discrepancy and does not provide sufficient reasoning for preferring
>the mean over the median when attempting to measure a centroid.

There is large intrinsic scatter in the CGM environments. In our revised manuscript, we included one new quasar pair
from our latest QPQ Survey database, making the total sample size for CII analysis 33. With this sample, the median
CII statistic has a centroid +120+/-195 km/s. We prefer the mean over the median, as the median statistic is not
sensitive to absorption signals and does not preserve equivalent width. The centroid measured from the median stack
is thus subject to larger uncertainty.

>3) It is quite odd that the quoted error in the centroid for the z=1 coadd is 388 km/s, larger than the 161 km/s
>dispersion. What is going on here? In addition, why would a shift be observed for z=2 quasars but not z=1 ones? The
>authors seem to take this as evidence that the redshift in the absorption centroid is real. I came to the opposite
>conclusions since accurate redshifts for low-z quasars are easier to come by.

The quoted uncertainty in the centroid is the standard deviation in the 10000 bootstrap realizations. The average
absorption of this stack is weak, and the measured dispersion too has a large intrinsic scatter. A shift is not
definitively observed in the 0.4 < z < 1.6 stack. It may be due to weaker average absorption, or it may be due to
lower average quasar luminosity should our interpretations be correct. The 0.4 < z < 1.6 quasars are largely SDSS
spectra, and we adopt [OIII] or MgII emission-line redshifts taken from Hewett&Wild10. The z ~ 2 quasars of our sample
have MgII, [OIII], or Halpha emission-line redshifts. We do not consider that the redshifts of the 0.4 < z < 1.6
quasars are more accurate, since the more precise [OIII] redshifts are only accessible in SDSS spectral coverage for
z < 0.84.

>4) Section 3.4 contributes little to the paper and is redundant with existing work in the literature. The authors may
>wish to remove it to avoid distracting readers.

We have moved this section to the Appendix in our revised manuscript.

>5) Figure 6 may be difficult for color-blind readers to interpret.

We consulted websites for generating color-blindness-friendly figures, and found that our navy color was challenging
for readers with total color-blindness. We have changed that to a brighter shade of blue in our revised manuscript.

Discussion Section:

>1) The paper cites Roos et al. 2015 and Gabor & Bournaud et al. 2014 when discussing quasar emission anisotropy. The
>should add references to observational papers that demonstrate this though polarization measurements and/or
>observations of ionization cones at lower redshifts.

At low z, both symmetric and asymmetric ionization cones around quasars and AGNs are observed. In the extended
emission-line region of 4C37.43, most of the [OIII] emission is blueshifted (Fu&Stockton07), but there are counter
examples in less extended sources in FU&Stockton09. Recently there has been Fabry-Perot velocity fields for less
extended narrow-line regions in more nearby sources (Keel+15,17), which show mostly symmetric velocity fields and gas
distributions.

>2) In the cartoons presented in Figure 8-9, my interpretation is that under this scenario, low ions should be
>redshifted and high ions such as CIV blue-shifted. This is not observed based on the measurements of CIV in Table 2.
>Please clarify and address this apparent contradiction between the observed data and model interpretation.

CIV may be regarded as an intermediate ion, and gas that receives an ionizing radiation from the quasar may be even
more highly ionized. We have access to a Cloudy grid that uses an extragalactic UV background spectral shape as input.
We have verified to ourselves the following. For the typical Lyman limit luminosity of our sample
10^31.5 erg s^-1 Hz^-1, for the average total column density of the QPQ8 sample 10^20.5 cm^-2 and the average [M/H] =
-0.6, at a distance = 150 kpc and density = 0.1 cm^-3, Cloudy predicts that CIV absorption is only marginally
detectable. Moreover, given the large intrinsic scatter, we do not explore whether there exists relative asymmetry
among CII, CIV, and MgII.

>3) Finally, if the authors are aware of any work simulation work demonstrating that gas flows at high-z on these
>scales are primarily outward, they should be discussed. For example, Shen et al. 2012, find significant column
>densities in inflowing gas, particularly at lower ionization states. Of course, this is a lower mass halo, but
>similar insights may be available from simulations of more massive systems.

Faucher-Giguere+16 represents the only simulation so far that is able to reproduce the substantial amount of cool gas
in quasar-mass haloes. Their group has not compared the fraction of gas in inflows and outflows. Furthermore, we
consulted Jared Gabor and we found no more simulation papers that predicted unipolar emission other than the two we
cited.

### 2017-07-20 QPQ9/Submit/qpq9_submit.tex
Responded to referee

@@
 to comoving distances we include explicitly an $h^{-1}$ term and follow modern convention of 
-scaling to a Hubble constant of $70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. 
+scaling to the Hubble constant $h = H_0/(70\,{\rm km\,s^{-1}\,Mpc^{-1}})$.
 %All equivalent width measurements are presented in the rest-frame, unless otherwise specified.
@@
 channel given equal weight. From the best-fit to the data, we measure the centroid of the 
-\ion{C}{2} stack to be $+208\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be 
-$318\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the standard 
+\ion{C}{2} stack to be $+196\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be 
+$313\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the standard 
 expectation, while the dispersion suggests extreme kinematics. The median stack, on the other 
@@
 absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
-$+249\,{\rm km\,s^{-1}}$, and a dispersion of $362\,{\rm km\,s^{-1}}$, consistent with the full 
+$+220\,{\rm km\,s^{-1}}$, and a dispersion of $362\,{\rm km\,s^{-1}}$, consistent with the full 
 sample.
@@
 limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
-$\delta v<+451\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore 
+$\delta v<+424\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
 whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
@@
 stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2} or H$\alpha$ 
-redshift when available. We are able to replace for 8 out of the 14 systems with [\ion{O}{3}] 
+redshift when available. We are able to replace for 11 out of the 15 systems with [\ion{O}{3}] 
 redshifts in the original sample. The new stack is similiar in velocity structure and again shows 
-a positive offset $\approx+240\,{\rm km\,s^{-1}}$. We thus conclude that our algorithm for 
+a positive offset $\approx+259\,{\rm km\,s^{-1}}$. We thus conclude that our algorithm for 
 measuring redshifts is not severely biased by the blue wing of the [\ion{O}{3}] emission-line.
@@
 dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
-absorption profile with $\sigma_v=573\,{\rm km\,s^{-1}}$, which is larger than the observed width 
+absorption profile with $\sigma_v=559\,{\rm km\,s^{-1}}$, which is larger than the observed width 
 by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity 
 width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with 
-$\sigma_v=231\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the 
+$\sigma_v=226\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
 modeling error. Unless gravitational and Hubble flows together with redshift error broadening 
@@
 $\sigma_{{\rm error}(z)}^{\rm full}=182\,{\rm km\,s^{-1}}$, we recover 
-$\sigma_{\rm intrinsic}^{\rm full}=261\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
+$\sigma_{\rm intrinsic}^{\rm full}=255\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
 redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=356\,{\rm km\,s^{-1}}$.
@@
 matter halos hosting QPQ9 quasars have a characteristic mass $10^{12.6}\,M_\odot$ and follow an 
-NFW profile \citep{NavarroFrenkWhite97} with concentration 
-parameter $c=4$, at $z\approx2$ the maximum circular velocity is $345\,{\rm km\,s^{-1}}$. 
-\cite{TormenBouchetWhite97} found that the maximum circular velocity is $\approx1.4$ times the 
-maximum of the one-dimensional velocity dispersion $\sigma_{\rm 1D}$. Hence, the line-of-sight 
-velocity dispersion typical of QPQ9 halos is $\sigma_{\rm 1D}=246\,{\rm km\,s^{-1}}$. We can 
-investigate whether gravitational motions and Hubble flows are sufficient to reproduce the 
-dispersion in the data, using Monte Carlo methods to simulate the absorption signals.
+NFW profile \citep{NavarroFrenkWhite97} with concentration parameter $c=4$, at $z\approx2$ the
+maximum circular velocity is $345\,{\rm km\,s^{-1}}$. \cite{TormenBouchetWhite97} found that the
+maximum circular velocity is $\approx1.4$ times the maximum of the average one-dimensional
+root-mean-square velocity $\sigma_{\rm rms}$. Hence, the average line-of-sight rms velocity
+typical of QPQ9 halos is $\sigma_{\rm rms}=246\,{\rm km\,s^{-1}}$. We can investigate
+whether gravitational motions and Hubble flows are sufficient to reproduce the dispersion in the
+data, using Monte Carlo methods to simulate the absorption signals.
 
@@
 assigned additional peculiar velocities drawn from a normal distribution with mean equal to 
-$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we assume a rest 
+$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm rms}$. For each absorber, we assume a rest
 equivalent width for \ion{C}{2} $W_{\rm CII}$ and a Gaussian absorption profile. We repeat the 
-above procedure for all 32 quasar pairs, and create a mean stack of the 32000 mock spectra 
+above procedure for all 33 quasar pairs, and create a mean stack of the 33000 mock spectra
 generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
@@
 amplitude of the best-fit Gaussian of the stack of mock spectra matches the 
-amplitude of the stack of the observational data. We find that $W_{\rm CII}=0.8\,{\rm \AA}$ well 
+amplitude of the stack of the observational data. We find that $W_{\rm CII}=0.6\,{\rm \AA}$ well
 reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
@@
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $284\,{\rm km\,s^{-1}}$. This is 
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $280\,{\rm km\,s^{-1}}$. This is
 about $1\sigma$ modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack for 
@@
 From the bootstrap 
-analysis of the observed dispersion, a width of $\sigma_v>573\,{\rm km\,s^{-1}}$ would be larger 
+analysis of the observed dispersion, a width of $\sigma_v>559\,{\rm km\,s^{-1}}$ would be larger 
 than the observed by three times the scatter (overplotted in Figure~\ref{fig:monte}). In other 
 words, taking into account the redshift errors, motions in addition to gravitational and Hubble 
-flows that will produce an intrinsic dispersion $\sigma_v>543\,{\rm km\,s^{-1}}$ can be ruled out.
+flows that will produce an intrinsic dispersion $\sigma_v>529\,{\rm km\,s^{-1}}$ can be ruled out.
 
 On the contrary, 
-$\sigma_{\rm 1D}<114\,{\rm km\,s^{-1}}$ together with Hubble velocities and 
+$\sigma_{\rm rms}<134\,{\rm km\,s^{-1}}$ together with Hubble velocities and
 broadening by redshift errors will result in a velocity width that is more than three times the 
 modeling error away from the observed width (overplotted in Figure~\ref{fig:monte}). This implies 
-that, unless the characteristic $M_{\rm halo}<10^{11.6}\,M_\odot$, 
+that, unless the characteristic $M_{\rm halo}<10^{11.8}\,M_\odot$,
 additional dynamical processes are not required to explain the observed width.
@@
 
-As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, radial 
-speeds relative to the foreground quasar of $500\textendash700\,{\rm km\,s^{-1}}$ and quasar 
-opening angles of $120^\circ\textendash140^\circ$ may reproduce the observed centroid and 
-intrinsic dispersion of the \ion{C}{2} mean absorption. The first explanation above to asymmetric 
+%As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, radial
+%speeds relative to the foreground quasar of $500\textendash700\,{\rm km\,s^{-1}}$ and quasar
+%opening angles of $120^\circ\textendash140^\circ$ may reproduce the observed centroid and
+%intrinsic dispersion of the \ion{C}{2} mean absorption.
+As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
+keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
+simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
+absorption to within two times the modeling error.
+The first explanation above to asymmetric
 absorption requires that the quasars emit their ionizing radiation anisotropically, while the 
@@
 the Keck, Gemini, Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar 
-Observatories. MWL thanks T.-K. Chan for a discussion on CGM simulations and Chi Po Choi for a 
-discussion on statistics.
+Observatories. The authors acknowledge the sharing of private data by Yue Shen. MWL thanks Hai Fu
+for a discussion on extended emission-line regions, T.-K. Chan for a discussion on CGM
+simulations, and Chi Po Choi for a discussion on statistics.
 

### 2017-07-20 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -24,8 +24,6 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
                 plot_indiv = True,
                 stack_tup=None,passback=False,debug=False):
     ''' Stack the QPQ9 sample
-    To do: add MgII redshifts to the QPQ9 structure
-    Find out what are the null redshifts
     '''
     # Rest wavelength
     if wrest is None:
@@ -48,7 +46,7 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
         stack_tup = qpqk.load_stack_img(qpq9.data,wrest,vmnx=vmnx,spec_dv=100.*u.km/u.s,high_res=0,
                                         S2N_cut=S2N_cut,atmosphere_cut=atmosphere_cut,
                                         stack_fg=stack_fg,plot_indiv=plot_indiv,
-                                        QPQ_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/QPQ/',
+                                        QPQ_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/QPQ/data/',
                                         igmspec_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/igmspec/')
         if passback:
             return stack_tup

### 2017-07-20 QPQ9/Analysis/py/monte_carlo.py

@@ -23,12 +23,12 @@ Deltav = 10.
 v_grid = -2000. + np.arange((2000.-(-2000.))/Deltav+1)*Deltav
 relativistic_equiv = u.doppler_relativistic(1334.5323*u.AA)
 wave_grid = (v_grid*u.km/u.s).to(u.AA,equivalencies=relativistic_equiv)
+Hubble_h = cosmo.H(0).value/100.
 
 # Generate a stack image of n_trials monte carlo trials
-def gen_stck_img(R_phys,z_fg,stddev_oneabs,sigma1D): # R_phys in kpc, Deltav in km/s
+def gen_stck_img(R_phys,z_fg,stddev_oneabs,sigma1D):  # R_phys in kpc, Deltav in km/s
     probs = np.zeros(len(v_grid))
     cumulative_probs = np.zeros(len(v_grid))
-    Hubble_h = cosmo.H(0).value/100.
     ell_IGM_DLA = 0.2*((1+z_fg)/(1+2.5))**2.1
     ell_IGM_SLLS = 0.44*((1+z_fg)/(1+2.5))**2.1
     ell_IGM_LLS = 1.05*((1+z_fg)/(1+2.5))**2.1
@@ -36,32 +36,25 @@ def gen_stck_img(R_phys,z_fg,stddev_oneabs,sigma1D): # R_phys in kpc, Deltav in 
     for ii,vv in enumerate(v_grid):
         gamma_DLA = 1.6
         r0_DLA = 3.9
-#        gamma_SLLS = 1.6
-#        r0_SLLS = 15.5
-#        gamma_LLS = 1.6
-#        r0_LLS = 13.9
         gamma_SLLS = 1.68
         r0_SLLS = 14.0
         gamma_LLS = 1.68
         r0_LLS = 12.5
         chi_DLA = 1./Deltav*integrate.quad(
-            lambda v:(np.sqrt(R_comov**2+(v/(cosmo.H(z_fg).value/(1+z_fg)))**2)/r0_DLA)**(-gamma_DLA),
+            lambda v:(np.sqrt(R_comov**2+(v/(cosmo.H(z_fg).value/(1+z_fg))*Hubble_h)**2)/r0_DLA)**(-gamma_DLA),
             v_grid[ii]-Deltav/2,v_grid[ii]+Deltav/2)[0]
         chi_SLLS = 1./Deltav*integrate.quad(
[…]

### 2017-07-20 QPQ9/Analysis/py/qpq9_strct.py

@@ -166,8 +166,8 @@ Table(QPQ9).write('qpq9_final.fits',format='fits',overwrite=True)
 QPQ9 = QTable(fits.open('qpq9_final.fits')[1].data)
 c_QPQ9 = SkyCoord(QPQ9['FG_RA']*u.deg,QPQ9['FG_DEC']*u.deg)
 c_QPQ9_bg = SkyCoord(ra=QPQ9['RA']*u.deg,dec=QPQ9['DEC']*u.deg)
-qpq_fil = '/Users/lwymarie/Desktop/qpq_optical.hdf5'
-qpqsp = SpecDB(db_file=qpq_fil,verbose=False,idkey='PRIV_ID')
+qpq_fil = '/Users/lwymarie/Documents/Databases/qpq_oir_spec.hdf5'
+qpqsp = SpecDB(db_file=qpq_fil,verbose=False,idkey='QPQ_ID')
 ID_fg, ID_bg = qpqsp.qcat.pairs(0.92*u.arcmin, 3000.*u.km/u.s)
 c_qpqsp = SkyCoord(qpqsp.cat['RA'][ID_fg]*u.deg,qpqsp.cat['DEC'][ID_fg]*u.deg)
 c_qpqsp_bg = SkyCoord(qpqsp.cat['RA'][ID_bg]*u.deg,qpqsp.cat['DEC'][ID_bg]*u.deg)
@@ -280,10 +280,10 @@ Table(QPQ9).write('qpq9_final.fits',format='fits',overwrite=True)
 QPQ9 = QTable(fits.open('qpq9_final.fits')[1].data)
 c_QPQ9 = SkyCoord(QPQ9['FG_RA']*u.deg,QPQ9['FG_DEC']*u.deg)
 c_QPQ9_bg = SkyCoord(ra=QPQ9['RA']*u.deg,dec=QPQ9['DEC']*u.deg)
-hdulist = fits.open('/Users/lwymarie/Desktop/DR12Q.fits')
+hdulist = fits.open('/Volumes/Data/Data of surveys/SDSS/DR12Q.fits')
 SDSSdr12 = hdulist[1].data
 c_SDSSdr12 = SkyCoord(list(SDSSdr12.field('RA'))*u.deg,list(SDSSdr12.field('DEC'))*u.deg)
-hdulist = fits.open('/Users/lwymarie/Desktop/dr7qso.fit')
[…]

### 2017-07-20 QPQ9/Figures/py/qpq9_figs.py

@@ -395,11 +395,11 @@ def monte(outfil=None):
     model_monte = model_conti*model_monte_gauss
     # Extra motion that is ruled out
     model_extra_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=573.)
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=559.)
     model_extra = model_conti*model_extra_gauss
     # Width that requires outflow
     model_outflow_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=231.)
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=226.)
     model_outflow = model_conti*model_outflow_gauss
 
     # Axes
@@ -498,7 +498,7 @@ def contour(outfil=None):
     mass = hdulist[1].data
     WCII = hdulist[2].data
     lvls = hdulist[3].data
-    lvls = lvls + 0.01  ## truncation error
+    lvls = lvls + 0.01  # truncation error
     hdulist.close()
 
     # Plot
@@ -509,7 +509,7 @@ def contour(outfil=None):
     ax.set_ylabel(r'$W_{\rm CII} ({\rm \AA})$')
 
     # Mark QPQ halo mass location
-    ax.text(12.6,0.84,'+',size=fontsize)
+    ax.text(12.6,0.58,'+',size=fontsize,ha='center',va='center')
 
     # Font
     for item in ([ax.title, ax.xaxis.label, ax.yaxis.label] +

### 2017-07-20 QPQ9/Tables/py/qpq9_tables.py

@@ -244,7 +244,7 @@ afile.write('\\colhead{$z_{\\rm bg}$} & \\colhead{BG Quasar Instrument} & \n')
 afile.write('\\colhead{$R_\\perp$ (kpc)} & \\colhead{$g_{\\rm UV}$}} \n')
 afile.write('\\startdata \n')
 for ii in np.arange(len(tab)):
-    afile.write(tab['fg_qso'][ii] + ' & ' + tab['zfg'][ii] + ' & ' + tab['line'][ii] + '& ')
+    afile.write(tab['fg_qso'][ii] + ' & ' + tab['zfg'][ii] + ' & ' + tab['line'][ii] + ' & ')
     afile.write(tab['bg_qso'][ii] + ' & ' + tab['zbg'][ii] + ' & ' + tab['bg_instr'][ii] + ' & ')
     afile.write(tab['Rphys'][ii] + ' & ' + tab['gUV'][ii] + ' \\\ \n')
 afile.write('\\enddata \n')

### 2017-07-20 QPQ9/Submit/response.txt
small changes

@@
 The distribution of absorbing components in velocity is non-Gaussian for each quasar-host associated system. However,
-we have 34 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
-analysis. The number of individual components can only be larger. The central limit theorem applies and the
+we have 33 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
+analyses. The number of individual components can only be larger. The central limit theorem applies and the
 distribution of all absorbing components should tend toward Gaussian distribution. A component-by-component analysis
@@
 difference between using the centroid versus using the peak for [OIII], and there is about 50 km/s difference for
-MgII. We may expect the difference between a mode and a peak is even smaller. Text have been added.
+MgII. We may expect the difference between a mode and a peak is even smaller.
+
+There are two redshift measurement techniques in the sample: our custom line-centering algorithm, and the algorithm of
+Hewett&Wild10. Shen+16 has stated throughout the paper that their work is consistent with Hewett&Wild10 on redshift
+estimates based on MgII emission and on the average systemic bias.
 
@@
 absorber is less than the average of QPQ8 CII absorber. Muzahid+15 found an absorber with Dv90 less than 555 km/s in
-OVI and NV, and still less for other ions. Zahedy+16's sample has average Dv90 elss than that of QPQ8. More text has
-been added.
+OVI and NV, and still less for other ions. Zahedy+16's sample has average Dv90 elss than that of QPQ8.
 

### 2017-07-20 QPQ9/Submit/qpq9_submit.tex
small changes

@@
 \citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 112 background 
-spectra that are paired with foreground quasars with precisely measured redshifts. 
-Among the sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or 
-echelle observations, and have been analyzed separately in QPQ8. Our primary 
-scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
-central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
-(ii) characterize the dynamics of the gas around these massive systems. We further describe 
-an aspect of this experiment that offers a unique opportunity to study galactic-scale flows: we 
-argue that, the anisotropic or intermittent radiation from the foreground quasars may break the 
-symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation field is 
-asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar 
-lifetime will result in different radiation fields impinged on the gas closer to versus 
-further away from the background quasar, due to different light travel times. 
-\cite{KirkmanTytler08} reported an asymmetry in \ion{H}{1} absorption on scales larger than the 
-CGM, and gave similar arguments on anisotropy or intermittence.
+spectra that are paired with foreground quasars with precisely measured redshifts. Among the
+sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or echelle
+observations, and have been analyzed separately in QPQ8 (see their Figure 8, 9, and 10). For this
+current work, we stack spectra of all resolutions instead of performing a component-by-component
+analysis. Our primary scientific interests are twofold: (i) search for signatures of galactic-scale
+outflows from the central galaxy, presumably driven by recent star formation and/or active galactic
+nuclei feedback; (ii) characterize the dynamics of the gas around these massive systems. We further
+describe an aspect of this experiment that offers a unique opportunity to study galactic-scale
+flows: we argue that, the anisotropic or intermittent radiation from the foreground quasars may
+break the symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation
+field is asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar
+lifetime will result in different radiation fields impinged on the gas closer to versus further
+away from the background quasar, due to different light travel times. \cite{KirkmanTytler08}
+reported an asymmetry in \ion{H}{1} absorption on scales larger than the CGM, and gave similar
+arguments on anisotropy or intermittence.
 
@@
 $\approx100\,{\rm km\,s^{-1}}$ \citep[][QPQ8]{Shen+16}.
+Our line-centering algorithm calculates the mode of a line given by
+$3\times{\rm median}-2\times{\rm mean}$, applied to the upper 60\% of the emission, while
+\cite{Shen+16} calculates the peak of a line. We expect that our line-centering algorithm gives
+emission redshifts very comparable to the \cite{Shen+16} algorithm, however. \cite{Shen+16}
+states that the difference between the peak and the centroid of an emission-line
+is not significant except for the broad line H$\beta$, which we do not use in redshift
+measurements. To quantify the above, we further obtain individual measurements of centroids and
+peaks in the \cite{Shen+16} sample through private communication. We found there is essentially no
+difference between using the centroid versus using the peak for [\ion{O}{3}] emission redshifts,
+and there is on average $50\,{\rm km\,s^{-1}}$ difference for \ion{Mg}{2}. We may expect the
+difference between the mode and the peak is even smaller. Hence, we argue that the average
+systemic bias corrections measured in \cite{Shen+16} may be self-consistently applied to our
+measured emission-line redshifts to obtain systemic redshifts.
+
 We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
@@
 Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
-QPQ publications for the details on the redshift centroiding algorithm, data reduction, and 
-continuum normalization (QPQ6; QPQ8).
+QPQ publications for the details on the emission-line centering algorithm, data reduction, and
+continuum normalization (QPQ1; QPQ6; QPQ8).
 
@@
 exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
-skewed toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
-allowing a constant pseudo-continuum level to vary. We perform $\chi^2$ minimization with each 
-channel given equal weight. From the best-fit to the data, we measure the centroid of the 
-\ion{C}{2} stack to be $+196\,{\rm km\,s^{-1}}$ and the $1\sigma$ dispersion to be 
-$313\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the standard 
-expectation, while the dispersion suggests extreme kinematics. The median stack, on the other 
-hand, shows weaker absorption, and the Gaussian model has a centroid with smaller offset and 
+skewed toward positive velocities. We have 33 pairs in the QPQ9 sample for \ion{C}{2} analysis
+and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
+of individual components can only be larger than the number of absorption systems. Hence, although
+QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
+individual quasar-host associated system. , the central limit theorem applies and the distribution
+of all absorbing components should tend toward Gaussian distribution. To model the absorption, we
+introduce a Gaussian profile while allowing a constant pseudo-continuum level to vary. We perform
+$\chi^2$ minimization with each channel given equal weight. From the best-fit to the data, we
+measure the centroid of the \ion{C}{2} stack to be $+196\,{\rm km\,s^{-1}}$ and the $1\sigma$
+dispersion to be $313\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the
+standard expectation, while the dispersion suggests extreme kinematics. The median stack, on the
+other hand, shows weaker absorption, and the Gaussian model has a centroid with smaller offset and
 comparable dispersion.
@@
 second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and 
-$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. The 
-modeling results show that the velocity fields of \ion{C}{4} and \ion{Mg}{2} are consistent with 
-\ion{C}{2}, i.e.\ large dispersion and centroid is skewed toward positive velocities.
+$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
+allow the doublet ratio to vary from 2:1 to 1:1. The modeling results show that the velocity fields
+of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
+is skewed toward positive velocities.
 
@@
 less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
-stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2} or H$\alpha$ 
-redshift when available. We are able to replace for 11 out of the 15 systems with [\ion{O}{3}] 
-redshifts in the original sample. The new stack is similiar in velocity structure and again shows 
-a positive offset $\approx+259\,{\rm km\,s^{-1}}$. We thus conclude that our algorithm for 
-measuring redshifts is not severely biased by the blue wing of the [\ion{O}{3}] emission-line.
+stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
+more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for 11 out
+of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
+velocity structure and again shows a positive offset $\approx+259\,{\rm km\,s^{-1}}$. We thus
+conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
+[\ion{O}{3}] emission-line.
 
@@
 edge of the black hole or the black hole's location being slightly above the disk.
+As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
+keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
+simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
+absorption to within two times the modeling error.
 
@@
 %intrinsic dispersion of the \ion{C}{2} mean absorption.
-As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
-keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
-simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
-absorption to within two times the modeling error.
 The first explanation above to asymmetric

### 2017-09-22 QPQ9/Submit/response.txt
Updated the sample

--- 2017-07-20 QPQ9/Submit/response.txt
@@
 The distribution of absorbing components in velocity is non-Gaussian for each quasar-host associated system. However,
-we have 34 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
-analysis. The number of individual components can only be larger. The central limit theorem applies and the
+we have 30 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
+analyses. The number of individual components can only be larger. The central limit theorem applies and the
 distribution of all absorbing components should tend toward Gaussian distribution. A component-by-component analysis
@@
 individual measurements of centroids and peaks in Shen+16 thru private communication. There is essentially no
-difference between using the centroid versus using the peak for [OIII], and there is about 50 km/s difference for
-MgII. We may expect the difference between a mode and a peak is even smaller. Text have been added.
+difference between using the centroid versus using the peak for [OIII], and there is about 50 km/s
+difference for MgII on average. We may expect the difference between a mode and a peak is even smaller.
+
+In the first version of the submitted manuscript, there are two redshift measurement techniques in the z ~ 2 sample:
+our custom line-centering algorithm, and the algorithm of Hewett&Wild10. We thank the referee for scrutinizing the
+redshift measurement techniques, which helps strengthen our results. In this re-submitted manuscript, for all z > 1.6
+sample we measure redshifts of all quasars using our own custom line-centering algorithm instead of adopting values
+from Hewett&Wild10. After we purge the quasars whose redshift measurement is dominated by CIII], we find that on
+average there is essentially no difference between the Hewett&Wild10 redshifts and our own measured redshifts.
+Furthermore, Shen+16 has stated throughout the paper that their work is consistent with Hewett&Wild10 on redshift
+estimates based on MgII emission and on the average systemic bias. Therefore, for the z ~ 1 sample, where either the
+[OIII] or the MgII emission has good data quality, and where we do not measure an intriguing asymmetry in the average
+absorption, we continue to adopt the Hewett&Wild10 redshifts.
 
@@
 >kinematic spread of the absorbing gas. This is a general weakness of stacked measurements and raises the question of
->why the study does not show a histogram of the velocity difference sbetween the quasar systemic and observed
+>why the study does not show a histogram of the velocity differences between the quasar systemic and observed
 >absorption centroids in individual cases where the S/N is sufficient. Previous QPQ papers reported absorber redshifts
@@
 absorption within the search window. The QPQ7 sample has spectra of all resolutions. It requires echellette or
-echelle resolution to identify the metal-associated absorbers. In QPQ8, a histogram of the optical depth weighted
+echelle resolution to identify the metal-associated absorbers. In QPQ8, a scatter plot of the optical depth weighted
 centroid of the absorption systems is shown. In the Appendix of QPQ8, the absorption profiles of the individual
@@
 
-In QPQ8, we have estimated the random incidence of optically thick and CIV absorbers. Text has been added to reflect
+In QPQ8, we have estimated the random incidence of optically thick absorbers. Text has been added to reflect
 these numbers. As our Monte Carlo simulations demonstrate, outflows are not required to reproduce the observed
@@
 absorber is less than the average of QPQ8 CII absorber. Muzahid+15 found an absorber with Dv90 less than 555 km/s in
-OVI and NV, and still less for other ions. Zahedy+16's sample has average Dv90 elss than that of QPQ8. More text has
-been added.
+OVI and NV, and still smaller for other ions. Zahedy+16's sample has average Dv90 smaller than that of QPQ8.
 
@@
 
-We have cited Rubin+12 and Rudie+17 in our revised manuscript. We intend that h = H_0 / (100 km s^-1 Mpc^-1), in
-accordance with the common convention, that is also widely used in cosmology papers such as Kravtsov+17. We have
-state this scaling explicitly in our revised manuscript. We thank the referee for above suggestions.
+We have cited Rudie+17 in our revised manuscript. As our focus is on absorbers in background sightlines, Rubin+12 is
+less relevant. We intend that h = H_0 / (100 km s^-1 Mpc^-1), in accordance with the common convention, that is also
+widely used in cosmology papers such as Kravtsov+17. We have state this scaling explicitly in our revised manuscript.
+We thank the referee for above suggestions.
 
@@
 
-There is large intrinsic scatter in the CGM environments. In our revised manuscript, we included one new quasar pair
-from our latest QPQ Survey database, making the total sample size for CII analysis 33. With this sample, the median
-CII statistic has a centroid +120+/-195 km/s. We prefer the mean over the median, as the median statistic is not
-sensitive to absorption signals and does not preserve equivalent width. The centroid measured from the median stack
-is thus subject to larger uncertainty.
+There is large intrinsic scatter in the CGM environments. In our revised manuscript, we update the sample to pairs
+retrieved from the latest QPQ Survey database and we re-measure the redshifts originally adopted from HeWitt&Wild10.
+With this sample the median CII statistic has a centroid +105+/-176 km/s. We prefer the mean over the median, as the
+median statistic is less sensitive to absorption signals and does not preserve equivalent width. The median opacity at
+any velocity channel can be rather small, since absorbers are spread out throughout the entire velocity window and are
+discretized. The centroid measured from the median stack is thus subject to larger uncertainty.
 
@@
 lower average quasar luminosity should our interpretations be correct. The 0.4 < z < 1.6 quasars are largely SDSS
-spectra, and we adopt [OIII] or MgII emission-line redshifts taken from Hewett&Wild10. The z ~ 2 quasars of our sample
-have MgII, [OIII], or Halpha emission-line redshifts. We do not consider that the redshifts of the 0.4 < z < 1.6
-quasars are more accurate, since the more precise [OIII] redshifts are only accessible in SDSS spectral coverage for
-z < 0.84.
+spectra, and we adopt redshifts taken from Hewett&Wild10, which are dominated by the [OIII] or the MgII emission-line.
+The z ~ 2 quasars of our sample have MgII, [OIII], or Halpha emission-line redshifts. We do not consider that the
+redshifts of the 0.4 < z < 1.6 quasars are more accurate, since the more precise [OIII] redshifts are only accessible
+in SDSS spectral coverage for z < 0.84.
 

### 2017-09-22 QPQ9/Submit/qpq9_submit.tex
Updated the sample

@@
 We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
-We employ 112 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
+We employ 102 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
 absorption. The sample selects foreground quasars with precise redshift measurements, using 
@@
 star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
-$z\sim1$ quasars, and 
-found large peculiar motions in the gas exceeding the expected virial velocity, which they 
-interpret as quasar-driven outflows. However, the velocity spreads were not well quantified. Other 
+$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial 
+velocity, with quasar-driven outflows being one possible explanation. However, we consider that 
+their velocity spreads can be better quantified. Other 
 existing studies that found large velocity spreads are limited to single sightlines with most of 
-the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11}, or with gas tracing 
+the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}, 
+or with gas tracing 
 a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
-the average velocity spread is smaller than that measured in QPQ8 
-\citep[e.g., ][]{Gauthier13,Muzahid+15,Zahedy+16}.
+the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier+13}, where a 
+single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the 
+average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with 
+$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still 
+smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller 
+than that of QPQ8.
 
@@
 galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
-\citep[][, hereafter QPQ1]{QPQ1} to use the standard techniques of absorption-line spectroscopy 
+\citep[][hereafter QPQ1]{QPQ1} to use the standard techniques of absorption-line spectroscopy 
 with background quasars. These quasar pairs 
@@
 that these galaxies are surrounded by a massive, cool, and enriched CGM 
-\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 112 background 
+\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 102 background 
 spectra that are paired with foreground quasars with precisely measured redshifts. Among the
 sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or echelle
-observations, and have been analyzed separately in QPQ8 (see their Figure 8, 9, and 10). For this
+observations, and have been analyzed separately in QPQ8 (see their Figure 8, 9, and 10, and their 
+Appendix). In QPQ8, where the individual metal-bearing absorption components are resolved, 15 out 
+of the 21 components are at positive velocities relative to the systemic redshift. For this
 current work, we stack spectra of all resolutions instead of performing a component-by-component
@@
 We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
-igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
-catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
-Twelfth Data Release \citep{Paris+17}. We only select pairs with $z_{\rm fg}$ measured by 
-\cite{HewettWild10} using the \ion{Mg}{2}\,2800 emission-line, and we add the median blueshift of 
-\ion{Mg}{2} from the systemic to these redshifts. We reach a final sample size of 112. 
+igmspec\footnote{https://github.com/specdb/igmspec} \citep{Prochaska+17}, which includes the 
+spectra from the quasar catalogs based upon the Sloan Digital Sky Survey Seventh Data Release 
+\citep{Schneider+10} and the Twelfth Data Release \citep{Paris+17}. We only select pairs with 
+$z_{\rm fg}$ measurable using a robust \ion{Mg}{2}\,2800 emission-line. 
+We reach a final sample size of 102. 
 Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
@@
 $1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are 
-$28\,{\rm km\,s^{-1}}$ and $29\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling 
+$19\,{\rm km\,s^{-1}}$ and $20\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling 
 errors of the other stacks.
@@
 yields a good estimate of the average absorption and preserves equivalent width. The median 
-statistic is less sensitive to outliers, however the averaged equivalent width is smaller and the 
-analysis on the velocity field becomes more uncertain. In the following we present stacked spectra 
-using both the mean and the median statistic.
+statistic is less sensitive to outliers, however the median opacity at any velocity channel is 
+rather small, since the discrete absorbers are spread throughout the entire velocity window. The 
+analysis on the median velocity field is thus subject to larger uncertainty. In the following we 
+present stacked spectra using both the mean and the median statistic.
 
@@
 exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
-skewed toward positive velocities. We have 33 pairs in the QPQ9 sample for \ion{C}{2} analysis
+skewed toward positive velocities. We have 30 pairs in the QPQ9 sample for \ion{C}{2} analysis
 and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
@@
 QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
-individual quasar-host associated system. , the central limit theorem applies and the distribution
-of all absorbing components should tend toward Gaussian distribution. To model the absorption, we
-introduce a Gaussian profile while allowing a constant pseudo-continuum level to vary. We perform
-$\chi^2$ minimization with each channel given equal weight. From the best-fit to the data, we
-measure the centroid of the \ion{C}{2} stack to be $+196\,{\rm km\,s^{-1}}$ and the $1\sigma$
-dispersion to be $313\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the
-standard expectation, while the dispersion suggests extreme kinematics. The median stack, on the
-other hand, shows weaker absorption, and the Gaussian model has a centroid with smaller offset and
-comparable dispersion.
+individual quasar-host associated system, the central limit theorem applies and the distribution
+of all absorbing components should tend toward Gaussian distribution. A visual inspection of the 
+stack confirms that a broader absorption component is not apparent. Therefore, to model the 
+absorption, we may introduce a Gaussian profile while allowing a constant pseudo-continuum level 
+to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
+to the data, we measure the centroid of the \ion{C}{2} stack to be $+254\,{\rm km\,s^{-1}}$ and 
+the $1\sigma$ dispersion to be $299\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
+contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median 
+stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with 
+smaller offset and comparable dispersion.
 
@@
 
-The above analyses are summarized in Table~\ref{tab:summary}. The 
-Gaussian models normalized to pseudo-continuum are overplotted on the data stacks in 
-Figure~\ref{fig:stacks_and_fits}.
+The above analyses are summarized in Table~\ref{tab:summary}. The Gaussian models normalized to 
+pseudo-continuum are overplotted on the data stacks in Figure~\ref{fig:stacks_and_fits}.
 
@@
 the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
-find that 98\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper 
+find that 99\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper 
 limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
-$\delta v<+424\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
+$\delta v<+509\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
 whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
@@
 of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
-velocity structure and again shows a positive offset $\approx+259\,{\rm km\,s^{-1}}$. We thus
+velocity structure and again shows a positive offset $\approx+319\,{\rm km\,s^{-1}}$. We thus
 conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
@@
 \caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
-for the \ion{C}{2} mean stack. 98\% of the centroids are positively offset from $z_{\rm fg}$.}
+for the \ion{C}{2} mean stack. 99\% of the centroids are positively offset from $z_{\rm fg}$.}
 \label{fig:histogram_cen}
@@
 dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
-absorption profile with $\sigma_v=559\,{\rm km\,s^{-1}}$, which is larger than the observed width 
+absorption profile with $\sigma_v=539\,{\rm km\,s^{-1}}$, which is larger than the observed width 
 by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity 
 width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with 
-$\sigma_v=226\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
+$\sigma_v=239\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
 modeling error. Unless gravitational and Hubble flows together with redshift error broadening 
@@
 mean stack. For the full QPQ9 sample, with the mean 
-$\sigma_{{\rm error}(z)}^{\rm full}=182\,{\rm km\,s^{-1}}$, we recover 
-$\sigma_{\rm intrinsic}^{\rm full}=255\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
+$\sigma_{{\rm error}(z)}^{\rm full}=174\,{\rm km\,s^{-1}}$, we recover 
+$\sigma_{\rm intrinsic}^{\rm full}=243\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
 redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=356\,{\rm km\,s^{-1}}$.
@@
 root-mean-square velocity $\sigma_{\rm rms}$. Hence, the average line-of-sight rms velocity
-typical of QPQ9 halos is $\sigma_{\rm rms}=246\,{\rm km\,s^{-1}}$. We can investigate
+typical of QPQ9 halos is $\sigma_{\rm rms}=246\,{\rm km\,s^{-1}}$. 
+In QPQ8, we estimated the probability of intercepting a random optically thick absorber is 4\%, 
+and clustering would only increase that to 24\%. 
+Although motions due to Hubble flows do not dominate, they nevertheless contribute to the observed 
+dispersion. 
+We can investigate
 whether gravitational motions and Hubble flows are sufficient to reproduce the dispersion in the
@@
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $280\,{\rm km\,s^{-1}}$. This is
-about $1\sigma$ modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack for 
-the full sample, and about 3 times the modeling error away from the intrinsic dispersion in the 
-stack of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $286\,{\rm km\,s^{-1}}$. This is
+about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack 
+for the full sample, and about 3 times the modeling error away from the intrinsic dispersion in 
+the stack of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
 sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering 
@@
 From the bootstrap 
-analysis of the observed dispersion, a width of $\sigma_v>559\,{\rm km\,s^{-1}}$ would be larger 
+analysis of the observed dispersion, a width of $\sigma_v>539\,{\rm km\,s^{-1}}$ would be larger 
 than the observed by three times the scatter (overplotted in Figure~\ref{fig:monte}). In other 
 words, taking into account the redshift errors, motions in addition to gravitational and Hubble 
-flows that will produce an intrinsic dispersion $\sigma_v>529\,{\rm km\,s^{-1}}$ can be ruled out.
+flows that will produce an intrinsic dispersion $\sigma_v>510\,{\rm km\,s^{-1}}$ can be ruled out.
 
 On the contrary, 
-$\sigma_{\rm rms}<134\,{\rm km\,s^{-1}}$ together with Hubble velocities and
+$\sigma_{\rm rms}<132\,{\rm km\,s^{-1}}$ together with Hubble velocities and
 broadening by redshift errors will result in a velocity width that is more than three times the 
@@
 
-\begin{thebibliography}{45}
+\begin{thebibliography}{46}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
   L. 2017, \aap, 597, A79
+
+\bibitem[{{Prochaska}(2017)}]{Prochaska+17}
+{Prochaska}, J.~X. 2017, Astronomy and Computing, 19, 27
 

### 2017-09-22 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -47,7 +47,8 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
                                         S2N_cut=S2N_cut,atmosphere_cut=atmosphere_cut,
                                         stack_fg=stack_fg,plot_indiv=plot_indiv,
                                         QPQ_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/QPQ/data/',
-                                        igmspec_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/igmspec/')
+                                        igmspec_conti_path='/Users/lwymarie/Dropbox/Marie_X/QPQ9/Continua/igmspec/',
+                                        igmsp_version="02.1")
         if passback:
             return stack_tup
 

### 2017-09-22 QPQ9/Analysis/py/monte_carlo.py

@@ -114,8 +114,8 @@ def contour_data(all_dict):
         for jj in np.arange(widths.shape[1]):
             widths[ii,jj],amps[ii,jj] = model_width(stddev_oneabs_GRID[ii,jj],sigma1D_GRID[ii,jj],all_dict)
     WCII_grid = np.zeros_like(stddev_oneabs_grid)
-    width_levels = [168,197,226,284,313,342]
-    amp_bounds = [0.107,0.173] # 3-sigma bounds
+    width_levels = [164,192,218,267,291,314]
+    amp_bounds = [0.117,0.164] # 3-sigma bounds
     for ii,wcii in enumerate(WCII_grid):
         WCII_grid[ii] = stddev_oneabs_to_WCII(stddev_oneabs_grid[ii])
     mass_grid = np.zeros_like(sigma1D_grid)
@@ -152,8 +152,8 @@ def main(contour_only="False"):
 
     if contour_only == "False":
         # 3 times the modeling error smaller than observed width, minus redshift error broadening,
-        # gives intrinsic width 168 km/s
-        width,amp = model_width(23.5,134.,all_dict)
+        # gives intrinsic width 164 km/s
+        width,amp = model_width(22.5,132.,all_dict)
         plt.figure(figsize=(8,5))
         plt.axis([-2000,2000,0.65,1.05])
         model_final = models.GaussianAbsorption1D(amplitude=amp,mean=0.,stddev=width)
@@ -170,7 +170,7 @@ def main(contour_only="False"):
         dict = {}
         for ii,pp in enumerate(model_final.parameters):
             dict[model_final.param_names[ii]] = [pp]
-        ascii.write(Table(dict),'monte.dat')
+        ascii.write(Table(dict),'monte.dat',overwrite=True)
         # Find mean equivalent width of QPQ8 LLS
         mean_QPQ8 = np.mean([0.000,0.042,0.345,0.195,0.025,0.030,0.053,0.168,0.504,0.248,0.779,0.281,
                              0.341,0.328,0.756,0.650,0.154,0.179,0.130,0.950])

### 2017-09-22 QPQ9/Analysis/py/qpq9_strct.py

@@ -17,44 +17,16 @@ import enigma
 
 cosmo = FlatLambdaCDM(H0=70, Om0=0.26)
 
-## List of near IR redshifts
+# Load newly measured redshifts
 
-# Load masterlists
-path = enigma.__path__[0]+'/data/redshifts/'
-c_NIR = []
-gnirs = Table.read(path+'gnirs_masterlist.dat',guess=False,format='ascii.csv',comment='#')
-for qq in gnirs:
-    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
-niri = Table.read(path+'niri_masterlist.dat',guess=False,format='ascii.csv',comment='#')
-for qq in niri:
-    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
-nirspec = Table.read(path+'nirspec_masterlist.dat',guess=False,format='ascii.csv',comment='#')
-for qq in nirspec:
-    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
-xshooter = Table.read(path+'xshooter_masterlist.dat',guess=False,format='ascii.csv',comment='#')
-for qq in xshooter:
-    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
-tspec = Table.read(path+'triplespec_masterlist.dat',guess=False,format='ascii.csv',comment='#')
-for qq in tspec:
-    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
-isaac = Table.read(path+'isaac_masterlist.dat',guess=False,format='ascii.csv',comment='#')
-for qq in isaac:
-    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
-lucifer = Table.read(path+'lucifer_masterlist.dat',guess=False,format='ascii.csv',comment='#')
-for qq in lucifer:
-    c_NIR.append(ltu.radec_to_coord(qq['ra_qso']+' '+qq['dec_qso']))
-liam = Table.read(path+'masterlist_liam.fits')
-for qq in liam:
-    c_NIR.append(SkyCoord(qq['RAJ2000']+qq['DEJ2000'],frame='fk5'))
[…]

### 2017-09-22 QPQ9/Figures/py/qpq9_figs.py

@@ -192,6 +192,7 @@ def stacks_and_fits(outfil=None):
         # Plot
         plt.plot(velo.value, mean_stack[0].data,drawstyle='steps-mid',linewidth=2,color='k')
         plt.plot(velo.value, model(velo.value),color='b',linewidth=3)
+        plt.plot([0,0],[0,2],color='gray',linewidth=2,linestyle='--')
         plt.plot([model.mean_1.value,model.mean_1.value],[0,2],'b--',linewidth=2)
 
         # Font
@@ -225,6 +226,7 @@ def stacks_and_fits(outfil=None):
                 ions.ion_name(aline.data)+', median',size=fontsize)
         plt.plot(velo.value, median_stack[0].data,drawstyle='steps-mid',linewidth=2,color='k')
         plt.plot(velo.value, model(velo.value),color='b',linewidth=3)
+        plt.plot([0,0],[0,2],color='gray',linewidth=2,linestyle='--')
         plt.plot([model.mean_1.value,model.mean_1.value],[0,2],'b--',linewidth=2)
         for item in ([ax.title, ax.xaxis.label, ax.yaxis.label] +
                          ax.get_xticklabels() + ax.get_yticklabels()):
@@ -388,18 +390,18 @@ def monte(outfil=None):
     model_conti = models.Const1D(amplitude=Gaussian_params['amplitude_0'])
     model_monte_gauss = models.GaussianAbsorption1D(
         amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],
-        stddev=np.sqrt((monte_params['stddev'])**2.+182**2.))
+        stddev=np.sqrt((monte_params['stddev'])**2.+174**2.))
     print('s.d. in monte carlo model, in monte carlo model with redshift error broadening, in data',
-          monte_params['stddev'],np.sqrt((monte_params['stddev'])**2.+182**2.),
+          monte_params['stddev'],np.sqrt((monte_params['stddev'])**2.+174**2.),
           Gaussian_params['stddev_1'])
     model_monte = model_conti*model_monte_gauss
     # Extra motion that is ruled out
     model_extra_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=559.)
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=539.)
     model_extra = model_conti*model_extra_gauss
[…]

### 2017-09-22 QPQ9/Tables/py/qpq9_tables.py

@@ -248,9 +248,7 @@ for ii in np.arange(len(tab)):
     afile.write(tab['bg_qso'][ii] + ' & ' + tab['zbg'][ii] + ' & ' + tab['bg_instr'][ii] + ' & ')
     afile.write(tab['Rphys'][ii] + ' & ' + tab['gUV'][ii] + ' \\\ \n')
 afile.write('\\enddata \n')
-afile.write('\\tablenotetext{a}{The emission-line analyzed for measuring $z_{\\rm fg}$. \n')
-afile.write('SDSS-HW stands for adopting the redshift measured by Hewett \\& Wild (2010) \n')
-afile.write('directly.} \n')
+afile.write('\\tablenotetext{a}{The emission-line analyzed for measuring $z_{\\rm fg}$.} \n')
 afile.write('\\end{deluxetable*}')
 afile.close()
 

### 2017-09-25 QPQ9/Analysis/Bootstrap/py/qpq9_boot.py
smal changes

@@ -104,7 +104,7 @@ def boot_trans(wrest=1334.5323*u.AA,full_sample=True,
                 stddev_2 = model.stddev_1
                 return stddev_2
             def tie_amplitude2(model):
-                amplitude_2 = model.amplitude_1
+                amplitude_2 = model.amplitude_1*0.5
                 return amplitude_2
             model_init.mean_2.tied = tie_mean2
             model_init.stddev_2.tied = tie_stddev2

### 2017-09-25 QPQ9/Analysis/Stacks/py/qpq9_stacks.py

@@ -69,7 +69,8 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
 def plt_qpq9(stack_tup=None,wrest=None,
              S2N_cut=None,atmosphere_cut=True,
              vmnx=(-3000.,3000.)*u.km/u.s,
-             stack_fg=False,zfg_mnx=(-9999,9999),plot_indiv=False):
+             stack_fg=False,zfg_mnx=(-9999,9999),plot_indiv=False,
+             outfil=None):
 
     # Rest wavelength
     if wrest is None:
@@ -92,10 +93,11 @@ def plt_qpq9(stack_tup=None,wrest=None,
     nrow = 5
     for ipage in range(pages):
         # Start the plot
-        if stack_fg is True:
-            outfil = 'plt_qpq9_IRMgII_{:d}_fg_page{:d}.pdf'.format(int(wrest.value),ipage+1)
-        else:
-            outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+        if outfil is None:
+            if stack_fg is True:
+                outfil = 'plt_qpq9_IRMgII_{:d}_fg_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+            else:
+                outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
         pp = PdfPages(outfil)
         plt.figure(figsize=(8,5))
         plt.clf()

### 2017-09-25 QPQ9/Figures/py/qpq9_figs.py

@@ -71,6 +71,8 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
             if ions.ion_name(aline.data) == 'CIV':
                 if 'J1002+0020' in idict['qpq']['NAME']: #overlaps with BAL of bg quasar
                     idx_mask.append(ii)
+                if 'J2255-0001' in idict['qpq']['NAME']: #test effect of removing bad MgII redshift
+                    idx_mask.append(ii)
             if ions.ion_name(aline.data) == 'MgII':
                 if (('J0822+1319' in idict['qpq']['NAME']) | ('J0908+4215' in idict['qpq']['NAME']) |
                         ('J1242+1817' in idict['qpq']['NAME']) | ('J1622+2031' in idict['qpq']['NAME'])):

### 2017-09-25 QPQ9/Tables/py/qpq9_tables.py

@@ -104,6 +104,8 @@ for ii,idict in enumerate(all_dict):
         continue
     if 'J1002+0020' in idict['qpq']['NAME']: #CIV overlaps with BAL of background quasar
         idx_mask.append(ii)
+    if 'J2255-0001' in idict['qpq']['NAME']: #test effect of removing bad MgII redshift
+        idx_mask.append(ii)
 for idx in idx_mask:
     stck_mskN[idx,:] = 0.
 

### 2017-09-27 QPQ9/Analysis/Stacks/py/qpq9_stacks.py
updated to linetools' latest

@@ -70,7 +70,7 @@ def plt_qpq9(stack_tup=None,wrest=None,
              S2N_cut=None,atmosphere_cut=True,
              vmnx=(-3000.,3000.)*u.km/u.s,
              stack_fg=False,zfg_mnx=(-9999,9999),plot_indiv=False,
-             outfil=None):
+             outfil_prefix=None):
 
     # Rest wavelength
     if wrest is None:
@@ -93,11 +93,12 @@ def plt_qpq9(stack_tup=None,wrest=None,
     nrow = 5
     for ipage in range(pages):
         # Start the plot
-        if outfil is None:
-            if stack_fg is True:
-                outfil = 'plt_qpq9_IRMgII_{:d}_fg_page{:d}.pdf'.format(int(wrest.value),ipage+1)
-            else:
-                outfil = 'plt_qpq9_IRMgII_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+        if outfil_prefix is None:
+            outfil_prefix = 'plt_qpq_IRMgII'
+        if stack_fg is True:
+            outfil = outfil_prefix+'_{:d}_fg_page{:d}.pdf'.format(int(wrest.value),ipage+1)
+        else:
+            outfil = outfil_prefix+'_{:d}_page{:d}.pdf'.format(int(wrest.value),ipage+1)
         pp = PdfPages(outfil)
         plt.figure(figsize=(8,5))
         plt.clf()

### 2017-09-27 QPQ9/Analysis/py/monte_carlo.py

@@ -87,7 +87,8 @@ def model_width(stddev_oneabs,sigma1D,all_dict):
     for ii,idict in enumerate(all_dict):
         if idict is None:
             continue
-        if 'J1508+3635' in idict['qpq']['NAME']:
+        if (('J0143+2954' in idict['qpq']['NAME']) or ('J0850+4755' in idict['qpq']['NAME']) or
+                ('J0951+4932' in idict['qpq']['NAME'])): # removing bad continua that gave fake S/N
             continue
         else:
             stck_img = gen_stck_img(idict['qpq']['R_PHYS'],idict['qpq']['Z_FG'],stddev_oneabs,sigma1D)
@@ -104,8 +105,8 @@ def model_width(stddev_oneabs,sigma1D,all_dict):
 
 # Generate the data points for the contour plot
 def contour_data(all_dict):
-    stddev_oneabs_grid = np.arange(12.,63.,2.5)  # for finer/coarser grid, step = 2.5/5
-    sigma1D_grid = np.arange(117.,318.,5)  # for finer/coarser grid, step = 5/10
+    stddev_oneabs_grid = np.arange(10.,41.,2.5)  # for finer/coarser grid, step = 2.5/5
+    sigma1D_grid = np.arange(60.,301.,10)  # for finer/coarser grid, step = 10/20
     sigma1D_GRID,stddev_oneabs_GRID = np.meshgrid(sigma1D_grid,stddev_oneabs_grid)
     widths = np.zeros_like(stddev_oneabs_GRID)
     amps = np.zeros_like(stddev_oneabs_GRID)
@@ -114,8 +115,8 @@ def contour_data(all_dict):
         for jj in np.arange(widths.shape[1]):
             widths[ii,jj],amps[ii,jj] = model_width(stddev_oneabs_GRID[ii,jj],sigma1D_GRID[ii,jj],all_dict)
     WCII_grid = np.zeros_like(stddev_oneabs_grid)
-    width_levels = [164,192,218,267,291,314]
-    amp_bounds = [0.117,0.164] # 3-sigma bounds
+    width_levels = [100,148,188,258,290,321]
+    amp_bounds = [0.089,0.141] # 3-sigma bounds
     for ii,wcii in enumerate(WCII_grid):
         WCII_grid[ii] = stddev_oneabs_to_WCII(stddev_oneabs_grid[ii])
     mass_grid = np.zeros_like(sigma1D_grid)
[…]

### 2017-09-27 QPQ9/Analysis/py/qpq9_strct.py

@@ -1,5 +1,5 @@
 # imports
-import copy, os, glob, imp, shutil
+import copy, os, glob, imp, shutil, pdb
 import numpy as np
 
 from astropy.coordinates import SkyCoord
@@ -298,6 +298,38 @@ for qq,cc in enumerate(c_QPQ9):
 ## write
 Table(QPQ9).write('qpq9_final.fits',format='fits',overwrite=True)
 
+# Add pairs of zfg < 1.6 and measured by SDSS-HW
+
+QPQ9 = QTable(fits.open('qpq9_final.fits')[1].data)
+c_QPQ9 = SkyCoord(QPQ9['FG_RA']*u.deg,QPQ9['FG_DEC']*u.deg)
+c_QPQ9_bg = SkyCoord(ra=QPQ9['RA']*u.deg,dec=QPQ9['DEC']*u.deg)
+for qq,cc in enumerate(c_igmsp):
+    if kpc_amin[qq]*ang_sep[qq] < 300 *u.kpc:
+        if 'SDSS-HW' in igmsp.cat[ID_fg[qq]]['flag_zem']: # good z
+            # Match Johnson+15 and Farina+ samples' redshifts, and MgII redshift or better
+            if (igmsp.cat[ID_fg[qq]]['zem'] >= 0.4) & (igmsp.cat[ID_fg[qq]]['zem'] <= 1.6):
+                # Lya forest cut for MgII stack
+                if 2796.354*(1+igmsp.cat['zem'][ID_fg[qq]]) > (1215.6701+15.)*(1+igmsp.cat['zem'][ID_bg[qq]]):
+                    if len(np.where(cc.separation(c_QPQ9) < 0.5*u.arcsec)[0]) > 0: # in QPQ9 already
+                        pdb.set_trace()
+                    if np.mod(igmsp.cat['flag_group'][ID_fg[qq]],2) == 0:
+                        name = 'BOSSJ'
+                    else:
+                        name = 'SDSSJ'
+                    name = name + c_igmsp_bg[qq].to_string('hmsdms')[0:2]
+                    name = name + c_igmsp_bg[qq].to_string('hmsdms')[3:5]
+                    ipos = c_igmsp_bg[qq].to_string('hmsdms').rfind(' ')+1
+                    name = name + c_igmsp_bg[qq].to_string('hmsdms')[ipos:ipos+3]
[…]

### 2017-09-27 QPQ9/Figures/py/qpq9_figs.py

@@ -65,15 +65,16 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
         for ii,idict in enumerate(all_dict):
             if idict is None:
                 continue
-            if ions.ion_name(aline.data) == 'CII':
-                if 'J1508+3635' in idict['qpq']['NAME']: #DLA, should be excluded now
+            if ions.ion_to_name(aline.data) == 'CII':
+                if (('J0143+2954' in idict['qpq']['NAME']) or ('J0850+4755' in idict['qpq']['NAME']) or
+                    ('J0951+4932' in idict['qpq']['NAME'])): #uncertain continua give fake S/N
                     idx_mask.append(ii)
-            if ions.ion_name(aline.data) == 'CIV':
+            if ions.ion_to_name(aline.data) == 'CIV':
                 if 'J1002+0020' in idict['qpq']['NAME']: #overlaps with BAL of bg quasar
                     idx_mask.append(ii)
-                if 'J2255-0001' in idict['qpq']['NAME']: #test effect of removing bad MgII redshift
+                if 'J2255-0001' in idict['qpq']['NAME']: #doubtful MgII redshift
                     idx_mask.append(ii)
-            if ions.ion_name(aline.data) == 'MgII':
+            if ions.ion_to_name(aline.data) == 'MgII':
                 if (('J0822+1319' in idict['qpq']['NAME']) | ('J0908+4215' in idict['qpq']['NAME']) |
                         ('J1242+1817' in idict['qpq']['NAME']) | ('J1622+2031' in idict['qpq']['NAME'])):
                     #BAL, strange emission, sky emission, sky emission
@@ -112,7 +113,7 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
             ax.set_xlabel(r'$R_\perp$ (kpc)')
         ax.text((ax.get_xlim()[1]-ax.get_xlim()[0])*0.05+ax.get_xlim()[0],
                 (ax.get_ylim()[1]-ax.get_ylim()[0])*0.85+ax.get_ylim()[0],
-                ions.ion_name(aline.data),size=fontsize)
+                ions.ion_to_name(aline.data),size=fontsize)
         # Scatter
[…]

### 2017-09-27 QPQ9/Tables/py/qpq9_tables.py

@@ -29,7 +29,8 @@ idx_mask = []
 for ii,idict in enumerate(all_dict):
     if idict is None:
         continue
-    if 'J1508+3635' in idict['qpq']['NAME']: #DLA not excluded by forest cut, should be excluded now
+    if (('J0143+2954' in idict['qpq']['NAME']) or ('J0850+4755' in idict['qpq']['NAME']) or
+            ('J0951+4932' in idict['qpq']['NAME'])): #uncertain continua give fake S/N
         idx_mask.append(ii)
 for idx in idx_mask:
     stck_mskN[idx,:] = 0.
@@ -104,7 +105,7 @@ for ii,idict in enumerate(all_dict):
         continue
     if 'J1002+0020' in idict['qpq']['NAME']: #CIV overlaps with BAL of background quasar
         idx_mask.append(ii)
-    if 'J2255-0001' in idict['qpq']['NAME']: #test effect of removing bad MgII redshift
+    if 'J2255-0001' in idict['qpq']['NAME']: #doubtful MgII redshift
         idx_mask.append(ii)
 for idx in idx_mask:
     stck_mskN[idx,:] = 0.
@@ -262,23 +263,24 @@ stack_tup0 = qpq9k.qpq9_IRMgII(passback=True,wrest=1334.5323*u.AA,S2N_cut=5.5/u.
 fin_velo, stck_img, stck_msk, all_dict = stack_tup0
 stck_mskN = copy.deepcopy(stck_msk)
 idx_mask = []
-for ii,dd in enumerate(all_dict):
-    if dd is None:
+for ii,idict in enumerate(all_dict):
+    if idict is None:
         continue
-    if 'J1508+3635' in dd['qpq']['NAME']: #DLA not excluded by forest cut, should be excluded now
+    if (('J0143+2954' in idict['qpq']['NAME']) or ('J0850+4755' in idict['qpq']['NAME']) or
+            ('J0951+4932' in idict['qpq']['NAME'])): #uncertain continua give fake S/N
         idx_mask.append(ii)
 for idx in idx_mask:
     stck_mskN[idx,:] = 0.
 npairs_CII = str(int(np.max((np.sum(stck_mskN,0)))))
 sv_zfg = []
 sv_Rperp = []
-for ii,dd in enumerate(all_dict):
-    if dd is None:
[…]

### 2017-09-28 QPQ9/Submit/response.txt
resubmission, before bolding

@@
 The distribution of absorbing components in velocity is non-Gaussian for each quasar-host associated system. However,
-we have 30 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
+we have 40 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
 analyses. The number of individual components can only be larger. The central limit theorem applies and the
@@
 retrieved from the latest QPQ Survey database and we re-measure the redshifts originally adopted from HeWitt&Wild10.
-With this sample the median CII statistic has a centroid +105+/-176 km/s. We prefer the mean over the median, as the
+With this sample the median CII statistic has a centroid +119+/-240 km/s. We prefer the mean over the median, as the
 median statistic is less sensitive to absorption signals and does not preserve equivalent width. The median opacity at

### 2017-09-28 QPQ9/Submit/qpq9_submit.tex
resubmission, before bolding

@@
 We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
-We employ 102 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
+We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
 absorption. The sample selects foreground quasars with precise redshift measurements, using 
@@
 a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
-the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier+13}, where a 
+the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
 single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the 
@@
 $1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are 
-$19\,{\rm km\,s^{-1}}$ and $20\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling 
+$25\,{\rm km\,s^{-1}}$ and $27\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling
 errors of the other stacks.
@@
 exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
-skewed toward positive velocities. We have 30 pairs in the QPQ9 sample for \ion{C}{2} analysis
+skewed toward positive velocities. We have 40 pairs in the QPQ9 sample for \ion{C}{2} analysis
 and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
@@
 to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
-to the data, we measure the centroid of the \ion{C}{2} stack to be $+254\,{\rm km\,s^{-1}}$ and 
-the $1\sigma$ dispersion to be $299\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
+to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
+the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that
 contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median 
@@
 absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
-$+220\,{\rm km\,s^{-1}}$, and a dispersion of $362\,{\rm km\,s^{-1}}$, consistent with the full 
+$+235\,{\rm km\,s^{-1}}$, and a dispersion of $330\,{\rm km\,s^{-1}}$, consistent with the full
 sample.
@@
 the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
-find that 99\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper 
+find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
 limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
-$\delta v<+509\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
+$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
 whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
@@
 of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
-velocity structure and again shows a positive offset $\approx+319\,{\rm km\,s^{-1}}$. We thus
+velocity structure and again shows a positive offset $\approx+303\,{\rm km\,s^{-1}}$. We thus
 conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
@@
 redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is 
-dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are 231 
+dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are 233
 pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present 
@@
 sample. Gaussian absorption models fitted to the stack recover a centroid of 
-$-9\pm388\,{\rm km\,s^{-1}}$ and a dispersion of $161\,{\rm km\,s^{-1}}$. The average offset 
+$-11\pm379\,{\rm km\,s^{-1}}$ and a dispersion of $172\,{\rm km\,s^{-1}}$. The average offset
 from $0\,{\rm km\,s^{-1}}$ is much smaller than the offsets in the $z\sim2$ sample.
@@
 \caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
-for the \ion{C}{2} mean stack. 99\% of the centroids are positively offset from $z_{\rm fg}$.}
+for the \ion{C}{2} mean stack. 97\% of the centroids are positively offset from $z_{\rm fg}$.}
 \label{fig:histogram_cen}
@@
 dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
-absorption profile with $\sigma_v=539\,{\rm km\,s^{-1}}$, which is larger than the observed width 
+absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
 by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity 
 width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with 
-$\sigma_v=239\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
+$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
 modeling error. Unless gravitational and Hubble flows together with redshift error broadening 
@@
 mean stack. For the full QPQ9 sample, with the mean 
-$\sigma_{{\rm error}(z)}^{\rm full}=174\,{\rm km\,s^{-1}}$, we recover 
-$\sigma_{\rm intrinsic}^{\rm full}=243\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}] 
-redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=356\,{\rm km\,s^{-1}}$.
+$\sigma_{{\rm error}(z)}^{\rm full}=189\,{\rm km\,s^{-1}}$, we recover
+$\sigma_{\rm intrinsic}^{\rm full}=224\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}]
+redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=323\,{\rm km\,s^{-1}}$.
 
@@
 root-mean-square velocity $\sigma_{\rm rms}$. Hence, the average line-of-sight rms velocity
-typical of QPQ9 halos is $\sigma_{\rm rms}=246\,{\rm km\,s^{-1}}$. 
-In QPQ8, we estimated the probability of intercepting a random optically thick absorber is 4\%, 
-and clustering would only increase that to 24\%. 
-Although motions due to Hubble flows do not dominate, they nevertheless contribute to the observed 
-dispersion. 
-We can investigate
+typical of QPQ9 halos is $\sigma_{\rm rms}=246\,{\rm km\,s^{-1}}$. In QPQ8, we estimated the
+probability of intercepting a random optically thick absorber is 4\%, and clustering would only
+increase that to 24\%. Although motions due to Hubble flows do not dominate, they nevertheless
+contribute to the observed dispersion. We can investigate
 whether gravitational motions and Hubble flows are sufficient to reproduce the dispersion in the
@@
 equivalent width for \ion{C}{2} $W_{\rm CII}$ and a Gaussian absorption profile. We repeat the 
-above procedure for all 33 quasar pairs, and create a mean stack of the 33000 mock spectra
+above procedure for all 33 quasar pairs, and create a mean stack of the 40000 mock spectra
 generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
 the stack of mock spectra. We adjust the $W_{\rm CII}$ adopted for the absorbers until the 
-amplitude of the best-fit Gaussian of the stack of mock spectra matches the 
-amplitude of the stack of the observational data. We find that $W_{\rm CII}=0.6\,{\rm \AA}$ well
-reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
-insensitive to the assumed $W_{\rm CII}$ or line profile for one absorber.
+amplitude of the best-fit Gaussian of the stack of mock spectra matches the amplitude of the stack
+of the observational data. We find that $W_{\rm CII}\approx0.5\,{\rm \AA}$ well reproduces the
+amplitude, and the dispersion of the Gaussian absorption model is insensitive to the assumed
+$W_{\rm CII}$ or line profile for one absorber.
 
@@
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $286\,{\rm km\,s^{-1}}$. This is
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$. This is
 about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack 
-for the full sample, and about 3 times the modeling error away from the intrinsic dispersion in 
-the stack of the sub-sample with [\ion{O}{3}] redshifts. We also test for the 
+for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
+stack of the sub-sample with [\ion{O}{3}] redshifts as well. We also test for the
 sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering 
@@
 
-From the bootstrap 
-analysis of the observed dispersion, a width of $\sigma_v>539\,{\rm km\,s^{-1}}$ would be larger 
-than the observed by three times the scatter (overplotted in Figure~\ref{fig:monte}). In other 
-words, taking into account the redshift errors, motions in addition to gravitational and Hubble 
-flows that will produce an intrinsic dispersion $\sigma_v>510\,{\rm km\,s^{-1}}$ can be ruled out.
+From the bootstrap analysis of the observed dispersion, a width of
+$\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter
+(overplotted in Figure~\ref{fig:monte}). In other words, taking into account the redshift errors,
+motions in addition to gravitational and Hubble flows that will produce an intrinsic dispersion
+$\sigma_v>521\,{\rm km\,s^{-1}}$ can be ruled out.
 
 On the contrary, 
-$\sigma_{\rm rms}<132\,{\rm km\,s^{-1}}$ together with Hubble velocities and
+$\sigma_{\rm rms}<70\,{\rm km\,s^{-1}}$ together with Hubble velocities and
 broadening by redshift errors will result in a velocity width that is more than three times the 
 modeling error away from the observed width (overplotted in Figure~\ref{fig:monte}). This implies 
-that, unless the characteristic $M_{\rm halo}<10^{11.8}\,M_\odot$,
+that, unless the characteristic $M_{\rm halo}<10^{11.0}\,M_\odot$,
 additional dynamical processes are not required to explain the observed width.
@@
 width is higher. If there are no extra dynamical processes, the intrinsic velocity width 
-corresponding to typical QPQ halo mass is well contained within the 1$\sigma$ contour.
+corresponding to typical QPQ halo mass is contained within the 2$\sigma$ contour.
 
-\subsection{Line-of-sight absorption}
-\label{sec:los_stacks}
+\section{Discussion}
+\label{sec:discussion}
+
+\begin{figure*}[!th]
+\begin{minipage}[!bp]{0.28\textwidth}
+%\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
+\includegraphics[width=\textwidth]{f08.pdf}
+\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
+absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation. 
+}
+\label{fig:monopolar}
+\end{minipage}%
+\hspace{0.3in}
+\begin{minipage}[!bp]{0.67\textwidth}
+%\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
+\includegraphics[width=\textwidth]{f09.pdf}
+\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
+asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining 
+long enough for its ionizing radiation to reach the gas behind it, when the light from the 
+background quasar reaches. The setup on the right shows the scenario after an amount of time 
+comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar 
+has been ionized, by the time the light from the background quasar reaches. 
+}
+\label{fig:lighttravel}
+\end{minipage}
+\end{figure*}
+
+At low redshift, both symmetric and asymmetric ionization cones around quasars and AGNs are
+observed. In the extended emission-line region of 4C37.43, most of the [\ion{O}{3}] emission is
+blueshifted \citep{FuStockton07}, but there are counter examples in less extended sources in
+\cite{FuStockton09}. Recently, there has been Fabry-Perot interferometric data for less extended
+narrow-line regions in more nearby sources \citep{Keel+15,Keel+17}, which show mostly symmetric
+velocity fields and gas distributions.
+
+In the following, we explore two possible explanations for the putative non-dynamical process that
+provides the asymmetry.
+
+One possibility is an asymmetric radiation field that preferentially ionizes the gas moving toward 
+the observer, where the quasar is known to shine. Alternatively, the asymmetric radiation field 
+may preferentially ionizes the gas at smaller Hubble velocity than the quasar. In 
+Figure~\ref{fig:monopolar}, we show a cartoon of a quasar that is blocked in the direction 
+pointing away from the observer. The gas observed in absorption preferentially lies behind the 
+quasar. The asymmetric absorption arises from a transverse proxmity effect. 
+\cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy 
+including thermal AGN feedback and calculated radiative transfer in post-processing. They found 
+the ionization radiation is typically asymmetric, due to either a dense clump that lies on one 
+edge of the black hole or the black hole's location being slightly above the disk.
+\cite{FaucherGiguere+16} represents the only simulation so far that is able to reproduce the
+substantial amount of cool gas in quasar-mass haloes. We eagerly await their group to compare the
+fraction of gas in inflows and outflows.
+
+As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
+keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
+simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
+absorption to within the modeling error.
+
+Another possible explanation arises from the finite lifetime of quasar episodes. 
+Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. Light from the 
+background quasar will travel smaller distance to reach the gas behind the foreground quasar 
+than the gas in front of it. The light from the background quasar may arrive at the gas behind 
+the foreground quasar before the ionizing radiation from the foreground quasar arrives. In 
+QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average 
+extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of 
+$\sim10^6$\,yr, which lies within existing constraints of quasar lifetime from observations 
+\citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
+
+%As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, radial
+%speeds relative to the foreground quasar of $500\textendash700\,{\rm km\,s^{-1}}$ and quasar
+%opening angles of $120^\circ\textendash140^\circ$ may reproduce the observed centroid and
+%intrinsic dispersion of the \ion{C}{2} mean absorption.
+The first explanation above to asymmetric
+absorption requires that the quasars emit their ionizing radiation anisotropically, while the 
+second explanation requires the quasars emit their ionizing radiation intermittently. Both 
+explanations will require the line-of-sight motions of the gas to be in either outflow or Hubble 
+flow. Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
+Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
+Using Cloud photoionization models, we find that, for the typical quasar luminosity of our sample,
+a CGM gas that is directly illuminated is highly ionized and shows only marginally detectable
+\ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate, and a
+blueshifted absorption signal needs to be searched in a higher ion.
+
+Motivated by the asymmetry found in metal ion absorption in the CGM using precise $z_{\rm fg}$ 
+measurements, and the asymmetry found by \cite{KirkmanTytler08} in \ion{H}{1} on larger 
+scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study 
+this asymmetry in \ion{H}{1} (J. F. Hennawi et al. 2017, in preparation). In conclusion, we 
+observe large and positively skewed velocity fields in absorption, of metal ions 
+in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
+explained if the detected gas is in gravitational motion, Hubble flow, or outflow, and the quasars 
+either shine preferentially toward the observer or shine intermittently.
+
+\acknowledgements
+
+JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and 
+AST-1412981. The authors gratefully acknowledge the support which enabled these observations at 
+the Keck, Gemini, Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar 
+Observatories. The authors acknowledge the sharing of private data by Yue Shen. MWL thanks Hai Fu
+for a discussion on extended emission-line regions, T.-K. Chan for a discussion on CGM
+simulations, and Chi Po Choi for a discussion on statistics.
+
+\appendix
+
+\section{Line-of-sight absorption}
+\label{sec:appendix}
 
@@
 
-\section{Discussion}
-\label{sec:discussion}
-
-\begin{figure*}[!th]
-\begin{minipage}[!bp]{0.28\textwidth}
-%\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
-\includegraphics[width=\textwidth]{f08.pdf}
-\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion 
-absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation. 
-}
-\label{fig:monopolar}
-\end{minipage}%
-\hspace{0.3in}
-\begin{minipage}[!bp]{0.67\textwidth}
-%\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
-\includegraphics[width=\textwidth]{f09.pdf}
-\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the 
-asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining 
-long enough for its ionizing radiation to reach the gas behind it, when the light from the 
-background quasar reaches. The setup on the right shows the scenario after an amount of time 
-comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar 
-has been ionized, by the time the light from the background quasar reaches. 
-}
-\label{fig:lighttravel}
-\end{minipage}
-\end{figure*}
-
-In the following, we explore two possible explanations for the putative non-dynamical process that 
-provides the asymmetry.
-
-One possibility is an asymmetric radiation field that preferentially ionizes the gas moving toward 
-the observer, where the quasar is known to shine. Alternatively, the asymmetric radiation field 
-may preferentially ionizes the gas at smaller Hubble velocity than the quasar. In 
-Figure~\ref{fig:monopolar}, we show a cartoon of a quasar that is blocked in the direction 
-pointing away from the observer. The gas observed in absorption preferentially lies behind the 
-quasar. The asymmetric absorption arises from a transverse proxmity effect. 
-\cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy 
-including thermal AGN feedback and calculated radiative transfer in post-processing. They found 
-the ionization radiation is typically asymmetric, due to either a dense clump that lies on one 
-edge of the black hole or the black hole's location being slightly above the disk.
-As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
-keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
-simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
-absorption to within two times the modeling error.
-
-Another possible explanation arises from the finite lifetime of quasar episodes. 
-Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. Light from the 
-background quasar will travel smaller distance to reach the gas behind the foreground quasar 
-than the gas in front of it. The light from the background quasar may arrive at the gas behind 
-the foreground quasar before the ionizing radiation from the foreground quasar arrives. In 
-QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average 
-extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of 
-$\sim10^6$\,yr, which lies within existing constraints of quasar lifetime from observations 
-\citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
-
-%As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, radial
-%speeds relative to the foreground quasar of $500\textendash700\,{\rm km\,s^{-1}}$ and quasar
-%opening angles of $120^\circ\textendash140^\circ$ may reproduce the observed centroid and
-%intrinsic dispersion of the \ion{C}{2} mean absorption.
-The first explanation above to asymmetric
-absorption requires that the quasars emit their ionizing radiation anisotropically, while the 
-second explanation requires the quasars emit their ionizing radiation intermittently. Both 
-explanations will require the line-of-sight motions of the gas to be in either outflow or Hubble 
-flow. Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
-
-Motivated by the asymmetry found in metal ion absorption in the CGM using precise $z_{\rm fg}$ 
-measurements, and the asymmetry found by \cite{KirkmanTytler08} in \ion{H}{1} on larger 
-scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study 
-this asymmetry in \ion{H}{1} (J. F. Hennawi et al. 2017, in preparation). In conclusion, we 
-observe large and positively skewed velocity fields in absorption, of metal ions 
-in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
-explained if the detected gas is in gravitational motion, Hubble flow, or outflow, and the quasars 
-either shine preferentially toward the observer or shine intermittently.
-
-\acknowledgements
-
-JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and 
-AST-1412981. The authors gratefully acknowledge the support which enabled these observations at 
-the Keck, Gemini, Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar 
-Observatories. The authors acknowledge the sharing of private data by Yue Shen. MWL thanks Hai Fu
-for a discussion on extended emission-line regions, T.-K. Chan for a discussion on CGM
-simulations, and Chi Po Choi for a discussion on statistics.
-
 %\bibliographystyle{/Users/lwymarie/Documents/Bibli/apj}
@@
 
-\begin{thebibliography}{46}
+\begin{thebibliography}{52}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
   I., \& {Streblyanska}, A. 2015, \mnras, 453, 2779
+
+\bibitem[{{Faucher-Gigu{\`e}re} {et~al.}(2016){Faucher-Gigu{\`e}re},
+  {Feldmann}, {Quataert}, {Kere{\v s}}, {Hopkins}, \&
+  {Murray}}]{FaucherGiguere+16}
+{Faucher-Gigu{\`e}re}, C.-A., {Feldmann}, R., {Quataert}, E., {Kere{\v s}}, D.,
+  {Hopkins}, P.~F., \& {Murray}, N. 2016, \mnras, 461, L32
+
+\bibitem[{{Fu} \& {Stockton}(2007)}]{FuStockton07}
+{Fu}, H., \& {Stockton}, A. 2007, \apj, 666, 794
+
+\bibitem[{{Fu} \& {Stockton}(2009)}]{FuStockton09}
+---. 2009, \apj, 690, 953
 
@@
 {Johnson}, S.~D., {Chen}, H.-W., \& {Mulchaey}, J.~S. 2015, \mnras, 452, 2553
+
+\bibitem[{{Keel} {et~al.}(2017){Keel}, {Lintott}, {Maksym}, {Bennert},
+  {Chojnowski}, {Moiseev}, {Smirnova}, {Schawinski}, {Sartori}, {Urry},
+  {Pancoast}, {Schirmer}, {Scott}, {Showley}, \& {Flatland}}]{Keel+17}
+{Keel}, W.~C., {Lintott}, C.~J., {Maksym}, W.~P., {Bennert}, V.~N.,
+  {Chojnowski}, S.~D., {Moiseev}, A., {Smirnova}, A., {Schawinski}, K.,
+  {Sartori}, L.~F., {Urry}, C.~M., {Pancoast}, A., {Schirmer}, M., {Scott}, B.,
+  {Showley}, C., \& {Flatland}, K. 2017, \apj, 835, 256
+
+\bibitem[{{Keel} {et~al.}(2015){Keel}, {Maksym}, {Bennert}, {Lintott},
+  {Chojnowski}, {Moiseev}, {Smirnova}, {Schawinski}, {Urry}, {Evans},
+  {Pancoast}, {Scott}, {Showley}, \& {Flatland}}]{Keel+15}
+{Keel}, W.~C., {Maksym}, W.~P., {Bennert}, V.~N., {Lintott}, C.~J.,
+  {Chojnowski}, S.~D., {Moiseev}, A., {Smirnova}, A., {Schawinski}, K., {Urry},
+  C.~M., {Evans}, D.~A., {Pancoast}, A., {Scott}, B., {Showley}, C., \&
+  {Flatland}, K. 2015, \aj, 149, 155
 
@@
   {Martin}, C.~L., \& {Winstrom}, L.~O. 2014, \apj, 794, 156
+
+\bibitem[{{Rudie} {et~al.}(2017){Rudie}, {Newman}, \&
+  {Murphy}}]{RudieNewmanMurphy17}
+{Rudie}, G.~C., {Newman}, A.~B., \& {Murphy}, M.~T. 2017, \apj, 843, 98
 

### 2017-09-28 QPQ9/Figures/py/qpq9_figs.py

@@ -393,18 +393,18 @@ def monte(outfil=None):
     model_conti = models.Const1D(amplitude=Gaussian_params['amplitude_0'])
     model_monte_gauss = models.GaussianAbsorption1D(
         amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],
-        stddev=np.sqrt((monte_params['stddev'])**2.+192**2.))
+        stddev=np.sqrt((monte_params['stddev'])**2.+188.7**2.))
     print('s.d. in monte carlo model, in monte carlo model with redshift error broadening, in data',
-          monte_params['stddev'],np.sqrt((monte_params['stddev'])**2.+192**2.),
+          monte_params['stddev'],np.sqrt((monte_params['stddev'])**2.+188.7**2.),
           Gaussian_params['stddev_1'])
     model_monte = model_conti*model_monte_gauss
     # Extra motion that is ruled out
     model_extra_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=539.)
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=554.)
     model_extra = model_conti*model_extra_gauss
     # Width that requires outflow
     model_outflow_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=118.)
+        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],stddev=213.5)
     model_outflow = model_conti*model_outflow_gauss
 
     # Axes

### 2017-09-28 QPQ9/Submit/qpq9_resubmit.tex
resubmission, after bolding

--- 2017-09-28 QPQ9/Submit/qpq9_submit.tex
@@
 We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
-We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
+We employ {\bf 148} projected quasar pairs to study the circumgalactic gas of the foreground quasars in
 absorption. The sample selects foreground quasars with precise redshift measurements, using 
@@
 $\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
-motion and Hubble flow, and galactic-scale outflows are not required to explain the large 
+motion and Hubble flow, and galactic-scale outflows {\bf are not required} to explain the large
 widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
@@
 star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
-$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial 
+$z\sim1$ {\bf quasars. They found large peculiar motions in the gas exceeding the expected virial
 velocity, with quasar-driven outflows being one possible explanation. However, we consider that 
-their velocity spreads can be better quantified. Other 
+their velocity spreads can be better quantified.} Other
 existing studies that found large velocity spreads are limited to single sightlines with most of 
-the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}, 
+the gas within several hundred ${\rm km\,s^{-1}}$ {\bf \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}},
 or with gas tracing 
 a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
-the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
+the average velocity spread is smaller than that measured in {\bf QPQ8. In \cite{Gauthier13}, where a
 single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the 
@@
 smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller 
-than that of QPQ8.
+than that of QPQ8.}
 
@@
 that these galaxies are surrounded by a massive, cool, and enriched CGM 
-\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 102 background 
+\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of {\bf 148} background
 spectra that are paired with foreground quasars with precisely measured redshifts. Among the
 sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or echelle
-observations, and have been analyzed separately in QPQ8 (see their Figure 8, 9, and 10, and their 
+observations, and have been analyzed separately in QPQ8 {\bf (see their Figure 8, 9, and 10, and their
 Appendix). In QPQ8, where the individual metal-bearing absorption components are resolved, 15 out
@@
 current work, we stack spectra of all resolutions instead of performing a component-by-component
-analysis. Our primary scientific interests are twofold: (i) search for signatures of galactic-scale
+analysis.} Our primary scientific interests are twofold: (i) search for signatures of galactic-scale
 outflows from the central galaxy, presumably driven by recent star formation and/or active galactic
@@
 to comoving distances we include explicitly an $h^{-1}$ term and follow modern convention of 
-scaling to the Hubble constant $h = H_0/(70\,{\rm km\,s^{-1}\,Mpc^{-1}})$.
+scaling to {\bf the Hubble constant $h = H_0/(70\,{\rm km\,s^{-1}\,Mpc^{-1}})$}.
 %All equivalent width measurements are presented in the rest-frame, unless otherwise specified.
@@
 $\approx100\,{\rm km\,s^{-1}}$ \citep[][QPQ8]{Shen+16}.
-Our line-centering algorithm calculates the mode of a line given by
+{\bf Our line-centering algorithm calculates the mode of a line given by
 $3\times{\rm median}-2\times{\rm mean}$, applied to the upper 60\% of the emission, while
@@
 systemic bias corrections measured in \cite{Shen+16} may be self-consistently applied to our
-measured emission-line redshifts to obtain systemic redshifts.
+measured emission-line redshifts to obtain systemic redshifts.}
 
@@
 spectra from the quasar catalogs based upon the Sloan Digital Sky Survey Seventh Data Release 
-\citep{Schneider+10} and the Twelfth Data Release \citep{Paris+17}. We only select pairs with 
+\citep{Schneider+10} and the Twelfth Data Release \citep{Paris+17}. {\bf We only select pairs with
 $z_{\rm fg}$ measurable using a robust \ion{Mg}{2}\,2800 emission-line. 
-We reach a final sample size of 102. 
+We reach a final sample size of 148.}
 Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
-QPQ publications for the details on the emission-line centering algorithm, data reduction, and
+QPQ publications for the details on the {\bf emission-line centering} algorithm, data reduction, and
 continuum normalization (QPQ1; QPQ6; QPQ8).
@@
 For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
-included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
+included in the modeling. The absorptions frequently exhibit large velocity widths. The {\bf blue} dashed
 lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
-$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are 
-$25\,{\rm km\,s^{-1}}$ and $27\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling
+$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack {\bf are
+$25\,{\rm km\,s^{-1}}$ and $27\,{\rm km\,s^{-1}}$} respectively, which is also the typical modeling
 errors of the other stacks.
@@
 yields a good estimate of the average absorption and preserves equivalent width. The median 
-statistic is less sensitive to outliers, however the median opacity at any velocity channel is 
+statistic is less sensitive to outliers, {\bf however the median opacity at any velocity channel is
 rather small, since the discrete absorbers are spread throughout the entire velocity window. The 
-analysis on the median velocity field is thus subject to larger uncertainty. In the following we 
+analysis on the median velocity field is thus subject to larger uncertainty.} In the following we
 present stacked spectra using both the mean and the median statistic.
@@
 analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
-and it is more challenging to analyze their kinematics.
+and it is more challenging to {\bf analyze} their kinematics.
 %To assess the average absorption of these transitions,
@@
 exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
-skewed toward positive velocities. We have 40 pairs in the QPQ9 sample for \ion{C}{2} analysis
+skewed toward positive velocities. {\bf We have 40 pairs in the QPQ9 sample for \ion{C}{2} analysis
 and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
@@
 of all absorbing components should tend toward Gaussian distribution. A visual inspection of the 
-stack confirms that a broader absorption component is not apparent. Therefore, to model the 
+stack confirms that a broader absorption component is not apparent. Therefore, to} model the
 absorption, we may introduce a Gaussian profile while allowing a constant pseudo-continuum level 
 to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
-to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
-the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that
+to the data, we measure the centroid of the \ion{C}{2} stack {\bf to be \bf $+232\,{\rm km\,s^{-1}}$ and
+the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$.} The centroid suggests an asymmetry that
 contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median 
 stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with 
-smaller offset and comparable dispersion.
+smaller offset and {\bf a more uncertain dispersion}.
 
 We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the 
-absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
-$+235\,{\rm km\,s^{-1}}$, and a dispersion of $330\,{\rm km\,s^{-1}}$, consistent with the full
+absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a {\bf centroid at
+$+235\,{\rm km\,s^{-1}}$, and a dispersion of $330\,{\rm km\,s^{-1}}$,} consistent with the full
 sample.
@@
 second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and 
-$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
-allow the doublet ratio to vary from 2:1 to 1:1. The modeling results show that the velocity fields
+$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. {\bf We
+allow the doublet ratio to vary from 2:1 to 1:1.} The modeling results show that the velocity fields
 of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
@@
 
-Given the small sample size, one must scrutinize the statistical significance of the measured 
-velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
+{\bf To assess the statistical significance of the measured velocity offsets, we perform a boostrap analysis by
 randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
@@
 the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
-find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
-limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
-$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
+find that {\bf 97\%} of the centroids are at positive velocities. We place a generous $3\sigma$ upper
+limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption {\bf at
+$\delta v<+526\,{\rm km\,s^{-1}}$.} Given the large intrinsic scatter, we do not attempt to explore
 whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
@@
 stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
-more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for 11 out
-of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
-velocity structure and again shows a positive offset $\approx+303\,{\rm km\,s^{-1}}$. We thus
+more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for {\bf 11 out
+of the} 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
+velocity structure and again shows a positive {\bf offset $\approx+303\,{\rm km\,s^{-1}}$.} We thus
 conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
@@
 redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is 
-dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are 233
+dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are {\bf 233}
 pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present 
 the mean stack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
-sample. Gaussian absorption models fitted to the stack recover a centroid of 
-$-11\pm379\,{\rm km\,s^{-1}}$ and a dispersion of $172\,{\rm km\,s^{-1}}$. The average offset
+sample. Gaussian absorption models fitted to the stack recover a {\bf centroid of
+$-11\pm379\,{\rm km\,s^{-1}}$ and a dispersion of $172\,{\rm km\,s^{-1}}$.} The average offset
 from $0\,{\rm km\,s^{-1}}$ is much smaller than the offsets in the $z\sim2$ sample.
@@
 \caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
-for the \ion{C}{2} mean stack. 97\% of the centroids are positively offset from $z_{\rm fg}$.}
+for the \ion{C}{2} mean stack. {\bf 97\%} of the centroids are positively offset from $z_{\rm fg}$.}
 \label{fig:histogram_cen}
@@
 dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an 
-absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
+absorption profile {\bf with $\sigma_v=554\,{\rm km\,s^{-1}}$}, which is larger than the observed width
 by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity 
-width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with 
-$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
+width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile {\bf with
+$\sigma_v=214\,{\rm km\,s^{-1}}$,} which is smaller than the observed width by three times the
 modeling error. Unless gravitational and Hubble flows together with redshift error broadening 
@@
 absorption profile. We mark contours for points that produce an absorption 
-profile of width that is 1, 2, and 3 times the modeling error away from the observed intrinsic 
+profile of width that is {\bf 1, 2, and 3 times} the modeling error away from the observed intrinsic
 width. The intrinsic velocity width corresponding to typical QPQ halo mass is marked with a plus 
-sign, and is well contained within the 1$\sigma$ contour.}
+sign, and is {\bf contained within the 2$\sigma$ contour}.}
 \label{fig:contour}
@@
 quadrature to give the observed width, we solve for the intrinsic dispersion in the \ion{C}{2} 
-mean stack. For the full QPQ9 sample, with the mean 
+mean stack. For the full QPQ9 sample, with the {\bf mean
 $\sigma_{{\rm error}(z)}^{\rm full}=189\,{\rm km\,s^{-1}}$, we recover
-$\sigma_{\rm intrinsic}^{\rm full}=224\,{\rm km\,s^{-1}}$. For the sub-sample with [\ion{O}{3}]
-redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=323\,{\rm km\,s^{-1}}$.
+$\sigma_{\rm intrinsic}^{\rm full}=224\,{\rm km\,s^{-1}}$.} For the sub-sample with [\ion{O}{3}]
+redshifts, we {\bf recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=323\,{\rm km\,s^{-1}}$.}
 
@@
 root-mean-square velocity $\sigma_{\rm rms}$. Hence, the average line-of-sight rms velocity
-typical of QPQ9 halos is $\sigma_{\rm rms}=246\,{\rm km\,s^{-1}}$. In QPQ8, we estimated the
+typical of QPQ9 halos is $\sigma_{\rm rms}=246\,{\rm km\,s^{-1}}$. {\bf In QPQ8, we estimated the
 probability of intercepting a random optically thick absorber is 4\%, and clustering would only
 increase that to 24\%. Although motions due to Hubble flows do not dominate, they nevertheless
-contribute to the observed dispersion. We can investigate
+contribute to the observed dispersion.} We can investigate
 whether gravitational motions and Hubble flows are sufficient to reproduce the dispersion in the
@@
 equivalent width for \ion{C}{2} $W_{\rm CII}$ and a Gaussian absorption profile. We repeat the 
-above procedure for all 33 quasar pairs, and create a mean stack of the 40000 mock spectra
+above procedure for all {\bf 40} quasar pairs, and create a mean stack of the 40000 mock spectra
 generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
@@
 amplitude of the best-fit Gaussian of the stack of mock spectra matches the amplitude of the stack
-of the observational data. We find that $W_{\rm CII}\approx0.5\,{\rm \AA}$ well reproduces the
+of the observational data. We find {\bf that $W_{\rm CII}\approx0.5\,{\rm \AA}$ well} reproduces the
 amplitude, and the dispersion of the Gaussian absorption model is insensitive to the assumed
@@
 broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$. This is
-about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack 
-for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
-stack of the sub-sample with [\ion{O}{3}] redshifts as well. We also test for the
+The resulting stack of mock spectra has a $1\sigma$ {\bf dispersion of $282\,{\rm km\,s^{-1}}$.} This is
+about {\bf 2} times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack
+for the full sample, and about {\bf 2} times the modeling error away from the intrinsic dispersion in the
+stack of the sub-sample with [\ion{O}{3}] redshifts {\bf as well}. We also test for the
 sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering 
@@
 
-From the bootstrap analysis of the observed dispersion, a width of
-$\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter
+From the bootstrap analysis of the observed dispersion, a width {\bf of
+$\sigma_v>554\,{\rm km\,s^{-1}}$ would} be larger than the observed by three times the scatter
 (overplotted in Figure~\ref{fig:monte}). In other words, taking into account the redshift errors,
-motions in addition to gravitational and Hubble flows that will produce an intrinsic dispersion
-$\sigma_v>521\,{\rm km\,s^{-1}}$ can be ruled out.
-
-On the contrary, 
-$\sigma_{\rm rms}<70\,{\rm km\,s^{-1}}$ together with Hubble velocities and
+motions in addition to gravitational and Hubble flows that will produce an intrinsic {\bf dispersion
+$\sigma_v>521\,{\rm km\,s^{-1}}$} can be ruled out.
+
+On the {\bf contrary,
+$\sigma_{\rm rms}<70\,{\rm km\,s^{-1}}$ together} with Hubble velocities and
 broadening by redshift errors will result in a velocity width that is more than three times the 
 modeling error away from the observed width (overplotted in Figure~\ref{fig:monte}). This implies 
-that, unless the characteristic $M_{\rm halo}<10^{11.0}\,M_\odot$,
+that, unless the {\bf characteristic $M_{\rm halo}<10^{11.0}\,M_\odot$,}
 additional dynamical processes are not required to explain the observed width.
@@
 mark contours for points in ($W_{\rm CII}$, $M_{\rm halo}$)-space that produce an absorption 
-profile of width within 1, 2, and 3 times the modeling error of the observed intrinsic width. 
+profile of width within {\bf 1, 2, and 3} times the modeling error of the observed intrinsic width.
 From the figure, a higher $W_{\rm CII}$ means the $M_{\rm halo}$ that will reproduce the observed 
@@
 
-At low redshift, both symmetric and asymmetric ionization cones around quasars and AGNs are
+{\bf At low redshift, both symmetric and asymmetric ionization cones around quasars and AGNs are
 observed. In the extended emission-line region of 4C37.43, most of the [\ion{O}{3}] emission is
@@
 narrow-line regions in more nearby sources \citep{Keel+15,Keel+17}, which show mostly symmetric
-velocity fields and gas distributions.
+velocity fields and gas distributions.}
 
@@
 edge of the black hole or the black hole's location being slightly above the disk.
-\cite{FaucherGiguere+16} represents the only simulation so far that is able to reproduce the
+{\bf \cite{FaucherGiguere+16} represents the only simulation so far that is able to reproduce the
 substantial amount of cool gas in quasar-mass haloes. We eagerly await their group to compare the
-fraction of gas in inflows and outflows.
-
-As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
+fraction of gas in inflows and outflows.}
+
+{\bf As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
 keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
 simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
-absorption to within the modeling error.
+absorption to within the modeling error.}
 
@@
 flow. Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
-Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
+{\bf Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
 Using Cloud photoionization models, we find that, for the typical quasar luminosity of our sample,
@@
 \ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate, and a
-blueshifted absorption signal needs to be searched in a higher ion.
+blueshifted absorption signal needs to be searched in a higher ion.}
 

### 2017-09-28 QPQ9/Submit/qpq9_resubmit.tex
small changes

@@
 
-{\bf To assess the statistical significance of the measured velocity offsets, we perform a boostrap analysis by
+{\bf To assess the statistical significance of the measured velocity offsets}, we perform a boostrap analysis by
 randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 

### 2017-09-28 QPQ9/Submit/qpq9_submit.tex

@@
 $\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
-motion and Hubble flow, and galactic-scale outflows are not required to explain the large 
+motion and Hubble flow, and galactic-scale outflows are not be required to explain the large
 widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
@@
 that these galaxies are surrounded by a massive, cool, and enriched CGM 
-\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 102 background 
+\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 148 background 
 spectra that are paired with foreground quasars with precisely measured redshifts. Among the
@@
 $z_{\rm fg}$ measurable using a robust \ion{Mg}{2}\,2800 emission-line. 
-We reach a final sample size of 102. 
+We reach a final sample size of 148. 
 Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
@@
 For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
-included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
+included in the modeling. The absorptions frequently exhibit large velocity widths. The blue dashed 
 lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
@@
 
-Given the small sample size, one must scrutinize the statistical significance of the measured 
-velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
-randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
-to model each bootstrap realization, and quote the standard deviation in the bootstrap 
-realizations to be the scatter in the centroids of the data. The scatters 
+To assess the statistical significance of the measured velocity offsets, we perform a boostrap 
+analysis by randomly resampling from the full sample 10000 times. We introduce a Gaussian 
+absorption profile to model each bootstrap realization, and quote the standard deviation in the 
+bootstrap realizations to be the scatter in the centroids of the data. The scatters 
 $\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
@@
 width. The intrinsic velocity width corresponding to typical QPQ halo mass is marked with a plus 
-sign, and is well contained within the 1$\sigma$ contour.}
+sign, and is contained within the 2$\sigma$ contour.}
 \label{fig:contour}
@@
 equivalent width for \ion{C}{2} $W_{\rm CII}$ and a Gaussian absorption profile. We repeat the 
-above procedure for all 33 quasar pairs, and create a mean stack of the 40000 mock spectra
+above procedure for all 40 quasar pairs, and create a mean stack of the 40000 mock spectra
 generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 

### 2017-09-28 QPQ9/qpq9_draft.tex

@@
 \cite{Eftekharzadeh+15} measured the clustering of quasars in the range $2.2<z<2.8$ while 
-\cite{RodriguezTorres+16} measured the clustering of quasars in the range $1.8<z<2.2$. They 
+\cite{RodriguezTorres+17} measured the clustering of quasars in the range $1.8<z<2.2$. They 
 estimated that these quasars are hosted by dark matter halos with mass 
@@
 
-JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1412981. The 
-authors gratefully acknowledge the support which enabled these observations at the Keck, Gemini, 
-Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar Observatories. MWL 
-thanks T.-K. Chan for a discussion on CGM simulations and Chi Po Choi for a discussion on 
-statistics.
+JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and 
+AST-1412981. The authors gratefully acknowledge the support which enabled these observations at 
+the Keck, Gemini, Large Binocular Telescope, Very Large Telescope, Las Campanas, and Palomar 
+Observatories. MWL thanks T.-K. Chan for a discussion on CGM simulations and Chi Po Choi for a 
+discussion on statistics.
 

### 2017-11-13 QPQ9/Analysis/Stacks/py/qpq9_stacks.py
Addressed PR5 issues

@@ -9,7 +9,11 @@ from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib import pyplot as plt
 import matplotlib.gridspec as gridspec
 from astropy import units as u
+from astropy.table import Table,Column
+from astropy.io import ascii,fits
 from linetools.spectra.xspectrum1d import XSpectrum1D
+from linetools.spectralline import AbsLine
+from linetools.abund import ions
 sys.path.append(os.path.abspath("../../../../py"))
 from enigma.qpq import stacks as qpqk
 from enigma.qpq import qpq as eqpq
@@ -65,12 +69,66 @@ def qpq9_IRMgII(wrest=None, outfil=None, nboot=10000,
 
     return stack_tup
 
-#######
+
+def msk_stcks(stack_tup0,wrest,write=False):
+    '''# Mask problematic spectra in the stacks
+    '''
+    aline = AbsLine(wrest)
+    fin_velo, stck_img, stck_msk, all_dict = stack_tup0
+    stck_mskN = copy.deepcopy(stck_msk)
+    idx_mask = []
+    for ii,idict in enumerate(all_dict):
+        if idict is None:
+            continue
+        if ions.ion_to_name(aline.data) == 'CII':
+            if (('J0143+2954' in idict['qpq']['NAME']) or ('J0850+4755' in idict['qpq']['NAME']) or
+                    ('J0951+4932' in idict['qpq']['NAME'])):  # uncertain continua give uncertain S/N
+                idx_mask.append(ii)
+        if ions.ion_to_name(aline.data) == 'CIV':
+            if 'J1002+0020' in idict['qpq']['NAME']:  # overlaps with BAL of bg quasar
+                idx_mask.append(ii)
+            if 'J2255-0001' in idict['qpq']['NAME']:  # doubtful MgII redshift
+                idx_mask.append(ii)
+        if ions.ion_to_name(aline.data) == 'MgII':
+            if (('J0822+1319' in idict['qpq']['NAME']) | ('J0908+4215' in idict['qpq']['NAME']) |
+                    ('J1242+1817' in idict['qpq']['NAME']) | ('J1622+2031' in idict['qpq']['NAME'])):
+                # BAL, intervening galaxy, sky emission, sky emission
+                idx_mask.append(ii)
+    for idx in idx_mask:
+        stck_mskN[idx,:] = 0.
+    stack_tup = (fin_velo, stck_img, stck_mskN, all_dict)
+
+    tab_qpq = None
[…]

### 2017-11-13 QPQ9/Analysis/py/monte_carlo.py

@@ -141,7 +141,7 @@ def contour_data(all_dict):
     hdu2 = fits.ImageHDU(WCII_GRID)
     hdu3 = fits.ImageHDU(levels)
     hdulist = fits.HDUList([hdu0,hdu1,hdu2,hdu3])
-    hdulist.writeto('contour.fits',clobber=True)
+    hdulist.writeto('contour.fits',overwrite=True)
 
 
 ######################

### 2017-11-13 QPQ9/Analysis/py/qpq9_strct.py

@@ -60,6 +60,7 @@ QPQ_zIR = QTable(fits.open(zIR_fil)[1].data)
 QPQ9 = copy.deepcopy(QPQ_zIR)
 QPQ9.rename_column('FG_ZIR', 'Z_FG')
 QPQ9.rename_column('FG_SIG_ZIR','Z_FSIG')
+QPQ9.keep_columns(['FG_RA','FG_DEC','NAME','RA','DEC','Z_FG','Z_FSIG','BG_Z','R_PHYS','ZFG_LINE','G_UV'])
 for ii,qq in enumerate(QPQ9):
     try:
         assert 'J0225+0048' in qq['NAME'] # redshift is marked to be OII by mistake

### 2017-11-13 QPQ9/Figures/py/qpq9_figs.py

@@ -4,6 +4,7 @@ from __future__ import print_function, absolute_import, division, unicode_litera
 import copy,os,sys,imp
 import matplotlib as mpl
 import numpy as np
+mpl.rcParams['mathtext.fontset'] = 'stix'
 mpl.rcParams['font.family'] = 'stixgeneral'
 from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib import pyplot as plt
@@ -19,26 +20,18 @@ from astropy.modeling import models
 from linetools.spectralline import AbsLine
 from linetools.abund import ions
 
-sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
-import qpq9_stacks as qpq9k
-
 
 #  Plot the Experiment
-def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2N_cut=5.5/u.AA,
-               zfg_mnx=(1.6,9999)):
+def experiment(outfil=None):
 
     if outfil is None:
         outfil = 'fig_experiment.pdf'
     fontsize = 20
 
-    # fixes
-    if not isiterable(wrest):
-        wrest = [wrest]
-
     # Read QPQ9, determine g_UV range
     QPQ9_fil = imp.find_module('enigma')[1] + '/data/qpq/qpq9_final.fits'
     QPQ9 = QTable.read(QPQ9_fil)
-    good_z = np.where((QPQ9['Z_FG'] > zfg_mnx[0]) & (QPQ9['Z_FG'] < zfg_mnx[1]))
+    good_z = np.where(QPQ9['Z_FG'] >= 1.6)
     logguv_min = np.min(np.log10(QPQ9[good_z]['G_UV']))
     logguv_max = np.max(np.log10(QPQ9[good_z]['G_UV']))
 
@@ -46,74 +39,43 @@ def experiment(outfil=None,wrest=[1334.5323*u.AA,1548.195*u.AA,2796.354*u.AA],S2
     pp = PdfPages(outfil)
     fig = plt.figure(figsize=(5,10))
     fig.clf()
-    gs = gridspec.GridSpec(len(wrest),1)
+    nplots = 3
+    gs = gridspec.GridSpec(nplots,1)
 
-
-    # Loop the lines
-    for kk,line in enumerate(wrest):
-
-        # Get line info
-        aline = AbsLine(line)
-
-        # Load stack_tup
[…]

### 2017-11-13 QPQ9/Tables/py/qpq9_tables.py

@@ -11,608 +11,357 @@ from astropy.coordinates import SkyCoord
 sys.path.append(os.path.abspath("../../../py"))
 sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
 import qpq9_stacks as qpq9k
-import enigma
 
-# Load QPQ9 structure
-path = enigma.__path__[0]+'/data/qpq/'
-QPQ9 = QTable(fits.open(path+'qpq9_final.fits')[1].data)
 
-## Make the table that lists the full QPQ9 sample
+# Make the table that lists the full QPQ9 sample
+def tab_sample():
+    # Save the properties of pairs used in stack for CII, CIV, MgII
+    ion_names = ['CII','CIV','MgII']
+    sv_fg_qso = []
+    sv_zfg = []
+    sv_line = []
+    sv_bg_qso = []
+    sv_zbg = []
+    sv_bg_instr = []
+    sv_Rphys = []
+    sv_gUV = []
 
-# Load the dictionaries of quasars used in stack for CII
-stack_tup0 = qpq9k.qpq9_IRMgII(passback=True,wrest=1334.5323*u.AA,S2N_cut=5.5/u.AA,zfg_mnx=(1.6,9999),
-                               vsig_cut=400*u.km/u.s,plot_indiv=False)
-# Mask
-fin_velo, stck_img, stck_msk, all_dict = stack_tup0
-stck_mskN = copy.deepcopy(stck_msk)
-idx_mask = []
-for ii,idict in enumerate(all_dict):
-    if idict is None:
-        continue
-    if (('J0143+2954' in idict['qpq']['NAME']) or ('J0850+4755' in idict['qpq']['NAME']) or
-            ('J0951+4932' in idict['qpq']['NAME'])): #uncertain continua give fake S/N
-        idx_mask.append(ii)
-for idx in idx_mask:
-    stck_mskN[idx,:] = 0.
+    # Loop on the ions
+    for kk in np.arange(3):
+        # Load the subsample table
+        subsample = Table(fits.open('../Analysis/Stacks/'+ion_names[kk]+'_sample.fits')[1].data)
+        # Format the table
+        for ii,row in enumerate(subsample):
+            # fg qso
+            coord = SkyCoord(row['FG_RA']*u.deg,row['FG_DEC']*u.deg)
[…]

### 2017-11-13 QPQ9/Tables/py/qpq9_tables.py
small changes

@@ -13,8 +13,9 @@ sys.path.append(os.path.abspath("../Analysis/Stacks/py"))
 import qpq9_stacks as qpq9k
 
 
-# Make the table that lists the full QPQ9 sample
 def tab_sample():
+    '''Make the table that lists the full QPQ9 sample
+    '''
     # Save the properties of pairs used in stack for CII, CIV, MgII
     ion_names = ['CII','CIV','MgII']
     sv_fg_qso = []
@@ -103,8 +104,9 @@ def tab_sample():
     afile.close()
 
 
-# Make the table of QPQ9 summary
 def tab_summary():
+    '''Make the table of QPQ9 summary
+    '''
 
     # Summary of the MgII + NIR samples
 

### 2018-01-26 QPQ9/Submit/response_2.txt
small changes

Dear referee,

We thank you very much for careful reading of our manuscript the second time. Your constructive criticism has been
very helpful.

>=== Major concern 1: failure to capture velocity spread of the absorption and misuse of the central limit theorem
>
>In response to one of my concerns, the authors now motivate Gaussian fitting to the mean absorption profile using the
>central limit theorem. This is a fundamental misuse of the central limit theorem. The central limit theorem implies
>(under fairly loose assumptions) that the sums of random variables will tend towards a normal distribution. This means,
>for example, that the measured flux in a particular pixel of the stack will be normally distributed. But it *does not*
>imply that the mean line profiles themsleves will be Gaussian. While there are conditions under which mean line
>profiles will converge to a Gaussian, these are significantly more demanding conditions that typically do not apply to
>astrophysical measurements and objects. For example, the mean stack of point sources in ground based images will not
>converge to a Gaussian because of the large fraction of flux contained in wings of the PSF. Similarly, mean line
>profiles in stacks are often far from Gaussian such as: both broad and narrow quasar emission lines (Schneider+2010,
>Shen+2016b), galaxy emission lines (Cicone+2016), and associated quasar absorption lines which are distinctly
>non-Gaussian as shown in Figure 9 of this paper.
>
>Previous QPQ papers (Prochaska & Hennawi 2009, Lau+2016) and those from other authors (e.g. Tripp+2011, Johnson+2015,
>Rudie+2017) have shown that AGN and quasar hosts often exhibit absorbing gas at "extreme" velocities of 500-1000 km/s.
>Indeed, these extreme velocities are discussed in the introduction. However, it is clear that the extreme velocities
>are not being captured by the measured Gaussian fit.
>
>This concern is raised not only by the previous works but also by careful examination of Figure 2. In particular the
>pseudo-continuum level in the mean stack is systematically lower than in the median stack for all three ions
>considered. This indicates that there is additional absorption at large velocities which is not being captured by the
>analysis in the paper but is instead being erroneously folded into the pseudo-continuum estimate.
>
>This is a major issue with the adopted methodology that must be addressed with careful thought, new
>experiments/testing, and detailed discussion.

We thank the referee for pointing out the misuse of central limit theorem. It applies to the fluxes at each pixel.
The absorption in the stack will follow the distribution from which it was sampled, by the law of large numbers. We
present a more careful argument for fitting one Gaussian component and one constant component, and removed the tex
relying on the central limit theorem.

The distribution of absorbers unassociated with the foreground quasars is expected to be uniform and random, and
depress the continuum level in the stack uniformly. This justifies our fitting of a pseudocontinuum, and is not
the quantity of interest. The questions to be addressed is, whether one component is a good description of the
dispersion in the average absorption, and if so, whether the dispersion in this component is well captured by a
Gaussian. We tried replacing a constant pseudocontinuum with a second Gaussian absorption component in our modeling
of the CII stack. We found this second Gaussian component to be weak and broad. The amplitude is 0.03, compared to our
original constant component of 0.97. The standard deviation is 3600 km/s, whose span is wider than the entire
velocity window for stacking. This weak and very broad component also has little effect on the centroid and width of
the narrower Gaussian component. We therefore see no convincing evidence for a broader component hidden in the
depressed continuum. We then calculated the dispersion in a +/-1300 km/s window surrounding the absorption centroid
using the standard deviation formula. We hae this large velocity window to encompass most of the associated absorption.
We found the dispersion measured this way is essentially the same as that found by fitting a Gaussian. This also leans
support to our approach of fitting two Gaussians to the CIV and MgII doublet, where we cannot directly apply the
standard deviation formula.

In our revised manuscript, we acknowledge the possibility our Gaussian model does not capture all the powers at extreme
velocities. However we also note that occasional large kinematic offsets do not make a strong case against
gravitational motions. Firstly, quasars occasionally inhabit extremely overdense environments, such as
protoclusters. Secondly, the probability of intercepting a random absorber is boosted by large scale clustering. Hence
occasional extreme velocities would not necessitate outflows. Our preferred kinematic measure is thus the dispersion in
the average absorption. We added the above text to the revised manuscript.

The uniformly depressed continuum results from absorbers unrelated to the foreground quasars, which is expected to
have a covering fraction less than 50%. For median stack, a pixel is not affected unless there are more than 50% of
quasar pairs with absorption at its velocity. The pseudo-continuum of the mean stack being lower than the median stack
is not a reflection of associated absorption at large velocities.

>=== Major concern 2: insufficient detail in how the doublet fitting is performed.
>
>I thank the authors for specifying the allowed range of doublet ratio. However, additional information is still needed
>on the doublet fitting, particularly regarding the pseudo continuum.
>
>The doublet ratio is degenerate with centroid in some cases, particularly for CIV and this possible degeneracy is not
>discussed.
>
>Depending on how the pseudo continuum fitting is performed, it could potentially suppress any broad wings in the mean
>absorption profile. The authors have most likely taken steps to prevent this from happening. But if so, these steps are
>note specified.f
>
>Provide additional details addressing both of these points.

We tried fitting the continuum separately in (-3000,-1300) km/s and (+1300, +3000) km/s instead of multiplying a
constant to a Gaussian. We found the continuum determined this way is essentially the same.

We acknowledge the degeneracy between the centroid and the doublet ratio for CIV. And hence, we state that the
results for the doublets are presented for consistency check, but the analysis focuses on CII. We emphasized this
point in the revised manuscript. For CIV, a doublet ratio
closer 2:1 is preferred. We found a doublet ratio of 2:1 captures the absorption at the central few pixels better than
a doublet ratio of 1:1 does.

>=== Main concern 3: mis-representation of papers in the literature
>
>While most of these have been corrected, one remains and a new one has been added. In particular, both Tripp+2011 and
>Rudie+2017 found absorbing gas spread over ~1000 km/s which is comparable to the velocity spreads from the QPQ series
>that are discussed as extreme in the introduction. The main conclusions of Tripp+2011 and Rudie+2017 focus on these
>large velocity spreads and the current description in the introduction is therefore misleading.

We thank the referee for scrutinizing our representation of the literature. We dropped the words that claim these
absorption systems have most of the gas within several hundred km/s.

>=== In addition:
>
>A) To more convincingly demonstrate that the velocity shift in the measured mean absorption profile is real the authors
>should:
>
>1) Remove possible contamination from absorption systems associated with the background quasar. The paper stacks the
>background spectra for pairs in which the redshift difference between the foreground and background quasar is
>>3000 km/s in order to prevent contamination by physical quasar pairs in the presence of redshift uncertainty. However,
>quasars also exhibit narrow associated absorption systems at large velocities of up to ~12,000 km/s (Wild+2008) which
>could also artificially introduce an asymmetry into the experiment. The authors can easily demonstrate that this is not
>the case by repeating the stacking procedure on quasars pairs with a more restrictive range of allowed velocity
>separation of >12,000 km/s.
>
>2) Demonstrating that CII* cannot bias the measurement of the CII velocity centroid. Previous QPQ papers have
>identified CII* absorption in the CGM of quasars. This absorption feature is blue-shifted from the ground state
>transition by 260 km/s which is comparable to the measured offset. With data from Lau+2016, the authors can easily
>demonstrate that contamination from CII* is not responsible for the observed shift.

We identified and removed all BAL and mini-BAL systems in the background quasars. Possible contamination from narrow
associated absorbers of background quasars should result in a tilt in the pseudo-continuum. Associated absorbers of
background quasars will not prefer the systemic velocity of the foreground quasars, and hence will not affect the
average absorption measured for the foreground quasars. The median pair velocity separation of the CII sample is
11140 km/s. Dividing the sample ino two bins of pair velocity separation does not result in meaningful comparison, due
to the smaller number of pairs in each bin. Hwever we see no evidence for a difference in the centroid's redshift of
the two bins.

>B) To demonstrate that the quasar variability effect can plausibly produce the observed shift from Hubble flow alone
>the authors need to calculate the distance to which the quasars can substantially contribute to the UV background and
>convert this distance to a line-of-sight velocity assuming Hubble flow. Most of the work for this has already been done
>for the calculation of g_UV for Figure 1 and Table 1 so only a few additional steps are needed. Implementing this
>calculation in the Monte Carlo approach in Section 3.3 would be particularly convincing.

The strength of absorption is not only affected by the strength of the ionizing radiation field which g_UV measures,
but also by the impact parameter of the pairs. As QPQ8 demonstrated, the strength of the absorption decreases with
impact parameter. Further, g_UV is calculated under the assumption that the quasar shines isotropically and
non-intermittently. It is therefore not straightforward to isolate the quasar variability effect by examining
any possible correlation between the strength of absorption and g_UV. We added more text in the revised manuscript to
explain how g_UV is calculated.

>C) To clarify the discussion the authors should:
>1) Rephrase or expand the sentence/paragraph: "As a test of reasonableness, we calculate that, for a quasar opening
>angle of 120...". It is not clear what calculation was performed and how it represents a test of reasonableness.
>2) Remove the sentence "Light from the background quasar will travel smaller distance to reach the gas behind the
>foreground quasar than the gas in front of it." It is repetitive and the subsequent sentence explains this physical
>picture more clearly.
>3) The last sentence of the paper is misleading because the observed velocity shift cannot be explained by
>gravitational motion.

We expanded on the test of an arbitrary, reasonable quasar opening angle. In this test, we removed all absorbers that
fall within the quasar opening angle in our Monte Carlo simulations. We found that for an opening angle of 120 degrees,
the observed centroid may be reproduced while the intrinsic dispersion is still wthin the modeling error.
We removed the sentence "Light from the background quasar will travel..." as the referee suggested. This indeed helps
clear up the test. We rewrote the last sentence to separately provide the explanation for the large velocity widths
and the explanation for the average shift.

>Finally, I would like to thank the authors for going the extra mile and researching color choices that improve figure
>legibility for color blind readers. However, the stated change does not appear to have been implemented in Figure 6.
>Since the work has already been done, implementing the color change would be an easy correction.

We examined the cartoon figures again. A lighter shade of blue had indeed been used for the CIV ions, and it seems the
poor legibility comes from the figures being too compact. We enlarged the figures in the revised manuscript. We are
very happy to use another color scheme should the referee or editor have better suggestion.

### 2018-01-26 QPQ9/Submit/qpq9_resubmit.tex
small changes

@@
 provides the asymmetry. 
+{\bf The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of 
+opacity in background sightlines passing close to foreground quasars.}
 
@@
 pointing away from the observer. The gas observed in absorption preferentially lies behind the 
-quasar. The asymmetric absorption arises from a transverse proxmity effect. 
+quasar. 
 \cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy 
@@
 extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of 
-$\sim10^6$\,yr, which lies within existing constraints of quasar lifetime from observations 
-\citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
+$\sim10^6$\,yr.
+{\bf In turn, this implies a minimum quasar lifetime of $10^6$\,yr, which lies within existing
+constraints from}
+observations \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
 

### 2018-01-28 QPQ9/Submit/qpq9_resubmit_2.tex
Resubmitted the second time.

--- 2017-09-28 QPQ9/Submit/qpq9_submit.tex
@@
 \documentclass[iop]{emulateapj}
-\usepackage{natbib,amsmath,graphicx,longtable,amssymb,latexsym,epsf}
+\usepackage{natbib,amsmath,graphicx,longtable,amssymb,latexsym,epsf,sidecap}
 \begin{document}
@@
 $\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational
-motion and Hubble flow, and galactic-scale outflows are not be required to explain the large
+motion and Hubble flow, and galactic-scale outflows are not required to explain the large
 widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift.
@@
 their velocity spreads can be better quantified. Other
-existing studies that found large velocity spreads are limited to single sightlines with most of 
-the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}, 
-or with gas tracing 
-a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
+existing studies that found large velocity spreads are {\bf single sightlines
+\citep[e.g.,][]{Tripp+11,RudieNewmanMurphy17}}, or with gas tracing
+a higher ionization state than the QPQ absorption systems \citep[e.g.,][]{Churchill+12}, or where
 the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
@@
 $100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to
-a common spectral resolution. The individual spectra are then combined with a mean or a median 
-statistic. Bad pixels in the individual spectra have been masked before generating the 
+a common spectral resolution.
+The individual spectra are then combined with a mean or a median
+statistic.
+{\bf Spectra with broad absorption-line systems and mini-broad absorption-line systems are excluded.}
+Bad pixels in the individual spectra have been masked before generating the
 composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal
@@
 yields a good estimate of the average absorption and preserves equivalent width. The median
-statistic is less sensitive to outliers, however the median opacity at any velocity channel is 
-rather small, since the discrete absorbers are spread throughout the entire velocity window. The 
-analysis on the median velocity field is thus subject to larger uncertainty. In the following we 
-present stacked spectra using both the mean and the median statistic.
+statistic is less sensitive to {\bf outliers. However, the median opacity at any velocity channel is
+rather small, since the discrete absorbers are spread throughout the entire velocity window.
+A pixel is not affected unless there are more than 50\% of quasar pairs with absorption at its
+velocity.} The analysis on the median velocity field is thus subject to larger uncertainty. In the
+following we present stacked spectra using both the mean and the median statistic.
 
@@
 exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely
-skewed toward positive velocities. We have 40 pairs in the QPQ9 sample for \ion{C}{2} analysis
-and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
-of individual components can only be larger than the number of absorption systems. Hence, although
-QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
-individual quasar-host associated system, the central limit theorem applies and the distribution
-of all absorbing components should tend toward Gaussian distribution. A visual inspection of the 
-stack confirms that a broader absorption component is not apparent. Therefore, to model the 
-absorption, we may introduce a Gaussian profile while allowing a constant pseudo-continuum level 
-to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
+skewed toward positive velocities.
+
+{\bf Visually, there are two absorption components. One component is the uniform depression in the
+continuum level in the stack resulting from absorbers unassociated with the foreground
+quasars. The other component comes from absorbers associated with the foreground quasars and
+distribute around their systemic velocities. To model the absorption, we introduce
+a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.}
+We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit
 to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
@@
 stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with
-smaller offset and comparable dispersion.
+smaller offset and a more uncertain dispersion.
+
+{\bf To test whether the dispersion in the average absorption associated with the foreground quasars is
+well-captured by a Gaussian model, we also calculate the dispersion separately using the standard
+deviation formula. Specifically, we apply the standard deviation formula to a $\pm1300\,{\rm km\,s^{-1}}$
+window surrounding the absorption centroid, while fitting a continuum to the rest of the
+$\pm3000\,{\rm km\,s^{-1}}$ window for stacking. The
+dispersion measured with the above method is essentially the same as that found by fitting a Gaussian.
+One may also speculate on the existence of a broader absorption component hidden in the depressed
+continuum. We try replacing the constant absorption component with a broad Gaussian component in our
+modeling. We find that this second Gaussian component has essentially the same amplitude as the initial
+constant absorption component, and is wider than the entire velocity window for stacking.
+This weak and very broad component has no effect on the centroid and width of the narrow,
+associated Gaussian component. We therefore consider that one single Gaussian component is a good
+description of the average absorption associated with the foreground quasars.
+Moreover, narrow associated absorbers of background quasars will not prefer the systemic velocities of
+the foreground quasars, and hence will not affect the average absorption measured for the foreground
+quasars. Their contribution to the average absorption should result in a tilt in the
+pseudo-continuum, which is insignificant.}
 
@@
 $769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
-allow the doublet ratio to vary from 2:1 to 1:1. The modeling results show that the velocity fields
+allow the doublet ratio to vary from 2:1 to 1:1.
+{\bf The centroid is degenerate with the doublet ratio in our modeling. This degeneracy is more
+pronounced for \ion{C}{4}, although we find that a double ratio closer to 2:1 better captures the
+absorption at the central few pixels. We state that the modeling of the doublets is presented for
+consistency check, but the analysis focuses on \ion{C}{2}.}
+The modeling results show that the velocity fields
 of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
@@
 
-To assess the statistical significance of the measured velocity offsets, we perform a boostrap 
-analysis by randomly resampling from the full sample 10000 times. We introduce a Gaussian 
-absorption profile to model each bootstrap realization, and quote the standard deviation in the 
-bootstrap realizations to be the scatter in the centroids of the data. The scatters 
+To assess the statistical significance of the measured velocity offsets, we perform a boostrap analysis
+by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile
+to model each bootstrap realization, and quote the standard deviation in the bootstrap
+realizations to be the scatter in the centroids of the data. The scatters
 $\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic
@@
 absorption.
+
+{\bf One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
+\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2*}\,1334, absorption from \ion{C}{2*}\,1335
+would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
+In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
+from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334. Among these nine subsystems, only one,
+labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
+Hence, contamination from \ion{C}{2*}\,1335 is insignificant and could not be responsible for the
+observed redshift in the centroid.}
 
@@
 absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is
-broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
+broadened by the mean redshift error by adding it in quadrature to the dispersion in the model, and
+is arbitrarily shifted to match the centroid in the stack of observations.
 The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$. This is
@@
 
+{\bf Although we acknowledge the possibility that our Gaussian model does not capture all the powers
+at extreme velocities, we also caution that occasional large kinematic offsets do not make a strong
+case against gravitational motions. Firstly, quasars occasionally inhabit extremely overdense environments
+such as protoclusters \citep[e.g.,][]{Hennawi+15}. Secondly, the probability of intercepting a random,
+unassociated absorber is boosted by large-scale clustering. Hence occasional extreme velocities would not
+necessitate outflows. Our preferred kinematic measure is thus the dispersion in the average absorption.}
+
 From the bootstrap analysis of the observed dispersion, a width of
@@
 
-\begin{figure*}[!th]
-\begin{minipage}[!bp]{0.28\textwidth}
+%\begin{figure*}[!th]
+%\begin{minipage}[!bp]{0.28\textwidth}
+%%\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
+%\includegraphics[width=\textwidth]{f08.pdf}
+%\caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion
+%absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation.
+%}
+%\label{fig:monopolar}
+%\end{minipage}%
+%\hspace{0.3in}
+%\begin{minipage}[!bp]{0.67\textwidth}
+%%\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
+%%\includegraphics[width=\textwidth]{f09.pdf}
+%\caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the
+%asymmetric absorption. The setup on the left shows that the foreground quasar has not been shining
+%long enough for its ionizing radiation to reach the gas behind it, when the light from the
+%background quasar reaches. The setup on the right shows the scenario after an amount of time
+%comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar
+%has been ionized, by the time the light from the background quasar reaches.
+%}
+%\label{fig:lighttravel}
+%\end{minipage}
+%\end{figure*}
+
+\sidecaptionvpos{figure}{c}
+\begin{SCfigure*}[10][!th]
 %\includegraphics[width=\textwidth]{Figures/fig_monopolar.pdf}
-\includegraphics[width=\textwidth]{f08.pdf}
+\includegraphics[height=0.49\textheight]{f08.pdf}
 \caption{A cartoon showing a unipolar quasar. The gas observed in low- to intermediate-ion
-absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation. 
-}
+absorption preferentially lies behind the quasar, and is shadowed from the ionizing radiation.}
 \label{fig:monopolar}
-\end{minipage}%
-\hspace{0.3in}
-\begin{minipage}[!bp]{0.67\textwidth}
+\end{SCfigure*}
+\sidecaptionvpos{figure}{c}
+\begin{SCfigure*}[10][!bh]
 %\includegraphics[width=\textwidth]{Figures/fig_lighttravel.pdf}
-\includegraphics[width=\textwidth]{f09.pdf}
+\includegraphics[height=0.49\textheight]{f09.pdf}
 \caption{A cartoon showing the finite lifetime of quasar episodes as an explanation to the
@@
 comparable to the light travelling time across CGM scale. Gas in front of the foreground quasar
-has been ionized, by the time the light from the background quasar reaches. 
-}
+has been ionized, by the time the light from the background quasar reaches.}
 \label{fig:lighttravel}
-\end{minipage}
-\end{figure*}
+\end{SCfigure*}
 
@@
 provides the asymmetry.
+{\bf The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of
+opacity in background sightlines passing close to foreground quasars.}
 
@@
 pointing away from the observer. The gas observed in absorption preferentially lies behind the
-quasar. The asymmetric absorption arises from a transverse proxmity effect. 
+quasar.
 \cite{Roos+15} and \cite{GaborBournaud14} performed simulations of a high-redshift disk galaxy
@@
 
-As a test of reasonableness, we calculate that, for a quasar opening angle of $120^\circ$ and
-keeping $\sigma_{\rm rms}$ at the expected value for the typical QPQ9 halo, our Monte Carlo
-simulations may reproduce the observed centroid and intrinsic dispersion of the \ion{C}{2} mean
-absorption to within the modeling error.
+{\bf As a test of reasonableness, we try implementing an arbitrary quasar opening angle in our
+Monte Carlo simulations to reproduce an absorption centroid that is redshifted from the systemic.
+In this test, we remove all absorbers at circumgalactic distances that fall within the quasar
+opening angle. We find that, for an opening angle of $120^\circ$ and keeping $\sigma_{\rm rms}$ at
+the expected value for the typical QPQ9 halo, the observed centroid and intrinsic dispersion of the
+\ion{C}{2} mean absorption may be reproduced within modeling errors.}
 
 Another possible explanation arises from the finite lifetime of quasar episodes.
-Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. Light from the 
-background quasar will travel smaller distance to reach the gas behind the foreground quasar 
-than the gas in front of it. The light from the background quasar may arrive at the gas behind 
+Figure~\ref{fig:lighttravel} presents a cartoon for a {\bf light travel time argument. The light from}
+the background quasar may arrive at the gas behind
 the foreground quasar before the ionizing radiation from the foreground quasar arrives. In
@@
 extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of
-$\sim10^6$\,yr, which lies within existing constraints of quasar lifetime from observations 
-\citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
-
-%As a test of reasonableness, we calculate that, at $R_\perp\approx50\textendash150$\,kpc, radial
-%speeds relative to the foreground quasar of $500\textendash700\,{\rm km\,s^{-1}}$ and quasar
-%opening angles of $120^\circ\textendash140^\circ$ may reproduce the observed centroid and
-%intrinsic dispersion of the \ion{C}{2} mean absorption.
+$\sim10^6$\,yr.
+In turn, this implies a minimum quasar lifetime of $10^6$\,yr, which lies within existing
+constraints from
+observations \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
+
 The first explanation above to asymmetric
@@
 scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study
-this asymmetry in \ion{H}{1} (J. F. Hennawi et al. 2017, in preparation). In conclusion, we 
+this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ 2017, in preparation). In conclusion, we
 observe large and positively skewed velocity fields in absorption, of metal ions
-in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
-explained if the detected gas is in gravitational motion, Hubble flow, or outflow, and the quasars 
-either shine preferentially toward the observer or shine intermittently.
+in the CGM of $z\sim2$ massive galaxies hosting quasars.
+{\bf We argue that the large velocity fields can be accounted for by gravitational motions and
+Hubble flows and do not necessitate outflows. Further, the positive skew can be explained if the
+detected gas is not in inflow on average, and the quasars either shine preferentially toward the
+observer or shine intermittently.}
 
@@
 
+{\bf MWL is immensely grateful to the referee's constructive comments, which help strengthen the
+paper.}
 JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and
@@
 for a discussion on extended emission-line regions, T.-K. Chan for a discussion on CGM
-simulations, and Chi Po Choi for a discussion on statistics.
+simulations, and Chi Po Choi {\bf and Yat Tin Chow for discussions} on statistics.
 

### 2018-01-28 QPQ9/Analysis/Bootstrap/py/qpq9_boot_2.py

@@ -1,0 +1,135 @@
+#Module for QPQ9 boot-strapping
+# Imports
+from __future__ import print_function, absolute_import, division, unicode_literals
+import numpy as np
+import glob, os, sys, copy, pdb
+import matplotlib as mpl
+mpl.rcParams['font.family'] = 'stixgeneral'
+from astropy.io import ascii, fits
+from astropy import units as u
+from astropy.modeling import models,fitting
+sys.path.append(os.path.abspath("../../../../py"))
+from enigma.qpq import stacks as qpqk
+
+#  Bootstrap one transition
+def boot_trans(outfil=None,nboot=10000,
+               stack_tup0=None,
+               median=False,
+               debug=False):
+    ''' Bootstrap on a single transition
+
+    Parameters:
+    ----------
+    wrest: Quantity, optional
+      Rest wavelength [CII 1334]
+    nboot: int, optional
+      Number of bootstraps [10000]
+
+    Returns:
+    --------
+    Outputs an image of the bootstraps
+    '''
+
+    # Can only do this for CII1334, not doublets.
+    wrest = 1334.5323*u.AA
+    if outfil is None:
+        outfil = 'Output/boot2_{:d}.fits'.format(int(wrest.value))
+
+    # For convenience            
+    fin_velo, stck_img0, stck_msk0, all_dict0 = stack_tup0
+    stck_msk = np.zeros(len(fin_velo))
+    stck_img = np.zeros(len(fin_velo))
+    all_dict = []
+    for ii,idict in enumerate(all_dict0):
+        if idict is None:
+            continue
+        if np.sum(stck_msk0[ii,:]) == 0:
+            continue
+        stck_msk = np.vstack([stck_msk,stck_msk0[ii,:]])
+        stck_img = np.vstack([stck_img,stck_img0[ii,:]])
+        all_dict.append(idict)
+    stck_msk = stck_msk[1:,:]
+    stck_img = stck_img[1:,:]
+    stack_tup = fin_velo,stck_img,stck_msk,all_dict
+
+    boot_list = [item for item in stack_tup]
+
+    # Generate bootstrap image
+    boot_img = np.zeros((nboot,len(fin_velo)))
+    sz = stck_img.shape
+    cen = np.zeros(nboot)
+    disp = np.zeros(nboot)
+    frac = np.zeros(nboot)
[…]

### 2018-01-28 QPQ9/Tables/py/qpq9_tables.py

@@ -92,7 +92,7 @@ def tab_sample():
     afile.write('\\tablehead{\\colhead{Foreground Quasar} & \\colhead{$z_{\\rm fg}$} & \n')
     afile.write('\\colhead{Line for $z_{\\rm fg}^a$} & \\colhead{Background Quasar} & \n')
     afile.write('\\colhead{$z_{\\rm bg}$} & \\colhead{BG Quasar Instrument} & \n')
-    afile.write('\\colhead{$R_\\perp$ (kpc)} & \\colhead{$g_{\\rm UV}$}} \n')
+    afile.write('\\colhead{$R_\\perp$ (kpc)} & \\colhead{$g_{\\rm UV}^b$}} \n')
     afile.write('\\startdata \n')
     for ii in np.arange(len(tab)):
         afile.write(tab['fg_qso'][ii] + ' & ' + tab['zfg'][ii] + ' & ' + tab['line'][ii] + ' & ')

### 2018-02-12 QPQ9/Analysis/py/monte_carlo.py
Addressed changes to pull request.

@@ -1,3 +1,8 @@
+# Simulate the stacked absorption signal from a purely clustering argument,
+# using Monte Carlo methods. Will take two days to run on a regular laptop.
+# May try coarser grid first using the monte_carlo.ipynb notebook. That
+# takes two hours.
+# imports
 from __future__ import print_function,absolute_import,division,unicode_literals
 import numpy as np
 import glob,os,sys,copy,imp

### 2018-02-12 QPQ9/Analysis/py/qpq9_strct.py

@@ -1,3 +1,7 @@
+# Generate the QPQ9 sample from the igmspec database and the QPQ database.
+# SDSS-HW (HewettWild10) redshifts are not used. All redshifts are measured
+# using Hennawi's custom algorithm.
+
 # imports
 import copy, os, glob, imp, shutil, pdb
 import numpy as np

### 2018-02-13 QPQ9/Submit/response.txt

@@
-Editor Walter,
+Dear referee,
 
-We thank very much the referee for their careful reading of our manuscript, and their comments and criticism.
-Following their recommendations, we have revised our manuscript in a number of ways detailed below. We are now
-resubmitting to the Astrophysical Journal and ask that you consider it further for publication.
-Summary of referee report:
+We thank you very much for careful reading of our manuscript, and your comments and criticism.
 
@@
 
-We thank the referee for pointing out the importance of accurate redshift measurements. We have addressed the
+We thank you for pointing out the importance of accurate redshift measurements. We have addressed the
 suggested additional work in the details to follow.
@@
 In the first version of the submitted manuscript, there are two redshift measurement techniques in the z ~ 2 sample:
-our custom line-centering algorithm, and the algorithm of Hewett&Wild10. We thank the referee for scrutinizing the
+our custom line-centering algorithm, and the algorithm of Hewett&Wild10. We thank you for scrutinizing the
 redshift measurement techniques, which helps strengthen our results. In this re-submitted manuscript, for all z > 1.6
@@
 
-We thank the referee for pointing out the insufficient detail in the text. The doublet ratio is allowed to vary
+We thank you for pointing out the insufficient detail in the text. The doublet ratio is allowed to vary
 between 2:1 to 1:1.
@@
 
-We thank the referee for clarifying the explanation to Johnson+15's results. We have updated the text to reflect that
+We thank you for clarifying the explanation to Johnson+15's results. We have updated the text to reflect that
 outflows is only one possibility. Gauthier+13 is a single sightline, and the velocity width Dv90 of the MgII
@@
 widely used in cosmology papers such as Kravtsov+17. We have state this scaling explicitly in our revised manuscript.
-We thank the referee for above suggestions.
+We thank you for above suggestions.
 
@@
 cited.
+
+Marie Wingyee Lau

### 2018-02-13 QPQ9/Submit/response_2.txt

@@
 
-We thank you very much for careful reading of our manuscript the second time. Your constructive criticism has been
-very helpful.
+We thank you very much for careful reading of our manuscript the second
+time. Your constructive criticism has been very helpful.
 
->=== Major concern 1: failure to capture velocity spread of the absorption and misuse of the central limit theorem
+>=== Major concern 1: failure to capture velocity spread of the absorption
+>and misuse of the central limit theorem
 >
->In response to one of my concerns, the authors now motivate Gaussian fitting to the mean absorption profile using the
->central limit theorem. This is a fundamental misuse of the central limit theorem. The central limit theorem implies
->(under fairly loose assumptions) that the sums of random variables will tend towards a normal distribution. This means,
->for example, that the measured flux in a particular pixel of the stack will be normally distributed. But it *does not*
->imply that the mean line profiles themsleves will be Gaussian. While there are conditions under which mean line
->profiles will converge to a Gaussian, these are significantly more demanding conditions that typically do not apply to
->astrophysical measurements and objects. For example, the mean stack of point sources in ground based images will not
->converge to a Gaussian because of the large fraction of flux contained in wings of the PSF. Similarly, mean line
->profiles in stacks are often far from Gaussian such as: both broad and narrow quasar emission lines (Schneider+2010,
->Shen+2016b), galaxy emission lines (Cicone+2016), and associated quasar absorption lines which are distinctly
->non-Gaussian as shown in Figure 9 of this paper.
+>In response to one of my concerns, the authors now motivate Gaussian
+>fitting to the mean absorption profile using the central limit theorem.
+>This is a fundamental misuse of the central limit theorem. The central
+>limit theorem implies (under fairly loose assumptions) that the sums of
+>random variables will tend towards a normal distribution. This means, for
+>example, that the measured flux in a particular pixel of the stack will be
+>normally >distributed. But it *does not* imply that the mean line profiles
+>themsleves will be Gaussian. While there are conditions under which mean
+>line profiles will converge to a Gaussian, these are significantly more
+>demanding conditions that typically do not apply to astrophysical
+>measurements and objects. For example, the mean stack of point sources in
+>ground based images will not converge to a Gaussian because of the large
+>fraction of flux contained in wings of the PSF. Similarly, mean line
+>profiles in stacks are often far from Gaussian such as: both broad and
+>narrow quasar emission lines (Schneider+2010, Shen+2016b), galaxy emission
+>lines (Cicone+2016), and associated quasar absorption lines which are
+>distinctly non-Gaussian as shown in Figure 9 of this paper.
 >
->Previous QPQ papers (Prochaska & Hennawi 2009, Lau+2016) and those from other authors (e.g. Tripp+2011, Johnson+2015,
->Rudie+2017) have shown that AGN and quasar hosts often exhibit absorbing gas at "extreme" velocities of 500-1000 km/s.
->Indeed, these extreme velocities are discussed in the introduction. However, it is clear that the extreme velocities
->are not being captured by the measured Gaussian fit.
+>Previous QPQ papers (Prochaska & Hennawi 2009, Lau+2016) and those from
+>other authors (e.g. Tripp+2011, Johnson+2015, Rudie+2017) have shown that
+>AGN and quasar hosts often exhibit absorbing gas at "extreme" velocities
+>of 500-1000 km/s. Indeed, these extreme velocities are discussed in the
+>introduction. However, it is clear that the extreme velocities are not
+>being captured by the measured Gaussian fit.
 >
->This concern is raised not only by the previous works but also by careful examination of Figure 2. In particular the
->pseudo-continuum level in the mean stack is systematically lower than in the median stack for all three ions
->considered. This indicates that there is additional absorption at large velocities which is not being captured by the
->analysis in the paper but is instead being erroneously folded into the pseudo-continuum estimate.
+>This concern is raised not only by the previous works but also by careful
+>examination of Figure 2. In particular the pseudo-continuum level in the
+>mean stack is systematically lower than in the median stack for all three
+>ions considered. This indicates that there is additional absorption at
+>large velocities which is not being captured by the analysis in the paper
+>but is instead being erroneously folded into the pseudo-continuum
+>estimate.
 >
->This is a major issue with the adopted methodology that must be addressed with careful thought, new
->experiments/testing, and detailed discussion.
+>This is a major issue with the adopted methodology that must be addressed
+>with careful thought, new experiments/testing, and detailed discussion.
 
-We thank the referee for pointing out the misuse of central limit theorem. It applies to the fluxes at each pixel.
-The absorption in the stack will follow the distribution from which it was sampled, by the law of large numbers. We
-present a more careful argument for fitting one Gaussian component and one constant component, and removed the tex
-relying on the central limit theorem.
+We thank the referee for pointing out the misuse of central limit theorem!
+It applies to the fluxes at each pixel. The absorption in the stack will
+follow the distribution from which it was sampled, by the law of large
+numbers. We present a more careful argument for fitting one Gaussian
+component and one constant component, and removed the text relying on the
+central limit theorem.
 
-The distribution of absorbers unassociated with the foreground quasars is expected to be uniform and random, and
-depress the continuum level in the stack uniformly. This justifies our fitting of a pseudocontinuum, and is not
-the quantity of interest. The questions to be addressed is, whether one component is a good description of the
-dispersion in the average absorption, and if so, whether the dispersion in this component is well captured by a
-Gaussian. We tried replacing a constant pseudocontinuum with a second Gaussian absorption component in our modeling
-of the CII stack. We found this second Gaussian component to be weak and broad. The amplitude is 0.03, compared to our
-original constant component of 0.97. The standard deviation is 3600 km/s, whose span is wider than the entire
-velocity window for stacking. This weak and very broad component also has little effect on the centroid and width of
-the narrower Gaussian component. We therefore see no convincing evidence for a broader component hidden in the
-depressed continuum. We then calculated the dispersion in a +/-1300 km/s window surrounding the absorption centroid
-using the standard deviation formula. We hae this large velocity window to encompass most of the associated absorption.
-We found the dispersion measured this way is essentially the same as that found by fitting a Gaussian. This also leans
-support to our approach of fitting two Gaussians to the CIV and MgII doublet, where we cannot directly apply the
-standard deviation formula.
+The distribution of absorbers unassociated with the foreground quasars is
+expected to be uniform and random, and depress the continuum level in the
+stack uniformly. This justifies our fitting of a pseudocontinuum, and is
+not the quantity of interest. The questions to be addressed is, whether
+one component is a good description of the dispersion in the average
+absorption, and if so, whether the dispersion in this component is well
+captured by a Gaussian. We tried replacing a constant pseudocontinuum with
+a second Gaussian absorption component in our modeling of the CII stack.
+We found this second Gaussian component to be weak and broad. The amplitude
+is 0.03, compared to our original constant component of 0.97. The standard
+deviation is 3600 km/s, whose span is wider than the entire velocity window
+for stacking. This weak and very broad component also has little effect on
+the centroid and width of the narrower Gaussian component. We therefore see
+no convincing evidence for a broader component hidden in the depressed
+continuum. We then calculated the dispersion in a +/-1300 km/s window
+surrounding the absorption centroidusing the standard deviation formula. We
+have this large velocity window to encompass most of the associated
+absorption. We found the dispersion measured this way is essentially the
+same as that found by fitting a Gaussian. This also leans support to our
+approach of fitting two Gaussians to the CIV and MgII doublet, where we
+cannot directly apply the standard deviation formula.
 
-In our revised manuscript, we acknowledge the possibility our Gaussian model does not capture all the powers at extreme
-velocities. However we also note that occasional large kinematic offsets do not make a strong case against
-gravitational motions. Firstly, quasars occasionally inhabit extremely overdense environments, such as
-protoclusters. Secondly, the probability of intercepting a random absorber is boosted by large scale clustering. Hence
-occasional extreme velocities would not necessitate outflows. Our preferred kinematic measure is thus the dispersion in
-the average absorption. We added the above text to the revised manuscript.
+In our revised manuscript, we acknowledge the possibility our Gaussian
+model does not capture all the powers at extreme velocities. However we
+also note that occasional large kinematic offsets do not make a strong case
+against gravitational motions. Firstly, quasars occasionally inhabit
+extremely overdense environments, such as protoclusters. Secondly, the
+probability of intercepting a random absorber is boosted by large scale
+clustering. Hence occasional extreme velocities would not necessitate
+outflows. Our preferred kinematic measure is thus the dispersion in the
+average absorption. We added the above text to the revised manuscript.
 
-The uniformly depressed continuum results from absorbers unrelated to the foreground quasars, which is expected to
-have a covering fraction less than 50%. For median stack, a pixel is not affected unless there are more than 50% of
-quasar pairs with absorption at its velocity. The pseudo-continuum of the mean stack being lower than the median stack
-is not a reflection of associated absorption at large velocities.
+The uniformly depressed continuum results from absorbers unrelated to the
+foreground quasars, which is expected to have a covering fraction less than
+50%. For median stack, a pixel is not affected unless there are more than
+50% of quasar pairs with absorption at its velocity. The pseudo-continuum
+of the mean stack being lower than the median stack is not a reflection of
+associated absorption at large velocities.
 
->=== Major concern 2: insufficient detail in how the doublet fitting is performed.
+>=== Major concern 2: insufficient detail in how the doublet fitting is
+>performed.
 >
->I thank the authors for specifying the allowed range of doublet ratio. However, additional information is still needed
->on the doublet fitting, particularly regarding the pseudo continuum.
+>I thank the authors for specifying the allowed range of doublet ratio.
+>However, additional information is still needed on the doublet fitting,
+>particularly regarding the pseudo continuum.
 >
->The doublet ratio is degenerate with centroid in some cases, particularly for CIV and this possible degeneracy is not
->discussed.
+>The doublet ratio is degenerate with centroid in some cases, particularly
+>for CIV and this possible degeneracy is not discussed.
 >
->Depending on how the pseudo continuum fitting is performed, it could potentially suppress any broad wings in the mean
->absorption profile. The authors have most likely taken steps to prevent this from happening. But if so, these steps are
->note specified.f
+>Depending on how the pseudo continuum fitting is performed, it could
+>potentially suppress any broad wings in the mean absorption profile. The
+>authors have most likely taken steps to prevent this from happening. But
+>if so, these steps are note specified.f
 >
@@
 
-We tried fitting the continuum separately in (-3000,-1300) km/s and (+1300, +3000) km/s instead of multiplying a
-constant to a Gaussian. We found the continuum determined this way is essentially the same.
+We tried fitting the continuum separately in (-3000,-1300) km/s and (+1300,
++3000) km/s instead of multiplying a constant to a Gaussian. We found the
+continuum determined this way is essentially the same.
 
-We acknowledge the degeneracy between the centroid and the doublet ratio for CIV. And hence, we state that the
-results for the doublets are presented for consistency check, but the analysis focuses on CII. We emphasized this
-point in the revised manuscript. For CIV, a doublet ratio
-closer 2:1 is preferred. We found a doublet ratio of 2:1 captures the absorption at the central few pixels better than
-a doublet ratio of 1:1 does.
+We acknowledge the degeneracy between the centroid and the doublet ratio
+for CIV. And hence, we state that the results for the doublets are
+presented for consistency check, but the analysis focuses on CII. We
+emphasized this point in the revised manuscript. For CIV, a doublet ratio
+closer 2:1 is preferred. We found a doublet ratio of 2:1 captures the
+absorption at the central few pixels better than a doublet ratio of 1:1
+does.
 
@@
 >
->While most of these have been corrected, one remains and a new one has been added. In particular, both Tripp+2011 and
->Rudie+2017 found absorbing gas spread over ~1000 km/s which is comparable to the velocity spreads from the QPQ series
->that are discussed as extreme in the introduction. The main conclusions of Tripp+2011 and Rudie+2017 focus on these
->large velocity spreads and the current description in the introduction is therefore misleading.
+>While most of these have been corrected, one remains and a new one has
+>been added. In particular, both Tripp+2011 and Rudie+2017 found absorbing
+>gas spread over ~1000 km/s which is comparable to the velocity spreads
+>from the QPQ series that are discussed as extreme in the introduction. The
+>main conclusions of Tripp+2011 and Rudie+2017 focus on these large
+>velocity spreads and the current description in the introduction is
+>therefore misleading.
 
-We thank the referee for scrutinizing our representation of the literature. We dropped the words that claim these
-absorption systems have most of the gas within several hundred km/s.
+>We thank the referee for scrutinizing our representation of the
+>literature. We dropped the words that claim these absorption systems have
+>most of the gas within several hundred km/s.
 
@@
 >
->A) To more convincingly demonstrate that the velocity shift in the measured mean absorption profile is real the authors
->should:
+>A) To more convincingly demonstrate that the velocity shift in the
+>measured mean absorption profile is real the authors should:
 >
->1) Remove possible contamination from absorption systems associated with the background quasar. The paper stacks the
->background spectra for pairs in which the redshift difference between the foreground and background quasar is
->>3000 km/s in order to prevent contamination by physical quasar pairs in the presence of redshift uncertainty. However,
->quasars also exhibit narrow associated absorption systems at large velocities of up to ~12,000 km/s (Wild+2008) which
->could also artificially introduce an asymmetry into the experiment. The authors can easily demonstrate that this is not
->the case by repeating the stacking procedure on quasars pairs with a more restrictive range of allowed velocity
->separation of >12,000 km/s.
+>1) Remove possible contamination from absorption systems associated with
+>the background quasar. The paper stacks the background spectra for pairs
+>in which the redshift difference between the foreground and background
+>quasar is >3000 km/s in order to prevent contamination by physical quasar
+>pairs in the presence of redshift uncertainty. However, quasars also
+>exhibit narrow associated absorption systems at large velocities of up to
+>~12,000 km/s (Wild+2008) which could also artificially introduce an
+>asymmetry into the experiment. The authors can easily demonstrate that
+>this is no tthe case by repeating the stacking procedure on quasars pairs
+>with a more restrictive range of allowed velocity separation of >12,000
+>km/s.
 >
->2) Demonstrating that CII* cannot bias the measurement of the CII velocity centroid. Previous QPQ papers have
->identified CII* absorption in the CGM of quasars. This absorption feature is blue-shifted from the ground state
->transition by 260 km/s which is comparable to the measured offset. With data from Lau+2016, the authors can easily
->demonstrate that contamination from CII* is not responsible for the observed shift.
+>2) Demonstrating that CII* cannot bias the measurement of the CII velocity
+>centroid. Previous QPQ papers have identified CII* absorption in the CGM
+>of quasars. This absorption feature is blue-shifted from the ground state
+>transition by 260 km/s which is comparable to the measured offset. With
+>data from Lau+2016, the authors can easily demonstrate that contamination
+>from CII* is not responsible for the observed shift.
 
-We identified and removed all BAL and mini-BAL systems in the background quasars. Possible contamination from narrow
-associated absorbers of background quasars should result in a tilt in the pseudo-continuum. Associated absorbers of
-background quasars will not prefer the systemic velocity of the foreground quasars, and hence will not affect the
-average absorption measured for the foreground quasars. The median pair velocity separation of the CII sample is
-11140 km/s. Dividing the sample ino two bins of pair velocity separation does not result in meaningful comparison, due
-to the smaller number of pairs in each bin. Hwever we see no evidence for a difference in the centroid's redshift of
-the two bins.
+We identified and excluded all spectra with BAL and mini-BAL systems.
+Possible contamination from narrow associated absorbers of background
+quasars should result in a tilt in the pseudo-continuum. Associated
+absorbers of background quasars will not prefer the systemic velocity of
+the foreground quasars, and hence will not affect the average absorption
+measured for the foreground quasars. The median pair velocity separation
+of the CII sample is 11140 km/s. Dividing the sample ino two bins of pair
+velocity separation does not result in meaningful comparison, due to the
+smaller number of pairs in each bin. Hwever we see no evidence for a
+difference in the centroid's redshift of the two bins.
 
->B) To demonstrate that the quasar variability effect can plausibly produce the observed shift from Hubble flow alone
->the authors need to calculate the distance to which the quasars can substantially contribute to the UV background and
->convert this distance to a line-of-sight velocity assuming Hubble flow. Most of the work for this has already been done
->for the calculation of g_UV for Figure 1 and Table 1 so only a few additional steps are needed. Implementing this
->calculation in the Monte Carlo approach in Section 3.3 would be particularly convincing.
+We examined all the nine CII-bearing subsystems in QPQ8 where CII* is not
+blended with CII. Among the above nine subsystems, only one, J1420
+subsystem F, has CII* equivalent width comparable to CII. Hence,
+contamination from CII* is insignifcant and could not be responsible for
+the observed shift. We thank the referee for suggesting us to add this to
+the text.
 
-The strength of absorption is not only affected by the strength of the ionizing radiation field which g_UV measures,
-but also by the impact parameter of the pairs. As QPQ8 demonstrated, the strength of the absorption decreases with
-impact parameter. Further, g_UV is calculated under the assumption that the quasar shines isotropically and
-non-intermittently. It is therefore not straightforward to isolate the quasar variability effect by examining
-any possible correlation between the strength of absorption and g_UV. We added more text in the revised manuscript to
-explain how g_UV is calculated.
+>B) To demonstrate that the quasar variability effect can plausibly
+>produce the observed shift from Hubble flow alone the authors need to
+>calculate the distance to which the quasars can substantially contribute
+>to the UV background and convert this distance to a line-of-sight
+>velocity assuming Hubble flow. Most of the work for this has already been
+>done for the calculation of g_UV for Figure 1 and Table 1 so only a few
+>additional steps are needed. Implementing this calculation in the Monte
+>Carlo approach in Section 3.3 would be particularly convincing.
+
+In our test of implementing an arbitrary quasar opening angle in our Monte
+Carlo simulations to reproduce the observed shift, we remove all absorbers
+at CGM distances that fall within the opening angle to mimic UV
+enhancement. We did not remove absorbers at larger distances/Hubble flow
+velocities as the effect of quasar variability is expected to be weaker.
+However, for the stack of mock spectra fro Monte Carlo simulations that we
+present in Figure 5, we did not include this quasar variability effect but
+merely shifted the absorption centroid to match with the observations. The
+goal of Figure 5 is to show that the observed velocity width can be
+reproduced without outflows. Introducing quasar variability would
+introduce more free parameters and the figure may be less informative.
 
 >C) To clarify the discussion the authors should:
->1) Rephrase or expand the sentence/paragraph: "As a test of reasonableness, we calculate that, for a quasar opening
->angle of 120...". It is not clear what calculation was performed and how it represents a test of reasonableness.
->2) Remove the sentence "Light from the background quasar will travel smaller distance to reach the gas behind the
->foreground quasar than the gas in front of it." It is repetitive and the subsequent sentence explains this physical
->picture more clearly.
->3) The last sentence of the paper is misleading because the observed velocity shift cannot be explained by
->gravitational motion.
+>1) Rephrase or expand the sentence/paragraph: "As a test of
+>reasonableness, we calculate that, for a quasar opening angle of 120...".
+>It is not clear what calculation was performed and how it represents a
+>test of reasonableness.
+>2) Remove the sentence "Light from the background quasar will travel
+>smaller  distance to reach the gas behind the foreground quasar than the
+>gas in front of it." It is repetitive and the subsequent sentence
+>explains this physical picture more clearly.
+>3) The last sentence of the paper is misleading because the observed
+>velocity shift cannot be explained by gravitational motion.
 
-We expanded on the test of an arbitrary, reasonable quasar opening angle. In this test, we removed all absorbers that
-fall within the quasar opening angle in our Monte Carlo simulations. We found that for an opening angle of 120 degrees,
-the observed centroid may be reproduced while the intrinsic dispersion is still wthin the modeling error.
-We removed the sentence "Light from the background quasar will travel..." as the referee suggested. This indeed helps
-clear up the test. We rewrote the last sentence to separately provide the explanation for the large velocity widths
-and the explanation for the average shift.
+We expanded the text on the test of an arbitrary, reasonable quasar
+opening angle. In this test, we removed all CGM absorbers that fall
+within the quasar opening angle in our Monte Carlo simulations. We found
+that for an opening angle of 120 degrees, the observed centroid may be
+reproduced while the intrinsic dispersion is still wthin the modeling
+error.
+We removed the sentence "Light from the background quasar will travel..."
+as the referee suggested. This indeed helps clear up the test.
+We rewrote the last sentence to separately provide the explanation for
+the large velocity widths and the explanation for the average shift.
 
->Finally, I would like to thank the authors for going the extra mile and researching color choices that improve figure
->legibility for color blind readers. However, the stated change does not appear to have been implemented in Figure 6.
->Since the work has already been done, implementing the color change would be an easy correction.
+>Finally, I would like to thank the authors for going the extra mile and
+>researching color choices that improve figure legibility for color blind
+>readers. However, the stated change does not appear to have been
+>implemented in Figure 6. Since the work has already been done,
+>implementing the color change would be an easy correction.
 
-We examined the cartoon figures again. A lighter shade of blue had indeed been used for the CIV ions, and it seems the
-poor legibility comes from the figures being too compact. We enlarged the figures in the revised manuscript. We are
-very happy to use another color scheme should the referee or editor have better suggestion.
+We examined the cartoon figures again. A lighter shade of blue instead
+of navy had been used for the CIV ions. It seems the poor legibility also
+came from the figures being too compact. We enlarged the figures in the
+revised manuscript. We are very happy to use another color scheme should
+the referee or editor have better suggestion.
+
+Marie Wingyee Lau

### 2018-02-27 QPQ9/Submit/response_3.txt
response to third referee report

Dear referee,

We thank you very much for the careful reading and constructive criticism
that will help toward the eventual acceptance for publication.

>Remaining major question 1:
>
>In the response to the second referee report and in the caption of
>Figure 5, the authors state that the Monte Carlo simulation absorption
>is shifted to match the centroid of the absorption.
>Am I correct in understanding that this is done to force a match
>between the observed absorption shift and the Monte Carlo model? If so,
>this would seem to invalidate the claim by the paper that the observed
>velocity shift can be explained by anisotropic and/or intermittent quasar
>radiation combined with the Hubble flow. Why can't the shift be
>reproduced by the Monte Carlo model which includes all of these effects?
>If the model cannot reproduce the shift, then some of the major
>conclusions of the paper, including the last sentence of the abstract,
>are not supported. I am sufficiently puzzled by this that I request the
>opportunity to review the paper one more time before acceptance. Please
>clarify and explain the need for an artificial velocity shift in order
>for the Monte Carlo model to match the observed stack.

We thank the referee very much for pushing us to examine our Monte Carlo
simulation outputs. Asymmetric distribution of Hubble velocities alone
cannot produce the observed redshifted centroid. We made a mistake in
our claim in the last response, as we mistook the simulation outputs
that incorporated outflows to be those without outflows. We find that,
with asymmetric distribution in Hubble velocities alone, the centroid
may at most be shifted ~80 km/s. Hence, the observed putative asymmetry
suggests the presence of an outflowing component! We crudely estimate
that, the observed dispersion and centroid may be reproduced with a
quasar opening angle of 120 degrees and radial velocities of 500 km/s.
We added text that justifies ionizing absorbers at Mpc distances from
the quasar. The argument comes from the observed anisotropic clustering
of absorbers around quasars.

We added text about outflows. In addition, we also restructured the text
somewhat to first discuss the observed dispersion and then discuss the
observed centroid. We put a confidence limit on the observed centroid
of the average absorption from CII at 232+/-98 km/s, with large intrinsic
scatter. Hence, we consider it worthwhile to also separately analyze the
observed disperson.

>Remaining major question 2:
>
>In the Monte Carlo model, the authors adopt a sigma_rms scatter of 246
>km/s based on the expected rms velocity for quasar host halos. But the
>absorption systems being considered in the model are in the Hubble flow
>at significant cosmological distance, not in the quasar host halo. Why
>then is a sigma_rms from massive halos appropriate? Does the adoption of
>a different sigma_rms change the results?

We thank the referee for this suggestion, that helps strengthen the
results. We try adopting a sigma_rms scatter more more typical of coeval
Lyman break galaxies, for absorbers at cosmological distances. We find
that the dispersion in the model is again consistent with the
observation. Relevant text has been added.

>Other points for improvement:

>1) Explicitly state the flux level of the psuedo-continuum by adding it
>to Table 2
>
>2) Similarly, the paper must explicitly give the width of the second
>Guassian component and equivalent width discussed on page 6. This means
>providing actual numbers with uncertainties in the text rather than
>qualitative assertions.
>
>3) The discussion of a bias from CII* is not convincing as is (though I
>am certain that the claim of small bias is correct). In order to make the
>given argument convincing, the authors need to give quantitative
>constraints on the mean CII to CII* ratio and then translate this ratio
>into an estimated bias. Again, the paper must include specific,
>quantitative information on the estimated level of this bias rather than
>simply assert that it is insignificant.
>
>4) On the color scheme in Figure 6: Anything that does not involve red
>and green would be a significant improvement. This figure could be made
>in greyscale, coolmap, heatmap, or any number of other options.
>Alternative, a color scheme could be dropped entirely by plotting the 1,
>2, and 3 sigma regions in solid, dashed, and dotted line respectively.
>Or different hatching schemes could be used for each reason.

We have added the pseudo-continuum levels to Table 2.

We also added text to quantify the width, amplitude, and uncertainties in
the wider and waeker Gaussian component.

The Mean CII to CII* ratio is 0.2, and we estimate that CII* may at most
add a ~40 km/s positive bias.

In our response to the last report, we overlooked the referee's request
for changing the color scheme of Figure 6, and we had only done that for
the two cartoon figures. We apologize for that, and we have now changed
the color scheme of Figure 6.

Marie Wingyee Lau

### 2018-02-27 QPQ9/Submit/qpq9_resubmit_3.tex
response to third referee report

--- 2018-01-28 QPQ9/Submit/qpq9_resubmit_2.tex
@@
 foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
-and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths
-$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational
-motion and Hubble flow, and galactic-scale outflows are not required to explain the large
-widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift.
-The mean absorption centroids exhibit small redshift relative to the
+and \ion{Mg}{2}.
+{\bf We find that the mean absorptions exhibit large velocity widths
+$\sigma_v\approx300\,{\rm km\,s^{-1}}$. Further, the mean absorptions appear to be asymmetric about
+the systemic redshifts. The mean absorption centroids exhibit small redshift relative to the
 systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
-velocities of the individual absorption systems. We show that the observed offsets may be produced
-if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the
-gas is not flowing into the galaxy.
+velocities of the individual absorption systems.
+We find the observed widths are consistent with gas in gravitational
+motion and Hubble flow. However, while the observation of large widths alone does not require
+galactic-scale outflows, the observed offsets suggest that the gas is on average outflowing from the
+galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
+is anisotropic or intermittent.}
 \end{abstract}
@@
 circumgalactic medium frequently exhibits large velocity widths that are offset from the systemic
-redshift. The offsets, $\delta v$, are often positive, with the sign convention that positive
-velocities indicate a redshift from the systemic. From a sample of 7 \ion{C}{2} systems and 10
-\ion{C}{4} systems, we measured the velocity interval that encompasses 90\% of the total optical
-depth, $\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$.
+redshift.
+{\bf From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4}
+systems, we measured the velocity interval that encompasses 90\% of the total optical depth,
+$\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$.
 The median $\Delta v_{90}$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is
@@
 all previous measurements from galaxies and/or absorption systems at any epoch.
+The offsets, $\delta v$, are often positive, with the sign convention that positive
+velocities indicate a redshift from the systemic.
+}
 
@@
 Furthermore, we include only those spectra with average signal-to-noise ratio (S/N) exceeding 5.5
-per rest-frame \AA \ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths
+per rest-frame \AA\ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths
 of the metal ion transitions. This criterion is a compromise between maximizing sample size versus
 maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame
-\AA \ is necessary for properly estimating the continuum, as well as identifying mini-broad
+\AA\ is necessary for properly estimating the continuum, as well as identifying mini-broad
 absorption line systems associated to the background quasar, which will significantly depress the
@@
 lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The
-$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are
-$25\,{\rm km\,s^{-1}}$ and $27\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling
-errors of the other stacks.
+$1\sigma$ modeling error for the
+{\bf dispersion and the centroid of the \ion{C}{2} mean stack are $27\,{\rm km\,s^{-1}}$ and
+$25\,{\rm km\,s^{-1}}$ respectively, which are}
+also the typical modeling errors of the other stacks.
 }
@@
 statistic.
-{\bf Spectra with broad absorption-line systems and mini-broad absorption-line systems are excluded.}
+Spectra with broad absorption-line systems and mini-broad absorption-line systems are excluded.
 Bad pixels in the individual spectra have been masked before generating the
@@
 yields a good estimate of the average absorption and preserves equivalent width. The median
-statistic is less sensitive to {\bf outliers. However, the median opacity at any velocity channel is
+statistic is less sensitive to outliers. However, the median opacity at any velocity channel is
 rather small, since the discrete absorbers are spread throughout the entire velocity window.
 A pixel is not affected unless there are more than 50\% of quasar pairs with absorption at its
-velocity.} The analysis on the median velocity field is thus subject to larger uncertainty. In the
+velocity. The analysis on the median velocity field is thus subject to larger uncertainty. In the
 following we present stacked spectra using both the mean and the median statistic.
@@
 
-{\bf Visually, there are two absorption components. One component is the uniform depression in the
+Visually, there are two absorption components. One component is the uniform depression in the
 continuum level in the stack resulting from absorbers unassociated with the foreground
@@
 distribute around their systemic velocities. To model the absorption, we introduce
-a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.}
+a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.
 We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit
-to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
-the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that
-contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median
-stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with
-smaller offset and a more uncertain dispersion.
-
-{\bf To test whether the dispersion in the average absorption associated with the foreground quasars is
+to the data, we measure
+{\bf the $1\sigma$ dispersion of the stack to be $293\,{\rm km\,s^{-1}}$ and the centroid of the
+\ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$. The dispersion suggests extreme kinematics, while
+the centroid suggests an asymmetry that contradicts the standard expectation.}
+The median
+stack, on the other hand, shows weaker absorption,
+{\bf and the Gaussian model has a more uncertain dispersion and a centroid with smaller offset.}
+
+To test whether the dispersion in the average absorption associated with the foreground quasars is
 well-captured by a Gaussian model, we also calculate the dispersion separately using the standard
@@
 continuum. We try replacing the constant absorption component with a broad Gaussian component in our
-modeling. We find that this second Gaussian component has essentially the same amplitude as the initial
-constant absorption component, and is wider than the entire velocity window for stacking.
-This weak and very broad component has no effect on the centroid and width of the narrow,
+modeling. We find that this second Gaussian component has
+{\bf an amplitude of $0.030\pm0.009$, i.e.\ essentially the same amplitude as the initial
+constant absorption component, and a $1\sigma$ dispersion of $3614\pm1731\,{\rm km\,s^{-1}}$, i.e.\ wider}
+than the entire velocity window for stacking.
+This weak and very broad component has no effect on the {\bf width and the centroid} of the narrow,
 associated Gaussian component. We therefore consider that one single Gaussian component is a good
@@
 quasars. Their contribution to the average absorption should result in a tilt in the
-pseudo-continuum, which is insignificant.}
+pseudo-continuum, which is insignificant.
 
 We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the
-absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at
-$+235\,{\rm km\,s^{-1}}$, and a dispersion of $330\,{\rm km\,s^{-1}}$, consistent with the full
-sample.
+absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has
+{\bf a dispersion of $330\,{\rm km\,s^{-1}}$, and a centroid at $+235\,{\rm km\,s^{-1}}$},
+consistent with the full sample.
 
@@
 allow the doublet ratio to vary from 2:1 to 1:1.
-{\bf The centroid is degenerate with the doublet ratio in our modeling. This degeneracy is more
+The centroid is degenerate with the doublet ratio in our modeling. This degeneracy is more
 pronounced for \ion{C}{4}, although we find that a double ratio closer to 2:1 better captures the
 absorption at the central few pixels. We state that the modeling of the doublets is presented for
-consistency check, but the analysis focuses on \ion{C}{2}.}
+consistency check, but the analysis focuses on \ion{C}{2}.
 The modeling results show that the velocity fields
@@
 \input{tab_summary.tex}
-
-\subsection{Interpretation of the asymmetric absorption}
-\label{sec:significance_+ve}
-
-To assess the statistical significance of the measured velocity offsets, we perform a boostrap analysis
-by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile
-to model each bootstrap realization, and quote the standard deviation in the bootstrap
-realizations to be the scatter in the centroids of the data. The scatters
-$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic
-variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show
-the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We
-find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
-limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at
-$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
-whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2}
-absorption.
-
-{\bf One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
-\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2*}\,1334, absorption from \ion{C}{2*}\,1335
-would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
-In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
-from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334. Among these nine subsystems, only one,
-labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
-Hence, contamination from \ion{C}{2*}\,1335 is insignificant and could not be responsible for the
-observed redshift in the centroid.}
-
-One may also ask whether the measured positive offsets come from systematic bias in redshift
-measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the
-[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically
-less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean
-stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
-more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for 11 out
-of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
-velocity structure and again shows a positive offset $\approx+303\,{\rm km\,s^{-1}}$. We thus
-conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
-[\ion{O}{3}] emission-line.
-
-Motivated by the study of \ion{Mg}{2} absorbers surrounding $z\sim1$ quasars by \cite{Johnson+15},
-we also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs.
-We select quasars with $0.4<z_{\rm fg}<1.6$ and use the same other selection criteria as the main
-QPQ9 sample. The quasar pairs are selected from the igmspec database, with $z_{\rm fg}$ measured
-by \cite{HewettWild10}. For quasars with $z_{\rm fg}<0.84$, as redshift determination is dominated
-by [\ion{O}{3}] emission, a shift of $+48\,{\rm km\,s^{-1}}$ is applied to bring the emission-line
-redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is
-dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are 233
-pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present
-the mean stack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9
-sample. Gaussian absorption models fitted to the stack recover a centroid of
-$-11\pm379\,{\rm km\,s^{-1}}$ and a dispersion of $172\,{\rm km\,s^{-1}}$. The average offset
-from $0\,{\rm km\,s^{-1}}$ is much smaller than the offsets in the $z\sim2$ sample.
-
-Since the large scatter in the centroids represents intrinsic variation rather than redshift
-errors, and the \ion{Mg}{2} stack for lower redshift suggests a different centroid, we
-consider that the asymmetry signal in the $z\sim2$ sample is likely to be real. In the Discussion
-section, we discuss two possible explanations for the asymmetry.
-
-\begin{figure}
-%\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
-\includegraphics[width=2.5in]{f03.pdf}
-\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample
-for the \ion{C}{2} mean stack. 97\% of the centroids are positively offset from $z_{\rm fg}$.}
-\label{fig:histogram_cen}
-\end{figure}
-
-\begin{figure}
-%\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
-\includegraphics[width=2.5in]{f04.pdf}
-\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at
-$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is
-approximately at $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample.
-}
-\label{fig:stack_z1}
-\end{figure}
 
@@
 \caption{The same \ion{C}{2} mean stack shown in the first panel of
-Figure~\ref{fig:stacks_and_fits} is shown in thin, black. In thick, green, we overplot the
-Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
-argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
-stack of the observational data, shifted to the centroid of the stack of the data, and broadened
-by the mean redshift error in the data. The model is a good description of the data, with a
-dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an
+Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
+{\bf We overplot in dashed, yellow an
 absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
 by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
-width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with
+width larger than this can be ruled out. We overplot in dot dashed, yellow an absorption profile with
 $\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
@@
 produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be
-required to explain the observation.
+required to explain the observed width.
+In thick, gold, we overplot the
+Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
+argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
+stack of the observational data, and broadened
+by the mean redshift error in the data. While this model has a dispersion within modeling error of the
+dispersion in the data. the centroid of the stack of the data appears to be redshifted
+from the systemic. A model with only gravitational motions and Hubble flows cannot explain
+this putative asymmetry.}
 }
@@
 redshifts, we recover $\sigma_{\rm intrinsic}^{\rm [OIII]}=323\,{\rm km\,s^{-1}}$.
+
+{\bf To assess the statistical significance of the observed dispersion, we perform a bootstrap
+analysis by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption
+profile to model each bootstrap realization. We find that} a width of
+$\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter in
+the bootstrap realizations
+(overplotted in Figure~\ref{fig:monte}). In other words, taking into account the redshift errors,
+motions in addition to gravitational and Hubble flows that will produce an intrinsic dispersion
+$\sigma_v>521\,{\rm km\,s^{-1}}$ can be ruled out.
+
+On the contrary,
+$\sigma_{\rm rms}<70\,{\rm km\,s^{-1}}$ together with Hubble velocities and
+broadening by redshift errors will result in a velocity width that is more than three times the
+modeling error away from the observed width (overplotted in Figure~\ref{fig:monte}). This implies
+that, unless the characteristic $M_{\rm halo}<10^{11.0}\,M_\odot$,
+additional dynamical processes are not required to explain the observed width.
 
@@
 In Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian
-absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is
-broadened by the mean redshift error by adding it in quadrature to the dispersion in the model, and
-is arbitrarily shifted to match the centroid in the stack of observations.
-The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$. This is
+absorption model of the Monte Carlo simulations.
+{\bf In the figure, the Gaussian absorption model is
+broadened by the mean redshift error by adding it in quadrature to the dispersion in the model.}
+The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$,
 about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack
 for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
-stack of the sub-sample with [\ion{O}{3}] redshifts as well. We also test for the
+stack of the sub-sample with [\ion{O}{3}] redshifts as well.
+{\bf One may also consider whether absorbers in Hubble flow and cosmological distances show peculiar
+velocities that are typical for quasar-mass halos, and adopt a different $\sigma_{\rm rms}$ accordingly.
+The best-studied coeval, more typical star-forming
+galaxies are the Lyman-break galaxies. Their clustering strength implies a characteristic halo
+mass of $M_{\rm halo}\approx10^{11.6}\,M/{\rm M_\odot}$ \citep{Bielby+13,Malkan+17}, corresponding to
+$\sigma_{\rm rms}=114\,{\rm km\,s^{-1}}$.
+If we adopt this smaller $\sigma_{\rm rms}$ insead,for absorbers outside the loosely
+defined quasar CGM boundary, at $\gtrsim300$\,kpc, the stack of mock spectra will have a $1\sigma$
+dispersion of $247\,{\rm km\,s^{-1}}$. This is again within modeling errors of the observed intrinsic
+dispersion.}
+We also test for the
 sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering
@@
 absorbers for each mock sightline, and find the measured dispersion only increases by several
-${\rm km\,s^{-1}}$. Thus, the hypothesis that the observed velocity width is only produced by a
+${\rm km\,s^{-1}}$. Thus, before the putative asymmetry is confirmed, the hypothesis that the
+observed velocity width is only produced by a
 combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical
@@
 
-{\bf Although we acknowledge the possibility that our Gaussian model does not capture all the powers
+Although we acknowledge the possibility that our Gaussian model does not capture all the powers
 at extreme velocities, we also caution that occasional large kinematic offsets do not make a strong
@@
 unassociated absorber is boosted by large-scale clustering. Hence occasional extreme velocities would not
-necessitate outflows. Our preferred kinematic measure is thus the dispersion in the average absorption.}
-
-From the bootstrap analysis of the observed dispersion, a width of
-$\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter
-(overplotted in Figure~\ref{fig:monte}). In other words, taking into account the redshift errors,
-motions in addition to gravitational and Hubble flows that will produce an intrinsic dispersion
-$\sigma_v>521\,{\rm km\,s^{-1}}$ can be ruled out.
-
-On the contrary,
-$\sigma_{\rm rms}<70\,{\rm km\,s^{-1}}$ together with Hubble velocities and
-broadening by redshift errors will result in a velocity width that is more than three times the
-modeling error away from the observed width (overplotted in Figure~\ref{fig:monte}). This implies
-that, unless the characteristic $M_{\rm halo}<10^{11.0}\,M_\odot$,
-additional dynamical processes are not required to explain the observed width.
+necessitate outflows. Our preferred kinematic measure is thus the dispersion in the average absorption.
 
@@
 corresponding to typical QPQ halo mass is contained within the 2$\sigma$ contour.
+
+\subsection{Interpretation of the asymmetric absorption}
+\label{sec:significance_+ve}
+
+{\bf We quote} the standard deviation in the bootstrap
+realizations to be the scatter in the centroids of the data. The scatters
+$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic
+variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show
+the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We
+find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
+limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at
+$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
+whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2}
+absorption.
+
+One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
+\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2}\,1334, absorption from \ion{C}{2*}\,1335
+would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
+In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
+from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334.
+{\bf Their mean \ion{C}{2} to \ion{C}{2*} equivalent width ratio is 0.2.}
+Among these nine subsystems, only one,
+labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
+{\bf We simulate that absorption from \ion{C}{2*} may only bias the \ion{C}{2} centroid by
+$\approx+40\,{\rm km\,s^{-1}}$.}
+Hence, contamination from \ion{C}{2*}\,1335 could not be responsible for the observed redshift in
+the centroid.
+
+One may also ask whether the measured positive offsets come from systematic bias in redshift
+measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the
+[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically
+less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean
+stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
+more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for 11 out
+of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
+velocity structure and again shows a positive offset $\approx+303\,{\rm km\,s^{-1}}$. We thus
+conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
+[\ion{O}{3}] emission-line.
+
+Motivated by the study of \ion{Mg}{2} absorbers surrounding $z\sim1$ quasars by \cite{Johnson+15},
+we also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs.
+We select quasars with $0.4<z_{\rm fg}<1.6$ and use the same other selection criteria as the main
+QPQ9 sample. The quasar pairs are selected from the igmspec database, with $z_{\rm fg}$ measured
+by \cite{HewettWild10}. For quasars with $z_{\rm fg}<0.84$, as redshift determination is dominated
+by [\ion{O}{3}] emission, a shift of $+48\,{\rm km\,s^{-1}}$ is applied to bring the emission-line
+redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is
+dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are 233
+pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present
+the mean stack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9
+sample. Gaussian absorption models fitted to the stack recover a centroid of
+$-11\pm379\,{\rm km\,s^{-1}}$ and a dispersion of $172\,{\rm km\,s^{-1}}$. The average offset
+from $0\,{\rm km\,s^{-1}}$ is much smaller than the offsets in the $z\sim2$ sample.
+
+Since the large scatter in the centroids represents intrinsic variation rather than redshift
+errors, and the \ion{Mg}{2} stack for lower redshift suggests a different centroid, we consider
+that
+{\bf systematic biases are unlikely to explain the asymmetry signal in the $z\sim2$ sample.}
+%the asymmetry signal in the $z\sim2$ sample is likely to be real.
+In the Discussion section, we discuss two possible explanations for the asymmetry.
+
+\begin{figure}
+%\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
+\includegraphics[width=2.5in]{f03.pdf}
+\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample
+for the \ion{C}{2} mean stack. 97\% of the centroids are positively offset from $z_{\rm fg}$.}
+\label{fig:histogram_cen}
+\end{figure}
+
+\begin{figure}
+%\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
+\includegraphics[width=2.5in]{f04.pdf}
+\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at
+$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is
+approximately at $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample.
+}
+\label{fig:stack_z1}
+\end{figure}
 
@@
 
-In the following, we explore two possible explanations for the putative non-dynamical process that
-provides the asymmetry.
-{\bf The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of
-opacity in background sightlines passing close to foreground quasars.}
+In the following, we explore two possible explanations for the {\bf non-dynamical processes} that
+provides the {\bf putative asymmetry}.
+The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of
+opacity in background sightlines passing close to foreground quasars.
 
@@
 
-{\bf As a test of reasonableness, we try implementing an arbitrary quasar opening angle in our
-Monte Carlo simulations to reproduce an absorption centroid that is redshifted from the systemic.
-In this test, we remove all absorbers at circumgalactic distances that fall within the quasar
-opening angle. We find that, for an opening angle of $120^\circ$ and keeping $\sigma_{\rm rms}$ at
-the expected value for the typical QPQ9 halo, the observed centroid and intrinsic dispersion of the
-\ion{C}{2} mean absorption may be reproduced within modeling errors.}
-
 Another possible explanation arises from the finite lifetime of quasar episodes.
-Figure~\ref{fig:lighttravel} presents a cartoon for a {\bf light travel time argument. The light from}
+Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. The light from
 the background quasar may arrive at the gas behind
@@
 second explanation requires the quasars emit their ionizing radiation intermittently. Both
-explanations will require the line-of-sight motions of the gas to be in either outflow or Hubble
-flow. Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
+explanations will require the line-of-sight motions of the gas to be {\bf not in a net inflow.}
+Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
 Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
@@
 a CGM gas that is directly illuminated is highly ionized and shows only marginally detectable
-\ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate, and a
+\ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate ion, and a
 blueshifted absorption signal needs to be searched in a higher ion.
+
+{\bf We test the case of Hubble flows versus galactic-scale outflows in producing the putative
+asymmetry. We try implementing an arbitrary quasar opening angle in our Monte Carlo simulations to
+reproduce an absorption centroid that is redshifted from the systemic. In QPQ6, we argued that
+the observed anisotropic clustering of optically thick systems around quasars demands that a quasar's
+radiation field must affect optically thick systems on Mpc scales. Hence in this test, we set the
+incidence of absorbers happening within the quasar opening angle to be zero, for absorbers at all
+disances from the quasar. In the case without
+outflows, even if we set the opening angle to be $180^\circ$, i.e. absorption only happens at
+positive velocities, the mean absorption centroid would merely reach $\approx+85\,{\rm km\,s^{-1}}$.
+Hence, the observed $\delta v\approx+200\,{\rm km\,s^{-1}}$ shift in the mean absorption cannot be
+produced by asymmetric distribution in Hubble velocities alone. This suggests the presence of an
+outflow component to account for extra asymmetry in line-of-sight velocities.
+We crudely estimate that, for an opening angle of $120^\circ$ and radial outflows at
+velocities $\approx500\,{\rm km\,s^{-1}}$, our Monte Carlo simulations may reproduce the
+observed centroid and intrinsic dispersion of the mean absorption by \ion{C}{2}.}
 
@@
 scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study
-this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ 2017, in preparation). In conclusion, we
+this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ {\bf 2018}, in preparation). In conclusion, we
 observe large and positively skewed velocity fields in absorption, of metal ions
 in the CGM of $z\sim2$ massive galaxies hosting quasars.
-{\bf We argue that the large velocity fields can be accounted for by gravitational motions and
-Hubble flows and do not necessitate outflows. Further, the positive skew can be explained if the
-detected gas is not in inflow on average, and the quasars either shine preferentially toward the
-observer or shine intermittently.}
+{\bf We argue that, the observation of large velocity fields alone can be accounted for by
+gravitational motions and Hubble flows and does not necessitate outflows. However, we argue that the
+positive skew suggests the detected gas is in outflow on average, and the quasars either shine
+preferentially toward the observer or shine intermittently.}
 
 \acknowledgements
-
-{\bf MWL is immensely grateful to the referee's constructive comments, which help strengthen the
-paper.}
+MWL is immensely grateful to the referee's constructive comments, which help strengthen the
+paper.
 JXP and MWL acknowledge support from the National Science Foundation (NSF) grants AST-1010004 and
@@
 for a discussion on extended emission-line regions, T.-K. Chan for a discussion on CGM
-simulations, and Chi Po Choi {\bf and Yat Tin Chow for discussions} on statistics.
+simulations, and Chi Po Choi and Yat Tin Chow for discussions on statistics.
 
@@
 
-\begin{thebibliography}{52}
+\begin{thebibliography}{54}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 {Baldwin}, J.~A. 1977, \apj, 214, 679
+
+\bibitem[{{Bielby} {et~al.}(2013){Bielby}, {Hill}, {Shanks}, {Crighton},
+  {Infante}, {Bornancini}, {Francke}, {H{\'e}raudeau}, {Lambas}, {Metcalfe},
+  {Minniti}, {Padilla}, {Theuns}, {Tummuangpak}, \& {Weilbacher}}]{Bielby+13}
+{Bielby}, R., {Hill}, M.~D., {Shanks}, T., {Crighton}, N.~H.~M., {Infante}, L.,
+  {Bornancini}, C.~G., {Francke}, H., {H{\'e}raudeau}, P., {Lambas}, D.~G.,
+  {Metcalfe}, N., {Minniti}, D., {Padilla}, N., {Theuns}, T., {Tummuangpak},
+  P., \& {Weilbacher}, P. 2013, \mnras, 430, 425
 
@@
 {Lau}, M.~W., {Prochaska}, J.~X., \& {Hennawi}, J.~F. 2016, \apjs, 226, 25
+
+\bibitem[{{Malkan} {et~al.}(2017){Malkan}, {Cohen}, {Maruyama}, {Kashikawa},
+  {Ly}, {Ishikawa}, {Shimasaku}, {Hayashi}, \& {Motohara}}]{Malkan+17}
+{Malkan}, M.~A., {Cohen}, D.~P., {Maruyama}, M., {Kashikawa}, N., {Ly}, C.,
+  {Ishikawa}, S., {Shimasaku}, K., {Hayashi}, M., \& {Motohara}, K. 2017, \apj,
+  850, 5
 

### 2018-02-27 QPQ9/Figures/py/qpq9_figs.py

@@ -353,7 +353,9 @@ def monte(outfil=None):
     Gaussian_params = (ascii.read(path+'CII_MgII_mean_fit.dat'))[0]
     model_conti = models.Const1D(amplitude=Gaussian_params['amplitude_0'])
     model_monte_gauss = models.GaussianAbsorption1D(
-        amplitude=monte_params['amplitude'],mean=Gaussian_params['mean_1'],
+        amplitude=monte_params['amplitude'],
+#        mean=Gaussian_params['mean_1'],
+        mean=0,  # do not apply arbitrary shift
         stddev=np.sqrt((monte_params['stddev'])**2.+188.7**2.))
     print('s.d. in monte carlo model, in monte carlo model with redshift error broadening, in data',
           monte_params['stddev'],np.sqrt((monte_params['stddev'])**2.+188.7**2.),
@@ -382,9 +384,9 @@ def monte(outfil=None):
 
     # Plot
     plt.plot(velo.value,mean_stack[0].data,drawstyle='steps-mid',linewidth=2,color='k')
-    plt.plot(velo.value,model_monte(velo.value),color='g',linewidth=3)
+    plt.plot(velo.value,model_monte(velo.value),color='gold',linewidth=3)
     plt.plot(velo.value,model_extra(velo.value),'y--',linewidth=3)
-    plt.plot(velo.value,model_outflow(velo.value),'m--',linewidth=3)
+    plt.plot(velo.value,model_outflow(velo.value),'y-.',linewidth=3)
 
     # Font
     for item in ([ax.title, ax.xaxis.label, ax.yaxis.label] +

### 2018-02-27 QPQ9/Tables/py/qpq9_tables.py

@@ -132,6 +132,7 @@ def tab_summary():
     if params['mean_1'] > 0:
         cenofmean_CII = '+'+cenofmean_CII
     dispofmean_CII = str(int(np.around(params['stddev_1'])))
+    contiofmean_CII = str(np.around(params['amplitude_0'],decimals=2))
     path = '../Analysis/Bootstrap/Output/'
     boot_hdulist = fits.open(path+'IRMgII_1334_mean.fits')
     scatterincenofmean_CII = str(int(np.around(np.std(boot_hdulist[3].data))))
@@ -143,6 +144,7 @@ def tab_summary():
     if params['mean_1'] > 0:
         cenofmedian_CII = '+'+cenofmedian_CII
     dispofmedian_CII = str(int(np.around(params['stddev_1'])))
+    contiofmedian_CII = str(np.around(params['amplitude_0'],decimals=2))
     path = '../Analysis/Bootstrap/Output/'
     boot_hdulist = fits.open(path+'IRMgII_1334_med.fits')
     scatterincenofmedian_CII = str(int(np.around(np.std(boot_hdulist[3].data))))
@@ -156,6 +158,7 @@ def tab_summary():
     if params['mean_1'] > 0:
         cenofmean_CIV = '+'+cenofmean_CIV
     dispofmean_CIV = str(int(np.around(params['stddev_1'])))
+    contiofmean_CIV = str(np.around(params['amplitude_0'],decimals=2))
     path = '../Analysis/Bootstrap/Output/'
     boot_hdulist = fits.open(path+'IRMgII_1548_mean.fits')
     scatterincenofmean_CIV = str(int(np.around(np.std(boot_hdulist[3].data))))
@@ -167,6 +170,7 @@ def tab_summary():
     if params['mean_1'] > 0:
         cenofmedian_CIV = '+'+cenofmedian_CIV
     dispofmedian_CIV = str(int(np.around(params['stddev_1'])))
+    contiofmedian_CIV = str(np.around(params['amplitude_0'],decimals=2))
     path = '../Analysis/Bootstrap/Output/'
     boot_hdulist = fits.open(path+'IRMgII_1548_med.fits')
     scatterincenofmedian_CIV = str(int(np.around(np.std(boot_hdulist[3].data))))
@@ -180,6 +184,7 @@ def tab_summary():
[…]

### 2018-02-28 QPQ9/Submit/qpq9_resubmit_3.tex
small changes

@@
 Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
-{\bf We overplot in dashed, yellow an
+{\bf We overplot in dashed, limegreen an
 absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
 by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
-width larger than this can be ruled out. We overplot in dot dashed, yellow an absorption profile with
+width larger than this can be ruled out. We overplot in dot dashed, limegreen an absorption profile with
 $\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
@@
 required to explain the observed width.
-In thick, gold, we overplot the
+In thick, green, we overplot the
 Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering

### 2018-02-28 QPQ9/Figures/py/qpq9_figs.py

@@ -384,9 +384,9 @@ def monte(outfil=None):
 
     # Plot
     plt.plot(velo.value,mean_stack[0].data,drawstyle='steps-mid',linewidth=2,color='k')
-    plt.plot(velo.value,model_monte(velo.value),color='gold',linewidth=3)
-    plt.plot(velo.value,model_extra(velo.value),'y--',linewidth=3)
-    plt.plot(velo.value,model_outflow(velo.value),'y-.',linewidth=3)
+    plt.plot(velo.value,model_monte(velo.value),color='green',linewidth=3)
+    plt.plot(velo.value,model_extra(velo.value),color='limegreen',linestyle='--',linewidth=3)
+    plt.plot(velo.value,model_outflow(velo.value),color='limegreen',linestyle='-.',linewidth=3)
 
     # Font
     for item in ([ax.title, ax.xaxis.label, ax.yaxis.label] +
@@ -470,7 +470,7 @@ def contour(outfil=None):
     hdulist.close()
 
     # Plot
-    ax.contourf(mass,WCII,lvls,levels=[1,2,3,4],colors=['b','g','r','m'])
+    ax.contourf(mass,WCII,lvls,levels=[1,2,3,4],colors=['lightgreen','limegreen','green','darkgreen'])
 
     # labels
     ax.set_xlabel(r'$\log\,(M_{\rm halo}/{\rm M}_\odot)$')

### 2018-03-11 QPQ9/Submit/qpq9_resubmit_4.tex
Addressed fourth referee report.

--- 2018-02-28 QPQ9/Submit/qpq9_resubmit_3.tex
@@
 and \ion{Mg}{2}.
-{\bf We find that the mean absorptions exhibit large velocity widths
+We find that the mean absorptions exhibit large velocity widths
 $\sigma_v\approx300\,{\rm km\,s^{-1}}$. Further, the mean absorptions appear to be asymmetric about
@@
 galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
-is anisotropic or intermittent.}
+is anisotropic {\bf and/or} intermittent.
 \end{abstract}
@@
 \citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions,
-\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy
+\citep[e.g.,][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy
 to detect and characterize the gas surrounding galaxies
-\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}.
+\citep[e.g.,][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}.
 In a previous paper of the Qussars Probing Quasars series \citep[][, hereafter QPQ8]{QPQ8}, we
@@
 redshift.
-{\bf From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4}
+From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4}
 systems, we measured the velocity interval that encompasses 90\% of the total optical depth,
@@
 velocities indicate a redshift from the systemic.
-}
 
@@
 their velocity spreads can be better quantified. Other
-existing studies that found large velocity spreads are {\bf single sightlines
-\citep[e.g.,][]{Tripp+11,RudieNewmanMurphy17}}, or with gas tracing
+existing studies that found large velocity spreads are single sightlines
+\citep[e.g.,][]{Tripp+11,RudieNewmanMurphy17}, or with gas tracing
 a higher ionization state than the QPQ absorption systems \citep[e.g.,][]{Churchill+12}, or where
@@
 $1\sigma$ modeling error for the
-{\bf dispersion and the centroid of the \ion{C}{2} mean stack are $27\,{\rm km\,s^{-1}}$ and
+dispersion and the centroid of the \ion{C}{2} mean stack are $27\,{\rm km\,s^{-1}}$ and
 $25\,{\rm km\,s^{-1}}$ respectively, which are}
 also the typical modeling errors of the other stacks.
-}
 \label{fig:stacks_and_fits}
@@
 to the data, we measure
-{\bf the $1\sigma$ dispersion of the stack to be $293\,{\rm km\,s^{-1}}$ and the centroid of the
+the $1\sigma$ dispersion of the stack to be $293\,{\rm km\,s^{-1}}$ and the centroid of the
 \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$. The dispersion suggests extreme kinematics, while
-the centroid suggests an asymmetry that contradicts the standard expectation.}
+the centroid suggests an asymmetry that contradicts the standard expectation.
 The median
 stack, on the other hand, shows weaker absorption,
-{\bf and the Gaussian model has a more uncertain dispersion and a centroid with smaller offset.}
+and the Gaussian model has a more uncertain dispersion and a centroid with smaller offset.
 
@@
 modeling. We find that this second Gaussian component has
-{\bf an amplitude of $0.030\pm0.009$, i.e.\ essentially the same amplitude as the initial
-constant absorption component, and a $1\sigma$ dispersion of $3614\pm1731\,{\rm km\,s^{-1}}$, i.e.\ wider}
+an amplitude of $0.030\pm0.009$, i.e.\ essentially the same amplitude as the initial
+constant absorption component, and a $1\sigma$ dispersion of $3614\pm1731\,{\rm km\,s^{-1}}$, i.e.\ wider
 than the entire velocity window for stacking.
-This weak and very broad component has no effect on the {\bf width and the centroid} of the narrow,
+This weak and very broad component has no effect on the width and the centroid of the narrow,
 associated Gaussian component. We therefore consider that one single Gaussian component is a good
@@
 absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has
-{\bf a dispersion of $330\,{\rm km\,s^{-1}}$, and a centroid at $+235\,{\rm km\,s^{-1}}$},
+a dispersion of $330\,{\rm km\,s^{-1}}$, and a centroid at $+235\,{\rm km\,s^{-1}}$,
 consistent with the full sample.
@@
 Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
-{\bf We overplot in dashed, limegreen an
+We overplot in dashed, limegreen an
 absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
@@
 from the systemic. A model with only gravitational motions and Hubble flows cannot explain
-this putative asymmetry.}
+this putative asymmetry.
 }
@@
 
-{\bf To assess the statistical significance of the observed dispersion, we perform a bootstrap
+To assess the statistical significance of the observed dispersion, we perform a bootstrap
 analysis by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption
-profile to model each bootstrap realization. We find that} a width of
+profile to model each bootstrap realization. We find that a width of
 $\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter in
@@
 absorption model of the Monte Carlo simulations.
-{\bf In the figure, the Gaussian absorption model is
-broadened by the mean redshift error by adding it in quadrature to the dispersion in the model.}
+n the figure, the Gaussian absorption model is
+broadened by the mean redshift error by adding it in quadrature to the dispersion in the model.
 The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$,
@@
 stack of the sub-sample with [\ion{O}{3}] redshifts as well.
-{\bf One may also consider whether absorbers in Hubble flow and cosmological distances show peculiar
+One may also consider whether absorbers in Hubble flow and cosmological distances show peculiar
 velocities that are typical for quasar-mass halos, and adopt a different $\sigma_{\rm rms}$ accordingly.
@@
 dispersion of $247\,{\rm km\,s^{-1}}$. This is again within modeling errors of the observed intrinsic
-dispersion.}
+dispersion.
 We also test for the
@@
 
-{\bf We quote} the standard deviation in the bootstrap
+We quote the standard deviation in the bootstrap
 realizations to be the scatter in the centroids of the data. The scatters
@@
 from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334.
-{\bf Their mean \ion{C}{2} to \ion{C}{2*} equivalent width ratio is 0.2.}
+Their mean \ion{C}{2} to \ion{C}{2*} equivalent width ratio is 0.2.
 Among these nine subsystems, only one,
 labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
-{\bf We simulate that absorption from \ion{C}{2*} may only bias the \ion{C}{2} centroid by
-$\approx+40\,{\rm km\,s^{-1}}$.}
+We simulate that absorption from \ion{C}{2*} may only bias the \ion{C}{2} centroid by
+$\approx+40\,{\rm km\,s^{-1}}$.
 Hence, contamination from \ion{C}{2*}\,1335 could not be responsible for the observed redshift in
@@
 that
-{\bf systematic biases are unlikely to explain the asymmetry signal in the $z\sim2$ sample.}
+systematic biases are unlikely to explain the asymmetry signal in the $z\sim2$ sample.
 %the asymmetry signal in the $z\sim2$ sample is likely to be real.
@@
 
-In the following, we explore two possible explanations for the {\bf non-dynamical processes} that
-provides the {\bf putative asymmetry}.
+In the following, we explore two possible explanations for the non-dynamical processes that
+provides the putative asymmetry.
 The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of
@@
 the background quasar may arrive at the gas behind
-the foreground quasar before the ionizing radiation from the foreground quasar arrives. In
-QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average
-extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of
-$\sim10^6$\,yr.
-In turn, this implies a minimum quasar lifetime of $10^6$\,yr, which lies within existing
-constraints from
-observations \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
+the foreground quasar before the ionizing radiation from the foreground quasar arrives.
+
+%In
+%QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average
+%extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of
+%$\sim10^6$\,yr.
+%n turn, this implies a minimum quasar lifetime of $10^6$\,yr, which lies within existing
+%constraints from
+%observations \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.
 
@@
 second explanation requires the quasars emit their ionizing radiation intermittently. Both
-explanations will require the line-of-sight motions of the gas to be {\bf not in a net inflow.}
+explanations will require the line-of-sight motions of the gas to be not in a net inflow.
 Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
@@
 
-{\bf We test the case of Hubble flows versus galactic-scale outflows in producing the putative
-asymmetry. We try implementing an arbitrary quasar opening angle in our Monte Carlo simulations to
+We test the case of Hubble flows versus galactic-scale outflows in producing the putative
+asymmetry.
+{\bf
+Anistropic emission is degenerate with intermittent emission in their asymmetric
+light-echo in the observer's frame. We first consider the scenario where
+the quasar's lifetime is infinite, and the observed ansymmetric absorption is only produced by
+anisotropic emission.}
+We try implementing an arbitrary quasar opening angle in our Monte Carlo simulations to
 reproduce an absorption centroid that is redshifted from the systemic. In QPQ6, we argued that
@@
 disances from the quasar. In the case without
-outflows, even if we set the opening angle to be $180^\circ$, i.e. absorption only happens at
+outflows, even if we set the opening angle to be $180^\circ$, i.e.\ absorption only happens at
 positive velocities, the mean absorption centroid would merely reach $\approx+85\,{\rm km\,s^{-1}}$.
@@
 outflow component to account for extra asymmetry in line-of-sight velocities.
-We crudely estimate that, for an opening angle of $120^\circ$ and radial outflows at
-velocities $\approx500\,{\rm km\,s^{-1}}$, our Monte Carlo simulations may reproduce the
-observed centroid and intrinsic dispersion of the mean absorption by \ion{C}{2}.}
+{\bf In order to produce the observed intrinsic dispersion and centroid of the mean absorption by
+\ion{C}{2}, we must add a radial outflow speed of $\approx450\,{\rm km\,s^{-1}}$ to the absorbers
+and a unipolar quasar opening angle of $\approx180^\circ$.
+Next, we consider another scenario where the quasar is isotropic, and the asymmetric absorption
+is only produced by short episodic lifetime. We further make the assumption the luminosity is
+constant during a quasar episode. In the quasar's rest frame, the light echo
+would be observed as a spherical region with the quasar at the origin. In the observer's frame, due
+to finite light travel time, the light-echo would not be spherically symmetric. The
+light-echo from the quasar at its luminosity $t$\,yr earlier traces a paraboloid
+with the quasar at the focus and the vertex $t/2$\,ly behind it \citep{Adelberger04,VisbalCroft08}.
+We find that, to reproduce the observation, the CGM absorbers need to have a radial outflow speed
+$\approx420\,{\rm km\,s^{-1}}$ and the quasar must have shined for $\approx0.4\times10^6$\,yr.
+For the anisotropy-only scenario, the opening angle deduced is rather large compared to literature
+findings, which give $30^\circ\textendash90^\circ$ \citep[e.g.,][]{TrainorSteidel13,Borisova+16}.
+For the intermittence-only scenario, if the quasars are on
+averaged observed near the middle of the episode, the lifetime deduced is somewhat small compared
+to other existing constraints from observations and simulations, which give
+$10^6\textendash10^8$\,yr \citep[e.g.,][]{Martini04,Hopkins+05}.
+We thus speculate that the asymmetric absorption is the result of a combination of anisotropic
+and intermittent emission.
+}
+
+{\bf We note that, \cite{Turner+17} conclude that the clustering of low to intermediate ions around
+Lyman-break galaxies in velocity space is
+most consistent with gas that is inflowing on average. The different conclusion from our analysis
+may originate from the higher masses of our systems, the presence of quasar-driven ouflows
+\citep[e.g.,][]{Greene+12}, and/or starburst-driven outflows that are correlated with the presence
+of quasars \citep[e.g.,][]{Barthel+17}.}
 
@@
 scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study
-this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ {\bf 2018}, in preparation). In conclusion, we
+this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ 2018, in preparation). In conclusion, we
 observe large and positively skewed velocity fields in absorption, of metal ions
 in the CGM of $z\sim2$ massive galaxies hosting quasars.
-{\bf We argue that, the observation of large velocity fields alone can be accounted for by
+We argue that, the observation of large velocity fields alone can be accounted for by
 gravitational motions and Hubble flows and does not necessitate outflows. However, we argue that the
-positive skew suggests the detected gas is in outflow on average, and the quasars either shine
-preferentially toward the observer or shine intermittently.}
+positive skew suggests the detected gas is in outflow on average, and the quasars {\bf shine
+preferentially toward the observer and/or intermittently.}
 
@@
 
-\begin{thebibliography}{54}
+\begin{thebibliography}{60}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Adelberger}(2004)}]{Adelberger04}
+{Adelberger}, K.~L. 2004, \apj, 612, 706
 
@@
 {Baldwin}, J.~A. 1977, \apj, 214, 679
+
+\bibitem[{{Barthel} {et~al.}(2017){Barthel}, {Podigachoski}, {Wilkes}, \&
+  {Haas}}]{Barthel+17}
+{Barthel}, P., {Podigachoski}, P., {Wilkes}, B., \& {Haas}, M. 2017, \apjl,
+  843, L16
 
@@
 
+\bibitem[{{Borisova} {et~al.}(2016){Borisova}, {Lilly}, {Cantalupo},
+  {Prochaska}, {Rakic}, \& {Worseck}}]{Borisova+16}
+{Borisova}, E., {Lilly}, S.~J., {Cantalupo}, S., {Prochaska}, J.~X., {Rakic},
+  O., \& {Worseck}, G. 2016, \apj, 830, 120
+
 \bibitem[{{Boroson}(2005)}]{Boroson05}
@@
 {Gauthier}, J.-R. 2013, \mnras, 432, 1444
+
+\bibitem[{{Greene} {et~al.}(2012){Greene}, {Zakamska}, \& {Smith}}]{Greene+12}
+{Greene}, J.~E., {Zakamska}, N.~L., \& {Smith}, P.~S. 2012, \apj, 746, 86
 
@@
 
+\bibitem[{{Trainor} \& {Steidel}(2013)}]{TrainorSteidel13}
+{Trainor}, R., \& {Steidel}, C.~C. 2013, \apjl, 775, L3
+
 \bibitem[{{Tripp} {et~al.}(2011){Tripp}, {Meiring}, {Prochaska}, {Willmer},
@@
 
+\bibitem[{{Turner} {et~al.}(2017){Turner}, {Schaye}, {Crain}, {Rudie},
+  {Steidel}, {Strom}, \& {Theuns}}]{Turner+17}
+{Turner}, M.~L., {Schaye}, J., {Crain}, R.~A., {Rudie}, G., {Steidel}, C.~C.,
+  {Strom}, A., \& {Theuns}, T. 2017, \mnras, 471, 690
+
+\bibitem[{{Visbal} \& {Croft}(2008)}]{VisbalCroft08}
+{Visbal}, E., \& {Croft}, R.~A.~C. 2008, \apj, 674, 660
+
 \bibitem[{{Weiner} {et~al.}(2009){Weiner}, {Coil}, {Prochaska}, {Newman},

### 2018-03-11 QPQ9/Figures/py/qpq9_figs.py

@@ -381,6 +381,8 @@ def monte(outfil=None):
     ax.text((ax.get_xlim()[1]-ax.get_xlim()[0])*0.05+ax.get_xlim()[0],
             (ax.get_ylim()[1]-ax.get_ylim()[0])*0.05+ax.get_ylim()[0],
             'CII, mean',size=fontsize)
+    ax.minorticks_on()
+    ax.yaxis.set_tick_params(which='minor',left='off')
 
     # Plot
     plt.plot(velo.value,mean_stack[0].data,drawstyle='steps-mid',linewidth=2,color='k')
@@ -475,6 +477,7 @@ def contour(outfil=None):
     # labels
     ax.set_xlabel(r'$\log\,(M_{\rm halo}/{\rm M}_\odot)$')
     ax.set_ylabel(r'$W_{\rm CII} ({\rm \AA})$')
+    ax.xaxis.set_major_locator(MaxNLocator(nbins=5))
 
     # Mark QPQ halo mass location
     ax.text(12.6,0.52,'+',size=fontsize,ha='center',va='center')

### 2018-03-19 QPQ9/Submit/qpq9_arXiv.tex
Fourth resubmission. Accepted. Made the final version for arXiv

--- 2018-03-11 QPQ9/Submit/qpq9_resubmit_4.tex
@@
 galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
-is anisotropic {\bf and/or} intermittent.
+is anisotropic and/or intermittent.
 \end{abstract}
 
-\keywords{glaxies: clusters: intracluster medium -- galaxies: formation -- galaxies: halos --
+\keywords{galaxies: clusters: intracluster medium -- galaxies: formation -- galaxies: halos --
 intergalactic medium -- quasars: absorption lines -- quasars: general}
@@
 asymmetry.
-{\bf
 Anistropic emission is degenerate with intermittent emission in their asymmetric
@@
 the quasar's lifetime is infinite, and the observed ansymmetric absorption is only produced by
-anisotropic emission.}
+anisotropic emission.
 We try implementing an arbitrary quasar opening angle in our Monte Carlo simulations to
@@
 outflow component to account for extra asymmetry in line-of-sight velocities.
-{\bf In order to produce the observed intrinsic dispersion and centroid of the mean absorption by
+In order to produce the observed intrinsic dispersion and centroid of the mean absorption by
 \ion{C}{2}, we must add a radial outflow speed of $\approx450\,{\rm km\,s^{-1}}$ to the absorbers
@@
 and intermittent emission.
-}
-
-{\bf We note that, \cite{Turner+17} conclude that the clustering of low to intermediate ions around
+
+We note that, \cite{Turner+17} conclude that the clustering of low to intermediate ions around
 Lyman-break galaxies in velocity space is
@@
 \citep[e.g.,][]{Greene+12}, and/or starburst-driven outflows that are correlated with the presence
-of quasars \citep[e.g.,][]{Barthel+17}.}
+of quasars \citep[e.g.,][]{Barthel+17}.
 
@@
 gravitational motions and Hubble flows and does not necessitate outflows. However, we argue that the
-positive skew suggests the detected gas is in outflow on average, and the quasars {\bf shine
-preferentially toward the observer and/or intermittently.}
+positive skew suggests the detected gas is in outflow on average, and the quasars shine
+preferentially toward the observer and/or intermittently.
 
@@
 
-\begin{thebibliography}{60}
+\begin{thebibliography}{61}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

### 2018-04-27 QPQ9/Submit/response_3.txt

@@
 In our response to the last report, we overlooked the referee's request
-for changing the color scheme of Figure 6, and we had only done that for
-the two cartoon figures. We apologize for that, and we have now changed
-the color scheme of Figure 6.
+for changing the color scheme of old Figure 6, and we had only done that
+for the two cartoon figures. We apologize for that, and we have now
+changed the color scheme of Figure 4, which used to be Figure 6.
 

### 2018-04-27 QPQ9/Submit/response_4.txt

Dear referee,

It's been very helpful to have these exchanges with you. Thank you
very much for your professional service. I have added your latest
suggestions.

>1) The paper now states that a 500 km/s outflow can reproduce the
>observed velocity shift based on "crude" estimates. Please give a bit
>more detail on how this estimate was obtained and state whether it is
>degenerate with e.g. the quasar opening angle or episodic lifetime.

We updated the text to be somewhat more quantitative and rigorous.
Anistropic emission is degenerate with intermittent emission.
First we consider the case where the quasar lifetime is infinite, and
the observed asymmetry is only produced by anisotropic emission. Then,
the radial outflow speed needs to be ~450 km/s and the opening
angle needs to be ~180 degrees, so that the observed intrinsic
dispersion and absorption centroid can be produced.
Second we consider the case where the quasar is isotropic, and the
observed asymmetry is only produced by finite lifetime. We further make
the assumption the quasar luminosity is constant during its lifetime.
Then, the radial outflow speed needs to be at least ~420 km/s and the
quasar must have shined for ~0.4e+6 years, to reproduce the observation.
For the anisotropy-only case, the opening angle
deduced is rather large compared to literature findings (e.g.
Borisova+16). For the intermittence-only case, if the quasars are on
averaged observed near the middle of the episode, the lifetime
deduced is somewhat small compared to literature findings. We thus
speculate that the asymmetry is the result of a combination of anisotropic
and intermittent emission. To better illustrate the second case, we also
updated the cartoon figure on finite lifetime to show a scenario where the
emission is isotropic.

>2) It would be useful to compare this outflow rate with other works and
>discuss possible origins of the putative outflows (e.g. supernovae vs.
>AGN). For example, a comparison with Turner+2014, 2017 would be
>enlightening. In particulary, Turner+2017 examined mean absorption
>optical depths around Lyman break galaxies and compared with simulations.
>For lower ionization state gas (HI, SiIV, and CIV in this case), the
>favored conclusion is that clustering of the absorption in velocity space
>is most consistent with gas that is *inflowing* on average. This is in
>apparent contrast with the new conclusions of the paper. This difference
>may be related to the masses of the systems being studied or the presence
>of the quasar due to quasar driven outflows (e.g. Green+2012) and/or
>supernovae driven outflows from starburst activity that is correlated
>with the presence of quasars (e.g. Barthel+2017).

We thank the referee for the literature suggestion, and the discussion
suggestion. We have added relevant text.

>1) It would be useful to add minor ticks to Figure 3, particularly on the
>x-axis.

We added minor ticks. We thank the referee's attentiveness to details.

>2) The numbering on the x-axis of Figure 4 is difficult to read
>currently.

We decreased the number of tick labels. We thank the referee for their
attentiveness.

Marie Wingyee Lau

### 2018-04-27 QPQ9/Submit/qpq9_arXiv.tex

@@
 the QPQ9 sample. We require that the spectra survive a S/N cut of 5.5 per rest-frame \AA\ at
-\ion{C}{2}\,1334, \ion{C}{4}\,1548, or \ion{Mg}{2}\,2796 at $z_{\rm fg}$. In constrast to the
+\ion{C}{2}\,1334, \ion{C}{4}\,1548, or \ion{Mg}{2}\,2796 at $z_{\rm fg}$. In contrast to the
 large equivalent widths exhibited in the stacks of background spectra, \ion{C}{2} and \ion{Mg}{2}
@@
 blueshifted velocity field. This excess \ion{C}{4} absorption has been well studied as narrow
-associated absorption line systems \citep[e.g., ][]{Wild+08}.
+associated absorption line systems \citep[e.g.,][]{Wild+08}.
+We note that, in the $z\sim4$ sample of narrow associated absorbers analyzed by \cite{Perrotta+16} 
+and Perrotta et al.\ (2018, in preparation), a higher ionization state is similarly found along 
+the line-of-sight to quasars compared to across the line-of-sight. In particular, an excess of 
+\ion{N}{5} absorption is found in proximity to the host quasars.
 
@@
 
-\begin{thebibliography}{61}
+\begin{thebibliography}{62}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
   L. 2017, \aap, 597, A79
+
+\bibitem[{{Perrotta} {et~al.}(2016){Perrotta}, {D'Odorico}, {Prochaska},
+  {Cristiani}, {Cupani}, {Ellison}, {L{\'o}pez}, {Becker}, {Berg},
+  {Christensen}, {Denney}, {Hamann}, {P{\^a}ris}, {Vestergaard}, \&
+  {Worseck}}]{Perrotta+16}
+{Perrotta}, S., {D'Odorico}, V., {Prochaska}, J.~X., {Cristiani}, S., {Cupani},
+  G., {Ellison}, S., {L{\'o}pez}, S., {Becker}, G.~D., {Berg}, T.~A.~M.,
+  {Christensen}, L., {Denney}, K.~D., {Hamann}, F., {P{\^a}ris}, I.,
+  {Vestergaard}, M., \& {Worseck}, G. 2016, \mnras, 462, 3285
 
